### 2019-05-03 main.tex
Change names.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.
\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2019-05-03 main.tex
Start to write abstract.

@@
 \begin{abstract}
+Multistage programming is a scheme of programming which enable us to generate codes at runtime.
+And it is important to ensure the quality of generated codes.
+In this paper, we extended existing multistage programming language by Hanada and Igarashi with dependent type.
+This extention
+
 The abstract should briefly summarize the contents of the paper in

### 2019-05-05 main.tex
Write abstract.

--- 2019-05-03 main.tex
@@
 \begin{abstract}
+We develop yet another typed multi-stage calculus Lambda-MD. It extends Hanada and Igarashi's Lambda-TP with dependent type.
+
+Multi-stage calculus enables us to generate and execute codes at runtime.
+And people have researched it as a method for improving the performance of programs.
+On the other hand, the dependent type is a type dependent on values.
+It is famous for its application for vectors with their length.
+
+In this article, we design Lambda-MD by introducing dependent type into Lamda-TP.
+It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization.
+In addition, we define an evaluation context which takes stages into account.
+Under the evaluation context progress is hold.
+
+As a result of the combination of multi-stage calculus and dependent type, we can test code-generating functions such as staged interpreter at type-checking time.
+Staged-interpreter takes an abstract syntax tree as its input and output a corresponding code.
+Using dependent type, we can check whether some conditions written as a term is true or not at type-checking time.
+Then we can check staged-interpreter returns the correct output for a given input.
+
+199 words
+
 The abstract should briefly summarize the contents of the paper in

### 2019-05-06 main.tex
Fix

@@
 \begin{abstract}
-We develop yet another typed multi-stage calculus Lambda-MD. It extends Hanada and Igarashi's Lambda-TP with dependent type.
+We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
+It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.
 
@@
 
-In this article, we design Lambda-MD by introducing dependent type into Lamda-TP.
+In this article, we design $\lambda^{\textrm{MD}}$ by introducing dependent type into Lamda-TP.
 It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization.
-In addition, we define an evaluation context which takes stages into account.
-Under the evaluation context progress is hold.
+In addition, we define an evaluation context which takes stages into account. Under the evaluation context progress is hold.
 
-As a result of the combination of multi-stage calculus and dependent type, we can test code-generating functions such as staged interpreter at type-checking time.
+As a result of the combination of multi-stage calculus and dependent type, 
+we can test code-generating functions such as staged interpreter at type-checking time.
 Staged-interpreter takes an abstract syntax tree as its input and output a corresponding code.
@@
 
-199 words
+Finally, we discuss the relationship between Cross Stage Persistent and decidability of type checking.
+If you import dependent type to multi-stage calculus naively, the type checking may fail into an infinite loop and doesn't finish forever.
+We impose a little restriction on typing rules and made the type checking finish in finite time.
 
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+238 words
+
+The abstract should briefly summarize the contents of the paper in 150--250 words.
 \keywords{Multistage programming \and Dependent type \and Specification verification by tests.}

### 2019-05-12 main.tex
Add research memo.
Correcting abstract.

--- 2019-05-03 main.tex
@@
 \newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
+\newcommand{\TW}{\triangleright}
 
@@
 %
-\title{Contribution Title\thanks{Supported by organization x.}}
+\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
 %
@@
 \institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
-\email{akira@kuis.kyoto-u.ac.jp} \and
+\email{akira@fos.kuis.kyoto-u.ac.jp} \and
 \email{igarashi@kuis.kyoto-u.ac.jp}
@@
 \begin{abstract}
-Multistage programming is a scheme of programming which enable us to generate codes at runtime.
-And it is important to ensure the quality of generated codes.
-In this paper, we extended existing multistage programming language by Hanada and Igarashi with dependent type.
-This extention
+We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
+It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.
 
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+Dependent types is types dependent on values. 
+Vectors with lengths is famous example of dependent types and they enable us to omit boundary checking.
+
+A multi-stage calculus enables us to generate and execute codes at runtime.
+It can improve the performance of programs by generating optimized codes for given inputs.
+
+In this paper, we design $\lambda^{\textrm{MD}}$ by introducing dependent type into $\lambda^{\TW\%}$.
+You can make more efficient programs from existing dependent typed programs with $\lambda^{\textrm{MD}}$.
+
+It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, strong normalization and progress.
+
+The main technical points of this paper is how to deal with Cross Stage Persistence of multi-stage calculuses in a dependent type system.
+CSP is a function of a multi-stage calculus which allows to use a value in quoted code.
+
+The first point is CSP in kinding rules.
+$\lambda^{\TW\%}$ contains kinding rules because dependent types need them.
+
+The second point is CSP in equivalence rules.
+
+The abstract should briefly summarize the contents of the paper in 150--250 words.
 \keywords{Multistage programming \and Dependent type \and Specification verification by tests.}

### 2019-05-13 main.tex
The second abstract

@@
 \usepackage{graphicx}
+\usepackage{color}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \begin{abstract}
+
 We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
@@
 The first point is CSP in kinding rules.
-$\lambda^{\TW\%}$ contains kinding rules because dependent types need them.
+$\lambda^{\TW\%}$ includes kinding rules because dependent types need them
+but the relationship between kinds and stages was't clear.
 
 The second point is CSP in equivalence rules.
+Prameters of dependent types may contain cross-staed terms.
+We give reasonable equivalence rules to handle them.
 
-The abstract should briefly summarize the contents of the paper in 150--250 words.
 \keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
 \end{abstract}
+
+\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
 %

### 2019-05-13 main.tex
Temporal sections.

@@
 \newcommand{\TW}{\triangleright}
+\newcommand{\LTP}{$\lambda^{\triangleright\%}$}
+\newcommand{\LMD}{$\lambda^{\textrm{MD}}$}
+\newcommand{\LLF}{$\lambda^{\textrm{LF}}$}
 
@@
 
-We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
-It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.
+We develop yet another typed multi-stage calculus \LMD.
+It extends Hanada and Igarashi's \LTP with dependent type.
 
@@
 
-In this paper, we design $\lambda^{\textrm{MD}}$ by introducing dependent type into $\lambda^{\TW\%}$.
-You can make more efficient programs from existing dependent typed programs with $\lambda^{\textrm{MD}}$.
+In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
+You can make more efficient programs from existing dependent typed programs with \LMD.
 
@@
 
-\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
+\keywords{Multistage programming \and Dependent type}
 \end{abstract}
@@
 %
+\section{Introduction}
+\subsection{Dependent Types}
+\subsection{Multi-Stage Calculus}
+\subsection{Organaization of the Paper}
+\section{Informal Overview of \LMD}
+\subsection{\LLF}
+\subsection{\LTP}
+\section{Formal Definition of \LMD}
+\subsection{Kinding Rules}
+\subsection{Equivalence Rules}
 \section{First Section}
+\section{Related Work}
+\section{Conclusions}
+
 \subsection{A Subsection Sample}

### 2019-05-13 main.tex
Writing subsubsections.
Fill out definitions and theorems.

@@
 \usepackage{color}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{bcprules, proof}
+\usepackage{fancybox}
+\usepackage{mathtools}
+\usepackage{float}
+\usepackage[truedimen,margin=15truemm]{geometry}
+\usepackage{xparse}
+\usepackage{ebproof}
+\usepackage{lscape}
+\usepackage{mdframed}
+
 % Used for displaying a sample figure. If possible, figure files should
@@
 \newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
-\newcommand{\TW}{\triangleright}
+
 \newcommand{\LTP}{$\lambda^{\triangleright\%}$}
@@
 \newcommand{\LLF}{$\lambda^{\textrm{LF}}$}
+
+\newcommand{\G}{\Gamma}
+\newcommand{\D}{\Delta}
+\newcommand{\V}{\vdash}
+\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
+\newcommand{\iskind}{\text{\ kind}}
+\newcommand{\TW}{\triangleright}
+\newcommand{\TWL}{\triangleleft}
+\newcommand{\F}{\forall}
+\newcommand{\TB}{\blacktriangleright}
+\newcommand{\TBL}{\blacktriangleleft}
+\newcommand{\E}{\equiv}
+\newcommand{\FV}{\text{FV}}
+\newcommand{\FTV}{\text{FTV}}
+
+\newcommand{\WStar}{\textsc{W-Star}}
+\newcommand{\WAbs}{\textsc{W-Abs}}
+\newcommand{\WCsp}{\textsc{W-Csp}}
+\newcommand{\WApp}{\textsc{W-App}}
+\newcommand{\WTW}{\textsc{W-$\TW$}}
+
+\newcommand{\KVar}{\textsc{K-Var}}
+\newcommand{\KAbs}{\textsc{K-Abs}}
+\newcommand{\KApp}{\textsc{K-App}}
+\newcommand{\KConv}{\textsc{K-Conv}}
+\newcommand{\KTW}{\textsc{K-$\TW$}}
+\newcommand{\KTWL}{\textsc{K-$\TWL$}}
+\newcommand{\KGen}{\textsc{K-Gen}}
+\newcommand{\KCsp}{\textsc{K-Csp}}
+
+\newcommand{\TVar}{\textsc{T-Var}}
+\newcommand{\TAbs}{\textsc{T-Abs}}
+\newcommand{\TApp}{\textsc{T-App}}
+\newcommand{\TConv}{\textsc{T-Conv}}
+\newcommand{\TTB}{\textsc{T-$\TB$}}
+\newcommand{\TTBL}{\textsc{T-$\TBL$}}
+\newcommand{\TGen}{\textsc{T-Gen}}
+\newcommand{\TIns}{\textsc{T-Ins}}
+\newcommand{\TCsp}{\textsc{T-Csp}}
+
+\newcommand{\QKAbs}{\textsc{QK-Abs}}
+\newcommand{\QKCsp}{\textsc{QK-Csp}}
+\newcommand{\QKRefl}{\textsc{QK-Refl}}
+\newcommand{\QKSym}{\textsc{QK-Sym}}
+\newcommand{\QKTrans}{\textsc{QK-Trans}}
+
+\newcommand{\QTAbs}{\textsc{QT-Abs}}
+\newcommand{\QTApp}{\textsc{QT-App}}
+\newcommand{\QTTW}{\textsc{QT-$\TW$}}
+\newcommand{\QTGen}{\textsc{QT-Gen}}
+\newcommand{\QTCsp}{\textsc{QT-Csp}}
+\newcommand{\QTRefl}{\textsc{QT-Refl}}
+\newcommand{\QTSym}{\textsc{QT-Sym}}
+\newcommand{\QTTrans}{\textsc{QT-Trans}}
+
+\newcommand{\QAbs}{\textsc{Q-Abs}}
+\newcommand{\QApp}{\textsc{Q-App}}
+\newcommand{\QTB}{\textsc{Q-$\TB$}}
+\newcommand{\QTBL}{\textsc{Q-$\TBL$}}
+\newcommand{\QGen}{\textsc{Q-Gen}}
+\newcommand{\QIns}{\textsc{Q-Ins}}
+\newcommand{\QCsp}{\textsc{Q-Csp}}
+\newcommand{\QRefl}{\textsc{Q-Refl}}
+\newcommand{\QSym}{\textsc{Q-Sym}}
+\newcommand{\QTrans}{\textsc{Q-Trans}}
+\newcommand{\QBeta}{\textsc{Q-$\beta$}}
+\newcommand{\QEta}{\textsc{Q-$\eta$}}
+\newcommand{\QTBLTB}{\textsc{Q-$\TBL\TB$}}
+\newcommand{\QLambda}{\textsc{Q-$\Lambda$}}
+\newcommand{\QPercent}{\textsc{Q-\%}}
+
+\newcommand{\ID}[1]{\infer[]{#1}{\vdots}}
+\newcommand{\MD}[1]{\mathcal{D}_#1}
 
@@
 %
-\authorrunning{F. Author et al.}
+\authorrunning{A. Kawata, A. Igarashi}
 % First names are abbreviated in the running head.
@@
 
+A multi-stage calculus enables us to generate and execute codes at runtime.
+It can improve the performance of programs by generating optimized codes for given inputs.
+
 Dependent types is types dependent on values. 
 Vectors with lengths is famous example of dependent types and they enable us to omit boundary checking.
-
-A multi-stage calculus enables us to generate and execute codes at runtime.
-It can improve the performance of programs by generating optimized codes for given inputs.
 
@@
 \section{Introduction}
+\subsection{Multi-Stage Calculus}
+\subsubsection{Introduction to Multi-Stage Calculus}
+\subsubsection{Application to Performance Imporving}
 \subsection{Dependent Types}
-\subsection{Multi-Stage Calculus}
+\subsubsection{Introduction to Dependent Types}
+\subsubsection{Application to Omitting Boundary Checking}
 \subsection{Organaization of the Paper}
+
 \section{Informal Overview of \LMD}
@@
 \subsection{\LTP}
+
 \section{Formal Definition of \LMD}
-\subsection{Kinding Rules}
-\subsection{Equivalence Rules}
-\section{First Section}
+\subsection{Syntax}
+
+\begin{align*}
+    \textrm{Terms} && M,N,L,O,P & ::= x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
+    \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
+    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
+    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
+    \textrm{Contexts} && \Gamma & ::= \phi \mid 
+    \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \mid 
+    \Gamma,X::K@A\ (X\not\in \textrm{FV}(\G))\\
+    \textrm{Transition variables} && & \alpha,\beta,\gamma,... \\
+    \textrm{Transition} && & A,B,C,... \\
+    \textrm{Variables} && & x,y,z,... \\
+    \textrm{Type variables} && & X,Y,Z,... \\
+\end{align*}
+
+\subsection{Reduction}
+
+\begin{definition}[Reduction]
+\begin{align*}
+    & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N] \\
+    % & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
+    & \TBL_\alpha (\TB_\alpha M)\longrightarrow_\blacklozenge M \\
+    & (\Lambda \alpha.M) \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
+\end{align*}
+And take a minimum compatible relationship on terms.
+\end{definition}
+
+\subsection{Type System}
+\subsubsection{Kinding Rules}
+\subsubsection{Equivalence Rules}
+
+\subsection{Properties}
+
+\begin{theorem}[Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
+    \begin{flalign*}
+        \text{If\ } \G,z:\xi@B \V M:\tau@A \text{\ and\ } \G\V P:\xi@B
+        &\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P]@A.&\\
+        \text{If\ } \G,z:\xi@B \V \tau::K@A \text{\ and\ } \G\V P:\xi@B
+        &\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P]@A.&\\
+        \text{If\ } \G,z:\xi@B \V K\iskind@A \text{\ and\ } \G\V P:\xi@B
+        &\text{\ then\ } \G\V K[z \mapsto P] \iskind @A.&\\
+        \text{If\ } \G,z:\xi@B \V M\E N : \tau@A \text{\ and\ } \G\V P:\xi@B
+        &\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P]@A.&\\
+        \text{If\ } \G,z:\xi@B \V \tau\E \sigma : K@A \text{\ and\ } \G\V P:\xi@B
+        &\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P]@A.&\\
+        \text{If\ } \G,z:\xi@B \V K\E J@A \text{\ and\ } \G\V P:\xi@B
+        &\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P]@A.&
+    \end{flalign*}    
+\end{theorem}
+
+\begin{theorem}[Stage Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
+    \begin{flalign*}
+        \text{If\ } \G \V M:\tau@A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V \tau::K@A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V K\iskind@A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind@A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V M\E N : \tau@A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V \tau\E \sigma : K@A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V K\E J@A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&
+    \end{flalign*}
+\end{theorem}
+
+\begin{theorem}[Preservation for term on $\beta$ reduction]
+    If $\G\V M:\tau@A$ and $M \longrightarrow_{\beta} M'$, then $\G\V M':\tau@A$\\
+\end{theorem}
+
+\begin{theorem}[Preservation for term on $\TBL\TB$ reduction]
+    If $\G\V M:\tau@A$ and $M\longrightarrow_\blacklozenge N$, then $\G\V N:\tau@A$\\
+\end{theorem}
+
+\begin{theorem}[Preservation for term on $\Lambda$ reduction]
+    If $\G\V M:\tau@A$ and $M \longrightarrow_{\Lambda} N$, then $\G\V N:\tau@A$.
+\end{theorem}
+
+\begin{theorem}[Strong Normalization]
+    If $\G\V^A t:T$ then there is no infinite sequence of terms $(t_i)_{i\ge1}$ and $t_i \longrightarrow_{\beta, \TBL \TB,\Lambda} t_{i+1}$ for $i\ge 1$
+\end{theorem}
+
+\begin{theorem}[Confluence(Church-Rosser Property)]
+    Define $M \longrightarrow N$ as $M \longrightarrow_{\beta} N$ or $M\longrightarrow_\blacklozenge N$ or  $M \longrightarrow_{\Lambda} N$.\\
+    For any term $M$, if $M \longrightarrow^* N$ and $M \longrightarrow^* L$,
+    there exists $O$ that satisfies $N \longrightarrow^* O$ and $L \longrightarrow^* O$.
+\end{theorem}
+
+\begin{definition}[Values]
+$A \neq \epsilon$\\
+\begin{align*}
+    \textrm{Values} && v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon & \\
+                    && v^A \in V^A & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} 
+                                           \mid \Lambda\alpha.v^A \mid v^A\ \epsilon &\\
+                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon) & \\
+                                    &&& \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A) & \\
+    \textrm{Redexes} && R^\epsilon & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon & \\
+                     && R^\alpha & ::=\ \TBL_\alpha \TB_\alpha M & \\
+\end{align*}
+\end{definition}
+
+\begin{definition}[Reduction]
+    $ M \longrightarrow M'$ iff \\
+    $ M \longrightarrow_\Lambda M' $, $ M \longrightarrow_\blacklozenge M' $ or $ M \longrightarrow_\beta M' $.
+\end{definition}
+
+\begin{theorem}[Progress]
+    If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then $ M \in V^A $ or $\exists M'$ such that $M \longrightarrow M'$.
+\end{theorem}
+
 \section{Related Work}
+
 \section{Conclusions}
 
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
-
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
+% \section{First Section}
+% \subsection{A Subsection Sample}
+% Please note that the first paragraph of a section or subsection is
+% not indented. The first paragraph that follows a table, figure,
+% equation etc. does not need an indent, either.
 % 
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
+% Subsequent paragraphs, however, are indented.
 % 
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+% \subsubsection{Sample Heading (Third Level)} Only two levels of
+% headings should be numbered. Lower level headings remain unnumbered;
+% they are formatted as run-in headings.
+% 
+% \paragraph{Sample Heading (Fourth Level)}
+% The contribution should contain no more than four levels of
+% headings. Table~\ref{tab1} gives a summary of all heading levels.
+% 
+% \begin{table}
+% \caption{Table captions should be placed above the
+% tables.}\label{tab1}
+% \begin{tabular}{|l|l|l|}
+% \hline
+% Heading level &  Example & Font size and style\\
+% \hline
+% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
+% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
+% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
+% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
+% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
+% \hline
+% \end{tabular}
+% \end{table}
+% 
+% 
+% \noindent Displayed equations are centered and set on a separate
+% line.
+% \begin{equation}
+% x + y = z
+% \end{equation}
+% Please try to avoid rasterized images for line-art diagrams and
+% schemas. Whenever possible, use vector graphics instead (see
+% Fig.~\ref{fig1}).
+% 
+% \begin{figure}
+% \includegraphics[width=\textwidth]{fig1.eps}
+% \caption{A figure caption is always placed below the illustration.
+% Please note that short captions are centered, while long ones are
+% justified by the macro package automatically.} \label{fig1}
+% \end{figure}
+% 
+% \begin{theorem}
+% This is a sample theorem. The run-in heading is set in bold, while
+% the following text appears in italics. Definitions, lemmas,
+% propositions, and corollaries are styled the same way.
+% \end{theorem}
+% %
+% % the environments 'definition', 'lemma', 'proposition', 'corollary',
+% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
+% %
+% \begin{proof}
+% Proofs, examples, and remarks have the initial word in italics,
+% while the following text appears in normal font.
+% \end{proof}
+% For citations of references, we prefer the use of square brackets
+% and consecutive numbers. Citations using labels or the author/year
+% convention are also acceptable. The following bibliography provides
+% a sample reference list with entries for journal
+% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
+% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
+% and a homepage~\cite{ref_url1}. Multiple citations are grouped
+% \cite{ref_article1,ref_lncs1,ref_book1},
+% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
 %
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
+\bibliographystyle{splncs04}
+\bibliography{main}
 %
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
+% \begin{thebibliography}{8}
+% \bibitem{ref_article1}
+% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
+% 
+% \bibitem{ref_lncs1}
+% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
+% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
+% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
+% 
+% \bibitem{ref_book1}
+% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
+% Location (1999)
+% 
+% \bibitem{ref_proc1}
+% Author, A.-B.: Contribution title. In: 9th International Proceedings
+% on Proceedings, pp. 1--2. Publisher, Location (2010)
+% 
+% \bibitem{ref_url1}
+% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
+% Oct 2017
+% \end{thebibliography}
 \end{document}

### 2019-05-14 main.tex
Fix.
Add CfP.

@@
 \usepackage{float}
-\usepackage[truedimen,margin=15truemm]{geometry}
 \usepackage{xparse}
@@
 And take a minimum compatible relationship on terms.
+
+    $ M \longrightarrow M'$ iff 
+    $ M \longrightarrow_\Lambda M' $, $ M \longrightarrow_\blacklozenge M' $ or $ M \longrightarrow_\beta M' $.
 \end{definition}
@@
 \end{align*}
-\end{definition}
-
-\begin{definition}[Reduction]
-    $ M \longrightarrow M'$ iff \\
-    $ M \longrightarrow_\Lambda M' $, $ M \longrightarrow_\blacklozenge M' $ or $ M \longrightarrow_\beta M' $.
 \end{definition}
@@
 % \end{thebibliography}
+
+\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
+Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures.
+This category encompasses both theoretical and implementation (also known as system descriptions) papers.
+In either case, submissions should clearly identify what has been accomplished and why it is significant.
+Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity.
+System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design.
+In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
 \end{document}

### 2019-05-15 main.tex
Making references.

@@
 
-\newcommand{\red}[1]{\textcolor{red}{ #1 }}
-\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
+\newcommand{\red}[1]{\textcolor{red}{#1 }}
+\newcommand{\blue}[1]{\textcolor{blue}{#1 }}
 
@@
 %
-\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
+\title{Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
 %
@@
 We develop yet another typed multi-stage calculus \LMD.
-It extends Hanada and Igarashi's \LTP with dependent type.
+It extends Hanada and Igarashi's \LTP with dependent types.
 
@@
 
-Dependent types is types dependent on values. 
-Vectors with lengths is famous example of dependent types and they enable us to omit boundary checking.
+Dependent types are types dependent on values. 
+Vectors with lengths are a famous example of dependent types and they enable us to omit boundary checking.
 
@@
 
-It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, strong normalization and progress.
+It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, strong normalization, and progress.
 
-The main technical points of this paper is how to deal with Cross Stage Persistence of multi-stage calculuses in a dependent type system.
-CSP is a function of a multi-stage calculus which allows to use a value in quoted code.
+The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses in a dependent type system.
+CSP is a function of a multi-stage calculus which allows using a value in quoted code.
 
@@
 $\lambda^{\TW\%}$ includes kinding rules because dependent types need them
-but the relationship between kinds and stages was't clear.
+but the relationship between kinds and stages wasn't clear.
 
 The second point is CSP in equivalence rules.
-Prameters of dependent types may contain cross-staed terms.
+Parameters of dependent types may contain cross-staged terms.
 We give reasonable equivalence rules to handle them.
@@
     \textrm{Contexts} && \Gamma & ::= \phi \mid 
-    \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \mid 
-    \Gamma,X::K@A\ (X\not\in \textrm{FV}(\G))\\
-    \textrm{Transition variables} && & \alpha,\beta,\gamma,... \\
-    \textrm{Transition} && & A,B,C,... \\
-    \textrm{Variables} && & x,y,z,... \\
-    \textrm{Type variables} && & X,Y,Z,... \\
+    \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G)) \mid 
+    \Gamma,X::K @A\ (X\not\in \textrm{FV}(\G))\\
+    \textrm{Transition variables} && & \alpha,\beta,\gamma, \dots \\
+    \textrm{Transition} && & A,B,C,\dots \\
+    \textrm{Variables} && & x,y,z,\dots \\
+    \textrm{Type variables} && & X,Y,Z,\dots \\
 \end{align*}
@@
     \begin{flalign*}
-        \text{If\ } \G,z:\xi@B \V M:\tau@A \text{\ and\ } \G\V P:\xi@B
-        &\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P]@A.&\\
-        \text{If\ } \G,z:\xi@B \V \tau::K@A \text{\ and\ } \G\V P:\xi@B
-        &\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P]@A.&\\
-        \text{If\ } \G,z:\xi@B \V K\iskind@A \text{\ and\ } \G\V P:\xi@B
+        \text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
+        &\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
+        \text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
+        &\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
+        \text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
         &\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-        \text{If\ } \G,z:\xi@B \V M\E N : \tau@A \text{\ and\ } \G\V P:\xi@B
-        &\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P]@A.&\\
-        \text{If\ } \G,z:\xi@B \V \tau\E \sigma : K@A \text{\ and\ } \G\V P:\xi@B
-        &\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P]@A.&\\
-        \text{If\ } \G,z:\xi@B \V K\E J@A \text{\ and\ } \G\V P:\xi@B
-        &\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P]@A.&
+        \text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
+        &\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
+        \text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
+        &\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
+        \text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
+        &\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
     \end{flalign*}    
@@
     \begin{flalign*}
-        \text{If\ } \G \V M:\tau@A
-        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
-        \text{If\ } \G \V \tau::K@A
-        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
-        \text{If\ } \G \V K\iskind@A
-        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind@A[\beta \mapsto \epsilon].&\\
-        \text{If\ } \G \V M\E N : \tau@A
+        \text{If\ } \G \V M:\tau @A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V \tau::K @A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V K\iskind @A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V M\E N : \tau @A
         &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
-        \text{If\ } \G \V \tau\E \sigma : K@A
-        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
-        \text{If\ } \G \V K\E J@A
-        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&
+        \text{If\ } \G \V \tau\E \sigma : K @A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+        \text{If\ } \G \V K\E J @A
+        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
     \end{flalign*}
@@
 \begin{theorem}[Preservation for term on $\beta$ reduction]
-    If $\G\V M:\tau@A$ and $M \longrightarrow_{\beta} M'$, then $\G\V M':\tau@A$\\
+    If $\G\V M:\tau @A$ and $M \longrightarrow_{\beta} M'$, then $\G\V M':\tau @A$\\
 \end{theorem}
@@
 \begin{theorem}[Preservation for term on $\TBL\TB$ reduction]
-    If $\G\V M:\tau@A$ and $M\longrightarrow_\blacklozenge N$, then $\G\V N:\tau@A$\\
+    If $\G\V M:\tau @A$ and $M\longrightarrow_\blacklozenge N$, then $\G\V N:\tau @A$\\
 \end{theorem}
@@
 \begin{theorem}[Preservation for term on $\Lambda$ reduction]
-    If $\G\V M:\tau@A$ and $M \longrightarrow_{\Lambda} N$, then $\G\V N:\tau@A$.
+    If $\G\V M:\tau @A$ and $M \longrightarrow_{\Lambda} N$, then $\G\V N:\tau @A$.
 \end{theorem}
@@
                                            \mid \Lambda\alpha.v^A \mid v^A\ \epsilon &\\
-                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon) & \\
+                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon) & \\
                                     &&& \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A) & \\
@@
 \begin{theorem}[Progress]
-    If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then $ M \in V^A $ or $\exists M'$ such that $M \longrightarrow M'$.
+    If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then $ M \in V^A $ or $\exists M'$ such that $M \longrightarrow M'$.
 \end{theorem}
@@
 \section{Related Work}
+
+\begin{itemize}
+   \item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
+   \item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
+   \item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
+   \item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
+   \item A Logical Foundation for Environment Classifiers\cite{Tsukada}
+   \item Environment classifiers\cite{taha2003environment}
+   \item A framework for defining logics\cite{harper1993framework}
+   \item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
+   \item Refined Environment Classifiers\cite{kiselyov2016refined}
+   \item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
+\end{itemize}
 

### 2019-05-15 main.tex
Add references.

@@
 %
-\title{Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
+\title{A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
 %
@@
    \item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
+   \item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
+   \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
+   \item \red{Dependent types in practical programming}\cite{xi1999dependent}
+
+        Section of Application
+   \item \red{A dependently typed assembly language}\cite{xi2001dependently}
+   \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
+   \item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
+   \item \red{Run-time bytecode specialization}\cite{masuhara2001run}
+   \item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
+   \item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
+   \item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
+
 \end{itemize}

### 2019-05-16 main.tex
とりあえずpush

@@
 
-It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, strong normalization, and progress.
+It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
+It also includes an evaluation context which satisfies unique decomposition.
 
-The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses in a dependent type system.
-CSP is a function of a multi-stage calculus which allows using a value in quoted code.
+The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
 
@@
 
-\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
+\blue{213 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
 %
@@
 \subsection{\LTP}
+\subsection{\LMD}
 
@@
 \subsection{Type System}
-\subsubsection{Kinding Rules}
 \subsubsection{Equivalence Rules}
 
-\subsection{Properties}
+\begin{definition}[Values]
+$A \neq \epsilon$\\
+\begin{align*}
+    \textrm{Values} && v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon & \\
+                    && v^A \in V^A & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} 
+                                           \mid \Lambda\alpha.v^A \mid v^A\ \epsilon &\\
+                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon) & \\
+                                    &&& \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A) & \\
+    \textrm{Redexes} && R^\epsilon & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon & \\
+                     && R^\alpha & ::=\ \TBL_\alpha \TB_\alpha M & \\
+\end{align*}
+\end{definition}
+
+\begin{definition}[Staged Reduction]
+$A \neq \epsilon$\\
+\begin{align*}
+    E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon] & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]] \\
+    E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
+    E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha] & \longrightarrow_s E^A_\alpha[v^\alpha] \\
+\end{align*}
+\end{definition}
+
+\begin{definition}[Evaluation Context]
+$A \neq \epsilon$\\
+\begin{align*}
+    E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B
+                                           \mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
+                                           \mid E^\epsilon_B\ \epsilon  \\
+    E^A_B \in ECtx^A_B & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B
+                                           \mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
+                                           \mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A) \\
+                                           & \quad \mid \Lambda\alpha.E^\epsilon_B
+                                           \mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)\\
+\end{align*}
+\end{definition}
+
+\section{Properties of \LMD}
 
@@
 
-\begin{definition}[Values]
-$A \neq \epsilon$\\
-\begin{align*}
-    \textrm{Values} && v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon & \\
-                    && v^A \in V^A & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} 
-                                           \mid \Lambda\alpha.v^A \mid v^A\ \epsilon &\\
-                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon) & \\
-                                    &&& \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A) & \\
-    \textrm{Redexes} && R^\epsilon & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon & \\
-                     && R^\alpha & ::=\ \TBL_\alpha \TB_\alpha M & \\
-\end{align*}
-\end{definition}
-
 \begin{theorem}[Progress]
     If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then $ M \in V^A $ or $\exists M'$ such that $M \longrightarrow M'$.
+\end{theorem}
+
+\begin{theorem}[Unique Decomposition]
+    If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
+    \begin{enumerate}
+        \item $ M \in V^A$
+        \item $\exists ! B, E^A_B, R^B$ such that ($B = \epsilon$ or $B = \beta$) and $M = E^A_B[R^B]$.
+    \end{enumerate}
 \end{theorem}

### 2019-05-16 main.tex
Add comments for refs.

@@
    \item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
+
+   CSPも入りました
    \item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
@@
    \item A framework for defining logics\cite{harper1993framework}
+
+    $\Sigma$ の使い方を確認した
    \item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
@@
    \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-   \item \red{Dependent types in practical programming}\cite{xi1999dependent}
+   \item Dependent types in practical programming\cite{xi1999dependent}
 
-        Section of Application
-   \item \red{A dependently typed assembly language}\cite{xi2001dependently}
+        Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
+
+   \item A dependently typed assembly language\cite{xi2001dependently}
+
+   DTALの定義と制約solverを用いた型検査の定義
    \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}

### 2019-05-17 main.tex
Delete one technical point.
Wrote the first line!!!!

@@
 The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-
-The first point is CSP in kinding rules.
-$\lambda^{\TW\%}$ includes kinding rules because dependent types need them
-but the relationship between kinds and stages wasn't clear.
-
-The second point is CSP in equivalence rules.
+Especially, handling CSP in equivalence rules of dependent types wasn't clear.
 Parameters of dependent types may contain cross-staged terms.
@@
 \section{Formal Definition of \LMD}
+
+In this section, we present \LMD in detail. we will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context which take stages into account.
+In the next section, we will discuss on properties of \LMD.
+
 \subsection{Syntax}
@@
 \begin{align*}
-    \textrm{Terms} && M,N,L,O,P & ::= x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
+    \textrm{Terms} && M,N,L,O,P & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
     \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
@@
     \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
-    \textrm{Contexts} && \Gamma & ::= \phi \mid 
-    \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G)) \mid 
-    \Gamma,X::K @A\ (X\not\in \textrm{FV}(\G))\\
-    \textrm{Transition variables} && & \alpha,\beta,\gamma, \dots \\
-    \textrm{Transition} && & A,B,C,\dots \\
-    \textrm{Variables} && & x,y,z,\dots \\
-    \textrm{Type variables} && & X,Y,Z,\dots \\
+    \textrm{Contexts} && \Gamma & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \\
+    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
+    \textrm{Transition variables} && & \alpha,\beta,\gamma,... \\
+    \textrm{Transition} && & A,B,C,... \\
+    \textrm{Variables} && & x,y,z,... \\
+    \textrm{Type variables} && & X,Y,Z,... \\
 \end{align*}
@@
 \subsection{Type System}
-\subsubsection{Equivalence Rules}
+\subsubsection{Type Equivalence Rules}
 

### 2019-05-17 main.tex
A part of explanation of syntax.

@@
 
+\LMD is defined by the following grammar.
+
 \begin{align*}
+    \textrm{Type variables} && & X,Y,Z \\
+    \textrm{Constants} && & c \\
+    \textrm{Variables} && & x,y,z \\
+    \textrm{Transition variables} && & \alpha,\beta,\gamma \\
+    \textrm{Transition} && & A,B,C \\
+    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
+    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
+    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
     \textrm{Terms} && M,N,L,O,P & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
     \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
-    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
-    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
     \textrm{Contexts} && \Gamma & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \\
-    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
-    \textrm{Transition variables} && & \alpha,\beta,\gamma,... \\
-    \textrm{Transition} && & A,B,C,... \\
-    \textrm{Variables} && & x,y,z,... \\
-    \textrm{Type variables} && & X,Y,Z,... \\
 \end{align*}
+
+The metavariables $X, Y, \text{and} Z$ range over the type variables, $c$ ranges over constants, the metavariables $x, y, \text{and}, z$ range over the variables.
+The metavariables $\alpha, \beta, \text{and} \gamma$ range over the transition variables.
+A transition, denoted by $A$ and $B$, is a finite sequence of transition variables.
+$\epsilon$ is a symbol for an empty transition.
+
+Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
+Because we adopted a \LLF like system, constants and type variables for base types are given in the signature $\Sigma$.
+
+A kind is $*$ or $\Pi x:\tau.K$. Types of terms have $*$ kinds and dependent types have $\Pi$ kinds.
+
+A type is a type variable which are declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
 

### 2019-05-17 main.tex
Description of types.
Description of quote, unquote, and CSP.

@@
     \textrm{Variables} && & x,y,z \\
-    \textrm{Transition variables} && & \alpha,\beta,\gamma \\
-    \textrm{Transition} && & A,B,C \\
+    \textrm{Stage variables} && & \alpha,\beta,\gamma \\
+    \textrm{Stage} && & A,B,C \\
     \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
     \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
-    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
+    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
     \textrm{Terms} && M,N,L,O,P & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
@@
 A type is a type variable which are declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
+A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
+A function type in ordinary type systems are omitted because it is an specialized case of a dependent type.
+A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
+An $\alpha$-closed type corresponds to a runnable code fragment.
+
+In addition to normal terms in Simply Typed Lambda Calculus, there are five more forms.
+$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.
+$\Lambda\alpha.M$ is a stage variable abstraction.
+$M\ \epsilon$ is an application of $\epsilon$ to a stage variable.
+$\%_\alpha M$ is a primitive operator for cross-stage persistence.
 

### 2019-05-17 main.tex
Fix abstract with grammarly.

@@
 Dependent types are types dependent on values. 
-Vectors with lengths are a famous example of dependent types and they enable us to omit boundary checking.
+A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
 
@@
 
-It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
+\LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
 It also includes an evaluation context which satisfies unique decomposition.
@@
 The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-Especially, handling CSP in equivalence rules of dependent types wasn't clear.
-Parameters of dependent types may contain cross-staged terms.
-We give reasonable equivalence rules to handle them.
+Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
+In this paper, we give reasonable equivalence rules to handle them.
 
@@
 
-\blue{213 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
+\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
 %

### 2019-05-17 main.tex
Fix mistakes.

@@
 Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
-Because we adopted a \LLF like system, constants and type variables for base types are given in the signature $\Sigma$.
+Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.
 
@@
 
-A type is a type variable which are declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
+A type is a type variable which is declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
 A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
-A function type in ordinary type systems are omitted because it is an specialized case of a dependent type.
+A function type in ordinary type systems is omitted because it is a specialized case of a dependent type.
 A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.

### 2019-05-18 main.tex
Write description on reductions.

@@
 
+% 演算子の結合順序
+
+% 自由変数
+
 \subsection{Reduction}
@@
 \begin{definition}[Reduction]
+There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
+Congruence rules which are omitted from the defnition.
 \begin{align*}
@@
     % & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
-    & \TBL_\alpha (\TB_\alpha M)\longrightarrow_\blacklozenge M \\
-    & (\Lambda \alpha.M) \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
+    & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M \\
+    & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
 \end{align*}
-And take a minimum compatible relationship on terms.
+We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
+\end{definition}
 
-    $ M \longrightarrow M'$ iff 
-    $ M \longrightarrow_\Lambda M' $, $ M \longrightarrow_\blacklozenge M' $ or $ M \longrightarrow_\beta M' $.
-\end{definition}
+$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
+$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it become the original code.
+$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
+where $\epsilon$ is substituted to the stage variable.
+There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
+$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
+$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.
 

### 2019-05-18 main.tex
Define substituition.

@@
 
+In this section, we define full reduction for \LMD.
+Before giving the definition of reduction, we define two substitutions.
+Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its defnition here.
+Substituition $M[\alpha \mapsto \epsilon]$ is defined below.
+
+\begin{align*}
+    % \newcommand{\SB}{}
+    (\lambda x:\tau.M)[\alpha \mapsto \epsilon] &= \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon] \\
+    (M\ N)[\alpha \mapsto \epsilon] &= (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon]) \\
+    (\TB_\beta M)[\alpha \mapsto \epsilon] &= \TB_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon] \\
+    (\TBL_\beta M)[\alpha \mapsto \epsilon] &= \TBL_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon] \\
+    (\Lambda\beta.M)[\alpha \mapsto \epsilon] &= \Lambda\beta.M[\alpha \mapsto \epsilon] & (\text{if } \alpha \neq \beta) \\
+    (\Lambda\beta.M)[\alpha \mapsto \epsilon] &= \Lambda\beta.M & (\text{if } \alpha = \beta) \\
+    (M\ \epsilon)[\alpha \mapsto \epsilon] &= M[\alpha \mapsto \epsilon]\ \epsilon \\
+    (\%_\beta M)[\alpha \mapsto \epsilon] &= \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] 
+\end{align*}
+
 \begin{definition}[Reduction]
@@
 where $\epsilon$ is substituted to the stage variable.
+Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
 There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.

### 2019-05-19 main.tex
Wrote connection degree and free variables.

@@
 \newcommand{\FV}{\text{FV}}
-\newcommand{\FTV}{\text{FTV}}
+\newcommand{\FTV}{\text{FSV}}
 
@@
 \subsubsection{Application to Omitting Boundary Checking}
-\subsection{Organaization of the Paper}
+\subsection{Organization of the Paper}
 
@@
 % 演算子の結合順序
+Connection degree of $\TB_\alpha, \TBL_\alpha, \%_\alpha$ is stronger than the two forms of applications
+and applications are left-associative
+and two abstractions extends as far to the right as possible.
 
 % 自由変数
+
+As usual, the variable $x$ is bound in $\lambda x:\tau.M$
+and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
+We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
+We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
+We omit their definitions.
 
@@
 Before giving the definition of reduction, we define two substitutions.
-Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its defnition here.
+Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
 Substituition $M[\alpha \mapsto \epsilon]$ is defined below.

### 2019-05-19 main.tex
Wrote on contexts.
Writing typing rules.
Writing details of typing rules.

@@
 
-\newcommand{\LTP}{$\lambda^{\triangleright\%}$}
-\newcommand{\LMD}{$\lambda^{\textrm{MD}}$}
-\newcommand{\LLF}{$\lambda^{\textrm{LF}}$}
+\newcommand{\LTP}{$\lambda^{\triangleright\%}$\ }
+\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\ }
+\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\ }
 
@@
 
+\newcommand{\TConst}{\textsc{T-Const}}
 \newcommand{\TVar}{\textsc{T-Var}}
@@
     \textrm{Stage} && & A,B,C \\
-    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
     \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
@@
     \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
+    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
     \textrm{Contexts} && \Gamma & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \\
@@
 $\epsilon$ is a symbol for an empty transition.
-
-Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
-Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.
 
@@
 
+Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
+Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.
+
+% Contexts
+Contexts are sequences of triplexes of a variable, its type, and its stage.
+In order to restrict contexts to only well-formed ones, there is a condition of $x\notin\FV(\G)$.
+Because of this condition, there is no type with free variables in contexts.
+
 % 演算子の結合順序
@@
 % 自由変数
-
 As usual, the variable $x$ is bound in $\lambda x:\tau.M$
@@
 There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
-Congruence rules which are omitted from the defnition.
+Congruence rules which are omitted from the definition.
 \begin{align*}
@@
 \subsection{Type System}
+
+% 総論
+
+In this section, we define the type system of \LMD.
+Especially, we discuss on the type equality of \LMD in detail
+because it is the main contribution of this paper.
+\LMD is developed on the basis of \LTP but there is no type equivalence rules in \LTP.
+
+\begin{definition}[Typing]
+    The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure \ref{fig:typing-rules}.
+\end{definition}
+
+% 各論
+The rules \TVar, \TAbs, and \TApp are almost same as those in simply typed lambda calculus if you ignore stage annotations.
+
+\begin{figure}
+\begin{center}
+    \infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau@A}{\TConst} \andalso
+    \infrule{x:\tau@A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau@A}{\TVar} \\[2mm]
+    \infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau@A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
+    \infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
+    \infrule{\G\V M:\tau@A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
+    \infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\textsc{T-$\TB$}} \andalso
+    \infrule{\G\V M:\TW_{\alpha}\tau@A}{\G\V\TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL} \\[2mm]
+    \infrule{\G\V M:\tau@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau@A}{\textsc{T-Gen}} \andalso
+    \infrule{\G\V M:\forall\alpha.\tau@A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
+    \infrule{\G\V M:\tau@A}{\G\V \%_\alpha M:\tau@{A\alpha}}{\textsc{T-Csp}} \andalso
+    \caption{Typing Rules}
+    \label{fig:typing-rules}
+\end{center}
+\end{figure}
+
 \subsubsection{Type Equivalence Rules}

### 2019-05-20 main.tex
Add comments for the outline.
Start wrinting the main technical point.

@@
 \usepackage{xparse}
-\usepackage{ebproof}
+% \usepackage{ebproof}
 \usepackage{lscape}
@@
 \newcommand{\D}{\Delta}
-\newcommand{\V}{\vdash}
+\newcommand{\V}{\vdash_\Sigma}
 \newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
@@
 \begin{align*}
-    \textrm{Type variables} && & X,Y,Z \\
-    \textrm{Constants} && & c \\
-    \textrm{Variables} && & x,y,z \\
-    \textrm{Stage variables} && & \alpha,\beta,\gamma \\
-    \textrm{Stage} && & A,B,C \\
-    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
-    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
-    \textrm{Terms} && M,N,L,O,P & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
-    \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
-    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
-    \textrm{Contexts} && \Gamma & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \\
+    \textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
+    \textrm{Constants}       &  &                          & c                                                                                 \\
+    \textrm{Variables}       &  &                          & x,y,z                                                                             \\
+    \textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
+    \textrm{Stage}           &  &                          & A,B,C                                                                             \\
+    \textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
+    \textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
+    \textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
+    \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
+    \textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
+    \textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G))                         \\
 \end{align*}
@@
     % \newcommand{\SB}{}
-    (\lambda x:\tau.M)[\alpha \mapsto \epsilon] &= \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon] \\
-    (M\ N)[\alpha \mapsto \epsilon] &= (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon]) \\
-    (\TB_\beta M)[\alpha \mapsto \epsilon] &= \TB_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon] \\
-    (\TBL_\beta M)[\alpha \mapsto \epsilon] &= \TBL_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon] \\
-    (\Lambda\beta.M)[\alpha \mapsto \epsilon] &= \Lambda\beta.M[\alpha \mapsto \epsilon] & (\text{if } \alpha \neq \beta) \\
-    (\Lambda\beta.M)[\alpha \mapsto \epsilon] &= \Lambda\beta.M & (\text{if } \alpha = \beta) \\
-    (M\ \epsilon)[\alpha \mapsto \epsilon] &= M[\alpha \mapsto \epsilon]\ \epsilon \\
-    (\%_\beta M)[\alpha \mapsto \epsilon] &= \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] 
+    (\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon]                                  \\
+    (M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
+    (\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon]                                     \\
+    (\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon]                                    \\
+    (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M[\alpha \mapsto \epsilon]                            & (\text{if } \alpha \neq \beta) \\
+    (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
+    (M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
+    (\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] 
 \end{align*}
@@
 % 各論
-The rules \TVar, \TAbs, and \TApp are almost same as those in simply typed lambda calculus if you ignore stage annotations.
+
+% 通常のルール
+The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus if you ignore stage annotations.
+The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
+The rule \TConst\ means any constants in the signature can appear at any stage.
+For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
+the following derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.
+
+\begin{figure}
+	\begin{center}
+		\begin{minipage}{0.50\hsize}
+			\infer[\TConst]
+			{\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
+			{\textrm{true}:\textrm{bool} \in \Sigma \andalso
+				\ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
+			}
+			\caption{A derivation tree using \TConst}
+			\label{fig:tconst-derivation-tree}
+		\end{minipage}
+	\end{center}
+\end{figure}
+
+% 多段階計算のルール
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp are rules for a multistage calculus.
+They are corresponding to quoting a code, unquoting a code, making a stage abstraction, 
+application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
+Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
+
+% \TConv
+The main technical point of this paper is \TConv and type equivalence rules needed in \TConv.
 
@@
 
+\begin{figure}
+	\begin{center}
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \andalso
+		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \andalso
+		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[4mm]
+		\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
+		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \andalso
+		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}} \\[4mm]
+		\caption{Type Equivalence Rules}
+		\label{fig:type-equivalence-rules}
+	\end{center}
+\end{figure}
+
+% Normal Conversion Rules
+
+% \QCsp
+
+% Example of QCsp (mulmat)
+
 \begin{definition}[Values]
@@
 	\begin{align*}
-    \textrm{Values} && v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon & \\
-                    && v^A \in V^A & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} 
-                                           \mid \Lambda\alpha.v^A \mid v^A\ \epsilon &\\
-                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon) & \\
-                                    &&& \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A) & \\
-    \textrm{Redexes} && R^\epsilon & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon & \\
-                     && R^\alpha & ::=\ \TBL_\alpha \TB_\alpha M & \\
+		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
+		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
+		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon)                           & \\
+		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
+		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
+		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
 	\end{align*}
+
+	% Valueの説明
+
 \end{definition}
@@
 		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B
-                                           \mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)\\
+		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                               \\
 	\end{align*}

### 2019-05-21 main.tex
Wrote on \TConv.

@@
 % 通常のルール
-The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus if you ignore stage annotations.
+The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
+if you ignore stage annotations and kind checking.
 The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
+It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
+\TAbs\ also checks the kind of the type.
+
 The rule \TConst\ means any constants in the signature can appear at any stage.
 For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
-the following derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.
+the derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.
 
@@
 The main technical point of this paper is \TConv and type equivalence rules needed in \TConv.
+This rule allows ut to replace a type with another type that is equivalent.
+In a type system which includes dependent types, this kind of rule is essential
+because two types which have different shapes may be equivalent.
+For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
+$\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.
 

### 2019-05-21 main.tex
Wrote outline.

@@
 % 通常のルール
+We show typing rules of \LMD in Figure \ref{fig:typing-rules}.
 The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
@@
 % \TConv
-The main technical point of this paper is \TConv and type equivalence rules needed in \TConv.
+The main technical point of this paper is \TConv\ and type equivalence rules needed in \TConv.
 This rule allows ut to replace a type with another type that is equivalent.
@@
 
-\subsubsection{Type Equivalence Rules}
+\subsubsection{Type Equivalence Rules\\}
+
+As mentioned above, type equivalence rules are needed in \LMD.
+We show the rules in Figure \ref{fig:type-equivalence-rules}.
+
+% 2つの設計手法と今回採用した理由
+
+% \QCsp以外の説明
+
+% \QCspの説明
+
+ % mulmatの例
 

### 2019-05-21 main.tex
Paste a figure.

@@
 % 2つの設計手法と今回採用した理由
+When we design type equivalence rules of \LMD, there are two design choices.
+One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
+Another is defining type equivalence directly by combination of type equivalence rules.
+We adopt the latter one because it is convenient to handle CSP in the type equivalence.
 
@@
 
+\begin{figure}
+	\begin{center}
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \andalso
+		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
+		\infrule{\G\V M \E N : \tau@{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau@A}{\QTB} \andalso
+		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
+		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \andalso
+		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
+		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[4mm]
+		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
+		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \andalso
+		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[4mm]
+		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \andalso
+		\infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
+		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
+		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
+		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent} \andalso
+		\caption{Tem Equivalence Rules}
+		\label{fig:tem-equivalence-rules}
+	\end{center}
+\end{figure}
+
 % Normal Conversion Rules
@@
 % Example of QCsp (mulmat)
+{
+\newcommand{\I}{\textrm{Int}}
+\newcommand{\M}{\textrm{Mat}}
+\begin{align*}
+	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
+	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
+	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
+\end{align*}
+}
 

### 2019-05-21 main.tex
Grammarly

@@
 Before giving the definition of reduction, we define two substitutions.
-Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
-Substituition $M[\alpha \mapsto \epsilon]$ is defined below.
+Substitution $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
+Substitution $M[\alpha \mapsto \epsilon]$ is defined below.
 
@@
 $\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
-$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it become the original code.
+$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it becomes the original code.
 $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
@@
 because it is the main contribution of this paper.
-\LMD is developed on the basis of \LTP but there is no type equivalence rules in \LTP.
+\LMD is developed on the basis of \LTP but there are no type equivalence rules in \LTP.
 
@@
 We show typing rules of \LMD in Figure \ref{fig:typing-rules}.
-The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
+The rules \TVar , \TAbs, and \TApp\ are almost the same as those in simply typed lambda calculus 
 if you ignore stage annotations and kind checking.
@@
 One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-Another is defining type equivalence directly by combination of type equivalence rules.
+Another is defining type equivalence directly by a combination of type equivalence rules.
 We adopt the latter one because it is convenient to handle CSP in the type equivalence.

### 2019-05-22 main.tex
Wrote type equivalence.

@@
     It extends Hanada and Igarashi's \LTP with dependent types.
-
     A multi-stage calculus enables us to generate and execute codes at runtime.
     It can improve the performance of programs by generating optimized codes for given inputs.
-
     Dependent types are types dependent on values. 
     A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
-
     In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
     You can make more efficient programs from existing dependent typed programs with \LMD.
-
     \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
     It also includes an evaluation context which satisfies unique decomposition.
-
     The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
@@
 % \QCsp以外の説明
+We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
+All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
+\QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
+The rule \QTApp means that if there are two equivalent $\Pi$ type and two equivalent terms,
+the result of applications are also equivalent.
+A judgement of $\G \V M \E N : \rho @ A$ means that $M$ and $N$ are equivalent.
+
+\begin{figure}
+	\begin{center}
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
+		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \\[2mm]
+		\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
+		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
+		\caption{Type Equivalence Rules}
+		\label{fig:type-equivalence-rules}
+	\end{center}
+\end{figure}
+
+The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
+\QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.
 
@@
  % mulmatの例
-
-\begin{figure}
-	\begin{center}
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \andalso
-		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
-		\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \andalso
-		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[4mm]
-		\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
-		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \andalso
-		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}} \\[4mm]
-		\caption{Type Equivalence Rules}
-		\label{fig:type-equivalence-rules}
-	\end{center}
-\end{figure}
 
@@
 		\caption{Tem Equivalence Rules}
-		\label{fig:tem-equivalence-rules}
+		\label{fig:term-equivalence-rules}
 	\end{center}

### 2019-05-22 main.tex
Wrote on equivalence rules other than \QCsp.

@@
 The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
+\QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns, \QCsp\ are generated directly from the syntax of a term.
 \QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.
+The rule \QBeta\ means when a term $M \longrightarrow_\beta M'$, $M$ is equivalent to $M'$.
+\QTBLTB and \QLambda are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.
 
@@
 	\begin{center}
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \andalso
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
 		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
@@
 		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
-		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \andalso
+		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \\[2mm]
 		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
-		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[4mm]
+		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[2mm]
 		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
-		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \andalso
-		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[4mm]
-		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \andalso
-		\infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
+		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \\[2mm]
+		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[2mm]
+		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
+		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
+		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
 		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
-		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent} \andalso
+		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
 		\caption{Tem Equivalence Rules}

### 2019-05-22 main.tex
Writing a decsription of QPercent.

@@
 The rule \QBeta\ means when a term $M \longrightarrow_\beta M'$, $M$ is equivalent to $M'$.
-\QTBLTB and \QLambda are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.
+\QTBLTB and \QLambda\ are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.
 
-% \QCspの説明
+% \QPercentの説明
+The rule \QPercent is something special because it has no background of syntax or reductions.
+But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
+For example, we can utilize a dependently typed multistage calculus to generate a code for matrix multiplication.
+When we know sizes of matrices before the multiplication,
+we can generate efficient code for multiplication by unrolling loops.
+
+% Example of QCsp (mulmat)
+{
+\newcommand{\I}{\textrm{Int}}
+\newcommand{\M}{\textrm{Mat}}
+\begin{align*}
+	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
+	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
+	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
+\end{align*}
+}
 
@@
 % \QCsp
-
-% Example of QCsp (mulmat)
-{
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\M}{\textrm{Mat}}
-\begin{align*}
-	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-\end{align*}
-}
 

### 2019-05-22 main.tex
Describe the main example.

@@
 
-% \QPercentの説明
-The rule \QPercent is something special because it has no background of syntax or reductions.
-But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
-For example, we can utilize a dependently typed multistage calculus to generate a code for matrix multiplication.
-When we know sizes of matrices before the multiplication,
-we can generate efficient code for multiplication by unrolling loops.
-
-% Example of QCsp (mulmat)
-{
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\M}{\textrm{Mat}}
-\begin{align*}
-	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-\end{align*}
-}
-
-% mulmatの例
-
 \begin{figure}
@@
 
-% Normal Conversion Rules
+% \QPercentの説明
+The rule \QPercent is something special because it has no background of syntax or reductions.
+But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
+For example, we can utilize a dependently typed multistage calculus to generate a code for matrix multiplication.
+When we know sizes of matrices before the multiplication,
+we can generate efficient code for multiplication by unrolling loops.
 
-% \QCsp
+\newcommand{\I}{\textrm{Int}}
+\newcommand{\M}{\textrm{Mat}}
+
+$\text{mulmat}$ function in following code fragment generate a code for matrix multiplication.
+$\text{mulmat}$ takes two integer which are the size of multiplicand matrix and generate a code.
+The last integer to decide the size of multiplier matrix is given at runtime.
+You can generate a code by applying two integers to $\text{mulmat}$.
+We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
+But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
+\QPercent\ states that we can erase this $\%_\alpha$ under some conditions.
+
+% Example of QCsp (mulmat)
+{
+\begin{align*}
+	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
+	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
+	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
+\end{align*}
+}
+
+% Describe "some conditions".
 

### 2019-05-25 main.tex
Yabaizo...

@@
 But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under some conditions.
+\QPercent\ states that we can erase this $\%_\alpha$ under a conditions which is explained in the next paragraph.
+
+The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
+For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
+In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
 
@@
 
-% Describe "some conditions".
+At the end of definition section, we define values, a staged reduction, and evaluation contexts of \LMD.
 
@@
 	\end{align*}
-
-	% Valueの説明
-
 \end{definition}

### 2019-05-26 main.tex
General descripltion on evaluation contexts.

@@
 
-At the end of definition section, we define values, a staged reduction, and evaluation contexts of \LMD.
+The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
+But we need to fix a order of reduction when we implement a interpreter of \LMD and
+the order must be appropriate in terms of stages.
+
+We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
+In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
+$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
 

### 2019-05-26 main.tex
Finished section 3.

@@
 \begin{definition}[Values]
-	$A \neq \epsilon$\\
+	The family $V^A$ of sets of values, ranged over by $v^A$ and 
+	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
+	are defined by following grammar. In the grammar $A \neq \epsilon$.
 	\begin{align*}
@@
 		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon)                           & \\
+		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                           & \\
 		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
@@
 
-\begin{definition}[Staged Reduction]
-	$A \neq \epsilon$\\
-	\begin{align*}
-		E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
-		E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
-		E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
-	\end{align*}
-\end{definition}
+Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
+The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
+This restriction means that the body of $Lambda$ abstraction must evaluated before application of an $\epsilon$ stage.
+Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
+This is because $\TBL_\alpha v^\epsilon$ is a redex.
 
 \begin{definition}[Evaluation Context]
+	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
+	$A$ is nonempty. (Although $B,A'$ can be empty.)
 	$A \neq \epsilon$\\
@@
 \end{definition}
+
+We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.
+
+\begin{definition}[Staged Reduction]
+	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
+	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
+\end{definition}
+
+\begin{figure}
+	\begin{center}
+		\begin{align*}
+			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
+			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
+			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
+		\end{align*}
+		\caption{Staged Reduction}
+		\label{fig:staged-reduction}
+	\end{center}
+\end{figure}
 

### 2019-05-26 main.tex
Writing properties.

@@
 
-\begin{theorem}[Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
+In this section, we prove some properties of \LMD: subject reduction, strong normalization, confluence,
+unique decomposition of evaluation contexts, and progress.
+
+Substitution lemma for \LMD\ is little more complicated than ordinary one 
+because there are six types of judgement and two types of substitution in \LMD.
+
+\begin{theorem}[Substituition Lemma]
 	\begin{flalign*}
@@
 
-\begin{theorem}[Stage Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
+\begin{proof}
+	Straightforward induction on derivations.
+\end{proof}
+
+\begin{theorem}[Stage Substituition Lemma]
 	\begin{flalign*}
@@
 \end{theorem}
+
+\begin{proof}
+	Straightforward induction on derivations.
+\end{proof}
 

### 2019-05-26 main.tex
Wrote until preservation.

@@
 
-\begin{theorem}[Preservation for term on $\beta$ reduction]
-	If $\G\V M:\tau @A$ and $M \longrightarrow_{\beta} M'$, then $\G\V M':\tau @A$\\
+\begin{theorem}[Preservation]
+	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
 \end{theorem}
 
-\begin{theorem}[Preservation for term on $\TBL\TB$ reduction]
-	If $\G\V M:\tau @A$ and $M\longrightarrow_\blacklozenge N$, then $\G\V N:\tau @A$\\
-\end{theorem}
-
-\begin{theorem}[Preservation for term on $\Lambda$ reduction]
-	If $\G\V M:\tau @A$ and $M \longrightarrow_{\Lambda} N$, then $\G\V N:\tau @A$.
-\end{theorem}
+\begin{proof}
+	Straightforward induction on derivations.
+\end{proof}
 
 \begin{theorem}[Strong Normalization]
-	If $\G\V^A t:T$ then there is no infinite sequence of terms $(t_i)_{i\ge1}$ and $t_i \longrightarrow_{\beta, \TBL \TB,\Lambda} t_{i+1}$ for $i\ge 1$
+	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
+	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
 \end{theorem}

### 2019-05-27 main.tex
Filling gaps.
Finish section 4.

@@
 
+\newcommand{\I}{\textrm{Int}}
+\newcommand{\M}{\textrm{Mat}}
+
 \begin{document}
@@
 Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.
+For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.
 
@@
 In this section, we define the type system of \LMD.
+\LMD\ is little complicated because it contains dependent types.
+It contains typing, kinding, well-formed kinding, term equality, type equality, and kind equality.
+
 Especially, we discuss on the type equality of \LMD in detail
@@
 
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\M}{\textrm{Mat}}
-
 $\text{mulmat}$ function in following code fragment generate a code for matrix multiplication.
@@
 }
+
+This kind of type equality is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
+We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
+because types of codes don't contains $\%_\alpha$ generally.
 
@@
 
+\begin{theorem}[Inversion Lemma for $\Pi$ type]
+	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
+	\begin{enumerate}
+		\item $\G \V \sigma \E \sigma'@A$
+		\item $\G ,x:\sigma@A\V M:\tau@A$
+	\end{enumerate}
+	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
+	\begin{enumerate}
+		\item $\rho = \Pi x:\sigma'.\tau'$
+		\item $\G \V \sigma \E \sigma' : K @A$
+		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
+	\end{enumerate}
+	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
+	\begin{enumerate}
+		\item $\rho = \Pi x:\sigma'.\tau'$
+		\item $\G \V \sigma \E \sigma' : K @A$
+		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
+	\end{enumerate}
+\end{theorem}
+
+\begin{proof}
+	Straightforward induction on derivations.
+\end{proof}
+
+\begin{theorem}[Inversion Lemma for $\TW$ type]
+	\begin{item}
+	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau@A$ then $\G \V M : \tau @A$.
+	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
+	      \begin{enumerate}
+		      \item $\rho = \TW_\alpha \tau'$
+		      \item $\G @A\V \tau \E \tau' : K @A$
+	      \end{enumerate}
+	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
+	      \begin{enumerate}
+		      \item $\rho = \TW_\alpha \tau'$
+		      \item $\G @A\V \tau \E \tau' : K @A$
+	      \end{enumerate}
+	\end{item}
+\end{theorem}
+
+\begin{proof}
+	Straightforward induction on derivations.
+\end{proof}
+
+\begin{theorem}[Inversion Lemma for $\Lambda$ type]
+	\begin{item}
+	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau@A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
+	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
+	      \begin{enumerate}
+		      \item $\rho = \forall\alpha.\tau'$
+		      \item $\G \V \tau \E \tau' : K @A$
+	      \end{enumerate}
+	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
+	      \begin{enumerate}
+		      \item $\rho = \forall\alpha.\tau'$
+		      \item $\G \V \tau \E \tau' : K @A$
+	      \end{enumerate}
+	\end{item}
+\end{theorem}
+
+\begin{proof}
+	Straightforward induction on derivations.
+\end{proof}
+
 \begin{theorem}[Preservation]
@@
 \begin{proof}
-	Straightforward induction on derivations.
+	First, there are three cases for $M \longrightarrow M'$.
+	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
+	For each case, we can use straightforward induction on derivations.
+	Difficult cases are \TApp, \TTBL, and \TIns.
+	We need Inversion Lemmas for them.
 \end{proof}
@@
 
-\begin{theorem}[Confluence(Church-Rosser Property)]
-	Define $M \longrightarrow N$ as $M \longrightarrow_{\beta} N$ or $M\longrightarrow_\blacklozenge N$ or  $M \longrightarrow_{\Lambda} N$.\\
-	For any term $M$, if $M \longrightarrow^* N$ and $M \longrightarrow^* L$,
-	there exists $O$ that satisfies $N \longrightarrow^* O$ and $L \longrightarrow^* O$.
+\begin{proof}
+	In order prove this theorem, we define a translation $\natural$ from \LMD\ to Simply Typed Lambda Calculus.
+	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
+	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of Simply Typed Lambda Calculus.
+\end{proof}
+
+\begin{theorem}[Confluence]
+	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
+	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
 \end{theorem}
 
+\begin{proof}
+	Because we proved Strong Normalization of \LMD, 
+	we can use Newman's lemma to prove Confluence of \LMD.
+	Then, what we must show is Weak Church-Rosser Property now.
+	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
+	In short, they are never overlapped each other.
+	So, we can reduce one of them after we reduce another.
+\end{proof}
+
 \begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then $ M \in V^A $ or $\exists M'$ such that $M \longrightarrow M'$.
+	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
+	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow M'$.
 \end{theorem}
+
+\begin{proof}
+	We can prove by straightforward induction on derivations.
+	Difficult cases are \TApp, \TTBL, and \TIns.
+	We need Inversion Lemmas for them.
+\end{proof}
 
@@
 		\item $ M \in V^A$
-		\item $\exists ! B, E^A_B, R^B$ such that ($B = \epsilon$ or $B = \beta$) and $M = E^A_B[R^B]$.
+		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
 	\end{enumerate}
 \end{theorem}
+
+\begin{proof}
+	We can prove by straightforward induction on derivations.
+	Difficult cases are \TApp, \TTBL, and \TIns.
+	We need Inversion Lemmas for them.
+\end{proof}
 

### 2019-05-28 main.tex
Fix by grammarly.

@@
 % 多段階計算のルール
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp are rules for a multistage calculus.
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multistage calculus.
 They are corresponding to quoting a code, unquoting a code, making a stage abstraction, 
@@
 % \TConv
-The main technical point of this paper is \TConv\ and type equivalence rules needed in \TConv.
+The main technical point of this paper is \TConv\ and type equivalence rules needed by \TConv.
 This rule allows ut to replace a type with another type that is equivalent.
@@
 \QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
-The rule \QTApp means that if there are two equivalent $\Pi$ type and two equivalent terms,
-the result of applications are also equivalent.
+The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
+the results of applications are also equivalent.
 A judgement of $\G \V M \E N : \rho @ A$ means that $M$ and $N$ are equivalent.
@@
 But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
-For example, we can utilize a dependently typed multistage calculus to generate a code for matrix multiplication.
+For example, we can utilize a dependently typed multistage calculus to generate code for matrix multiplication.
 When we know sizes of matrices before the multiplication,
@@
 
-$\text{mulmat}$ function in following code fragment generate a code for matrix multiplication.
-$\text{mulmat}$ takes two integer which are the size of multiplicand matrix and generate a code.
-The last integer to decide the size of multiplier matrix is given at runtime.
-You can generate a code by applying two integers to $\text{mulmat}$.
+$\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
+$\text{mulmat}$ takes two integers which are the size of the multiplicand matrix and generate a code.
+The last integer to decide the size of the multiplier matrix is given at runtime.
+You can generate code by applying two integers to $\text{mulmat}$.
 We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
 But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under a conditions which is explained in the next paragraph.
+\QPercent\ states that we can erase this $\%_\alpha$ under a condition which is explained in the next paragraph.
 
@@
 We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
-because types of codes don't contains $\%_\alpha$ generally.
+because types of codes don't contain $\%_\alpha$ generally.
 
 The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
-But we need to fix a order of reduction when we implement a interpreter of \LMD and
+But we need to fix order of reduction when we implement an interpreter of \LMD and
 the order must be appropriate in terms of stages.
@@
 The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
-This restriction means that the body of $Lambda$ abstraction must evaluated before application of an $\epsilon$ stage.
+This restriction means that the body of $Lambda$ abstraction must be evaluated before application of an $\epsilon$ stage.
 Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
@@
 
-Substitution lemma for \LMD\ is little more complicated than ordinary one 
-because there are six types of judgement and two types of substitution in \LMD.
+Substitution lemma for \LMD\ is little more complicated than an ordinary one 
+because there are six types of judgment and two types of substitution in \LMD.
 

### 2019-05-29 main.tex
Writing on \LTP.

@@
 \section{Informal Overview of \LMD}
+
+In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
+
+\subsection{\LTP}
+
+% quote and unquote
+
+In \LTP, quote and unquote are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
+The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ when $M$ has $\tau$ type.
+The type of $\TBL_\alpha M$ is $\tau$ when $M$ has $\TW_\alpha \tau$.
+Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
+
+% transition variable
+
+The subscription $\alpha$ is a transition variable which is called a stage variable in \LMD.
+It is used to show the thickness of quoting.
+For example, $\TB_\alpha 1$ is a fragment of code which becomes $1$ after run it once and
+$\TB_\alpha \TB_\beta 1$ becomes $1$ after run it twice.
+
+% transition
+
+A sequence of transition variables is a transition which is called a stage in \LMD.
+In \LTP, all judgement has a transition.
+Especially, terms without quoting exist at the empty transition which is represented by $\epsilon$.
+For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
+$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
+
+% transition abstraction
+
+There are abstraction for transition variables and application for transition abstraction in \LTP.
+They looks like $\Lambda\alpha.M$ and $M\ A$, respectively.
+
+% transition application
+
+% run
+
+% CSP
+
+% omitting residualization
+
 \subsection{\LLF}
-\subsection{\LTP}
 \subsection{\LMD}

### 2019-05-29 main.tex
Wrote on transition abstraction and application.

@@
 \usepackage{mdframed}
+\usepackage{xspace}
 
@@
 
-\newcommand{\LTP}{$\lambda^{\triangleright\%}$\ }
-\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\ }
-\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\ }
+\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
+\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
+\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\xspace}
 
@@
 Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
+In addition to normal $\beta$-reduction, there is an reduction rule for unquoted quoted code.
+\begin{align*}
+	\TBL_\alpha (\TB_\alpha M) \longrightarrow M
+\end{align*}
+It means when a quoted code fragment is unquoted, it returns back to the original code fragment.
+\red{This reduction is called $\longrightarrow_\Lambda$ in \LMD.}
 
@@
 It is used to show the thickness of quoting.
-For example, $\TB_\alpha 1$ is a fragment of code which becomes $1$ after run it once and
-$\TB_\alpha \TB_\beta 1$ becomes $1$ after run it twice.
+For example, $\TB_\alpha (\lambda x:\I.x+10)$ is a fragment of code which becomes $(\lambda x:\I.x+10)$ after run it once and
+\red{$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after run it twice.}
 
@@
 
-% transition abstraction
+% transition abstraction and application
 
@@
 They looks like $\Lambda\alpha.M$ and $M\ A$, respectively.
+A transition abstraction binds a transition variable in a term.
+For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
+It is only natural there is a rule for transition application in \LTP.
+The rule is following.
 
-% transition application
+\begin{align*}
+	(\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
+\end{align*}
+
+For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
+\red{Although we can apply any transition to a transition abstraction in \LTP,
+we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
 

### 2019-05-30 main.tex
Writing CSP.

@@
 
+% transition-related symbols disappears when the empty transition is substituted.
+
+Another important rule about a transition variable is 
+that a transition variable related symbol disappears when the empty transition is substituted to the transition variable.
+For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
+This rule is applied all transition variable related symbols: $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$.
+
 % run
+The main purpose of transition abstractions and transition applications are to represent {\bf{run}} operator.
+In multistage calculus, {\bf{run}} is a very important operator.
+It changes quoted code to the original code.
+{\bf{run}} is realized with application of the empty transition $\epsilon$.
+For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
+because $\TB_\epsilon$ is disappeared.
 
 % CSP
+CSP, cross-stage persistence is an important feature of multistage calculus.
+\red{It enable us to embed value at an outer transition into an inner transition}.
 

### 2019-05-31 main.tex
Extending \LTP with Dependent Types.

@@
 % CSP
-CSP, cross-stage persistence is an important feature of multistage calculus.
+CSP, cross-stage persistence, is an important feature of multistage calculus.
 \red{It enable us to embed value at an outer transition into an inner transition}.
+$\%$ is dedicated for CSP in \LTP.
+For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
 
@@
 
-\subsection{\LLF}
-\subsection{\LMD}
+There is another important function called program residualization in \LTP.
+It means that a generated code can be dumped into a file.
+We can load the dumped file and run it.
+The difficulty is arise when program residualization is used with CSP.
+Transition variables are classified to two kinds in \LTP in order to deal with this difficulty.
+
+\subsection{Extending \LTP with Dependent Types}
+
+Next, we develop \LMD by extending \LTP with dependent types.
 

### 2019-05-31 main.tex
Add six types of judgement.
Add descriptions for every theorem.

@@
 
+\subsection{Dependent Types}
+
+% Dependent Types
+
+% Kind, Well-formed kind
+
+% Type Equality
+
 \subsection{Extending \LTP with Dependent Types}
@@
 It contains typing, kinding, well-formed kinding, term equality, type equality, and kind equality.
+In other words, there are six types of judgement in \LMD.
+We show them in Figure \ref{fig:LMD-six-judgements}.
+
+\begin{figure}
+	\begin{center}
+		\begin{align*}
+			\G & \V M : \tau @ A \\
+			\G & \V \tau :: K @ A \\
+			\G & \V K \iskind @ A \\
+			\G & \V M \E N @ A \\
+			\G & \V \tau \E \sigma \\
+			\G & \V K \E J @ A
+		\end{align*}
+		\caption{Six types of judgement in \LMD}
+		\label{fig:LMD-six-judgements}
+	\end{center}
+\end{figure}
 
@@
 
+We need to prove another substitution lemma because there are stage variables.
 \begin{theorem}[Stage Substituition Lemma]
@@
 
-\begin{theorem}[Inversion Lemma for $\Pi$ type]
+Following three inversion lemmas are needed in proving later theorems.
+\begin{lemma}[Inversion Lemma for $\Pi$ type]
 	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
@@
 	\end{enumerate}
-\end{theorem}
+\end{lemma}
 
@@
 
+Reductions preserve typing.
 \begin{theorem}[Preservation]
@@
 
+No typed term has an infinite reduction sequence.
 \begin{theorem}[Strong Normalization]
@@
 
+Any reduction sequences from one typed term converge.
+Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
 \begin{theorem}[Confluence]
@@
 
+Every typed term is a value or can be reduced to another typed term.
 \begin{theorem}[Progress]
@@
 \end{proof}
+
+For every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
+This theorem is important because it ensure 
+that the evaluation context decides a redex to reduce deterministically.
+Specifically, this theorem guarantee that 
+when you write a interpreter using the evaluation context of \LMD,
+your interpreter works just as intended.
 

### 2019-06-01 main.tex
Wrote on Dependent Types.

@@
 \blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
+\blue{コードとかはボールドを使ったほうが良いかもしれない。}
+\red{Suspicious senetences are colored red.}
 %
@@
 
-% Dependent Types
+% \LLF
+\LLF is a simple \red{system} of dependent types introduced in \cite{attapl}.
+It is based on Edinburgh LF\cite{harper1993framework}.
+Therefore, all constants and base types are declared in the signature.
+The \LLF type theory generalizes simply typed lambda calculus
+by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.
 
 % Kind, Well-formed kind
+In addition to ordinary typing rules like simply typed lambda calculus,
+there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
+Kinding rules and well-formed kinding rules are 
+introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
+For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
+for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under en environment $\G$.
 
 % Type Equality
+Type equality rules are needed because the type equivalence is not obivious unlike simply typed lambda calculus.
+For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
+but they are not equivalent seemingly. Thus, we must define equivalence rules.
+In \LLF, equivalence is expressed with a symbol of $\E$.
+$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
+$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
+$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
 

### 2019-06-01 main.tex
Transition in typing rules in \LTP.

@@
 \newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
-\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\xspace}
+\newcommand{\LLF}{$\lambda\textrm{LF}$\xspace}
 
@@
 
+% transition in typing rules
+
+\blue{Should we use $\vdash^A$? or $\vdash @ A$?}
+
+A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
+Transition $A$ means in which transition $M$ exists.
+Therefore, transitions appear in typing rules, too.
+\begin{center}
+	\infrule{\G\vdash M:\tau@{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
+	\infrule{\G\vdash M:\TW_{\alpha}\tau@A}{\G\vdash \TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL}
+\end{center}
+\TTB, corresponding to quoting, means 
+if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
+\TTBL is converse of \TTB.
+
 % transition abstraction and application
@@
 
-Next, we develop \LMD by extending \LTP with dependent types.
+Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
 
@@
 		\infrule{\G\V M:\tau@A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
-		\infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\textsc{T-$\TB$}} \andalso
+		\infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
 		\infrule{\G\V M:\TW_{\alpha}\tau@A}{\G\V\TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL} \\[2mm]

### 2019-06-01 main.tex
Wrote on Kidinding and Well-formed Kinding Rules.

@@
 
-% run
+% Run
 The main purpose of transition abstractions and transition applications are to represent {\bf{run}} operator.
@@
 
-% omitting residualization
+% Omitting Residualization
 
@@
 
-\subsection{Dependent Types}
+\subsection{\LLF}
 
@@
 Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
+From here, we use the word of stage instead of transition 
+because \red{we develop a multistage calculus not a multitransition calculus.}
+
+% Kidinding and Well-formed Kinding Rules
+
+In order to extend \LMD with dependent types, we need kinding rules and well-formed kinding rules.
+It was lucky that almost all rules are determined easily.
+This is because multistage calculus and dependent types are almost \red{orthogonal}.
+Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
+attaching stage anotations to ones of \LLF.
+For example, \KAbs' is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
+\begin{center}
+	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau@A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs'} \\[2mm]
+	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau@A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
+\end{center}
+
+% Constants and Base Types
+
+The way of handling of constants and base types is diffrence between \LMD and \LTP.
+We adopt signature $\Sigma$ to handle constants and base types.
+This is because signature simplify kinding rules relating to type variables.
+
+% Equivalence Rules
+
+% Q-% rule
 
@@
 		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
-		\caption{Tem Equivalence Rules}
+		\caption{Term Equivalence Rules}
 		\label{fig:term-equivalence-rules}

### 2019-06-02 main.tex
コメントを質問の形に書き換えた。

--- 2019-06-01 main.tex
@@
 \newcommand{\I}{\textrm{Int}}
+\newcommand{\B}{\textrm{Bool}}
 \newcommand{\M}{\textrm{Mat}}
@@
 It means when a quoted code fragment is unquoted, it returns back to the original code fragment.
-\red{This reduction is called $\longrightarrow_\Lambda$ in \LMD.}
+This reduction is called $\longrightarrow_\Lambda$ in \LMD.
+\red{この文はここに来るべきなのか? LTPの説明ではないが}
 
@@
 For example, $\TB_\alpha (\lambda x:\I.x+10)$ is a fragment of code which becomes $(\lambda x:\I.x+10)$ after run it once and
-\red{$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after run it twice.}
+$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after run it twice.
+\red{run twiceは表現が微妙}
 
@@
 
-\blue{Should we use $\vdash^A$? or $\vdash @ A$?}
+\red{LTPに合わせて$\vdash^A$を使うべきか? それともLMDに合わせて$\vdash @ A$を使うべきか?}
 
@@
 For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
-\red{Although we can apply any transition to a transition abstraction in \LTP,
-we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
+Although we can apply any transition to a transition abstraction in \LTP,
+we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.
+\red{この文はここに来るべきなのか? LTPの説明ではないが}
 
@@
 CSP, cross-stage persistence, is an important feature of multistage calculus.
-\red{It enable us to embed value at an outer transition into an inner transition}.
+It enable us to embed value at an outer transition into an inner transition.
+\red{inner / outer は適切か?}
 $\%$ is dedicated for CSP in \LTP.
@@
 
-\subsection{Dependent Types}
+\subsection{\LLF}
 
 % \LLF
-\LLF is a simple \red{system} of dependent types introduced in \cite{attapl}.
+\LLF is a simple system of dependent types introduced in \cite{attapl}.
+\red{system / type system / calculus ?}
 It is based on Edinburgh LF\cite{harper1993framework}.
@@
 Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
+From here, we use the word of stage instead of transition 
+because we develop a multistage calculus not a multitransition calculus.
+\red{stageのほうが言葉としてふさわしいと言いたい}
+There are three technical points in the extension from \LTP to \LMD.
+
+% Constants and Base Types
+
+First, the way of handling of constants and base types is diffrence between \LMD and \LTP.
+We adopt a signature $\Sigma$ to handle constants and base types.
+This is because a signature simplify kinding rules relating to type variables.
+A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
+For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
+\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}
+
+% Kidinding and Well-formed Kinding Rules
+
+Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
+It was lucky that almost all rules are determined easily.
+This is because multistage calculus and dependent types are almost orthogonal.
+\red{orthogonal は抽象的すぎるか?}
+Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
+attaching stage anotations to ones of \LLF.
+For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
+\begin{center}
+	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau@A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
+	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau@A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
+\end{center}
+
+% Equivalence Rules
+
+Third, we also need type equivalence rules in \LMD as a dependent type system.
+
+% Q-% rule
 

### 2019-06-02 main.tex
Wrote on Q-% rule.

@@
 Third, we also need type equivalence rules in \LMD as a dependent type system.
+Although there are new primitives relating to stages which aren't in \LLF,
+we can design all rules except \QPercent\ easily.
+\red{design?}
+\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
 
 % Q-% rule
+
+The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
+The equvalence simple rule to handle CSP is \QCsp.
+\begin{center}
+	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp}
+\end{center}
+However, this rule isn't enough when the parameters of dependent types are cross-staed.
+We will discuss on this problem in later section and solve this problem with the new rule \QPercent.
+\begin{center}
+	\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
+\end{center}
+\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
 

### 2019-06-02 main.tex
Fix section 2 with grammarly.

@@
 Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is an reduction rule for unquoted quoted code.
+In addition to normal $\beta$-reduction, there is a reduction rule for unquoted quoted code.
 \begin{align*}
@@
 A sequence of transition variables is a transition which is called a stage in \LMD.
-In \LTP, all judgement has a transition.
+In \LTP, all judgment has a transition.
 Especially, terms without quoting exist at the empty transition which is represented by $\epsilon$.
@@
 
-There are abstraction for transition variables and application for transition abstraction in \LTP.
-They looks like $\Lambda\alpha.M$ and $M\ A$, respectively.
+There are abstractions for transition variables and applications for transition abstraction in \LTP.
+They look like $\Lambda\alpha.M$ and $M\ A$, respectively.
 A transition abstraction binds a transition variable in a term.
@@
 It is only natural there is a rule for transition application in \LTP.
-The rule is following.
+The rule is the following.
 
@@
 
-% transition-related symbols disappears when the empty transition is substituted.
+% transition-related symbols disappear when the empty transition is substituted.
 
@@
 CSP, cross-stage persistence, is an important feature of multistage calculus.
-It enable us to embed value at an outer transition into an inner transition.
+It enables us to embed value at an outer transition into an inner transition.
 \red{inner / outer は適切か?}
-$\%$ is dedicated for CSP in \LTP.
+$\%$ is dedicated to CSP in \LTP.
 For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
@@
 We can load the dumped file and run it.
-The difficulty is arise when program residualization is used with CSP.
-Transition variables are classified to two kinds in \LTP in order to deal with this difficulty.
+The difficulty arises when program residualization is used with CSP.
+Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
 
@@
 For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
-for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under en environment $\G$.
+for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
 
 % Type Equality
-Type equality rules are needed because the type equivalence is not obivious unlike simply typed lambda calculus.
+Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
 For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
@@
 Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-From here, we use the word of stage instead of transition 
-because we develop a multistage calculus not a multitransition calculus.
+From here, we use the word "stage" instead of "transition" 
+because we develop a multi-stage calculus, not a multi-transition calculus.
 \red{stageのほうが言葉としてふさわしいと言いたい}
@@
 
-First, the way of handling of constants and base types is diffrence between \LMD and \LTP.
+First, the way of handling of constants and base types is the difference between \LMD and \LTP.
 We adopt a signature $\Sigma$ to handle constants and base types.
-This is because a signature simplify kinding rules relating to type variables.
+This is because a signature simplifies kinding rules relating to type variables.
 A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
@@
 The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
-The equvalence simple rule to handle CSP is \QCsp.
+The equivalence simple rule to handle CSP is \QCsp.
 \begin{center}
@@
 However, this rule isn't enough when the parameters of dependent types are cross-staed.
-We will discuss on this problem in later section and solve this problem with the new rule \QPercent.
+We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
 \begin{center}

### 2019-06-03 main.tex
Writing Related Works.

@@
 
-\section{Related Work}
+\section{Related Works}
+
+The theory of dependent types was established in 1980s.
+$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
+and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types,
+which were published in that age.
+
+プログラミング言語における依存型の理論は1980年代半ばに確立された．
+この時期の依存型に関する論文として，
+MeyerとReinholdによる$\lambda^\Pi$\cite{Meyer1986}，
+CoquandとHuetによるCalculus of Constructions\cite{coquand:inria-00076024}，
+Harper，Honsell，Plotkinによる\LLF \cite{harper1993framework} が挙げられる．
+この中でも\LLF\cite{harper1993framework} は
+PierceによるAdvanced topics in types and programming languages\cite{attapl}
+で依存型を解説する際に基礎とされている．
+本研究では依存型の基礎として Aspinall, Hoffman \cite{attapl}を使った．
+% 
+依存型を扱えるプログラミング言語としてはIdris\cite{brady2013idris}が存在する．
+また，Coq\cite{09thecoq}やAgdaなどの定理証明支援システムでも依存型を使うことができる．
+% 
+依存型を実際にプログラムの安全性向上のために用いた研究としてはXiとPfenningによるもの\cite{Xi98}がある．
+この研究ではStandard MLを限定された形の依存型を使えるように拡張し，配列の境界検査の回数を減らすことに成功している．
+Dependent types in practical programming\cite{xi1999dependent}.
+% 
+一方，マルチステージプログラミングの型理論も長く研究されている．
+Daviesは$\lambda^\circ$\cite{davies1996temporal}でマルチステージプログラミングと様相論理の間にカリーハワード同型があることを明らかにした．
+しかし，$\lambda^\circ$にはコードの実行やCSPが存在しなかった．
+
+TahaとSheardはMetaML\cite{MetaML}でコードの実行とCSPを導入した．
+さらにTahaとNielsenは$\lambda^\alpha$\cite{taha2003environment}でEnvironment Classiferを導入し，
+bracket，escape，run，cross-stage persistenceの4種類の操作を可能であり，型安全な型システムを構築した．
+また，TsukadaとIgarashiは$\lambda^\TW$\cite{Tsukada}で
+Environment Classiferを含む計算体系に対応する論理体系を発見し，
+Environment Classiferを$\epsilon$で置き換えることでコードの実行を表現できることを示した．
+
+HanadaとIgarashiは\LTP で\LTP にCSPを付け加えることに成功した．
+\LTP は本研究におけるマルチステージプログラミングの体系の基礎である．
+
+実際に使えるマルチステージプログラミング言語としてはBER MetaOCaml\cite{oleg2014}が挙げられる．
+MetaOCaml BERはコードの実行やCSPをサポートしている．
+
+いずれの体系も依存型を扱っておらず，我々の知る限り bracket, escape, run, CSP を持つ依存型システムは本研究が初めてである．
 

### 2019-06-03 main.tex
The first paragraph.

@@
 
-The theory of dependent types was established in 1980s.
+There are many papers on dependent types 
+and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
 $\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types,
-which were published in that age.
+and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
+In Advanced Topics in Types and Programming Languages\cite{attapl},
+a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
+We adopted \cite{attapl}-like dependent types for \LMD.
+
+One can use depent types in programming languages such as Idris\cite{brady2013idris} or
+interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
+\red{この段落要らないかも}
+
+Applications of dependent types for real problems were also
 

### 2019-06-04 main.tex
Applications of dependent types.

@@
 interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らないかも}
-
-Applications of dependent types for real problems were also
+\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
+
+Applications of dependent types for real problems were also researched.
+In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
+and succeeded in reducing boundary checking of arrays.
+Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
 

### 2019-06-04 main.tex
Wrote related works.

@@
 
-プログラミング言語における依存型の理論は1980年代半ばに確立された．
-この時期の依存型に関する論文として，
-MeyerとReinholdによる$\lambda^\Pi$\cite{Meyer1986}，
-CoquandとHuetによるCalculus of Constructions\cite{coquand:inria-00076024}，
-Harper，Honsell，Plotkinによる\LLF \cite{harper1993framework} が挙げられる．
-この中でも\LLF\cite{harper1993framework} は
-PierceによるAdvanced topics in types and programming languages\cite{attapl}
-で依存型を解説する際に基礎とされている．
-本研究では依存型の基礎として Aspinall, Hoffman \cite{attapl}を使った．
-% 
-依存型を扱えるプログラミング言語としてはIdris\cite{brady2013idris}が存在する．
-また，Coq\cite{09thecoq}やAgdaなどの定理証明支援システムでも依存型を使うことができる．
-% 
-依存型を実際にプログラムの安全性向上のために用いた研究としてはXiとPfenningによるもの\cite{Xi98}がある．
-この研究ではStandard MLを限定された形の依存型を使えるように拡張し，配列の境界検査の回数を減らすことに成功している．
-Dependent types in practical programming\cite{xi1999dependent}.
-% 
-一方，マルチステージプログラミングの型理論も長く研究されている．
-Daviesは$\lambda^\circ$\cite{davies1996temporal}でマルチステージプログラミングと様相論理の間にカリーハワード同型があることを明らかにした．
-しかし，$\lambda^\circ$にはコードの実行やCSPが存在しなかった．
-
-TahaとSheardはMetaML\cite{MetaML}でコードの実行とCSPを導入した．
-さらにTahaとNielsenは$\lambda^\alpha$\cite{taha2003environment}でEnvironment Classiferを導入し，
-bracket，escape，run，cross-stage persistenceの4種類の操作を可能であり，型安全な型システムを構築した．
-また，TsukadaとIgarashiは$\lambda^\TW$\cite{Tsukada}で
-Environment Classiferを含む計算体系に対応する論理体系を発見し，
-Environment Classiferを$\epsilon$で置き換えることでコードの実行を表現できることを示した．
-
-HanadaとIgarashiは\LTP で\LTP にCSPを付け加えることに成功した．
-\LTP は本研究におけるマルチステージプログラミングの体系の基礎である．
-
-実際に使えるマルチステージプログラミング言語としてはBER MetaOCaml\cite{oleg2014}が挙げられる．
-MetaOCaml BERはコードの実行やCSPをサポートしている．
-
-いずれの体系も依存型を扱っておらず，我々の知る限り bracket, escape, run, CSP を持つ依存型システムは本研究が初めてである．
+\red{Besides,} multistage calculi also have long history of research.
+Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
+However, $\lambda^\circ$ don't have operators for run and CSP.
+\red{runはboldかな?}
+
+Taha and Sheard introduced run and CSP to a multistage calculus in \cite{MetaML}.
+Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
+construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
+In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multistage calculus with environment classifiers and
+show that run can be represented as application of $\epsilon$ to transition abstractions.
+In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
+which allows us to dump quoted code into an external file.
 

### 2019-06-04 main.tex
Fix by Grammarly.

@@
 
-There are many papers on dependent types 
-and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
+There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
 $\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
@@
 
-One can use depent types in programming languages such as Idris\cite{brady2013idris} or
+One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
 interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
@@
 In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing boundary checking of arrays.
+and succeeded in reducing the bounds checking of arrays.
 Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
 
-\red{Besides,} multistage calculi also have long history of research.
+\red{Besides,} multistage calculi also have a long history of research.
 Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
@@
 In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump quoted code into an external file.
+which allows us to dump the quoted code into an external file.
 

### 2019-06-06 main.tex
Application of multistage calculi.
Make subsubsections of  section 1.
Wrote the first sentences of each paragraph.

@@
 %
+\red{Multistage Programming と Multistage Calculus をどう使い分けるか?}
 \section{Introduction}
-\subsection{Multi-Stage Calculus}
-\subsubsection{Introduction to Multi-Stage Calculus}
-\subsubsection{Application to Performance Imporving}
+
+\subsection{Multistage Programming}
+
+\subsubsection{多段階計算とは何か?}
+
+Multistage programming enable us to generate and run fragments of code at runtime.
+
+\subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
+
+The main application of multistage calculi is program optimization.
+
+\subsubsection{行列計算も高速化できる}
+
+Multistage calculi can also optimize matrices calculation.
+
+\subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
+このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
+
+Generated code is specialized for a given size of matrix and we cannot use it for different sizes.
+We call this problem \red{Specialized Code Problem}.
+
 \subsection{Dependent Types}
-\subsubsection{Introduction to Dependent Types}
-\subsubsection{Application to Omitting Boundary Checking}
-\subsection{Organization of the Paper}
+
+\subsubsection{依存型とは何か?}
+
+Dependent types are types which is dependent on values.
+For example, we can realize vectors with their sizes with them.
+
+\subsubsection{依存型のメリットをサイズ付きのvector, matrixの例を用いて説明する}
+
+The merit of dependent types is guarantee of properties of programs more precisely.
+
+\subsection{Multistage Programming with Dependent Types}
+
+\subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
+このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
+
+We resolve Specialized Code Problem using dependent types.
+
+\subsubsection{Organization of the Paper}
+
+The organization of this paper is following.
 
@@
 
+% 依存型の歴史
+
 There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
@@
 
+% 依存型の応用
+
 Applications of dependent types for real problems were also researched.
@@
 
+% 多段階計算の歴史
+
 \red{Besides,} multistage calculi also have a long history of research.
@@
 However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldかな?}
+\red{runはboldか? Besidesより適切な接続詞はないのか?}
 
@@
 which allows us to dump the quoted code into an external file.
+
+% 多段階計算の応用
+
+MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
+Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
+which include filtering in signal processing, matrix-vector product, and DSL compiler.
 

### 2019-06-07 main.tex
Write the paragraph of 多段階計算とは何か?

@@
 \usepackage{xparse}
-% \usepackage{ebproof}
 \usepackage{lscape}
@@
 Multistage programming enable us to generate and run fragments of code at runtime.
+MetaOCaml\cite{oleg2014} provide features for multistage programming, which are quote, unquote, and running code.
+Quote, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
+Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
+Unqote, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
+Unlike run, unquote is supposed to use in quote, that is, unquote cannot be used as alternative of run.
+For example, the following MetaOCaml expression
+
+\begin{verbatim}
+        let a = .< fun x -> x + 1 >. in .< .~a 2 >.
+\end{verbatim}
+
+evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
+
+\begin{verbatim}
+        run (let a = .< fun x -> x + 1 >. in .< .~a 2 >.)
+\end{verbatim}
+
+is reduced to 3.
 
@@
 \begin{center}
-    \infrule{\G\vdash M:\tau@{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
-    \infrule{\G\vdash M:\TW_{\alpha}\tau@A}{\G\vdash \TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL}
+    \infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
+    \infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
 \end{center}
@@
 \LLF is a simple system of dependent types introduced in \cite{attapl}.
-\red{system / type system / calculus ?}
+\red{system / type system / calculus?}
 It is based on Edinburgh LF\cite{harper1993framework}.
@@
 \begin{center}
-    \infrule{\G\vdash \tau :: * \andalso \G,x:\tau@A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
-    \infrule{\G\V \tau :: *@A \andalso \G,x:\tau@A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
+    \infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
+    \infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
 \end{center}
@@
 \begin{center}
-    \infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp}
+    \infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
 \end{center}
@@
 \begin{center}
-    \infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
+    \infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
 \end{center}
@@
 	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
-	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G))                         \\
+	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G))                         \\
 \end{align*}
@@
 	\begin{center}
-		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau@A}{\TConst} \andalso
-		\infrule{x:\tau@A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau@A}{\TVar} \\[2mm]
-		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau@A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
+		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A}{\TConst} \andalso
+		\infrule{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A}{\TVar} \\[2mm]
+		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
 		\infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
-		\infrule{\G\V M:\tau@A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
-		\infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
-		\infrule{\G\V M:\TW_{\alpha}\tau@A}{\G\V\TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL} \\[2mm]
-		\infrule{\G\V M:\tau@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau@A}{\textsc{T-Gen}} \andalso
-		\infrule{\G\V M:\forall\alpha.\tau@A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
-		\infrule{\G\V M:\tau@A}{\G\V \%_\alpha M:\tau@{A\alpha}}{\textsc{T-Csp}} \andalso
+		\infrule{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
+		\infrule{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
+		\infrule{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL} \\[2mm]
+		\infrule{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A}{\textsc{T-Gen}} \andalso
+		\infrule{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
+		\infrule{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}{\textsc{T-Csp}} \andalso
 		\caption{Typing Rules}
@@
 	\begin{center}
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
 		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
@@
 	\begin{center}
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
+		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
 		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
-		\infrule{\G\V M \E N : \tau@{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau@A}{\QTB} \andalso
-		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
-		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \\[2mm]
-		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
-		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[2mm]
-		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
-		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \\[2mm]
-		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[2mm]
-		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
+		\infrule{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A}{\QTB} \andalso
+		\infrule{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}}{\QTBL} \\[2mm]
+		\infrule{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A}{\QGen} \\[2mm]
+		\infrule{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
+		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp} \\[2mm]
+		\infrule{\G\V M:\tau @A}{\G\V M\E M : \tau @A}{\QRefl} \andalso
+		\infrule{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A}{\QSym} \\[2mm]
+		\infrule{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A}{\QTrans} \\[2mm]
+		\infrule{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
 		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
-		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
-		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
+		\infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
+		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
+		\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
 		\caption{Term Equivalence Rules}
@@
 		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau@A$
+		\item $\G ,x:\sigma@A\V M:\tau @A$
 	\end{enumerate}
@@
 	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau@A$ then $\G \V M : \tau @A$.
+	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
 	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
@@
 	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau@A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
+	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
 	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
@@
 \begin{theorem}[Unique Decomposition]
-	If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
+	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
 	\begin{enumerate}

### 2019-06-07 main.tex
Wrote a paragraph of CSPに関する補足説明.

@@
 \begin{verbatim}
-        let a = .< fun x -> x + 1 >. in .< .~a 2 >.
+        let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
 \end{verbatim}
-
 evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
-
 \begin{verbatim}
-        run (let a = .< fun x -> x + 1 >. in .< .~a 2 >.)
+        run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
 \end{verbatim}
-
 is reduced to 3.
+
+\subsubsection{CSPに関する補足説明}
+Cross-stage Persistence (CSP) is another primitive of multistage programming, which enable us to embed computed values into a code value.
+This is an example of CSP.
+\begin{verbatim}
+        let plusone = fun x -> x + 1 in
+        let a = plusone 2 in  .< a >.
+\end{verbatim}
+This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
+This is because the variable \verb|a| is introduced into a code fragment using CSP.
+Therefore, the variable \verb|a| is embeded after \verb|a| is calculated.
+CSP is very important when we write practival programs 
+because CSP enables us to use library functions in code fragments.
 

### 2019-06-07 main.tex
Wrote a paragraph of 多段階計算のメリットをべき乗の例を用いて説明する.

@@
 
-\subsubsection{多段階計算とは何か?}
+% \subsubsection{多段階計算とは何か?}
 
@@
 
-\subsubsection{CSPに関する補足説明}
+% \subsubsection{CSPに関する補足説明}
+
 Cross-stage Persistence (CSP) is another primitive of multistage programming, which enable us to embed computed values into a code value.
@@
 
-\subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
+% \subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
 
 The main application of multistage calculi is program optimization.
+A famous example is \verb|power| function.
+\verb|power| takes two arguments, which are base and exponent.
+We can make specialized \verb|power| functions for given exponents with multistage calculi and 
+optimize them by unrolling a loop in functions for given exponents.
+\red{powerの実際のコードを持ってくるか?}
 

### 2019-06-07 main.tex
Wrote a paragraph of ベクトル計算も高速化できる.

@@
 
-\subsubsection{行列計算も高速化できる}
-
-Multistage calculi can also optimize matrices calculation.
+% \subsubsection{ベクトル計算も高速化できる}
+
+Multistage programming can also optimize vector calculation.
+For example, an add function of two vectors is impremented with loop in many cases
+though it is used very often in programs handling vectors.
+We can unrolling an add function and optimize it with multistage programming.
 

### 2019-06-07 main.tex
Wrote a paragraph on Specialized Code Problem.

--- 2019-06-07 main.tex
@@
 
-\subsubsection{行列計算も高速化できる}
-
-Multistage calculi can also optimize matrices calculation.
-
-\subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
-
-Generated code is specialized for a given size of matrix and we cannot use it for different sizes.
-We call this problem \red{Specialized Code Problem}.
+% \subsubsection{ベクトル計算も高速化できる}
+
+Multistage programming can also optimize vector calculation.
+For example, \verb|add| function, which takes two vectors and return the sum of them,
+is impremented with loop in many cases.
+We can unroll \verb|add| function for a given vector length and optimize it with multistage programming.
+\red{MetaOCamlで書いた長さ付きベクトルの例?}
+
+% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
+% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
+
+Although unrolled \verb|add| function is optimzied, we cannot use it for different vector length.
+For example, when you optimize for the length of 5, you shoudn't use it for vectors of 3 lengths.
+This problem is serious but existing type systems for multistage calculi cannot prevent it.
+
+% We call this problem \red{Specialized Code Problem}.
 

### 2019-06-08 main.tex
Wrote a paragraph of Multistage Programming with Dependent Types

@@
 For example, when you optimize for the length of 5, you shoudn't use it for vectors of 3 lengths.
+Otherwise, we will get Segmentation Fault error.
 This problem is serious but existing type systems for multistage calculi cannot prevent it.
@@
 
-\subsubsection{依存型とは何か?}
+% \subsubsection{依存型とは何か?}
 
 Dependent types are types which is dependent on values.
+We can use dependent types for securer programming than ordinary types.
 For example, we can realize vectors with their sizes with them.
-
-\subsubsection{依存型のメリットをサイズ付きのvector, matrixの例を用いて説明する}
-
-The merit of dependent types is guarantee of properties of programs more precisely.
+\begin{verbatim}
+        Vector :: Int -> *
+\end{verbatim}
+\verb|Vector| is a type constor which takes the length of vectors.
+\verb|Vector 3| is a type for vectors whose lengths are 3.
+We can confirm the arguments of \verb|add| function is the same with dependent types.
+\red{secure programming? finer grained typing? とか}
 
 \subsection{Multistage Programming with Dependent Types}
-
-\subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
-
-We resolve Specialized Code Problem using dependent types.
+\red{このsectionは短いので上とくっつけてもいいかもしれない}
+
+% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
+% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
+
+As above, functions generated with multistage programming can take more restricted values as arguments.
+When you optimize \verb|add| function for the length of 5, you should it only for 5 length vectors.
+We introduce dependent types into a multistage calculus
+so that the type sysytem can guarantee optimzied functions are used properly.
 

### 2019-06-08 main.tex
Section 1 finished.
Fix typos.

@@
 \red{Multistage Programming と Multistage Calculus をどう使い分けるか?}
+
 \section{Introduction}
@@
 
-Multistage programming enable us to generate and run fragments of code at runtime.
+Multistage programming enables us to generate and run fragments of code at runtime.
 MetaOCaml\cite{oleg2014} provide features for multistage programming, which are quote, unquote, and running code.
@@
 Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Unqote, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, unquote is supposed to use in quote, that is, unquote cannot be used as alternative of run.
+Unquote, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
+Unlike run, unquote is supposed to use in a quoted fragment of code, that is, unquote cannot be used as an alternative of run.
 For example, the following MetaOCaml expression
@@
 This is because the variable \verb|a| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|a| is embeded after \verb|a| is calculated.
-CSP is very important when we write practival programs 
+Therefore, the variable \verb|a| is embedded after \verb|a| is calculated.
+CSP is very important when we write practical programs 
 because CSP enables us to use library functions in code fragments.
@@
 \verb|power| takes two arguments, which are base and exponent.
-We can make specialized \verb|power| functions for given exponents with multistage calculi and 
-optimize them by unrolling a loop in functions for given exponents.
+We can make specialized \verb|power| functions for given exponents with multistage calculi and optimize them by unrolling a loop in functions for given exponents.
 \red{powerの実際のコードを持ってくるか?}
@@
 For example, \verb|add| function, which takes two vectors and return the sum of them,
-is impremented with loop in many cases.
+is implemented with a loop in many cases.
 We can unroll \verb|add| function for a given vector length and optimize it with multistage programming.
@@
 
-Although unrolled \verb|add| function is optimzied, we cannot use it for different vector length.
-For example, when you optimize for the length of 5, you shoudn't use it for vectors of 3 lengths.
-Otherwise, we will get Segmentation Fault error.
+Although unrolled \verb|add| function is optimized, we cannot use it for different vector length.
+For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
+Otherwise, we will get a Segmentation Fault error.
 This problem is serious but existing type systems for multistage calculi cannot prevent it.
@@
 We introduce dependent types into a multistage calculus
-so that the type sysytem can guarantee optimzied functions are used properly.
-
-\subsubsection{Organization of the Paper}
-
-The organization of this paper is following.
-
+so that the type system can guarantee optimized functions are used properly.
+
+\subsection{Organization of the Paper}
+
+The organization of this paper is the following.
+Section 2 gives an informal overview of \LMD.
+Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
+Section 4 shows the properties of \LMD including Unique Decomposition.
+Section 5 discusses future works.
+Finally, Section 6 discusses related works.
 \section{Informal Overview of \LMD}

### 2019-06-08 main.tex
Revise abstract.

@@
 
+\newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}
+
 \begin{document}
@@
 
-    We develop yet another typed multi-stage calculus \LMD.
-    It extends Hanada and Igarashi's \LTP with dependent types.
-    A multi-stage calculus enables us to generate and execute codes at runtime.
-    It can improve the performance of programs by generating optimized codes for given inputs.
-    Dependent types are types dependent on values. 
-    A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
-    In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
-    You can make more efficient programs from existing dependent typed programs with \LMD.
-    \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
-    It also includes an evaluation context which satisfies unique decomposition.
-    The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-    Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
-    In this paper, we give reasonable equivalence rules to handle them.
+  We study a dependently typed extension of a multi-stage programming
+  language \`a la MetaOCaml, which supports quasi-quotation and
+  cross-stage persistence for manipulation of code fragments as
+  first-class values and run for execution of programs dynamically
+  generated by the code manipulation.  Dependent types are expected to
+  bring to multi-stage programming enforcement of strong
+  invariants---beyond simple type safety---on the behavior of
+  dynamically generated code.  An extension is not trivial, however,
+  because a type system would have to take stages---roughly speaking,
+  the number of surrounding quotations---of types into account.
+
+  To rigorously study properties of such an extension, we develop
+  \LMD, which is an extension of Hanada and Igarashi's typed calculus
+  \LTP with dependent types, and prove its properties including
+  subject reduction, confluence, strong normalization for full
+  reduction, and progress \AI{?} for evaluation semantics.  Motivated
+  by code generators such that the type of generated code depends on a
+  value from an earlier stage, we argue the significance of
+  cross-stage persistence in dependently typed multi-stage programming
+  and certain type equivalence that are not directly derived from
+  reduction rules.
+
+    % A multi-stage calculus enables us to generate and execute codes at runtime.
+    % It can improve the performance of programs by generating optimized codes for given inputs.
+    % Dependent types are types dependent on values. 
+    % A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
+    % In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
+    % You can make more efficient programs from existing dependent typed programs with \LMD.
+    % \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
+    % It also includes an evaluation context which satisfies unique decomposition.
+    % The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
+    % Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
+    % In this paper, we give reasonable equivalence rules to handle them.
 

### 2019-06-09 main.tex
Improve Introduction of Multistage Programming.

--- 2019-06-08 main.tex
@@
 Multistage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multistage programming, which are quote, unquote, and running code.
-Quote, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
+MetaOCaml\cite{oleg2014} provide features for multistage programming, which are brackets, escape, and run.
+Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
 Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Unquote, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, unquote is supposed to use in a quoted fragment of code, that is, unquote cannot be used as an alternative of run.
+Escape, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
+Unlike run, escape is supposed to use in a fragment of code, that is, escape cannot be used as an alternative of run.
 For example, the following MetaOCaml expression
@@
         let plusone = fun x -> x + 1 in
-        let a = plusone 2 in  .< a >.
+        let y = plusone 2 in  .< y >.
 \end{verbatim}
 This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
-This is because the variable \verb|a| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|a| is embedded after \verb|a| is calculated.
+This is because the variable \verb|y| is introduced into a code fragment using CSP.
+Therefore, the variable \verb|y| is embedded after it was calculated.
 CSP is very important when we write practical programs 
-because CSP enables us to use library functions in code fragments.
+because CSP enables us to use library functions in code fragments as in \verb|.<List.combine [1;2] ['a';'b']>.|.
 
@@
 The main application of multistage calculi is program optimization.
-A famous example is \verb|power| function.
-\verb|power| takes two arguments, which are base and exponent.
-We can make specialized \verb|power| functions for given exponents with multistage calculi and optimize them by unrolling a loop in functions for given exponents.
-\red{powerの実際のコードを持ってくるか?}
+A famous example is power functions.
+Usual power functions take two arguments, which are the base and the exponent.
+We can make a specialized power function for given exponents with multistage programming and 
+optimize them by unrolling a loop in functions for given exponents.
+The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
+\verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
+Multistage programming can optimize functions which take more than two arguments 
+by generating a code fragment optimized to a given argument.
 
@@
 
+However, there is a sever problem in functions which are optimized by multistage programming.
 Although unrolled \verb|add| function is optimized, we cannot use it for different vector length.

### 2019-06-09 main.tex
Improve Introduction.

@@
 Multistage programming can also optimize vector calculation.
-For example, \verb|add| function, which takes two vectors and return the sum of them,
+For example, \verb|vadd| function, which takes two vectors and return the sum of them,
 is implemented with a loop in many cases.
-We can unroll \verb|add| function for a given vector length and optimize it with multistage programming.
+We can unroll \verb|vadd| function for a given vector length and optimize it with multistage programming.
 \red{MetaOCamlで書いた長さ付きベクトルの例?}
@@
 However, there is a sever problem in functions which are optimized by multistage programming.
-Although unrolled \verb|add| function is optimized, we cannot use it for different vector length.
+Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
 For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
@@
 Dependent types are types which is dependent on values.
-We can use dependent types for securer programming than ordinary types.
+We can use dependent types for securer programming.
 For example, we can realize vectors with their sizes with them.
@@
 \end{verbatim}
-\verb|Vector| is a type constor which takes the length of vectors.
+\verb|Vector| is a type constor which takes the length of vectors, that is, 
 \verb|Vector 3| is a type for vectors whose lengths are 3.
-We can confirm the arguments of \verb|add| function is the same with dependent types.
+If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n|,
+we can confirm the two arguments of \verb|vadd| function has the same length.
 \red{secure programming? finer grained typing? とか}
@@
 \subsection{Multistage Programming with Dependent Types}
-\red{このsectionは短いので上とくっつけてもいいかもしれない}
+\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
 
@@
 
-As above, functions generated with multistage programming can take more restricted values as arguments.
-When you optimize \verb|add| function for the length of 5, you should it only for 5 length vectors.
+As we pointed out in the above section,
+functions optimized with multistage programming can take only restricted values as arguments.
+When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
 We introduce dependent types into a multistage calculus
 so that the type system can guarantee optimized functions are used properly.
+
+In this paper, we design new multistage calculus \LMD by 
+merging dependent types into existing multistage calculus \LTP\cite{Hanada2014}.
+\LMD is multistage calculus which contains dependent types.
+\LMD makes multistage programming more safer with the power of dependent types.
 

### 2019-06-09 main.tex
Revice quote and unqote.

@@
 Finally, Section 6 discusses related works.
+
 \section{Informal Overview of \LMD}
 
+We designed \LMD, a multistage calculus with dependent type.
+\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multistage calculus with CSP and
+we introduced dependent types based on \LTP\cite{attapl}.
 In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
 
+\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
 \subsection{\LTP}
@@
 
-In \LTP, quote and unquote are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
-The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ when $M$ has $\tau$ type.
-The type of $\TBL_\alpha M$ is $\tau$ when $M$ has $\TW_\alpha \tau$.
-Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is a reduction rule for unquoted quoted code.
+\LTP\cite{Hanada2014} is a multistage calculus with CSP by Hanada and Igarashi.
+In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
+The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
+The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
+% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
+In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
 \begin{align*}
@@
 \end{align*}
-It means when a quoted code fragment is unquoted, it returns back to the original code fragment.
-This reduction is called $\longrightarrow_\Lambda$ in \LMD.
-\red{この文はここに来るべきなのか? LTPの説明ではないが}
+It means escape cancels brackets.
+% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
+% \red{この文はここに来るべきなのか? LTPの説明ではないが}
 

### 2019-06-09 main.tex
transition variable

@@
 
-The subscription $\alpha$ is a transition variable which is called a stage variable in \LMD.
-It is used to show the thickness of quoting.
-For example, $\TB_\alpha (\lambda x:\I.x+10)$ is a fragment of code which becomes $(\lambda x:\I.x+10)$ after run it once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after run it twice.
+The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable}.
+It is used to show the thickness of brackets.
+For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
+$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after it was run it twice.
 \red{run twiceは表現が微妙}
@@
 There are three technical points in the extension from \LTP to \LMD.
+
+\red{, which is called a \textit{stage variable} in \LMD.}
 

### 2019-06-09 main.tex
Sync.
Revice until run.

@@
 
-% transition variable
-
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable}.
-It is used to show the thickness of brackets.
+% transition variable and transition
+
+The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
+a sequence of transition variables is called \textit{transition}.
+They are used to show the thickness of brackets.
 For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after it was run it twice.
+$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
+ becomes $(\lambda x:\I.x+10)$ after it was run it twice.
 \red{run twiceは表現が微妙}
 
-% transition
-
-A sequence of transition variables is a transition which is called a stage in \LMD.
+% transition abstraction and application
+
+There are abstractions for transition variables and applications for transition abstraction in \LTP.
+They look like $\Lambda\alpha.M$ and $M A$, respectively.
+A transition abstraction binds a transition variable in a term.
+For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
+It is only natural there is a reduction rule for transition application in \LTP.
+The rule is the following.
+\begin{align*}
+    (\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
+\end{align*}
+For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
+
+% transition-related symbols disappear when the empty transition is substituted.
+% In short, about "run"
+
+Another important rule about a transition variable is 
+that symbols with transition variables disappear 
+when the empty transition $\epsilon$ is substituted to the transition variable.
+The purpose of this rule is express \verb|run| without any special symbol.
+In multistage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
+For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
+In \LTP, \verb|run| is realized with application of the empty transition $\epsilon$.
+
 In \LTP, all judgment has a transition.
@@
 
-% transition abstraction and application
-
-There are abstractions for transition variables and applications for transition abstraction in \LTP.
-They look like $\Lambda\alpha.M$ and $M\ A$, respectively.
-A transition abstraction binds a transition variable in a term.
-For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural there is a rule for transition application in \LTP.
-The rule is the following.
-
-\begin{align*}
-    (\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
-\end{align*}
-
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
-Although we can apply any transition to a transition abstraction in \LTP,
-we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.
-\red{この文はここに来るべきなのか? LTPの説明ではないが}
-
-% transition-related symbols disappear when the empty transition is substituted.
-
-Another important rule about a transition variable is 
-that a transition variable related symbol disappears when the empty transition is substituted to the transition variable.
-For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-This rule is applied all transition variable related symbols: $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$.
-
-% Run
-The main purpose of transition abstractions and transition applications are to represent {\bf{run}} operator.
-In multistage calculus, {\bf{run}} is a very important operator.
-It changes quoted code to the original code.
-{\bf{run}} is realized with application of the empty transition $\epsilon$.
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-because $\TB_\epsilon$ is disappeared.
-
 % CSP
@@
 \red{, which is called a \textit{stage variable} in \LMD.}
+\red{ which is called a stage in \LMD.}
+\red{Although we can apply any transition to a transition abstraction in \LTP,
+we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
 

### 2019-06-09 main.tex
Revice the paragraph of transition in typing rules.

@@
 a sequence of transition variables is called \textit{transition}.
+The empty transition is represented by $\epsilon$.
 They are used to show the thickness of brackets.
@@
 For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
+Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
 In \LTP, \verb|run| is realized with application of the empty transition $\epsilon$.
 
-In \LTP, all judgment has a transition.
-Especially, terms without quoting exist at the empty transition which is represented by $\epsilon$.
+% transition in typing rules
+
+A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
+A transition in a judgement represents where the judgement is true.
+For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
+term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
+Especially, terms without quoting exist at the empty transition $\epsilon$.
 For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
 $\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
-
-% transition in typing rules
-
-\red{LTPに合わせて$\vdash^A$を使うべきか? それともLMDに合わせて$\vdash @ A$を使うべきか?}
-
-A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-Transition $A$ means in which transition $M$ exists.
-Therefore, transitions appear in typing rules, too.
+Terefore, transitions appear in typing rules, too.
 \begin{center}
@@
 \end{center}
-\TTB, corresponding to quoting, means 
+\TTB, corresponding to brackets, means 
 if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
-\TTBL is converse of \TTB.
+\TTBL\ is converse of \TTB.
 

### 2019-06-09 main.tex
Add e-mail.

@@
 Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application of the empty transition $\epsilon$.
+In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.
 
@@
 % CSP
-CSP, cross-stage persistence, is an important feature of multistage calculus.
+
+CSP, cross-stage persistence, is an important feature of \LTP.
 It enables us to embed value at an outer transition into an inner transition.
-\red{inner / outer は適切か?}
 $\%$ is dedicated to CSP in \LTP.
 For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
+\red{inner / outer は適切か?}
 
 % Omitting Residualization
-
-There is another important function called program residualization in \LTP.
-It means that a generated code can be dumped into a file.
-We can load the dumped file and run it.
-The difficulty arises when program residualization is used with CSP.
-Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
+% この段落は3章のM eのあとに、この制限の結果として...という形で入れる
+
+% There is another important feature called program residualization in \LTP.
+% It means that a generated code can be dumped into a file.
+% We can load the dumped file and run it.
+% The difficulty arises when program residualization is used with CSP.
+% Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
 
@@
 
-In this section, we present \LMD in detail. we will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context which take stages into account.
+In this section, we present \LMD in detail. 
+We will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context, which take stages into account.
 In the next section, we will discuss on properties of \LMD.
@@
 In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
+\blue{Review Process
+APLAS 2019 will use a lightweight double-blind reviewing process.
+Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper.
+The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
+To facilitate this process, submitted papers must adhere to the following:
+Author names and institutions must be omitted and
+References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
+The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
+Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas.
+For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure.
+Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would.
+For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
 \end{document}

### 2019-06-10 main.tex
Fix the defnition of Context.
Polish.

@@
   cross-stage persistence for manipulation of code fragments as
-  first-class values and run for execution of programs dynamically
+  first-class values and eval for execution of programs dynamically
   generated by the code manipulation.  Dependent types are expected to
@@
   invariants---beyond simple type safety---on the behavior of
-  dynamically generated code.  An extension is not trivial, however,
+  dynamically generated code.  An extension is, however, not trivial
   because a type system would have to take stages---roughly speaking,
@@
   \LTP with dependent types, and prove its properties including
-  subject reduction, confluence, strong normalization for full
-  reduction, and progress \AI{?} for evaluation semantics.  Motivated
+  preservation, confluence, strong normalization for full
+  reduction, and progress for staged reduction.  Motivated
   by code generators such that the type of generated code depends on a
-  value from an earlier stage, we argue the significance of
+  value from outside of quotations, we argue the significance of
   cross-stage persistence in dependently typed multi-stage programming
@@
 	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
-	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G))                         \\
+	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\tau))                         \\
 \end{align*}

### 2019-06-10 main.tex
Anonymize by using \ifnotanonymous.
Add two papers into the section of reference.

@@
 %
+\newif\ifnotanonymous \notanonymousfalse
 \documentclass[runningheads]{llncs}
@@
 %
-\title{A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
+\title{A Dependently Typed Multi-Stage Calculus%
+  \ifnotanonymous\thanks{Supported by organization x.}\fi
+}
 %
@@
 %
+\ifnotanonymous
 \author{Akira Kawata\inst{1} \and
     Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
-%
+% %
 \authorrunning{A. Kawata, A. Igarashi}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
+% % First names are abbreviated in the running head.
+% % If there are more than two authors, 'et al.' is used.
+% %
 \institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
@@
 }
+\fi
 %
@@
 
-    \keywords{Multistage programming \and Dependent type}
+    \keywords{multi-stage programming, cross-stage persistence, dependent types}
 \end{abstract}
@@
 	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
-	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
-	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\tau))                         \\
+	\textrm{Signature}       &  & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                                    \\
+	\textrm{Contexts}        &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G))                         \\
 \end{align*}
@@
 and succeeded in reducing the bounds checking of arrays.
+In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
+it is useful for spped up.
 Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
@@
 
+% 他段階計算の機能拡張
+
+Combination of multistage programming and another programming feature has been studied.
+Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multistage programming with mutable cells and
+Oishi and Kameyama\cite{oishi2017staging} extended a multistage calculus so that it can handle control operators such as shift and reset.
+
 % 多段階計算の応用
@@
 
-\begin{itemize}
-	\item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
+\begin{enumerate}
+	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
 
 	      CSPも入りました
-	\item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-	\item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-	\item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-	\item A Logical Foundation for Environment Classifiers\cite{Tsukada}
-	\item Environment classifiers\cite{taha2003environment}
-	\item A framework for defining logics\cite{harper1993framework}
+	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
+	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
+	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
+	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
+	\item Done: Environment classifiers\cite{taha2003environment}
+	\item Done: A framework for defining logics\cite{harper1993framework}
 
 	      $\Sigma$ の使い方を確認した
-	\item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-	\item Refined Environment Classifiers\cite{kiselyov2016refined}
-	\item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
+	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
+	\item Done: Dependent types in practical programming\cite{xi1999dependent}
+
+	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
+
+	\item Done: A dependently typed assembly language\cite{xi2001dependently}
+
+		  DTALの定義と制約solverを用いた型検査の定義
+	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
+	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
 	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-	\item Dependent types in practical programming\cite{xi1999dependent}
-
-	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-	\item A dependently typed assembly language\cite{xi2001dependently}
-
-	      DTALの定義と制約solverを用いた型検査の定義
 	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
@@
 
-\end{itemize}
+\end{enumerate}
 

### 2019-06-10 main.tex
Finish the section of references.

@@
 \red{runはboldか? Besidesより適切な接続詞はないのか?}
-
+Benaissa, et al. \cite{benaissa1999logical} study the relationship between multistage calculus and category theory or modal logic.
 Taha and Sheard introduced run and CSP to a multistage calculus in \cite{MetaML}.
@@
 construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
+
 In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multistage calculus with environment classifiers and
@@
 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
-	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
-	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
-	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
-	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
-	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
-	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-
+	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
+	% \item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
+	% \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
+	% \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
+	% \item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
+	% \item \red{Run-time bytecode specialization}\cite{masuhara2001run}
+	% \item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
+	% \item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
+	% \item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
 \end{enumerate}

### 2019-06-10 main.tex
Use the term of multi-stage.

@@
 %
-\red{Multistage Programming と Multistage Calculus をどう使い分けるか?}
+\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}
 
@@
 
-\subsection{Multistage Programming}
+\subsection{Multi-stage Programming}
 
@@
 
-Multistage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multistage programming, which are brackets, escape, and run.
+Multi-stage programming enables us to generate and run fragments of code at runtime.
+MetaOCaml\cite{oleg2014} provide features for multi-stage programming, which are brackets, escape, and run.
 Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
@@
 
-Cross-stage Persistence (CSP) is another primitive of multistage programming, which enable us to embed computed values into a code value.
+Cross-stage Persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
 This is an example of CSP.
@@
 
-The main application of multistage calculi is program optimization.
+The main application of multi-stage calculi is program optimization.
 A famous example is power functions.
 Usual power functions take two arguments, which are the base and the exponent.
-We can make a specialized power function for given exponents with multistage programming and 
+We can make a specialized power function for given exponents with multi-stage programming and 
 optimize them by unrolling a loop in functions for given exponents.
@@
 \verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
-Multistage programming can optimize functions which take more than two arguments 
+Multi-stage programming can optimize functions which take more than two arguments 
 by generating a code fragment optimized to a given argument.
@@
 
-Multistage programming can also optimize vector calculation.
+Multi-stage programming can also optimize vector calculation.
 For example, \verb|vadd| function, which takes two vectors and return the sum of them,
 is implemented with a loop in many cases.
-We can unroll \verb|vadd| function for a given vector length and optimize it with multistage programming.
+We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
 \red{MetaOCamlで書いた長さ付きベクトルの例?}
@@
 
-However, there is a sever problem in functions which are optimized by multistage programming.
+However, there is a sever problem in functions which are optimized by multi-stage programming.
 Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
@@
 Otherwise, we will get a Segmentation Fault error.
-This problem is serious but existing type systems for multistage calculi cannot prevent it.
+This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
 
@@
 
-\subsection{Multistage Programming with Dependent Types}
+\subsection{Multi-stage Programming with Dependent Types}
 \red{このsubsectionは短いので上とくっつけてもいいかもしれない}
@@
 As we pointed out in the above section,
-functions optimized with multistage programming can take only restricted values as arguments.
+functions optimized with multi-stage programming can take only restricted values as arguments.
 When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
-We introduce dependent types into a multistage calculus
+We introduce dependent types into a multi-stage calculus
 so that the type system can guarantee optimized functions are used properly.
 
-In this paper, we design new multistage calculus \LMD by 
-merging dependent types into existing multistage calculus \LTP\cite{Hanada2014}.
-\LMD is multistage calculus which contains dependent types.
-\LMD makes multistage programming more safer with the power of dependent types.
+In this paper, we design new multi-stage calculus \LMD by 
+merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
+\LMD is multi-stage calculus which contains dependent types.
+\LMD makes multi-stage programming more safer with the power of dependent types.
 
@@
 
-We designed \LMD, a multistage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multistage calculus with CSP and
+We designed \LMD, a multi-stage calculus with dependent type.
+\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP and
 we introduced dependent types based on \LTP\cite{attapl}.
@@
 
-\LTP\cite{Hanada2014} is a multistage calculus with CSP by Hanada and Igarashi.
+\LTP\cite{Hanada2014} is a multi-stage calculus with CSP by Hanada and Igarashi.
 In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
@@
 The purpose of this rule is express \verb|run| without any special symbol.
-In multistage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
+In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
 For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
@@
 It was lucky that almost all rules are determined easily.
-This is because multistage calculus and dependent types are almost orthogonal.
+This is because multi-stage calculus and dependent types are almost orthogonal.
 \red{orthogonal は抽象的すぎるか?}
@@
 % 多段階計算のルール
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multistage calculus.
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
 They are corresponding to quoting a code, unquoting a code, making a stage abstraction, 
@@
 But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
-For example, we can utilize a dependently typed multistage calculus to generate code for matrix multiplication.
+For example, we can utilize a dependently typed multi-stage calculus to generate code for matrix multiplication.
 When we know sizes of matrices before the multiplication,
@@
 
-\red{Besides,} multistage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
+\red{Besides,} multi-stage calculi also have a long history of research.
+Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
 However, $\lambda^\circ$ don't have operators for run and CSP.
 \red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multistage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multistage calculus in \cite{MetaML}.
+Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
+Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
 Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
@@
 
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multistage calculus with environment classifiers and
+In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
 show that run can be represented as application of $\epsilon$ to transition abstractions.
@@
 
-Combination of multistage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multistage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multistage calculus so that it can handle control operators such as shift and reset.
+Combination of multi-stage programming and another programming feature has been studied.
+Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
+Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
 

### 2019-06-10 main.tex
Wrote the first paragraph of Conclusions.

@@
 \section{Conclusions}
+
+We proposed new multi-stage calculus \LMD, which can use dependent types.
+\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
+This extention prevent some bugs relating to generated functions with multi-stage programming,
+such as \verb|vadd| function for vectors of a fixed length.
+We proved properties of \LMD including preservation, confluence, 
+strong normalization for full reduction, and progress for staged reduction.
+The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
+We resolve this problem by ignoring $\%$ under some condition.
 

### 2019-06-11 main.tex
Finish Conclusions.
Revise Description on meta variables

@@
 
+\red{以下の3文をどこかに入れる必要がある}
 \red{, which is called a \textit{stage variable} in \LMD.}
@@
 	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
-	\textrm{Constants}       &  &                          & c                                                                                 \\
 	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
@@
 	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
-	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
-	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
+	\textrm{Constants}       &  &                          & c                                                                                 \\
+	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
+	                         &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M         \\  
 	\textrm{Signature}       &  & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                               \\
@@
 
-The metavariables $X, Y, \text{and} Z$ range over the type variables, $c$ ranges over constants, the metavariables $x, y, \text{and}, z$ range over the variables.
+% Description on meta variables
+
+The metavariables $X, Y$, and $Z$ range over the type variables.
+$x, y$, and, $z$ range over the variables.
 The metavariables $\alpha, \beta, \text{and} \gamma$ range over the transition variables.
 A transition, denoted by $A$ and $B$, is a finite sequence of transition variables.
-$\epsilon$ is a symbol for an empty transition.
+$\epsilon$ is a symbol for the empty transition.
 
@@
 
+\red{ 
+$c$ ranges over constants, 
+}
 In addition to normal terms in Simply Typed Lambda Calculus, there are five more forms.
@@
 We resolve this problem by ignoring $\%$ under some condition.
+
+Making algorithmic typing and equality rules for \LMD is a future work.
+They would be complicated but possible 
+because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
 

### 2019-06-11 main.tex
Revise the paragraph of kinds.

@@
 
-The metavariables $X, Y$, and $Z$ range over the type variables.
-$x, y$, and, $z$ range over the variables.
-The metavariables $\alpha, \beta, \text{and} \gamma$ range over the transition variables.
-A transition, denoted by $A$ and $B$, is a finite sequence of transition variables.
+The metavariables $X, Y$, and $Z$ range over a countably infinite set of type variables.
+$x, y$, and, $z$ range over a countably infinite set of variables.
+The metavariables $\alpha, \beta, \text{and} \gamma$ range over the stage variables.
+A transition, denoted by $A$ and $B$, is a finite sequence of stage variables.
 $\epsilon$ is a symbol for the empty transition.
 
-A kind is $*$ or $\Pi x:\tau.K$. Types of terms have $*$ kinds and dependent types have $\Pi$ kinds.
-
-A type is a type variable which is declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
+% Kinds
+
+A kind is either $*$ or $\Pi x:\tau.K$.
+Types of terms have kind $*$ and dependent types have $\Pi$-kinds.
+For example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
+\red{この段落は短いので型の段落と結合するか?}
+
+% Types
+
+A type is a type variable which is declared in the signature, a dependent function type,
+an application of a term to a dependent function type, a code type, or an $\alpha$-closed type.
 A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
@@
 }
-In addition to normal terms in Simply Typed Lambda Calculus, there are five more forms.
+In addition to ordinary terms in Simply Typed Lambda Calculus, there are five more forms.
 $\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.

### 2019-06-11 main.tex
Revise the paragraph of Types.

@@
 an application of a term to a dependent function type, a code type, or an $\alpha$-closed type.
-A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
-A function type in ordinary type systems is omitted because it is a specialized case of a dependent type.
+A function type in ordinary type systems is omitted 
+because it is a special case of a dependent type $\Pi x:\tau$, which has no free occurrence of $x$  in $\tau$.
+An application of a term to a dependent function type is, for example, $\text{Vector}\ 10$
+if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
 A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
 An $\alpha$-closed type corresponds to a runnable code fragment.
+Type constructors tie strongly in the order of 
+an application of a term to a dependent function type $\tau\ M$, a dependent function type $\Pi x:\tau.\tau$, 
+a code type $\TW_{\alpha} \tau$, an $\alpha$-closed type $\F\alpha.\tau$
+Therefore, $\F\alpha.\TW_{\alpha}.\Pi x:\I.\text{Vector}\ 5$ is interpreted as
+$\F\alpha.(\TW_{\alpha}.(\Pi x:\I.(\text{Vector}\ 5)))$.
 

### 2019-06-11 main.tex
Wrote on Substitution Lemma

@@
 
+\subsubsection{Staged Semantics}
+
 The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
@@
 
-In this section, we prove some properties of \LMD: subject reduction, strong normalization, confluence,
+In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
 unique decomposition of evaluation contexts, and progress.
-
-Substitution lemma for \LMD\ is little more complicated than an ordinary one 
+These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
+
+\subsection{Substitution Lemma}
+
+Substitution lemma in \LMD\ is little more complicated than an ordinary one 
 because there are six types of judgment and two types of substitution in \LMD.
-
-\begin{theorem}[Substituition Lemma]
+Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
+typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
+Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
+
+\begin{lemma}[Substitution Lemma on Terms]
 	\begin{flalign*}
@@
 	\end{flalign*}
-\end{theorem}
+\end{lemma}
 
@@
 
-We need to prove another substitution lemma because there are stage variables.
-\begin{theorem}[Stage Substituition Lemma]
+\begin{theorem}[Substitution Lemma on Stages]
 	\begin{flalign*}

### 2019-06-11 main.tex
Wrote the subsection of Inversion Lemma.

@@
 
-Following three inversion lemmas are needed in proving later theorems.
+\subsection{Inversion Lemma}
+
+Following three Inversion Lemmas are needed in proving later theorems.
+Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
+They are composed of three part.
+The first part state that we can infer types of subterms.
+The second and third parts state 
+that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
+We need both of the second and the third because of the reflexivity of the type equivalence.
+
 \begin{lemma}[Inversion Lemma for $\Pi$ type]

### 2019-06-11 main.tex
Wrote a paragraph of Strong Normalization

@@
 
-\subsection{Substitution Lemma}
-
-Substitution lemma in \LMD\ is little more complicated than an ordinary one 
+% Substitution Lemma
+
+Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
 because there are six types of judgment and two types of substitution in \LMD.
@@
 
-\subsection{Inversion Lemma}
+% Inversion Lemma
 
@@
 
-Reductions preserve typing.
+% Preservation
+
+Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
+Preservation ensure that any one step reduction preserves type.
+
 \begin{theorem}[Preservation]
@@
 
-No typed term has an infinite reduction sequence.
+% Strong Normalization
+
+Strong Normalization is also important property which guarantee that
+no typed term has an infinite reduction sequence.
+We prove this thorem by translating \LMD to Simply Typed Lambda Calculus.
+
 \begin{theorem}[Strong Normalization]

### 2019-06-11 main.tex
Finish section 4.

@@
 
-Any reduction sequences from one typed term converge.
+Confluence is a property that any reduction sequences from one typed term converge.
 Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
+
 \begin{theorem}[Confluence]
@@
 
-Every typed term is a value or can be reduced to another typed term.
-\begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow M'$.
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-For every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it ensure 
+Unique Decomposition ensure that
+,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
+This theorem is important because it guarantee
 that the evaluation context decides a redex to reduce deterministically.
-Specifically, this theorem guarantee that 
+Specifically speaking, this theorem guarantee that 
 when you write a interpreter using the evaluation context of \LMD,
@@
 	\end{enumerate}
+\end{theorem}
+
+\begin{proof}
+	We can prove by straightforward induction on derivations.
+	Difficult cases are \TApp, \TTBL, and \TIns.
+	We need Inversion Lemmas for them.
+\end{proof}
+
+Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
+Thanks to Unique Decomposition, we can prove this theorem easily.
+
+\begin{theorem}[Progress]
+	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
+	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
 \end{theorem}

### 2019-06-11 main.tex
Revise until Contexts.

@@
 	\textrm{Signature}       &  & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                               \\
-	\textrm{Contexts}        &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G))               \\
+	\textrm{Contexts}        &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau))               \\
 \end{align*}
@@
 Type constructors tie strongly in the order of 
-an application of a term to a dependent function type $\tau\ M$, a dependent function type $\Pi x:\tau.\tau$, 
-a code type $\TW_{\alpha} \tau$, an $\alpha$-closed type $\F\alpha.\tau$
+an application of a term to a dependent function type $\tau\ M$,
+a code type $\TW_{\alpha} \tau$,
+a dependent function type $\Pi x:\tau.\tau$, 
+an $\alpha$-closed type $\F\alpha.\tau$.
 Therefore, $\F\alpha.\TW_{\alpha}.\Pi x:\I.\text{Vector}\ 5$ is interpreted as
@@
 
-\red{ 
-$c$ ranges over constants, 
-}
+% Terms
+
+Terms include a constant $c$ which is declared in signature $\Sigma$.
 In addition to ordinary terms in Simply Typed Lambda Calculus, there are five more forms.
-$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.
+$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents escape.
 $\Lambda\alpha.M$ is a stage variable abstraction.
@@
 $\%_\alpha M$ is a primitive operator for cross-stage persistence.
-
-Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
+$\TB_\alpha, \TBL_\alpha, \%_\alpha$ tie stronger than the two forms of applications
+and applications are left-associative
+and two abstractions extends as far to the right as possible.
+For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
+
+% Signature
+
+Signatures are sequences of pairs of a type variable and its kind or a constant and its type.
 Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.
 For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.
-
-% Contexts
-Contexts are sequences of triplexes of a variable, its type, and its stage.
-In order to restrict contexts to only well-formed ones, there is a condition of $x\notin\FV(\G)$.
-Because of this condition, there is no type with free variables in contexts.
-
-% 演算子の結合順序
-Connection degree of $\TB_\alpha, \TBL_\alpha, \%_\alpha$ is stronger than the two forms of applications
-and applications are left-associative
-and two abstractions extends as far to the right as possible.
 
@@
 We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
+
+% Contexts
+Contexts are sequences of triples of a variable, its type, and its stage.
 We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
-We omit their definitions.
+$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
+The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
+$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.
 
@@
 
+\section{Appendix}
+
 \blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.

### 2019-06-11 main.tex
Revise substituition of stage variable.

@@
 
-% 自由変数
+% Free variables
 As usual, the variable $x$ is bound in $\lambda x:\tau.M$
@@
 We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
+We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
 
@@
 Contexts are sequences of triples of a variable, its type, and its stage.
-We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
 $\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
@@
 	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon]                                     \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon]                                    \\
+	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
+	(\TB_\beta M)[\alpha \mapsto \epsilon]    & = \TB_\beta M[\alpha \mapsto \epsilon]                            & (\text{if } \alpha \neq \beta) \\
+	(\TB_\beta M)[\alpha \mapsto \epsilon]    & = M[\alpha \mapsto \epsilon] & (\text{if } \alpha = \beta) \\
+	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta M[\alpha \mapsto \epsilon]   & (\text{if } \alpha \neq \beta)                                 \\
+	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]   & (\text{if } \alpha = \beta)                                 \\
 	(\Lambda\beta.M)[\alpha \mapsto \epsilon] & = \Lambda\beta.M[\alpha \mapsto \epsilon]                         & (\text{if } \alpha \neq \beta) \\
 	(\Lambda\beta.M)[\alpha \mapsto \epsilon] & = \Lambda\beta.M                                                  & (\text{if } \alpha = \beta)    \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] 
+	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] & (\text{if } \alpha \neq \beta) \\
+	(\%_\beta M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon] & (\text{if } \alpha = \beta) \\
 \end{align*}

### 2019-06-11 main.tex
Format by vim-latex.

@@
 
-$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
-$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it becomes the original code.
+  $\longrightarrow_\beta$ is ordinary $\beta-$reduction in lambda calculus.
+  $\longrightarrow_\blacklozenge$ means that when a code fragment is escaped, it becomes the original code.
   $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
@@
   $\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
-$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.
+  $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
 
@@
 
-\subsubsection{Type Equivalence Rules\\}
+  \subsubsection{Type Equivalence Rules}
 
@@
       \begin{center}
-			\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
-			\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
+          \infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs } \\[2mm]
+          \infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp } \\[2mm]
           \infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso

### 2019-06-11 main.tex
Format.
[WIP] revising and adding comments

@@
 \newcommand{\iskind}{\text{\ kind}}
-\newcommand{\TW}{\triangleright}
-\newcommand{\TWL}{\triangleleft}
+\newcommand{\TW}{{\mathop{\triangleright}}}
+\newcommand{\TWL}{{\mathop{\triangleleft}}}
 \newcommand{\F}{\forall}
-\newcommand{\TB}{\blacktriangleright}
-\newcommand{\TBL}{\blacktriangleleft}
+\newcommand{\TB}{{\mathop{\blacktriangleright}}}
+\newcommand{\TBL}{{\mathop{\blacktriangleleft}}}
 \newcommand{\E}{\equiv}
@@
 Finally, Section 6 discusses related works.
+\AI{Use $\backslash$label and $\backslash$ref!}
+\AI{``Related work'' and ``future work'' (they are uncountable).}
 
@@
 
-In this section, we present \LMD in detail. 
-We will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context, which take stages into account.
-In the next section, we will discuss on properties of \LMD.
+In this section, we give a formal definition of \LMD, including
+the syntax, full reduction, and type system.  In addition to full reduction,
+in which any redex at any stage can be reduced, we also give staged reduction,
+which models execution as programs.
 
@@
 
-\LMD is defined by the following grammar.
+We assume the denumerable set of type variables, ranged over by
+metavariables \(X, Y, Z\), the denumerable set of variables, ranged
+over by \(x,y,z\), the denumerable set of constants, ranged over by
+\(c\), and the denumerable set of stage variables, ranged over by
+\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
+sequences of stage variables; we write \(\varepsilon\) for the empty
+sequence.  \AI{I think $\varepsilon$ is a more standard symbol for
+  the nonempty sequence.}  \LMD is defined by the following grammar:
+
+\AI{``Transition'' is still used.}
 
 \begin{align*}
-    \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
-    \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
-    \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
-    \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
+    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
+    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
+    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
+    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
     \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
     \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
-    \textrm{Constants}       &   &                          & c                                                                                                          \\
+%     \textrm{Constants}       &   &                          & c                                                                                                          \\
     \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
                              &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
-    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                                                        \\
+    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
     \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
@@
 
+\AI{Is $O$ used as a metavariable?}
+\AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
+
 % Description on meta variables
 
-The metavariables $X, Y$, and $Z$ range over a countably infinite set of type variables.
-$x, y$, and, $z$ range over a countably infinite set of variables.
-The metavariables $\alpha, \beta, \text{and} \gamma$ range over the stage variables.
-A transition, denoted by $A$ and $B$, is a finite sequence of stage variables.
-$\epsilon$ is a symbol for the empty transition.
-
 % Kinds
 
-A kind is either $*$ or $\Pi x:\tau.K$.
-Types of terms have kind $*$ and dependent types have $\Pi$-kinds.
-For example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
-\red{この段落は短いので型の段落と結合するか?}
-
+A kind, which is used to classify types, is either $*$, the kind of
+proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
+of type operators that takes $x$ as an argument of type $\tau$ and returns a type
+of kind $K$.
 % Types
-
-A type is a type variable which is declared in the signature, a dependent function type,
-an application of a term to a dependent function type, a code type, or an $\alpha$-closed type.
-A function type in ordinary type systems is omitted 
-because it is a special case of a dependent type $\Pi x:\tau$, which has no free occurrence of $x$  in $\tau$.
-An application of a term to a dependent function type is, for example, $\text{Vector}\ 10$
+% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
+% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
+% \red{この段落は短いので型の段落と結合するか?}
+% Types
+A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
+an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
+We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
+$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
+An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
 if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
@@
 An $\alpha$-closed type corresponds to a runnable code fragment.
-Type constructors tie strongly in the order of 
+Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
 an application of a term to a dependent function type $\tau\ M$,
@@
 Therefore, $\F\alpha.\TW_{\alpha}.\Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha}.(\Pi x:\I.(\text{Vector}\ 5)))$.
+$\F\alpha.(\TW_{\alpha}.(\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
 
@@
 
-Terms include a constant $c$ which is declared in signature $\Sigma$.
-In addition to ordinary terms in Simply Typed Lambda Calculus, there are five more forms.
-$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents escape.
-$\Lambda\alpha.M$ is a stage variable abstraction.
-$M\ \epsilon$ is an application of $\epsilon$ to a stage variable.
-$\%_\alpha M$ is a primitive operator for cross-stage persistence.
-$\TB_\alpha, \TBL_\alpha, \%_\alpha$ tie stronger than the two forms of applications
+Terms include ordinary explicitly typed \(\lambda\)-terms, constants,
+whose type is declared in signature $\Sigma$, and the following five forms
+related to multi-stage programming:
+$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
+$\Lambda\alpha.M$ is a stage variable abstraction;
+$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
+$\%_\alpha M$ is an operator for cross-stage persistence.
+The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
 and applications are left-associative
@@
 
-Signatures are sequences of pairs of a type variable and its kind or a constant and its type.
-Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.
-For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.
+We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
+are a sequence of declarations of the form $c:\tau$ and $X:K$.
+For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
 
@@
 and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
+\AI{What about other binders such as $\Pi$?}
 We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
@@
 
+\AI{We should note that constants and type variables are not staged.}
 \subsection{Reduction}

### 2019-06-11 main.tex
Wrote till Typing rules for a multi-stage calculus.

--- 2019-06-11 main.tex
@@
 Terms include a constant $c$ which is declared in signature $\Sigma$.
-In addition to ordinary terms in Simply Typed Lambda Calculus, there are five more forms.
+In addition to ordinary terms in the symply typed lambda calculus, there are five more forms.
 $\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents escape.
@@
 
-In this section, we define full reduction for \LMD.
+Next, we define full reduction for \LMD.
 Before giving the definition of reduction, we define two substitutions.
@@
 In this section, we define the type system of \LMD.
-  \LMD\ is little complicated because it contains dependent types.
+\LMD is little complicated because it contains dependent types.
 It contains typing, kinding, well-formed kinding, term equality, type equality, and kind equality.
@@
 		\begin{align*}
-              \G & \V M : \tau @ A   \\
-              \G & \V \tau :: K @ A  \\
-              \G & \V K \iskind @ A  \\
-              \G & \V M \E N @ A     \\
-              \G & \V \tau \E \sigma \\
-              \G & \V K \E J @ A     
+			\G & \V M : \tau @ A   & \text{typing} \\
+			\G & \V \tau :: K @ A  & \text{kinding} \\
+			\G & \V K \iskind @ A  & \text{well-formed kinding} \\
+			\G & \V M \E N @ A     & \text{term equality} \\
+			\G & \V \tau \E \sigma & \text{type equality} \\
+			\G & \V K \E J @ A     & \text{kind equality}
 		\end{align*}
@@
 
-  Especially, we discuss on the type equality of \LMD in detail
-  because it is the main contribution of this paper.
-  \LMD is developed on the basis of \LTP but there are no type equivalence rules in \LTP.
-
 \begin{definition}[Typing]
@@
 \end{definition}
-
-  % 各論
-
-  % 通常のルール
-  We show typing rules of \LMD in Figure \ref{fig:typing-rules}.
-  The rules \TVar , \TAbs, and \TApp\ are almost the same as those in simply typed lambda calculus 
+We start from defining typing of \LMD.
+Typing rules of \LMD are shown in Figure \ref{fig:typing-rules}.
+The rule \TConst\ means any constants in the signature can appear at any stage.
+For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
+the derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.
+The rules \TVar , \TAbs, and \TApp\ are almost the same as those in the simply typed lambda calculus 
 if you ignore stage annotations and kind checking.
@@
 It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
-  \TAbs\ also checks the kind of the type.
-
-  The rule \TConst\ means any constants in the signature can appear at any stage.
-  For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
-  the derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.
+The rule \TAbs\ also checks the kind of the type.
+The rule \TApp\ requires $M$ and $N$ are typed at the same stage.
 
@@
 
-  % 多段階計算のルール
+% Typing rules for a multi-stage calculus
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
-  They are corresponding to quoting a code, unquoting a code, making a stage abstraction, 
+They are corresponding to brackets, escaping a code, making a stage abstraction, 
 application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
@@
 no typed term has an infinite reduction sequence.
-  We prove this thorem by translating \LMD to Simply Typed Lambda Calculus.
+We prove this thorem by translating \LMD to the symply typed lambda calculus.
 
@@
 \begin{proof}
-      In order prove this theorem, we define a translation $\natural$ from \LMD\ to Simply Typed Lambda Calculus.
+	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
 	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-      Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of Simply Typed Lambda Calculus.
+	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
 \end{proof}

### 2019-06-11 main.tex
[WIP] Resolve conflict
Remove itemized references.

@@
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
-They are corresponding to brackets, escaping a code, making a stage abstraction, 
+They are corresponding to brackets, escape, making a stage abstraction, 
 application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
@@
 The main technical point of this paper is \TConv\ and type equivalence rules needed by \TConv.
-This rule allows ut to replace a type with another type that is equivalent.
+This rule allows us to replace a type with another type that is equivalent.
 In a type system which includes dependent types, this kind of rule is essential
 because two types which have different shapes may be equivalent.
-For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
-$\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.
+For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
+$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
 
@@
 
-% 2つの設計手法と今回採用した理由
-When we design type equivalence rules of \LMD, there are two design choices.
-One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-Another is defining type equivalence directly by a combination of type equivalence rules.
-We adopt the latter one because it is convenient to handle CSP in the type equivalence.
-
 % \QCsp以外の説明
@@
 		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
 		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
+		\infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
 		\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
@@
 
-\begin{enumerate}
-	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
-
-	      CSPも入りました
-	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
-	\item Done: Environment classifiers\cite{taha2003environment}
-	\item Done: A framework for defining logics\cite{harper1993framework}
-
-	      $\Sigma$ の使い方を確認した
-	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-	\item Done: Dependent types in practical programming\cite{xi1999dependent}
-
-	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-	\item Done: A dependently typed assembly language\cite{xi2001dependently}
-
-	      DTALの定義と制約solverを用いた型検査の定義
-	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
-	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
+% \begin{enumerate}
+% 	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
+
+% 	      CSPも入りました
+% 	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
+% 	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
+% 	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
+% 	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
+% 	\item Done: Environment classifiers\cite{taha2003environment}
+% 	\item Done: A framework for defining logics\cite{harper1993framework}
+
+% 	      $\Sigma$ の使い方を確認した
+% 	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
+% 	\item Done: Dependent types in practical programming\cite{xi1999dependent}
+
+% 	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
+
+% 	\item Done: A dependently typed assembly language\cite{xi2001dependently}
+
+% 	      DTALの定義と制約solverを用いた型検査の定義
+% 	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
+% 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
+% 	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
 % 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
@@
 % 	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-\end{enumerate}
+% \end{enumerate}
 
@@
 because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
+
+% 2つの設計手法と今回採用した理由
+% Conclusion送りか?
+% When we design type equivalence rules of \LMD, there are two design choices.
+% One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
+% Another is defining type equivalence directly by a combination of type equivalence rules.
+% We adopt the latter one because it is convenient to handle CSP in the type equivalence.
 

### 2019-06-12 main.tex

--- 2019-06-11 main.tex
@@
 
-  % 多段階計算のルール
+% Typing rules for a multi-stage calculus
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
-  They are corresponding to quoting a code, unquoting a code, making a stage abstraction, 
+They are corresponding to brackets, escape, making a stage abstraction, 
 application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
@@
 The main technical point of this paper is \TConv\ and type equivalence rules needed by \TConv.
-  This rule allows ut to replace a type with another type that is equivalent.
+This rule allows us to replace a type with another type that is equivalent.
 In a type system which includes dependent types, this kind of rule is essential
 because two types which have different shapes may be equivalent.
-  For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
-  $\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.
+For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
+$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
 
@@
 
-  % 2つの設計手法と今回採用した理由
-  When we design type equivalence rules of \LMD, there are two design choices.
-  One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-  Another is defining type equivalence directly by a combination of type equivalence rules.
-  We adopt the latter one because it is convenient to handle CSP in the type equivalence.
-
 % \QCsp以外の説明
@@
 		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-          \infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
 		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
+		\infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
 		\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
@@
 
-  \begin{enumerate}
-      \item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
-
-          CSPも入りました
-      \item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-      \item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-      \item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-      \item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
-      \item Done: Environment classifiers\cite{taha2003environment}
-      \item Done: A framework for defining logics\cite{harper1993framework}
-
-          $\Sigma$ の使い方を確認した
-      \item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-      \item Done: Dependent types in practical programming\cite{xi1999dependent}
-
-          Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-      \item Done: A dependently typed assembly language\cite{xi2001dependently}
-
-          DTALの定義と制約solverを用いた型検査の定義
-      \item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
-      \item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-      \item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
+% \begin{enumerate}
+% 	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
+
+% 	      CSPも入りました
+% 	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
+% 	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
+% 	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
+% 	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
+% 	\item Done: Environment classifiers\cite{taha2003environment}
+% 	\item Done: A framework for defining logics\cite{harper1993framework}
+
+% 	      $\Sigma$ の使い方を確認した
+% 	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
+% 	\item Done: Dependent types in practical programming\cite{xi1999dependent}
+
+% 	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
+
+% 	\item Done: A dependently typed assembly language\cite{xi2001dependently}
+
+% 	      DTALの定義と制約solverを用いた型検査の定義
+% 	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
+% 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
+% 	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
 % 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
@@
 % 	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-  \end{enumerate}
+% \end{enumerate}
 

### 2019-06-12 main.tex
[WIP] Add some more comments.

@@
 
-Terms include ordinary explicitly typed \(\lambda\)-terms, constants,
+Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
 whose type is declared in signature $\Sigma$, and the following five forms
@@
 % Contexts
-Contexts are sequences of triples of a variable, its type, and its stage.
+Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
 $\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
+\AI{I'd prefer \textit{dom}.}
 The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
@@
 \AI{We should note that constants and type variables are not staged.}
+\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
+
 \subsection{Reduction}
@@
 Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define two substitutions.
-Substitution $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
-Substitution $M[\alpha \mapsto \epsilon]$ is defined below.
+Before giving the definition of reduction, we define two kinds of substitutions.
+Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
+$N$ for $x$ in $M$, and we omit its definition here.
+Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
+for stage variable $\alpha$ in $M$ is defined below.
+\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}
 
@@
 	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon]                                  \\
+	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
 	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta M[\alpha \mapsto \epsilon]                               & (\text{if } \alpha \neq \beta) \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                         & (\text{if } \alpha = \beta)    \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta M[\alpha \mapsto \epsilon]                              & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        & (\text{if } \alpha = \beta)    \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M[\alpha \mapsto \epsilon]                            & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon]      & (\text{if } \alpha \neq \beta) \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         & (\text{if } \alpha = \beta)    \\
+	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
+	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
+	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
+	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
+	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
+	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
+	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
+	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
+	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
 \end{align*}

### 2019-06-12 main.tex
[WIP] Revising Section 3 still.

@@
 sequences of stage variables; we write \(\varepsilon\) for the empty
-sequence.  \AI{I think $\varepsilon$ is a more standard symbol for
-  the nonempty sequence.}  \LMD is defined by the following grammar:
+sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:
 
@@
 
+\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
+
 \begin{align*}
@@
 \begin{definition}[Reduction]
+  \AI{It's not clear what are defined here.  You are talking only about rules.
+    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
 	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
@@
 
-$\longrightarrow_\beta$ is ordinary $\beta-$reduction in lambda calculus.
-$\longrightarrow_\blacklozenge$ means that when a code fragment is escaped, it becomes the original code.
-$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
-where $\epsilon$ is substituted to the stage variable.
-Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
+The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
+$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
+the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
+where $\epsilon$ is substituted for the stage variable.
+Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
 There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
-$\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
+The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
+% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
+
+\AI{A few examples are desirable.}
 
@@
 In this section, we define the type system of \LMD.
-\LMD is little complicated because it contains dependent types.
-It contains typing, kinding, well-formed kinding, term equality, type equality, and kind equality.
-In other words, there are six types of judgement in \LMD.
-We show them in Figure \ref{fig:LMD-six-judgements}.
+% \LMD is little complicated because it contains dependent types.
+It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
+We list the judgments forms in Figure~\ref{fig:LMD-six-judgements}.
+\AI{equality vs. equivalence?}
+\AI{A few judgment forms do not match rules.}
 
@@
 		\end{align*}
-		\caption{Six types of judgement in \LMD}
+		\caption{Six judgment forms of the type system of \LMD.}
 		\label{fig:LMD-six-judgements}
@@
 
+\AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
 \begin{definition}[Typing]
-	The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure \ref{fig:typing-rules}.
+  The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
+  \AI{Precisely speaking, it cannot be defined independently of other judgments.
+  How is dependency between judgments?}
 \end{definition}
-We start from defining typing of \LMD.
-Typing rules of \LMD are shown in Figure \ref{fig:typing-rules}.
-The rule \TConst\ means any constants in the signature can appear at any stage.
-For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
-the derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.
-The rules \TVar , \TAbs, and \TApp\ are almost the same as those in the simply typed lambda calculus 
-if you ignore stage annotations and kind checking.
-The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
-It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
-The rule \TAbs\ also checks the kind of the type.
-The rule \TApp\ requires $M$ and $N$ are typed at the same stage.
+
+\AI{``judgment'' vs. ``judgement''.}  We start from defining typing of
+\LMD.  Typing rules of \LMD are shown in Figure
+\ref{fig:typing-rules}.  The rule \TConst{} means any constants in the
+signature can appear at any stage.  \AI{This should be discussed
+  earlier.}  For example, if we have a signature $\Sigma$ which is
+$\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
+\textrm{bool}$, the derivation tree in
+Figure~\ref{fig:tconst-derivation-tree} is admissible.  \AI{Don't we
+  need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$
+  should be a well-formed type under ... what?}  The rules \TVar,
+\TAbs, and \TApp{} are almost the same as those in the simply typed
+lambda calculus.  \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}  Additional conditions are that subterms must be
+typed at the same stage (\TAbs{} and \TApp); the type
+annotation/declaration on a variable has to be a proper type of kind
+$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
 
@@
 
-% Typing rules for a multi-stage calculus
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
-They are corresponding to brackets, escape, making a stage abstraction, 
-application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
-Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
-
 % \TConv
-The main technical point of this paper is \TConv\ and type equivalence rules needed by \TConv.
-This rule allows us to replace a type with another type that is equivalent.
+\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is opposite.}
+As in standard dependent type systems, \TConv{} allows us to replace
+the type of a term with an equivalent one.  
 In a type system which includes dependent types, this kind of rule is essential
@@
 
+% Typing rules for a multi-stage calculus
+\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
+They are corresponding to brackets, escape, making a stage abstraction, 
+application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
+Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
+
 \begin{figure}
 	\begin{center}
-		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A}{\TConst} \andalso
-		\infrule{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A}{\TVar} \\[2mm]
-		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
-		\infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
-		\infrule{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
-		\infrule{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
-		\infrule{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL} \\[2mm]
-		\infrule{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A}{\textsc{T-Gen}} \andalso
-		\infrule{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
-		\infrule{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}{\textsc{T-Csp}} \andalso
-		\caption{Typing Rules}
+		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
+		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
+		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
+		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
+		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
+		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
+		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
+		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
+		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
+		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
+		\caption{Typing Rules.}
 		\label{fig:typing-rules}
@@
 
-\subsubsection{Type Equivalence Rules}
-
-As mentioned above, type equivalence rules are needed in \LMD.
-We show the rules in Figure \ref{fig:type-equivalence-rules}.
+\subsubsection{Type and Term Equivalence}
+
+As usual in dependent type systems, type equivalence, used in \TConv,
+is important.  The type equivalence judgment of the form
+$\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
+are equivalent as types of kind $K$ at stage $A$ under $\G$.
+Figure~\ref{fig:type-equivalence-rules} shows the rules for type
+equivalence.  Type equivalence is basically the least congruence
+closed under term equivalence.  The ules for compatibility (closure
+under type formation) are derived from corresponding typing rules in a
+straightforward manner.  The rules are a little simpler than some
+dependent type systems \AI{such as?}  because there is no abstraction
+at the type level.
 
 % \QCsp以外の説明
-We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
-All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
-\QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
-The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
-the results of applications are also equivalent.
-A judgement of $\G \V M \E N : \rho @ A$ means that $M$ and $N$ are equivalent.
+% We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
+% All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
+% \QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
+% The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
+% the results of applications are also equivalent.
 
@@
 		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
-		\caption{Type Equivalence Rules}
+		\caption{Type Equivalence Rules.}
 		\label{fig:type-equivalence-rules}
@@
 \end{figure}
+
+The term equivalence judgment of the form $\G \V M \E N : \rho @ A$
+means that terms $M$ and $N$ are equivalent as terms of type $\rho$ at
+stage $A$ under $\G$.
+
+%%%%%%%%%%%%%%%%%%%%%%% RESUME FROM HERE %%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-06-12 main.tex
[WIP] Review existing comments.

@@
 
+\AI{Rename ``type variables'' to ``type-level constants''. }
 We assume the denumerable set of type variables, ranged over by
@@
 \end{align*}
+
+\AI{Add $M\,\alpha$ to terms.}
 
@@
 an $\alpha$-closed type $\F\alpha.\tau$.
-Therefore, $\F\alpha.\TW_{\alpha}.\Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha}.(\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
+Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
+$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
 
@@
 For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
+\AI{Change Int to Bool.}
 
@@
 \AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
+\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
 

### 2019-06-13 main.tex
Comments on term equivalence.

@@
 equivalence.  Type equivalence is basically the least congruence
-closed under term equivalence.  The ules for compatibility (closure
+closed under term equivalence.  The rules for compatibility (closure
 under type formation) are derived from corresponding typing rules in a
@@
 	\begin{center}
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs } \\[2mm]
-		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp } \\[2mm]
-		\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
-		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[2mm]
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \\[2mm]
-		\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
-		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \\[2mm]
-		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
+		\infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
+		\infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
+		\infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
+		\infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
+		\infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
+		\infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
+		\infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
+		\infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
 		\caption{Type Equivalence Rules.}
@@
 
-The term equivalence judgment of the form $\G \V M \E N : \rho @ A$
-means that terms $M$ and $N$ are equivalent as terms of type $\rho$ at
-stage $A$ under $\G$.
-
-%%%%%%%%%%%%%%%%%%%%%%% RESUME FROM HERE %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
-\QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns, \QCsp\ are generated directly from the syntax of a term.
-\QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.
-The rule \QBeta\ means when a term $M \longrightarrow_\beta M'$, $M$ is equivalent to $M'$.
-\QTBLTB and \QLambda\ are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.
+The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
+which means that terms $M$ and $N$ are equivalent as terms of type
+$\rho$ at stage $A$ under $\G$, is defined by the rules in
+Figure~\ref{fig:term-equivalence-rules}.  Most rules are
+straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
+\QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
+rules \QBeta, \QTBLTB, and \QLambda{} correspond to the reduction rules.
+\AI{Don't we give names to those reduction rules?}
 
@@
 	\begin{center}
-		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
-		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
-		\infrule{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A}{\QTB} \andalso
-		\infrule{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}}{\QTBL} \\[2mm]
-		\infrule{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A}{\QGen} \\[2mm]
-		\infrule{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
-		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp} \\[2mm]
-		\infrule{\G\V M:\tau @A}{\G\V M\E M : \tau @A}{\QRefl} \andalso
-		\infrule{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A}{\QSym} \\[2mm]
-		\infrule{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A}{\QTrans} \\[2mm]
-		\infrule{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
+		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
+		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
+		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
+		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
+		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
+		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
+		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
+		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
+		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
+		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
+		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
 		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
-		\infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
-		\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-		\caption{Term Equivalence Rules}
+		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
+		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
+		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
+		\caption{Term Equivalence Rules.}
 		\label{fig:term-equivalence-rules}
@@
 % \QPercentの説明
-The rule \QPercent is something special because it has no background of syntax or reductions.
-But we add this rule to \LMD\ because it is essential when you use dependent types in code type.
-For example, we can utilize a dependently typed multi-stage calculus to generate code for matrix multiplication.
-When we know sizes of matrices before the multiplication,
-we can generate efficient code for multiplication by unrolling loops.
-
+The only rule that deserves elaboration is the last rule \QPercent.
+Intuitively, it means that the CSP operator applied to term $M$ can be
+removed if $M$ is also well typed at the next stage \(A\alpha\).
+For example, constants do not depend on the stage (see \TConst) and
+so \(\G\V \%_\alpha c \E c : \tau @ A\alpha\) holds but variables
+do depend on stages and so this rule does not apply.
+
+Interestingly, Hanada and Igarashi~\cite{} rejected the idea of
+reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
+reduction does not match the operational behavior of the CSP operator
+in implementation.  However, as an equational system for multi-stage
+programs, the rule \QPercent makes sense and as we argue \AI{where?}
+it is practically significant.
+
+%%%%%%%%%%%%%%%%%%% SKIP FROM HERE %%%%%%%%%%%%%%%%%%%%
 $\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
@@
 because types of codes don't contain $\%_\alpha$ generally.
+
+%%%%%%%%%%%%%%%%%%% TO HERE %%%%%%%%%%%%%%%%%%%%
 

### 2019-06-13 main.tex
Add comments to the section on staged semantics.

@@
 
-The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
-But we need to fix order of reduction when we implement an interpreter of \LMD and
-the order must be appropriate in terms of stages.
-
-We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
-In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
-$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
+The reduction given above is full reduction and any redexes---even
+under quotation---can be reduced in an arbitrary order.  Following
+previous work~\cite{}, we introduce (small-step, call-by-value) staged
+semantics, where only redexes at stage $\varepsilon$\AI{not quite true
+  because of unquote--quote reduction} are reduced, modeling an
+implementation.
+
+We start with the definition of values.  Since terms under quotations are
+not executed, the grammar is indexed by stages.
 
 \begin{definition}[Values]
-	The family $V^A$ of sets of values, ranged over by $v^A$ and 
-	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
-	are defined by following grammar. In the grammar $A \neq \epsilon$.
+	The family $V^A$ of sets of values, ranged over by $v^A$,
+	is defined by following grammar.  In the grammar, $A \neq \epsilon$ is assumed.
 	\begin{align*}
-		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
-		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                          & \\
-		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
-		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
-		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
+		v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
+		v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
+		                         & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \epsilon)                          & \\
+                                          & \quad\   \mid\ \%_\alpha v^{A'} (\text{if } A = A'\alpha  \text{ for some } \alpha, A')
 	\end{align*}
@@
 
-Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
-The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
-This restriction means that the body of $Lambda$ abstraction must be evaluated before application of an $\epsilon$ stage.
-Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
-This is because $\TBL_\alpha v^\epsilon$ is a redex.
-
-\begin{definition}[Evaluation Context]
-	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
-	$A$ is nonempty. (Although $B,A'$ can be empty.)
-	$A \neq \epsilon$\\
+Values at $\epsilon$ stage are a $\lambda$-abstraction, a quoted code,
+or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
+be any term but the body of $\Lambda$-abstraction has to a value.  It
+means that the body of $\Lambda$-abstraction must be evaluated.  The
+side condition for $\TBL_\alpha v^{A'}$ means that escapes in a value
+can appear only under nested quotations (because an escape under a
+single quotation will splice the code value into the surrounding
+code).  See Hanada and Igarashi~\cite{} for details.
+
+\begin{definition}[Evaluation Context and Redex]
+  The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$,
+the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
+	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
 	\begin{align*}
@@
 		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
-	\end{align*}
+\\
+		 R^\epsilon  & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
+		 R^\alpha    & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\	\end{align*}
 \end{definition}
 
-We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.
+\AI{some more explanation of the syntax of evaluation contexts.}
+
+We write $E^A_B[M]$ for the term obtained by filling the hole in $E^A_B$ by $M$
+and define the staged reduction relation.
 
@@
 	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
-	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
-\end{definition}
-
-\begin{figure}
-	\begin{center}
+	the least relation closed under the rules below.
+% \begin{figure}
+% 	\begin{center}
 		\begin{align*}
@@
 		\end{align*}
-		\caption{Staged Reduction}
-		\label{fig:staged-reduction}
-	\end{center}
-\end{figure}
+     %    	\caption{Staged Reduction}
+     %    	\label{fig:staged-reduction}
+     %    \end{center}
+     % \end{figure}
+\end{definition}
 

### 2019-06-13 main.tex
[WIP] Revising Section 4.

@@
 
-In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
-unique decomposition of evaluation contexts, and progress.
-These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
+In this section, we prove \AI{use ``show'' because we omit proofs from the paper} basic properties of \LMD: preservation, strong normalization, confluence, and progress.
+These theorem shows that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
+\AI{In this setting, a simple type system is already sufficient to guarantee
+  ``a well-typed term never goes wrong.''  If the language has
+  case analysis that uses dependent types, then
+  we could say more.
+}
 
@@
 
+\AI{Since the order of variable declarations is significant,
+  we cannot assume $z$ is always declared at the end.}
+
 \begin{proof}
@@
 
-Following three Inversion Lemmas are needed in proving later theorems.
-Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
-They are composed of three part.
-The first part state that we can infer types of subterms.
+The following three Inversion Lemmas are needed to prove main theorems.
+As usual~\cite{TAPL}, Inversion Lemmas enable us to infer the types of subterms of a term from the type of the term.
+They are composed of three parts.
+The first part states that we can infer types of subterms.
 The second and third parts state 
 that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence.
-
-\begin{lemma}[Inversion Lemma for $\Pi$ type]
+We need both of the second and the third because of the reflexivity of the type equivalence. \AI{Symmetry?  We can omit the third one.}
+
+\begin{lemma}[Inversion Lemma for $\Pi$-types]
 	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
 	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau @A$
+		\item $\G \V \sigma \E \sigma'@A$ and
+		\item $\G ,x:\sigma@A\V M:\tau @A$.
 	\end{enumerate}
@@
 	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
+		\item $\rho = \Pi x:\sigma'.\tau'$,
+		\item $\G \V \sigma \E \sigma' : K @A$, and
+		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$.
 	\end{enumerate}
@@
 
-\begin{theorem}[Inversion Lemma for $\TW$ type]
+\begin{theorem}[Inversion Lemma for $\TW$-types]
 	\begin{item}
@@
 	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
+		      \item $\rho = \TW_\alpha \tau'$ and
+		      \item $\G @A\V \tau \E \tau' : K @A$.
 	      \end{enumerate}
@@
 
-\begin{theorem}[Inversion Lemma for $\Lambda$ type]
+\begin{theorem}[Inversion Lemma for $\forall$-types]
 	\begin{item}
@@
 	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
+		      \item $\rho = \forall\alpha.\tau'$ and
+		      \item $\G \V \tau \E \tau' : K @A$.
 	      \end{enumerate}
@@
 
-Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
-Preservation ensure that any one step reduction preserves type.
+Thanks to Substitution Lemmas and Inversion Lemmas, we can prove Preservation easily.
+Preservations ensure that any one step reduction preserves type.
 
 \begin{theorem}[Preservation]
-	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
+	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$.
 \end{theorem}
@@
 	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
-	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
+	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$.
 \end{theorem}
@@
 \begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
+	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then either
 	\begin{enumerate}
-		\item $ M \in V^A$
-		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
+		\item $ M \in V^A$, or
+		\item there exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$ with $B = \epsilon$ or $B = \beta$ for some $\beta$.
 	\end{enumerate}
@@
 
-\section{Related Works}
+\AI{Explain the condition on $\G$.}
+
+\section{Related Work}
 

### 2019-06-14 conclusions.tex
Split main.tex.

--- 2019-06-13 main.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\newif\ifnotanonymous \notanonymousfalse
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bcprules, proof}
-\usepackage{fancybox}
-\usepackage{mathtools}
-\usepackage{float}
-\usepackage{xparse}
-\usepackage{lscape}
-\usepackage{mdframed}
-\usepackage{xspace}
-
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\newcommand{\red}[1]{\textcolor{red}{#1 }}
-\newcommand{\blue}[1]{\textcolor{blue}{#1 }}
-
-\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
-\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
-\newcommand{\LLF}{$\lambda\textrm{LF}$\xspace}
-
-\newcommand{\G}{\Gamma}
-\newcommand{\D}{\Delta}
-\newcommand{\V}{\vdash_\Sigma}
-\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
-\newcommand{\iskind}{\text{\ kind}}
-\newcommand{\TW}{{\mathop{\triangleright}}}
-\newcommand{\TWL}{{\mathop{\triangleleft}}}
-\newcommand{\F}{\forall}
-\newcommand{\TB}{{\mathop{\blacktriangleright}}}
-\newcommand{\TBL}{{\mathop{\blacktriangleleft}}}
-\newcommand{\E}{\equiv}
-\newcommand{\FV}{\text{FV}}
-\newcommand{\FTV}{\text{FSV}}
-
-\newcommand{\WStar}{\textsc{W-Star}}
-\newcommand{\WAbs}{\textsc{W-Abs}}
-\newcommand{\WCsp}{\textsc{W-Csp}}
-\newcommand{\WApp}{\textsc{W-App}}
-\newcommand{\WTW}{\textsc{W-$\TW$}}
-
-\newcommand{\KVar}{\textsc{K-Var}}
-\newcommand{\KAbs}{\textsc{K-Abs}}
-\newcommand{\KApp}{\textsc{K-App}}
-\newcommand{\KConv}{\textsc{K-Conv}}
-\newcommand{\KTW}{\textsc{K-$\TW$}}
-\newcommand{\KTWL}{\textsc{K-$\TWL$}}
-\newcommand{\KGen}{\textsc{K-Gen}}
-\newcommand{\KCsp}{\textsc{K-Csp}}
-
-\newcommand{\TConst}{\textsc{T-Const}}
-\newcommand{\TVar}{\textsc{T-Var}}
-\newcommand{\TAbs}{\textsc{T-Abs}}
-\newcommand{\TApp}{\textsc{T-App}}
-\newcommand{\TConv}{\textsc{T-Conv}}
-\newcommand{\TTB}{\textsc{T-$\TB$}}
-\newcommand{\TTBL}{\textsc{T-$\TBL$}}
-\newcommand{\TGen}{\textsc{T-Gen}}
-\newcommand{\TIns}{\textsc{T-Ins}}
-\newcommand{\TCsp}{\textsc{T-Csp}}
-
-\newcommand{\QKAbs}{\textsc{QK-Abs}}
-\newcommand{\QKCsp}{\textsc{QK-Csp}}
-\newcommand{\QKRefl}{\textsc{QK-Refl}}
-\newcommand{\QKSym}{\textsc{QK-Sym}}
-\newcommand{\QKTrans}{\textsc{QK-Trans}}
-
-\newcommand{\QTAbs}{\textsc{QT-Abs}}
-\newcommand{\QTApp}{\textsc{QT-App}}
-\newcommand{\QTTW}{\textsc{QT-$\TW$}}
-\newcommand{\QTGen}{\textsc{QT-Gen}}
-\newcommand{\QTCsp}{\textsc{QT-Csp}}
-\newcommand{\QTRefl}{\textsc{QT-Refl}}
-\newcommand{\QTSym}{\textsc{QT-Sym}}
-\newcommand{\QTTrans}{\textsc{QT-Trans}}
-
-\newcommand{\QAbs}{\textsc{Q-Abs}}
-\newcommand{\QApp}{\textsc{Q-App}}
-\newcommand{\QTB}{\textsc{Q-$\TB$}}
-\newcommand{\QTBL}{\textsc{Q-$\TBL$}}
-\newcommand{\QGen}{\textsc{Q-Gen}}
-\newcommand{\QIns}{\textsc{Q-Ins}}
-\newcommand{\QCsp}{\textsc{Q-Csp}}
-\newcommand{\QRefl}{\textsc{Q-Refl}}
-\newcommand{\QSym}{\textsc{Q-Sym}}
-\newcommand{\QTrans}{\textsc{Q-Trans}}
-\newcommand{\QBeta}{\textsc{Q-$\beta$}}
-\newcommand{\QEta}{\textsc{Q-$\eta$}}
-\newcommand{\QTBLTB}{\textsc{Q-$\TBL\TB$}}
-\newcommand{\QLambda}{\textsc{Q-$\Lambda$}}
-\newcommand{\QPercent}{\textsc{Q-\%}}
-
-\newcommand{\ID}[1]{\infer[]{#1}{\vdots}}
-\newcommand{\MD}[1]{\mathcal{D}_#1}
-
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\B}{\textrm{Bool}}
-\newcommand{\M}{\textrm{Mat}}
-
-\newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}
-
-\begin{document}
-%
-\title{A Dependently Typed Multi-Stage Calculus%
-	\ifnotanonymous\thanks{Supported by organization x.}\fi
-}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\ifnotanonymous
-	\author{Akira Kawata\inst{1} \and
-		Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
-	% %
-	\authorrunning{A. Kawata, A. Igarashi}
-	% % First names are abbreviated in the running head.
-	% % If there are more than two authors, 'et al.' is used.
-	% %
-	\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
-		\email{akira@fos.kuis.kyoto-u.ac.jp} \and
-		\email{igarashi@kuis.kyoto-u.ac.jp}
-	}
-\fi
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-
-	We study a dependently typed extension of a multi-stage programming
-	language \`a la MetaOCaml, which supports quasi-quotation and
-	cross-stage persistence for manipulation of code fragments as
-	first-class values and eval for execution of programs dynamically
-	generated by the code manipulation.  Dependent types are expected to
-	bring to multi-stage programming enforcement of strong
-	invariants---beyond simple type safety---on the behavior of
-	dynamically generated code.  An extension is, however, not trivial
-	because a type system would have to take stages---roughly speaking,
-	the number of surrounding quotations---of types into account.
-
-	To rigorously study properties of such an extension, we develop
-	\LMD, which is an extension of Hanada and Igarashi's typed calculus
-	\LTP with dependent types, and prove its properties including
-	preservation, confluence, strong normalization for full
-	reduction, and progress for staged reduction.  Motivated
-	by code generators such that the type of generated code depends on a
-	value from outside of quotations, we argue the significance of
-	cross-stage persistence in dependently typed multi-stage programming
-	and certain type equivalence that are not directly derived from
-	reduction rules.
-
-	% A multi-stage calculus enables us to generate and execute codes at runtime.
-	% It can improve the performance of programs by generating optimized codes for given inputs.
-	% Dependent types are types dependent on values. 
-	% A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
-	% In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
-	% You can make more efficient programs from existing dependent typed programs with \LMD.
-	% \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
-	% It also includes an evaluation context which satisfies unique decomposition.
-	% The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-	% Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
-	% In this paper, we give reasonable equivalence rules to handle them.
-
-	\keywords{multi-stage programming, cross-stage persistence, dependent types}
-\end{abstract}
-
-\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
-\blue{コードとかはボールドを使ったほうが良いかもしれない。}
-\red{Suspicious senetences are colored red.}
-%
-%
-%
-\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}
-
-\section{Introduction}
-
-\subsection{Multi-stage Programming}
-
-% \subsubsection{多段階計算とは何か?}
-
-Multi-stage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multi-stage programming, which are brackets, escape, and run.
-Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
-Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Escape, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, escape is supposed to use in a fragment of code, that is, escape cannot be used as an alternative of run.
-For example, the following MetaOCaml expression
-
-\begin{verbatim}
-        let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
-\end{verbatim}
-evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
-\begin{verbatim}
-        run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
-\end{verbatim}
-is reduced to 3.
-
-% \subsubsection{CSPに関する補足説明}
-
-Cross-stage Persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
-This is an example of CSP.
-\begin{verbatim}
-        let plusone = fun x -> x + 1 in
-        let y = plusone 2 in  .< y >.
-\end{verbatim}
-This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
-This is because the variable \verb|y| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|y| is embedded after it was calculated.
-CSP is very important when we write practical programs 
-because CSP enables us to use library functions in code fragments as in \verb|.<List.combine [1;2] ['a';'b']>.|.
-
-% \subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
-
-The main application of multi-stage calculi is program optimization.
-A famous example is power functions.
-Usual power functions take two arguments, which are the base and the exponent.
-We can make a specialized power function for given exponents with multi-stage programming and 
-optimize them by unrolling a loop in functions for given exponents.
-The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
-\verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
-Multi-stage programming can optimize functions which take more than two arguments 
-by generating a code fragment optimized to a given argument.
-
-% \subsubsection{ベクトル計算も高速化できる}
-
-Multi-stage programming can also optimize vector calculation.
-For example, \verb|vadd| function, which takes two vectors and return the sum of them,
-is implemented with a loop in many cases.
-We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
-\red{MetaOCamlで書いた長さ付きベクトルの例?}
-
-% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
-
-However, there is a sever problem in functions which are optimized by multi-stage programming.
-Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
-For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
-Otherwise, we will get a Segmentation Fault error.
-This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
-
-% We call this problem \red{Specialized Code Problem}.
-
-\subsection{Dependent Types}
-
-% \subsubsection{依存型とは何か?}
-
-Dependent types are types which is dependent on values.
-We can use dependent types for securer programming.
-For example, we can realize vectors with their sizes with them.
-\begin{verbatim}
-        Vector :: Int -> *
-\end{verbatim}
-\verb|Vector| is a type constor which takes the length of vectors, that is, 
-\verb|Vector 3| is a type for vectors whose lengths are 3.
-If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n|,
-we can confirm the two arguments of \verb|vadd| function has the same length.
-\red{secure programming? finer grained typing? とか}
-
-\subsection{Multi-stage Programming with Dependent Types}
-\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
-
-% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
-
-As we pointed out in the above section,
-functions optimized with multi-stage programming can take only restricted values as arguments.
-When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
-We introduce dependent types into a multi-stage calculus
-so that the type system can guarantee optimized functions are used properly.
-
-In this paper, we design new multi-stage calculus \LMD by 
-merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
-\LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming more safer with the power of dependent types.
-
-\subsection{Organization of the Paper}
-
-The organization of this paper is the following.
-Section 2 gives an informal overview of \LMD.
-Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
-Section 4 shows the properties of \LMD including Unique Decomposition.
-Section 5 discusses future works.
-Finally, Section 6 discusses related works.
-\AI{Use $\backslash$label and $\backslash$ref!}
-\AI{``Related work'' and ``future work'' (they are uncountable).}
-
-\section{Informal Overview of \LMD}
-
-We designed \LMD, a multi-stage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP and
-we introduced dependent types based on \LTP\cite{attapl}.
-In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
-
-\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
-\subsection{\LTP}
-
-% quote and unquote
-
-\LTP\cite{Hanada2014} is a multi-stage calculus with CSP by Hanada and Igarashi.
-In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
-The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
-The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
-% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
-\begin{align*}
-	\TBL_\alpha (\TB_\alpha M) \longrightarrow M 
-\end{align*}
-It means escape cancels brackets.
-% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
-% \red{この文はここに来るべきなのか? LTPの説明ではないが}
-
-% transition variable and transition
-
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
-a sequence of transition variables is called \textit{transition}.
-The empty transition is represented by $\epsilon$.
-They are used to show the thickness of brackets.
-For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
-becomes $(\lambda x:\I.x+10)$ after it was run it twice.
-\red{run twiceは表現が微妙}
-
-% transition abstraction and application
-
-There are abstractions for transition variables and applications for transition abstraction in \LTP.
-They look like $\Lambda\alpha.M$ and $M A$, respectively.
-A transition abstraction binds a transition variable in a term.
-For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural there is a reduction rule for transition application in \LTP.
-The rule is the following.
-\begin{align*}
-	(\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
-\end{align*}
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
-
-% transition-related symbols disappear when the empty transition is substituted.
-% In short, about "run"
-
-Another important rule about a transition variable is 
-that symbols with transition variables disappear 
-when the empty transition $\epsilon$ is substituted to the transition variable.
-The purpose of this rule is express \verb|run| without any special symbol.
-In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
-For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.
-
-% transition in typing rules
-
-A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-A transition in a judgement represents where the judgement is true.
-For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
-term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
-Especially, terms without quoting exist at the empty transition $\epsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
-$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
-Terefore, transitions appear in typing rules, too.
-\begin{center}
-	\infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
-	\infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
-\end{center}
-\TTB, corresponding to brackets, means 
-if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
-\TTBL\ is converse of \TTB.
-
-% CSP
-
-CSP, cross-stage persistence, is an important feature of \LTP.
-It enables us to embed value at an outer transition into an inner transition.
-$\%$ is dedicated to CSP in \LTP.
-For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
-\red{inner / outer は適切か?}
-
-% Omitting Residualization
-% この段落は3章のM eのあとに、この制限の結果として...という形で入れる
-
-% There is another important feature called program residualization in \LTP.
-% It means that a generated code can be dumped into a file.
-% We can load the dumped file and run it.
-% The difficulty arises when program residualization is used with CSP.
-% Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
-
-\subsection{\LLF}
-
-% \LLF
-\LLF is a simple system of dependent types introduced in \cite{attapl}.
-\red{system / type system / calculus?}
-It is based on Edinburgh LF\cite{harper1993framework}.
-Therefore, all constants and base types are declared in the signature.
-The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.
-
-% Kind, Well-formed kind
-In addition to ordinary typing rules like simply typed lambda calculus,
-there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
-Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
-For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
-for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
-
-% Type Equality
-Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
-For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
-but they are not equivalent seemingly. Thus, we must define equivalence rules.
-In \LLF, equivalence is expressed with a symbol of $\E$.
-$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
-$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
-$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
-
-\subsection{Extending \LTP with Dependent Types}
-
-Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-From here, we use the word "stage" instead of "transition" 
-because we develop a multi-stage calculus, not a multi-transition calculus.
-\red{stageのほうが言葉としてふさわしいと言いたい}
-There are three technical points in the extension from \LTP to \LMD.
-
-\red{以下の3文をどこかに入れる必要がある}
-\red{, which is called a \textit{stage variable} in \LMD.}
-\red{ which is called a stage in \LMD.}
-\red{Although we can apply any transition to a transition abstraction in \LTP,
-	we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
-
-% Constants and Base Types
-
-First, the way of handling of constants and base types is the difference between \LMD and \LTP.
-We adopt a signature $\Sigma$ to handle constants and base types.
-This is because a signature simplifies kinding rules relating to type variables.
-A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
-For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
-\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}
-
-% Kidinding and Well-formed Kinding Rules
-
-Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
-It was lucky that almost all rules are determined easily.
-This is because multi-stage calculus and dependent types are almost orthogonal.
-\red{orthogonal は抽象的すぎるか?}
-Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
-attaching stage anotations to ones of \LLF.
-For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
-\begin{center}
-	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
-	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
-\end{center}
-
-% Equivalence Rules
-
-Third, we also need type equivalence rules in \LMD as a dependent type system.
-Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily.
-\red{design?}
-\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
-
-% Q-% rule
-
-The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
-The equivalence simple rule to handle CSP is \QCsp.
-\begin{center}
-	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
-\end{center}
-However, this rule isn't enough when the parameters of dependent types are cross-staed.
-We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
-\begin{center}
-	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-\end{center}
-\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
-
-\section{Formal Definition of \LMD}
-
-In this section, we give a formal definition of \LMD, including
-the syntax, full reduction, and type system.  In addition to full reduction,
-in which any redex at any stage can be reduced, we also give staged reduction,
-which models execution as programs.
-
-\subsection{Syntax}
-
-\AI{Rename ``type variables'' to ``type-level constants''. }
-We assume the denumerable set of type variables, ranged over by
-metavariables \(X, Y, Z\), the denumerable set of variables, ranged
-over by \(x,y,z\), the denumerable set of constants, ranged over by
-\(c\), and the denumerable set of stage variables, ranged over by
-\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
-sequences of stage variables; we write \(\varepsilon\) for the empty
-sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:
-
-\AI{``Transition'' is still used.}
-
-\begin{align*}
-    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
-    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
-    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
-    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
-    \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
-    \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
-%     \textrm{Constants}       &   &                          & c                                                                                                          \\
-    \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
-                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
-    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
-    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
-\end{align*}
-
-\AI{Add $M\,\alpha$ to terms.}
-
-\AI{Is $O$ used as a metavariable?}
-\AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
-
-% Description on meta variables
-
-% Kinds
-
-A kind, which is used to classify types, is either $*$, the kind of
-proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
-of type operators that takes $x$ as an argument of type $\tau$ and returns a type
-of kind $K$.
-% Types
-% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
-% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
-% \red{この段落は短いので型の段落と結合するか?}
-% Types
-A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
-$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
-An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
-if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
-A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
-An $\alpha$-closed type corresponds to a runnable code fragment.
-Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
-an application of a term to a dependent function type $\tau\ M$,
-a code type $\TW_{\alpha} \tau$,
-a dependent function type $\Pi x:\tau.\tau$, 
-an $\alpha$-closed type $\F\alpha.\tau$.
-Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
-
-% Terms
-
-Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
-whose type is declared in signature $\Sigma$, and the following five forms
-related to multi-stage programming:
-$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
-$\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
-$\%_\alpha M$ is an operator for cross-stage persistence.
-The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
-and applications are left-associative
-and two abstractions extends as far to the right as possible.
-For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
-
-% Signature
-
-We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
-are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
-\AI{Change Int to Bool.}
-
-% Free variables
-As usual, the variable $x$ is bound in $\lambda x:\tau.M$
-and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
-\AI{What about other binders such as $\Pi$?}
-We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
-We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
-
-% Contexts
-Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
-$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
-\AI{I'd prefer \textit{dom}.}
-The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
-$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.
-
-\AI{We should note that constants and type variables are not staged.}
-\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
-
-\subsection{Reduction}
-
-Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define two kinds of substitutions.
-Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
-$N$ for $x$ in $M$, and we omit its definition here.
-Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
-for stage variable $\alpha$ in $M$ is defined below.
-\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}
-
-\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
-\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
-
-\begin{align*}
-	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
-	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
-	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
-	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
-\end{align*}
-
-\begin{definition}[Reduction]
-  \AI{It's not clear what are defined here.  You are talking only about rules.
-    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
-	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
-	Congruence rules which are omitted from the definition.
-	\begin{align*}
-		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                       \\
-		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
-		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
-		 & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
-	\end{align*}
-	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
-\end{definition}
-
-The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
-$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
-where $\epsilon$ is substituted for the stage variable.
-Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
-There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
-% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
-
-\AI{A few examples are desirable.}
-
-\subsection{Type System}
-
-% 総論
-
-In this section, we define the type system of \LMD.
-% \LMD is little complicated because it contains dependent types.
-It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
-We list the judgments forms in Figure~\ref{fig:LMD-six-judgements}.
-\AI{equality vs. equivalence?}
-\AI{A few judgment forms do not match rules.}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			\G & \V M : \tau @ A   & \text{typing} \\
-			\G & \V \tau :: K @ A  & \text{kinding} \\
-			\G & \V K \iskind @ A  & \text{well-formed kinding} \\
-			\G & \V M \E N @ A     & \text{term equality} \\
-			\G & \V \tau \E \sigma & \text{type equality} \\
-			\G & \V K \E J @ A     & \text{kind equality}
-		\end{align*}
-		\caption{Six judgment forms of the type system of \LMD.}
-		\label{fig:LMD-six-judgements}
-	\end{center}
-\end{figure}
-
-\AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
-\begin{definition}[Typing]
-  The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
-  \AI{Precisely speaking, it cannot be defined independently of other judgments.
-  How is dependency between judgments?}
-\end{definition}
-
-\AI{``judgment'' vs. ``judgement''.}  We start from defining typing of
-\LMD.  Typing rules of \LMD are shown in Figure
-\ref{fig:typing-rules}.  The rule \TConst{} means any constants in the
-signature can appear at any stage.  \AI{This should be discussed
-  earlier.}  For example, if we have a signature $\Sigma$ which is
-$\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
-\textrm{bool}$, the derivation tree in
-Figure~\ref{fig:tconst-derivation-tree} is admissible.  \AI{Don't we
-  need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$
-  should be a well-formed type under ... what?}  The rules \TVar,
-\TAbs, and \TApp{} are almost the same as those in the simply typed
-lambda calculus.  \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}  Additional conditions are that subterms must be
-typed at the same stage (\TAbs{} and \TApp); the type
-annotation/declaration on a variable has to be a proper type of kind
-$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
-
-\begin{figure}
-	\begin{center}
-		\begin{minipage}{0.50\hsize}
-			\infer[\TConst]
-			{\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
-			{\textrm{true}:\textrm{bool} \in \Sigma \andalso
-				\ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
-			}
-			\caption{A derivation tree using \TConst}
-			\label{fig:tconst-derivation-tree}
-		\end{minipage}
-	\end{center}
-\end{figure}
-
-% \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is opposite.}
-As in standard dependent type systems, \TConv{} allows us to replace
-the type of a term with an equivalent one.  
-In a type system which includes dependent types, this kind of rule is essential
-because two types which have different shapes may be equivalent.
-For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
-
-% Typing rules for a multi-stage calculus
-\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-They are corresponding to brackets, escape, making a stage abstraction, 
-application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
-Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
-
-\begin{figure}
-	\begin{center}
-		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
-		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
-		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
-		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
-		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
-		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
-		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
-		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
-		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
-		\caption{Typing Rules.}
-		\label{fig:typing-rules}
-	\end{center}
-\end{figure}
-
-\subsubsection{Type and Term Equivalence}
-
-As usual in dependent type systems, type equivalence, used in \TConv,
-is important.  The type equivalence judgment of the form
-$\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
-are equivalent as types of kind $K$ at stage $A$ under $\G$.
-Figure~\ref{fig:type-equivalence-rules} shows the rules for type
-equivalence.  Type equivalence is basically the least congruence
-closed under term equivalence.  The rules for compatibility (closure
-under type formation) are derived from corresponding typing rules in a
-straightforward manner.  The rules are a little simpler than some
-dependent type systems \AI{such as?}  because there is no abstraction
-at the type level.
-
-% \QCsp以外の説明
-% We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
-% All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
-% \QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
-% The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
-% the results of applications are also equivalent.
-
-\begin{figure}
-	\begin{center}
-		\infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
-		\infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
-		\infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
-		\infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
-		\infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
-		\infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
-		\infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
-		\infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
-		\caption{Type Equivalence Rules.}
-		\label{fig:type-equivalence-rules}
-	\end{center}
-\end{figure}
-
-The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
-which means that terms $M$ and $N$ are equivalent as terms of type
-$\rho$ at stage $A$ under $\G$, is defined by the rules in
-Figure~\ref{fig:term-equivalence-rules}.  Most rules are
-straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
-\QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
-rules \QBeta, \QTBLTB, and \QLambda{} correspond to the reduction rules.
-\AI{Don't we give names to those reduction rules?}
-
-\begin{figure}
-	\begin{center}
-		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
-		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
-		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
-		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
-		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
-		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
-		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
-		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
-		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
-		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
-		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
-		\caption{Term Equivalence Rules.}
-		\label{fig:term-equivalence-rules}
-	\end{center}
-\end{figure}
-
-% \QPercentの説明
-The only rule that deserves elaboration is the last rule \QPercent.
-Intuitively, it means that the CSP operator applied to term $M$ can be
-removed if $M$ is also well typed at the next stage \(A\alpha\).
-For example, constants do not depend on the stage (see \TConst) and
-so \(\G\V \%_\alpha c \E c : \tau @ A\alpha\) holds but variables
-do depend on stages and so this rule does not apply.
-
-Interestingly, Hanada and Igarashi~\cite{} rejected the idea of
-reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
-in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and as we argue \AI{where?}
-it is practically significant.
-
-%%%%%%%%%%%%%%%%%%% SKIP FROM HERE %%%%%%%%%%%%%%%%%%%%
-$\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
-$\text{mulmat}$ takes two integers which are the size of the multiplicand matrix and generate a code.
-The last integer to decide the size of the multiplier matrix is given at runtime.
-You can generate code by applying two integers to $\text{mulmat}$.
-We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
-But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under a condition which is explained in the next paragraph.
-
-The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
-For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
-In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
-
-	% Example of QCsp (mulmat)
-	{
-		\begin{align*}
-			\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-			\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-			                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-		\end{align*}
-	}
-
-This kind of type equality is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
-We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
-because types of codes don't contain $\%_\alpha$ generally.
-
-%%%%%%%%%%%%%%%%%%% TO HERE %%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Staged Semantics}
-
-The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
-But we need to fix order of reduction when we implement an interpreter of \LMD and
-the order must be appropriate in terms of stages.
-
-We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
-In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
-$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
-
-\begin{definition}[Values]
-	The family $V^A$ of sets of values, ranged over by $v^A$ and 
-	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
-	are defined by following grammar. In the grammar $A \neq \epsilon$.
-	\begin{align*}
-		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
-		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                          & \\
-		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
-		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
-		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
-	\end{align*}
-\end{definition}
-
-Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
-The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
-This restriction means that the body of $Lambda$ abstraction must be evaluated before application of an $\epsilon$ stage.
-Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
-This is because $\TBL_\alpha v^\epsilon$ is a redex.
-
-\begin{definition}[Evaluation Context]
-	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
-	$A$ is nonempty. (Although $B,A'$ can be empty.)
-	$A \neq \epsilon$\\
-	\begin{align*}
-		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B     
-		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
-		\mid E^\epsilon_B\ \epsilon                                                                                                 \\
-		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
-		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
-		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
-		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B                                                   
-		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
-	\end{align*}
-\end{definition}
-
-We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.
-
-\begin{definition}[Staged Reduction]
-	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
-	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
-\end{definition}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
-			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
-			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
-		\end{align*}
-		\caption{Staged Reduction}
-		\label{fig:staged-reduction}
-	\end{center}
-\end{figure}
-
-\section{Properties of \LMD}
-
-In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
-unique decomposition of evaluation contexts, and progress.
-These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
-
-% Substitution Lemma
-
-Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
-because there are six types of judgment and two types of substitution in \LMD.
-Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
-typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
-
-\begin{lemma}[Substitution Lemma on Terms]
-	\begin{flalign*}
-		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
-	\end{flalign*}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Substitution Lemma on Stages]
-	\begin{flalign*}
-		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
-	\end{flalign*}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Inversion Lemma
-
-Following three Inversion Lemmas are needed in proving later theorems.
-Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
-They are composed of three part.
-The first part state that we can infer types of subterms.
-The second and third parts state 
-that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence.
-
-\begin{lemma}[Inversion Lemma for $\Pi$ type]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
-	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau @A$
-	\end{enumerate}
-	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\TW$ type]
-	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\Lambda$ type]
-	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Preservation
-
-Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
-Preservation ensure that any one step reduction preserves type.
-
-\begin{theorem}[Preservation]
-	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
-\end{theorem}
-
-\begin{proof}
-	First, there are three cases for $M \longrightarrow M'$.
-	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-% Strong Normalization
-
-Strong Normalization is also important property which guarantee that
-no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus.
-
-\begin{theorem}[Strong Normalization]
-	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
-	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
-\end{theorem}
-
-\begin{proof}
-	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
-	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
-\end{proof}
-
-Confluence is a property that any reduction sequences from one typed term converge.
-Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
-
-\begin{theorem}[Confluence]
-	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
-	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
-\end{theorem}
-
-\begin{proof}
-	Because we proved Strong Normalization of \LMD, 
-	we can use Newman's lemma to prove Confluence of \LMD.
-	Then, what we must show is Weak Church-Rosser Property now.
-	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
-	In short, they are never overlapped each other.
-	So, we can reduce one of them after we reduce another.
-\end{proof}
-
-Unique Decomposition ensure that
-,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it guarantee
-that the evaluation context decides a redex to reduce deterministically.
-Specifically speaking, this theorem guarantee that 
-when you write a interpreter using the evaluation context of \LMD,
-your interpreter works just as intended.
-
-\begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
-	\begin{enumerate}
-		\item $ M \in V^A$
-		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
-	\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
-Thanks to Unique Decomposition, we can prove this theorem easily.
-
-\begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-\section{Related Works}
-
-% 依存型の歴史
-
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
-
-% 依存型の応用
-
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
-
-% 多段階計算の歴史
-
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
-However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
-construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
-
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\epsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump the quoted code into an external file.
-
-% 他段階計算の機能拡張
-
-Combination of multi-stage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
-
-% 多段階計算の応用
-
-MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
-Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
-which include filtering in signal processing, matrix-vector product, and DSL compiler.
-
-% \begin{enumerate}
-% 	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
-
-% 	      CSPも入りました
-% 	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-% 	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-% 	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-% 	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
-% 	\item Done: Environment classifiers\cite{taha2003environment}
-% 	\item Done: A framework for defining logics\cite{harper1993framework}
-
-% 	      $\Sigma$ の使い方を確認した
-% 	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-% 	\item Done: Dependent types in practical programming\cite{xi1999dependent}
-
-% 	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-% 	\item Done: A dependently typed assembly language\cite{xi2001dependently}
-
-% 	      DTALの定義と制約solverを用いた型検査の定義
-% 	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
-% 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-% 	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
-% 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
-% 	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-% 	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
-% 	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
-% 	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
-% 	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
-% 	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
-% 	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-% \end{enumerate}
-
 \section{Conclusions}
@@
 because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
-
-% 2つの設計手法と今回採用した理由
-% Conclusion送りか?
-% When we design type equivalence rules of \LMD, there are two design choices.
-% One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-% Another is defining type equivalence directly by a combination of type equivalence rules.
-% We adopt the latter one because it is convenient to handle CSP in the type equivalence.
-
-% \section{First Section}
-% \subsection{A Subsection Sample}
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc. does not need an indent, either.
-% 
-% Subsequent paragraphs, however, are indented.
-% 
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-% 
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-% 
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-% 
-% 
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-% 
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-% 
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-% %
-% % the environments 'definition', 'lemma', 'proposition', 'corollary',
-% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
-% %
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\bibliographystyle{splncs04}
-\bibliography{main}
-%
-% \begin{thebibliography}{8}
-% \bibitem{ref_article1}
-% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-% 
-% \bibitem{ref_lncs1}
-% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-% 
-% \bibitem{ref_book1}
-% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-% Location (1999)
-% 
-% \bibitem{ref_proc1}
-% Author, A.-B.: Contribution title. In: 9th International Proceedings
-% on Proceedings, pp. 1--2. Publisher, Location (2010)
-% 
-% \bibitem{ref_url1}
-% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-% Oct 2017
-% \end{thebibliography}
-
-\section{Appendix}
-
-\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
-Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures.
-This category encompasses both theoretical and implementation (also known as system descriptions) papers.
-In either case, submissions should clearly identify what has been accomplished and why it is significant.
-Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity.
-System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design.
-In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
-\blue{Review Process
-	APLAS 2019 will use a lightweight double-blind reviewing process.
-Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper.
-The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
-	To facilitate this process, submitted papers must adhere to the following:
-	Author names and institutions must be omitted and
-	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
-	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
-Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas.
-For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure.
-Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would.
-For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
-\end{document}

### 2019-06-14 formal-defnition.tex
Split main.tex.

--- 2019-06-13 main.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\newif\ifnotanonymous \notanonymousfalse
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bcprules, proof}
-\usepackage{fancybox}
-\usepackage{mathtools}
-\usepackage{float}
-\usepackage{xparse}
-\usepackage{lscape}
-\usepackage{mdframed}
-\usepackage{xspace}
-
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\newcommand{\red}[1]{\textcolor{red}{#1 }}
-\newcommand{\blue}[1]{\textcolor{blue}{#1 }}
-
-\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
-\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
-\newcommand{\LLF}{$\lambda\textrm{LF}$\xspace}
-
-\newcommand{\G}{\Gamma}
-\newcommand{\D}{\Delta}
-\newcommand{\V}{\vdash_\Sigma}
-\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
-\newcommand{\iskind}{\text{\ kind}}
-\newcommand{\TW}{{\mathop{\triangleright}}}
-\newcommand{\TWL}{{\mathop{\triangleleft}}}
-\newcommand{\F}{\forall}
-\newcommand{\TB}{{\mathop{\blacktriangleright}}}
-\newcommand{\TBL}{{\mathop{\blacktriangleleft}}}
-\newcommand{\E}{\equiv}
-\newcommand{\FV}{\text{FV}}
-\newcommand{\FTV}{\text{FSV}}
-
-\newcommand{\WStar}{\textsc{W-Star}}
-\newcommand{\WAbs}{\textsc{W-Abs}}
-\newcommand{\WCsp}{\textsc{W-Csp}}
-\newcommand{\WApp}{\textsc{W-App}}
-\newcommand{\WTW}{\textsc{W-$\TW$}}
-
-\newcommand{\KVar}{\textsc{K-Var}}
-\newcommand{\KAbs}{\textsc{K-Abs}}
-\newcommand{\KApp}{\textsc{K-App}}
-\newcommand{\KConv}{\textsc{K-Conv}}
-\newcommand{\KTW}{\textsc{K-$\TW$}}
-\newcommand{\KTWL}{\textsc{K-$\TWL$}}
-\newcommand{\KGen}{\textsc{K-Gen}}
-\newcommand{\KCsp}{\textsc{K-Csp}}
-
-\newcommand{\TConst}{\textsc{T-Const}}
-\newcommand{\TVar}{\textsc{T-Var}}
-\newcommand{\TAbs}{\textsc{T-Abs}}
-\newcommand{\TApp}{\textsc{T-App}}
-\newcommand{\TConv}{\textsc{T-Conv}}
-\newcommand{\TTB}{\textsc{T-$\TB$}}
-\newcommand{\TTBL}{\textsc{T-$\TBL$}}
-\newcommand{\TGen}{\textsc{T-Gen}}
-\newcommand{\TIns}{\textsc{T-Ins}}
-\newcommand{\TCsp}{\textsc{T-Csp}}
-
-\newcommand{\QKAbs}{\textsc{QK-Abs}}
-\newcommand{\QKCsp}{\textsc{QK-Csp}}
-\newcommand{\QKRefl}{\textsc{QK-Refl}}
-\newcommand{\QKSym}{\textsc{QK-Sym}}
-\newcommand{\QKTrans}{\textsc{QK-Trans}}
-
-\newcommand{\QTAbs}{\textsc{QT-Abs}}
-\newcommand{\QTApp}{\textsc{QT-App}}
-\newcommand{\QTTW}{\textsc{QT-$\TW$}}
-\newcommand{\QTGen}{\textsc{QT-Gen}}
-\newcommand{\QTCsp}{\textsc{QT-Csp}}
-\newcommand{\QTRefl}{\textsc{QT-Refl}}
-\newcommand{\QTSym}{\textsc{QT-Sym}}
-\newcommand{\QTTrans}{\textsc{QT-Trans}}
-
-\newcommand{\QAbs}{\textsc{Q-Abs}}
-\newcommand{\QApp}{\textsc{Q-App}}
-\newcommand{\QTB}{\textsc{Q-$\TB$}}
-\newcommand{\QTBL}{\textsc{Q-$\TBL$}}
-\newcommand{\QGen}{\textsc{Q-Gen}}
-\newcommand{\QIns}{\textsc{Q-Ins}}
-\newcommand{\QCsp}{\textsc{Q-Csp}}
-\newcommand{\QRefl}{\textsc{Q-Refl}}
-\newcommand{\QSym}{\textsc{Q-Sym}}
-\newcommand{\QTrans}{\textsc{Q-Trans}}
-\newcommand{\QBeta}{\textsc{Q-$\beta$}}
-\newcommand{\QEta}{\textsc{Q-$\eta$}}
-\newcommand{\QTBLTB}{\textsc{Q-$\TBL\TB$}}
-\newcommand{\QLambda}{\textsc{Q-$\Lambda$}}
-\newcommand{\QPercent}{\textsc{Q-\%}}
-
-\newcommand{\ID}[1]{\infer[]{#1}{\vdots}}
-\newcommand{\MD}[1]{\mathcal{D}_#1}
-
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\B}{\textrm{Bool}}
-\newcommand{\M}{\textrm{Mat}}
-
-\newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}
-
-\begin{document}
-%
-\title{A Dependently Typed Multi-Stage Calculus%
-	\ifnotanonymous\thanks{Supported by organization x.}\fi
-}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\ifnotanonymous
-	\author{Akira Kawata\inst{1} \and
-		Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
-	% %
-	\authorrunning{A. Kawata, A. Igarashi}
-	% % First names are abbreviated in the running head.
-	% % If there are more than two authors, 'et al.' is used.
-	% %
-	\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
-		\email{akira@fos.kuis.kyoto-u.ac.jp} \and
-		\email{igarashi@kuis.kyoto-u.ac.jp}
-	}
-\fi
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-
-	We study a dependently typed extension of a multi-stage programming
-	language \`a la MetaOCaml, which supports quasi-quotation and
-	cross-stage persistence for manipulation of code fragments as
-	first-class values and eval for execution of programs dynamically
-	generated by the code manipulation.  Dependent types are expected to
-	bring to multi-stage programming enforcement of strong
-	invariants---beyond simple type safety---on the behavior of
-	dynamically generated code.  An extension is, however, not trivial
-	because a type system would have to take stages---roughly speaking,
-	the number of surrounding quotations---of types into account.
-
-	To rigorously study properties of such an extension, we develop
-	\LMD, which is an extension of Hanada and Igarashi's typed calculus
-	\LTP with dependent types, and prove its properties including
-	preservation, confluence, strong normalization for full
-	reduction, and progress for staged reduction.  Motivated
-	by code generators such that the type of generated code depends on a
-	value from outside of quotations, we argue the significance of
-	cross-stage persistence in dependently typed multi-stage programming
-	and certain type equivalence that are not directly derived from
-	reduction rules.
-
-	% A multi-stage calculus enables us to generate and execute codes at runtime.
-	% It can improve the performance of programs by generating optimized codes for given inputs.
-	% Dependent types are types dependent on values. 
-	% A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
-	% In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
-	% You can make more efficient programs from existing dependent typed programs with \LMD.
-	% \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
-	% It also includes an evaluation context which satisfies unique decomposition.
-	% The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-	% Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
-	% In this paper, we give reasonable equivalence rules to handle them.
-
-	\keywords{multi-stage programming, cross-stage persistence, dependent types}
-\end{abstract}
-
-\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
-\blue{コードとかはボールドを使ったほうが良いかもしれない。}
-\red{Suspicious senetences are colored red.}
-%
-%
-%
-\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}
-
-\section{Introduction}
-
-\subsection{Multi-stage Programming}
-
-% \subsubsection{多段階計算とは何か?}
-
-Multi-stage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multi-stage programming, which are brackets, escape, and run.
-Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
-Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Escape, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, escape is supposed to use in a fragment of code, that is, escape cannot be used as an alternative of run.
-For example, the following MetaOCaml expression
-
-\begin{verbatim}
-        let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
-\end{verbatim}
-evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
-\begin{verbatim}
-        run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
-\end{verbatim}
-is reduced to 3.
-
-% \subsubsection{CSPに関する補足説明}
-
-Cross-stage Persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
-This is an example of CSP.
-\begin{verbatim}
-        let plusone = fun x -> x + 1 in
-        let y = plusone 2 in  .< y >.
-\end{verbatim}
-This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
-This is because the variable \verb|y| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|y| is embedded after it was calculated.
-CSP is very important when we write practical programs 
-because CSP enables us to use library functions in code fragments as in \verb|.<List.combine [1;2] ['a';'b']>.|.
-
-% \subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
-
-The main application of multi-stage calculi is program optimization.
-A famous example is power functions.
-Usual power functions take two arguments, which are the base and the exponent.
-We can make a specialized power function for given exponents with multi-stage programming and 
-optimize them by unrolling a loop in functions for given exponents.
-The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
-\verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
-Multi-stage programming can optimize functions which take more than two arguments 
-by generating a code fragment optimized to a given argument.
-
-% \subsubsection{ベクトル計算も高速化できる}
-
-Multi-stage programming can also optimize vector calculation.
-For example, \verb|vadd| function, which takes two vectors and return the sum of them,
-is implemented with a loop in many cases.
-We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
-\red{MetaOCamlで書いた長さ付きベクトルの例?}
-
-% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
-
-However, there is a sever problem in functions which are optimized by multi-stage programming.
-Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
-For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
-Otherwise, we will get a Segmentation Fault error.
-This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
-
-% We call this problem \red{Specialized Code Problem}.
-
-\subsection{Dependent Types}
-
-% \subsubsection{依存型とは何か?}
-
-Dependent types are types which is dependent on values.
-We can use dependent types for securer programming.
-For example, we can realize vectors with their sizes with them.
-\begin{verbatim}
-        Vector :: Int -> *
-\end{verbatim}
-\verb|Vector| is a type constor which takes the length of vectors, that is, 
-\verb|Vector 3| is a type for vectors whose lengths are 3.
-If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n|,
-we can confirm the two arguments of \verb|vadd| function has the same length.
-\red{secure programming? finer grained typing? とか}
-
-\subsection{Multi-stage Programming with Dependent Types}
-\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
-
-% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
-
-As we pointed out in the above section,
-functions optimized with multi-stage programming can take only restricted values as arguments.
-When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
-We introduce dependent types into a multi-stage calculus
-so that the type system can guarantee optimized functions are used properly.
-
-In this paper, we design new multi-stage calculus \LMD by 
-merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
-\LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming more safer with the power of dependent types.
-
-\subsection{Organization of the Paper}
-
-The organization of this paper is the following.
-Section 2 gives an informal overview of \LMD.
-Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
-Section 4 shows the properties of \LMD including Unique Decomposition.
-Section 5 discusses future works.
-Finally, Section 6 discusses related works.
-\AI{Use $\backslash$label and $\backslash$ref!}
-\AI{``Related work'' and ``future work'' (they are uncountable).}
-
-\section{Informal Overview of \LMD}
-
-We designed \LMD, a multi-stage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP and
-we introduced dependent types based on \LTP\cite{attapl}.
-In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
-
-\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
-\subsection{\LTP}
-
-% quote and unquote
-
-\LTP\cite{Hanada2014} is a multi-stage calculus with CSP by Hanada and Igarashi.
-In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
-The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
-The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
-% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
-\begin{align*}
-	\TBL_\alpha (\TB_\alpha M) \longrightarrow M 
-\end{align*}
-It means escape cancels brackets.
-% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
-% \red{この文はここに来るべきなのか? LTPの説明ではないが}
-
-% transition variable and transition
-
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
-a sequence of transition variables is called \textit{transition}.
-The empty transition is represented by $\epsilon$.
-They are used to show the thickness of brackets.
-For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
-becomes $(\lambda x:\I.x+10)$ after it was run it twice.
-\red{run twiceは表現が微妙}
-
-% transition abstraction and application
-
-There are abstractions for transition variables and applications for transition abstraction in \LTP.
-They look like $\Lambda\alpha.M$ and $M A$, respectively.
-A transition abstraction binds a transition variable in a term.
-For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural there is a reduction rule for transition application in \LTP.
-The rule is the following.
-\begin{align*}
-	(\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
-\end{align*}
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
-
-% transition-related symbols disappear when the empty transition is substituted.
-% In short, about "run"
-
-Another important rule about a transition variable is 
-that symbols with transition variables disappear 
-when the empty transition $\epsilon$ is substituted to the transition variable.
-The purpose of this rule is express \verb|run| without any special symbol.
-In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
-For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.
-
-% transition in typing rules
-
-A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-A transition in a judgement represents where the judgement is true.
-For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
-term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
-Especially, terms without quoting exist at the empty transition $\epsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
-$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
-Terefore, transitions appear in typing rules, too.
-\begin{center}
-	\infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
-	\infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
-\end{center}
-\TTB, corresponding to brackets, means 
-if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
-\TTBL\ is converse of \TTB.
-
-% CSP
-
-CSP, cross-stage persistence, is an important feature of \LTP.
-It enables us to embed value at an outer transition into an inner transition.
-$\%$ is dedicated to CSP in \LTP.
-For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
-\red{inner / outer は適切か?}
-
-% Omitting Residualization
-% この段落は3章のM eのあとに、この制限の結果として...という形で入れる
-
-% There is another important feature called program residualization in \LTP.
-% It means that a generated code can be dumped into a file.
-% We can load the dumped file and run it.
-% The difficulty arises when program residualization is used with CSP.
-% Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
-
-\subsection{\LLF}
-
-% \LLF
-\LLF is a simple system of dependent types introduced in \cite{attapl}.
-\red{system / type system / calculus?}
-It is based on Edinburgh LF\cite{harper1993framework}.
-Therefore, all constants and base types are declared in the signature.
-The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.
-
-% Kind, Well-formed kind
-In addition to ordinary typing rules like simply typed lambda calculus,
-there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
-Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
-For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
-for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
-
-% Type Equality
-Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
-For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
-but they are not equivalent seemingly. Thus, we must define equivalence rules.
-In \LLF, equivalence is expressed with a symbol of $\E$.
-$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
-$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
-$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
-
-\subsection{Extending \LTP with Dependent Types}
-
-Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-From here, we use the word "stage" instead of "transition" 
-because we develop a multi-stage calculus, not a multi-transition calculus.
-\red{stageのほうが言葉としてふさわしいと言いたい}
-There are three technical points in the extension from \LTP to \LMD.
-
-\red{以下の3文をどこかに入れる必要がある}
-\red{, which is called a \textit{stage variable} in \LMD.}
-\red{ which is called a stage in \LMD.}
-\red{Although we can apply any transition to a transition abstraction in \LTP,
-	we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
-
-% Constants and Base Types
-
-First, the way of handling of constants and base types is the difference between \LMD and \LTP.
-We adopt a signature $\Sigma$ to handle constants and base types.
-This is because a signature simplifies kinding rules relating to type variables.
-A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
-For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
-\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}
-
-% Kidinding and Well-formed Kinding Rules
-
-Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
-It was lucky that almost all rules are determined easily.
-This is because multi-stage calculus and dependent types are almost orthogonal.
-\red{orthogonal は抽象的すぎるか?}
-Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
-attaching stage anotations to ones of \LLF.
-For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
-\begin{center}
-	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
-	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
-\end{center}
-
-% Equivalence Rules
-
-Third, we also need type equivalence rules in \LMD as a dependent type system.
-Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily.
-\red{design?}
-\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
-
-% Q-% rule
-
-The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
-The equivalence simple rule to handle CSP is \QCsp.
-\begin{center}
-	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
-\end{center}
-However, this rule isn't enough when the parameters of dependent types are cross-staed.
-We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
-\begin{center}
-	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-\end{center}
-\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
-
 \section{Formal Definition of \LMD}
@@
 \end{definition}
-
-\section{Properties of \LMD}
-
-In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
-unique decomposition of evaluation contexts, and progress.
-These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
-
-% Substitution Lemma
-
-Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
-because there are six types of judgment and two types of substitution in \LMD.
-Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
-typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
-
-\begin{lemma}[Substitution Lemma on Terms]
-	\begin{flalign*}
-		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
-	\end{flalign*}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Substitution Lemma on Stages]
-	\begin{flalign*}
-		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
-	\end{flalign*}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Inversion Lemma
-
-Following three Inversion Lemmas are needed in proving later theorems.
-Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
-They are composed of three part.
-The first part state that we can infer types of subterms.
-The second and third parts state 
-that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence.
-
-\begin{lemma}[Inversion Lemma for $\Pi$ type]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
-	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau @A$
-	\end{enumerate}
-	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\TW$ type]
-	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\Lambda$ type]
-	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Preservation
-
-Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
-Preservation ensure that any one step reduction preserves type.
-
-\begin{theorem}[Preservation]
-	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
-\end{theorem}
-
-\begin{proof}
-	First, there are three cases for $M \longrightarrow M'$.
-	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-% Strong Normalization
-
-Strong Normalization is also important property which guarantee that
-no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus.
-
-\begin{theorem}[Strong Normalization]
-	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
-	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
-\end{theorem}
-
-\begin{proof}
-	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
-	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
-\end{proof}
-
-Confluence is a property that any reduction sequences from one typed term converge.
-Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
-
-\begin{theorem}[Confluence]
-	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
-	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
-\end{theorem}
-
-\begin{proof}
-	Because we proved Strong Normalization of \LMD, 
-	we can use Newman's lemma to prove Confluence of \LMD.
-	Then, what we must show is Weak Church-Rosser Property now.
-	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
-	In short, they are never overlapped each other.
-	So, we can reduce one of them after we reduce another.
-\end{proof}
-
-Unique Decomposition ensure that
-,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it guarantee
-that the evaluation context decides a redex to reduce deterministically.
-Specifically speaking, this theorem guarantee that 
-when you write a interpreter using the evaluation context of \LMD,
-your interpreter works just as intended.
-
-\begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
-	\begin{enumerate}
-		\item $ M \in V^A$
-		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
-	\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
-Thanks to Unique Decomposition, we can prove this theorem easily.
-
-\begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-\section{Related Works}
-
-% 依存型の歴史
-
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
-
-% 依存型の応用
-
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
-
-% 多段階計算の歴史
-
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
-However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
-construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
-
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\epsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump the quoted code into an external file.
-
-% 他段階計算の機能拡張
-
-Combination of multi-stage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
-
-% 多段階計算の応用
-
-MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
-Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
-which include filtering in signal processing, matrix-vector product, and DSL compiler.
-
-% \begin{enumerate}
-% 	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
-
-% 	      CSPも入りました
-% 	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-% 	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-% 	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-% 	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
-% 	\item Done: Environment classifiers\cite{taha2003environment}
-% 	\item Done: A framework for defining logics\cite{harper1993framework}
-
-% 	      $\Sigma$ の使い方を確認した
-% 	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-% 	\item Done: Dependent types in practical programming\cite{xi1999dependent}
-
-% 	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-% 	\item Done: A dependently typed assembly language\cite{xi2001dependently}
-
-% 	      DTALの定義と制約solverを用いた型検査の定義
-% 	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
-% 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-% 	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
-% 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
-% 	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-% 	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
-% 	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
-% 	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
-% 	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
-% 	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
-% 	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-% \end{enumerate}
-
-\section{Conclusions}
-
-We proposed new multi-stage calculus \LMD, which can use dependent types.
-\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
-This extention prevent some bugs relating to generated functions with multi-stage programming,
-such as \verb|vadd| function for vectors of a fixed length.
-We proved properties of \LMD including preservation, confluence, 
-strong normalization for full reduction, and progress for staged reduction.
-The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
-We resolve this problem by ignoring $\%$ under some condition.
-
-Making algorithmic typing and equality rules for \LMD is a future work.
-They would be complicated but possible 
-because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
-
-% 2つの設計手法と今回採用した理由
-% Conclusion送りか?
-% When we design type equivalence rules of \LMD, there are two design choices.
-% One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-% Another is defining type equivalence directly by a combination of type equivalence rules.
-% We adopt the latter one because it is convenient to handle CSP in the type equivalence.
-
-% \section{First Section}
-% \subsection{A Subsection Sample}
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc. does not need an indent, either.
-% 
-% Subsequent paragraphs, however, are indented.
-% 
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-% 
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-% 
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-% 
-% 
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-% 
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-% 
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-% %
-% % the environments 'definition', 'lemma', 'proposition', 'corollary',
-% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
-% %
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\bibliographystyle{splncs04}
-\bibliography{main}
-%
-% \begin{thebibliography}{8}
-% \bibitem{ref_article1}
-% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-% 
-% \bibitem{ref_lncs1}
-% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-% 
-% \bibitem{ref_book1}
-% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-% Location (1999)
-% 
-% \bibitem{ref_proc1}
-% Author, A.-B.: Contribution title. In: 9th International Proceedings
-% on Proceedings, pp. 1--2. Publisher, Location (2010)
-% 
-% \bibitem{ref_url1}
-% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-% Oct 2017
-% \end{thebibliography}
-
-\section{Appendix}
-
-\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
-Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures.
-This category encompasses both theoretical and implementation (also known as system descriptions) papers.
-In either case, submissions should clearly identify what has been accomplished and why it is significant.
-Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity.
-System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design.
-In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
-\blue{Review Process
-	APLAS 2019 will use a lightweight double-blind reviewing process.
-Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper.
-The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
-	To facilitate this process, submitted papers must adhere to the following:
-	Author names and institutions must be omitted and
-	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
-	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
-Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas.
-For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure.
-Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would.
-For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
-\end{document}

### 2019-06-14 informal-overview.tex
Split main.tex.

--- 2019-06-13 main.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\newif\ifnotanonymous \notanonymousfalse
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bcprules, proof}
-\usepackage{fancybox}
-\usepackage{mathtools}
-\usepackage{float}
-\usepackage{xparse}
-\usepackage{lscape}
-\usepackage{mdframed}
-\usepackage{xspace}
-
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\newcommand{\red}[1]{\textcolor{red}{#1 }}
-\newcommand{\blue}[1]{\textcolor{blue}{#1 }}
-
-\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
-\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
-\newcommand{\LLF}{$\lambda\textrm{LF}$\xspace}
-
-\newcommand{\G}{\Gamma}
-\newcommand{\D}{\Delta}
-\newcommand{\V}{\vdash_\Sigma}
-\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
-\newcommand{\iskind}{\text{\ kind}}
-\newcommand{\TW}{{\mathop{\triangleright}}}
-\newcommand{\TWL}{{\mathop{\triangleleft}}}
-\newcommand{\F}{\forall}
-\newcommand{\TB}{{\mathop{\blacktriangleright}}}
-\newcommand{\TBL}{{\mathop{\blacktriangleleft}}}
-\newcommand{\E}{\equiv}
-\newcommand{\FV}{\text{FV}}
-\newcommand{\FTV}{\text{FSV}}
-
-\newcommand{\WStar}{\textsc{W-Star}}
-\newcommand{\WAbs}{\textsc{W-Abs}}
-\newcommand{\WCsp}{\textsc{W-Csp}}
-\newcommand{\WApp}{\textsc{W-App}}
-\newcommand{\WTW}{\textsc{W-$\TW$}}
-
-\newcommand{\KVar}{\textsc{K-Var}}
-\newcommand{\KAbs}{\textsc{K-Abs}}
-\newcommand{\KApp}{\textsc{K-App}}
-\newcommand{\KConv}{\textsc{K-Conv}}
-\newcommand{\KTW}{\textsc{K-$\TW$}}
-\newcommand{\KTWL}{\textsc{K-$\TWL$}}
-\newcommand{\KGen}{\textsc{K-Gen}}
-\newcommand{\KCsp}{\textsc{K-Csp}}
-
-\newcommand{\TConst}{\textsc{T-Const}}
-\newcommand{\TVar}{\textsc{T-Var}}
-\newcommand{\TAbs}{\textsc{T-Abs}}
-\newcommand{\TApp}{\textsc{T-App}}
-\newcommand{\TConv}{\textsc{T-Conv}}
-\newcommand{\TTB}{\textsc{T-$\TB$}}
-\newcommand{\TTBL}{\textsc{T-$\TBL$}}
-\newcommand{\TGen}{\textsc{T-Gen}}
-\newcommand{\TIns}{\textsc{T-Ins}}
-\newcommand{\TCsp}{\textsc{T-Csp}}
-
-\newcommand{\QKAbs}{\textsc{QK-Abs}}
-\newcommand{\QKCsp}{\textsc{QK-Csp}}
-\newcommand{\QKRefl}{\textsc{QK-Refl}}
-\newcommand{\QKSym}{\textsc{QK-Sym}}
-\newcommand{\QKTrans}{\textsc{QK-Trans}}
-
-\newcommand{\QTAbs}{\textsc{QT-Abs}}
-\newcommand{\QTApp}{\textsc{QT-App}}
-\newcommand{\QTTW}{\textsc{QT-$\TW$}}
-\newcommand{\QTGen}{\textsc{QT-Gen}}
-\newcommand{\QTCsp}{\textsc{QT-Csp}}
-\newcommand{\QTRefl}{\textsc{QT-Refl}}
-\newcommand{\QTSym}{\textsc{QT-Sym}}
-\newcommand{\QTTrans}{\textsc{QT-Trans}}
-
-\newcommand{\QAbs}{\textsc{Q-Abs}}
-\newcommand{\QApp}{\textsc{Q-App}}
-\newcommand{\QTB}{\textsc{Q-$\TB$}}
-\newcommand{\QTBL}{\textsc{Q-$\TBL$}}
-\newcommand{\QGen}{\textsc{Q-Gen}}
-\newcommand{\QIns}{\textsc{Q-Ins}}
-\newcommand{\QCsp}{\textsc{Q-Csp}}
-\newcommand{\QRefl}{\textsc{Q-Refl}}
-\newcommand{\QSym}{\textsc{Q-Sym}}
-\newcommand{\QTrans}{\textsc{Q-Trans}}
-\newcommand{\QBeta}{\textsc{Q-$\beta$}}
-\newcommand{\QEta}{\textsc{Q-$\eta$}}
-\newcommand{\QTBLTB}{\textsc{Q-$\TBL\TB$}}
-\newcommand{\QLambda}{\textsc{Q-$\Lambda$}}
-\newcommand{\QPercent}{\textsc{Q-\%}}
-
-\newcommand{\ID}[1]{\infer[]{#1}{\vdots}}
-\newcommand{\MD}[1]{\mathcal{D}_#1}
-
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\B}{\textrm{Bool}}
-\newcommand{\M}{\textrm{Mat}}
-
-\newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}
-
-\begin{document}
-%
-\title{A Dependently Typed Multi-Stage Calculus%
-	\ifnotanonymous\thanks{Supported by organization x.}\fi
-}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\ifnotanonymous
-	\author{Akira Kawata\inst{1} \and
-		Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
-	% %
-	\authorrunning{A. Kawata, A. Igarashi}
-	% % First names are abbreviated in the running head.
-	% % If there are more than two authors, 'et al.' is used.
-	% %
-	\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
-		\email{akira@fos.kuis.kyoto-u.ac.jp} \and
-		\email{igarashi@kuis.kyoto-u.ac.jp}
-	}
-\fi
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-
-	We study a dependently typed extension of a multi-stage programming
-	language \`a la MetaOCaml, which supports quasi-quotation and
-	cross-stage persistence for manipulation of code fragments as
-	first-class values and eval for execution of programs dynamically
-	generated by the code manipulation.  Dependent types are expected to
-	bring to multi-stage programming enforcement of strong
-	invariants---beyond simple type safety---on the behavior of
-	dynamically generated code.  An extension is, however, not trivial
-	because a type system would have to take stages---roughly speaking,
-	the number of surrounding quotations---of types into account.
-
-	To rigorously study properties of such an extension, we develop
-	\LMD, which is an extension of Hanada and Igarashi's typed calculus
-	\LTP with dependent types, and prove its properties including
-	preservation, confluence, strong normalization for full
-	reduction, and progress for staged reduction.  Motivated
-	by code generators such that the type of generated code depends on a
-	value from outside of quotations, we argue the significance of
-	cross-stage persistence in dependently typed multi-stage programming
-	and certain type equivalence that are not directly derived from
-	reduction rules.
-
-	% A multi-stage calculus enables us to generate and execute codes at runtime.
-	% It can improve the performance of programs by generating optimized codes for given inputs.
-	% Dependent types are types dependent on values. 
-	% A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
-	% In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
-	% You can make more efficient programs from existing dependent typed programs with \LMD.
-	% \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
-	% It also includes an evaluation context which satisfies unique decomposition.
-	% The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-	% Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
-	% In this paper, we give reasonable equivalence rules to handle them.
-
-	\keywords{multi-stage programming, cross-stage persistence, dependent types}
-\end{abstract}
-
-\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
-\blue{コードとかはボールドを使ったほうが良いかもしれない。}
-\red{Suspicious senetences are colored red.}
-%
-%
-%
-\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}
-
-\section{Introduction}
-
-\subsection{Multi-stage Programming}
-
-% \subsubsection{多段階計算とは何か?}
-
-Multi-stage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multi-stage programming, which are brackets, escape, and run.
-Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
-Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Escape, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, escape is supposed to use in a fragment of code, that is, escape cannot be used as an alternative of run.
-For example, the following MetaOCaml expression
-
-\begin{verbatim}
-        let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
-\end{verbatim}
-evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
-\begin{verbatim}
-        run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
-\end{verbatim}
-is reduced to 3.
-
-% \subsubsection{CSPに関する補足説明}
-
-Cross-stage Persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
-This is an example of CSP.
-\begin{verbatim}
-        let plusone = fun x -> x + 1 in
-        let y = plusone 2 in  .< y >.
-\end{verbatim}
-This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
-This is because the variable \verb|y| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|y| is embedded after it was calculated.
-CSP is very important when we write practical programs 
-because CSP enables us to use library functions in code fragments as in \verb|.<List.combine [1;2] ['a';'b']>.|.
-
-% \subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
-
-The main application of multi-stage calculi is program optimization.
-A famous example is power functions.
-Usual power functions take two arguments, which are the base and the exponent.
-We can make a specialized power function for given exponents with multi-stage programming and 
-optimize them by unrolling a loop in functions for given exponents.
-The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
-\verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
-Multi-stage programming can optimize functions which take more than two arguments 
-by generating a code fragment optimized to a given argument.
-
-% \subsubsection{ベクトル計算も高速化できる}
-
-Multi-stage programming can also optimize vector calculation.
-For example, \verb|vadd| function, which takes two vectors and return the sum of them,
-is implemented with a loop in many cases.
-We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
-\red{MetaOCamlで書いた長さ付きベクトルの例?}
-
-% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
-
-However, there is a sever problem in functions which are optimized by multi-stage programming.
-Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
-For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
-Otherwise, we will get a Segmentation Fault error.
-This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
-
-% We call this problem \red{Specialized Code Problem}.
-
-\subsection{Dependent Types}
-
-% \subsubsection{依存型とは何か?}
-
-Dependent types are types which is dependent on values.
-We can use dependent types for securer programming.
-For example, we can realize vectors with their sizes with them.
-\begin{verbatim}
-        Vector :: Int -> *
-\end{verbatim}
-\verb|Vector| is a type constor which takes the length of vectors, that is, 
-\verb|Vector 3| is a type for vectors whose lengths are 3.
-If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n|,
-we can confirm the two arguments of \verb|vadd| function has the same length.
-\red{secure programming? finer grained typing? とか}
-
-\subsection{Multi-stage Programming with Dependent Types}
-\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
-
-% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
-
-As we pointed out in the above section,
-functions optimized with multi-stage programming can take only restricted values as arguments.
-When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
-We introduce dependent types into a multi-stage calculus
-so that the type system can guarantee optimized functions are used properly.
-
-In this paper, we design new multi-stage calculus \LMD by 
-merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
-\LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming more safer with the power of dependent types.
-
-\subsection{Organization of the Paper}
-
-The organization of this paper is the following.
-Section 2 gives an informal overview of \LMD.
-Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
-Section 4 shows the properties of \LMD including Unique Decomposition.
-Section 5 discusses future works.
-Finally, Section 6 discusses related works.
-\AI{Use $\backslash$label and $\backslash$ref!}
-\AI{``Related work'' and ``future work'' (they are uncountable).}
-
 \section{Informal Overview of \LMD}
@@
 \red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
-
-\section{Formal Definition of \LMD}
-
-In this section, we give a formal definition of \LMD, including
-the syntax, full reduction, and type system.  In addition to full reduction,
-in which any redex at any stage can be reduced, we also give staged reduction,
-which models execution as programs.
-
-\subsection{Syntax}
-
-\AI{Rename ``type variables'' to ``type-level constants''. }
-We assume the denumerable set of type variables, ranged over by
-metavariables \(X, Y, Z\), the denumerable set of variables, ranged
-over by \(x,y,z\), the denumerable set of constants, ranged over by
-\(c\), and the denumerable set of stage variables, ranged over by
-\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
-sequences of stage variables; we write \(\varepsilon\) for the empty
-sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:
-
-\AI{``Transition'' is still used.}
-
-\begin{align*}
-    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
-    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
-    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
-    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
-    \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
-    \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
-%     \textrm{Constants}       &   &                          & c                                                                                                          \\
-    \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
-                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
-    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
-    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
-\end{align*}
-
-\AI{Add $M\,\alpha$ to terms.}
-
-\AI{Is $O$ used as a metavariable?}
-\AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
-
-% Description on meta variables
-
-% Kinds
-
-A kind, which is used to classify types, is either $*$, the kind of
-proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
-of type operators that takes $x$ as an argument of type $\tau$ and returns a type
-of kind $K$.
-% Types
-% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
-% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
-% \red{この段落は短いので型の段落と結合するか?}
-% Types
-A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
-$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
-An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
-if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
-A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
-An $\alpha$-closed type corresponds to a runnable code fragment.
-Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
-an application of a term to a dependent function type $\tau\ M$,
-a code type $\TW_{\alpha} \tau$,
-a dependent function type $\Pi x:\tau.\tau$, 
-an $\alpha$-closed type $\F\alpha.\tau$.
-Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
-
-% Terms
-
-Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
-whose type is declared in signature $\Sigma$, and the following five forms
-related to multi-stage programming:
-$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
-$\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
-$\%_\alpha M$ is an operator for cross-stage persistence.
-The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
-and applications are left-associative
-and two abstractions extends as far to the right as possible.
-For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
-
-% Signature
-
-We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
-are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
-\AI{Change Int to Bool.}
-
-% Free variables
-As usual, the variable $x$ is bound in $\lambda x:\tau.M$
-and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
-\AI{What about other binders such as $\Pi$?}
-We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
-We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
-
-% Contexts
-Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
-$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
-\AI{I'd prefer \textit{dom}.}
-The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
-$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.
-
-\AI{We should note that constants and type variables are not staged.}
-\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
-
-\subsection{Reduction}
-
-Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define two kinds of substitutions.
-Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
-$N$ for $x$ in $M$, and we omit its definition here.
-Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
-for stage variable $\alpha$ in $M$ is defined below.
-\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}
-
-\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
-\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
-
-\begin{align*}
-	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
-	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
-	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
-	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
-\end{align*}
-
-\begin{definition}[Reduction]
-  \AI{It's not clear what are defined here.  You are talking only about rules.
-    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
-	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
-	Congruence rules which are omitted from the definition.
-	\begin{align*}
-		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                       \\
-		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
-		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
-		 & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
-	\end{align*}
-	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
-\end{definition}
-
-The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
-$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
-where $\epsilon$ is substituted for the stage variable.
-Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
-There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
-% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
-
-\AI{A few examples are desirable.}
-
-\subsection{Type System}
-
-% 総論
-
-In this section, we define the type system of \LMD.
-% \LMD is little complicated because it contains dependent types.
-It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
-We list the judgments forms in Figure~\ref{fig:LMD-six-judgements}.
-\AI{equality vs. equivalence?}
-\AI{A few judgment forms do not match rules.}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			\G & \V M : \tau @ A   & \text{typing} \\
-			\G & \V \tau :: K @ A  & \text{kinding} \\
-			\G & \V K \iskind @ A  & \text{well-formed kinding} \\
-			\G & \V M \E N @ A     & \text{term equality} \\
-			\G & \V \tau \E \sigma & \text{type equality} \\
-			\G & \V K \E J @ A     & \text{kind equality}
-		\end{align*}
-		\caption{Six judgment forms of the type system of \LMD.}
-		\label{fig:LMD-six-judgements}
-	\end{center}
-\end{figure}
-
-\AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
-\begin{definition}[Typing]
-  The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
-  \AI{Precisely speaking, it cannot be defined independently of other judgments.
-  How is dependency between judgments?}
-\end{definition}
-
-\AI{``judgment'' vs. ``judgement''.}  We start from defining typing of
-\LMD.  Typing rules of \LMD are shown in Figure
-\ref{fig:typing-rules}.  The rule \TConst{} means any constants in the
-signature can appear at any stage.  \AI{This should be discussed
-  earlier.}  For example, if we have a signature $\Sigma$ which is
-$\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
-\textrm{bool}$, the derivation tree in
-Figure~\ref{fig:tconst-derivation-tree} is admissible.  \AI{Don't we
-  need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$
-  should be a well-formed type under ... what?}  The rules \TVar,
-\TAbs, and \TApp{} are almost the same as those in the simply typed
-lambda calculus.  \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}  Additional conditions are that subterms must be
-typed at the same stage (\TAbs{} and \TApp); the type
-annotation/declaration on a variable has to be a proper type of kind
-$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
-
-\begin{figure}
-	\begin{center}
-		\begin{minipage}{0.50\hsize}
-			\infer[\TConst]
-			{\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
-			{\textrm{true}:\textrm{bool} \in \Sigma \andalso
-				\ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
-			}
-			\caption{A derivation tree using \TConst}
-			\label{fig:tconst-derivation-tree}
-		\end{minipage}
-	\end{center}
-\end{figure}
-
-% \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is opposite.}
-As in standard dependent type systems, \TConv{} allows us to replace
-the type of a term with an equivalent one.  
-In a type system which includes dependent types, this kind of rule is essential
-because two types which have different shapes may be equivalent.
-For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
-
-% Typing rules for a multi-stage calculus
-\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-They are corresponding to brackets, escape, making a stage abstraction, 
-application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
-Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
-
-\begin{figure}
-	\begin{center}
-		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
-		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
-		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
-		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
-		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
-		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
-		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
-		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
-		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
-		\caption{Typing Rules.}
-		\label{fig:typing-rules}
-	\end{center}
-\end{figure}
-
-\subsubsection{Type and Term Equivalence}
-
-As usual in dependent type systems, type equivalence, used in \TConv,
-is important.  The type equivalence judgment of the form
-$\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
-are equivalent as types of kind $K$ at stage $A$ under $\G$.
-Figure~\ref{fig:type-equivalence-rules} shows the rules for type
-equivalence.  Type equivalence is basically the least congruence
-closed under term equivalence.  The rules for compatibility (closure
-under type formation) are derived from corresponding typing rules in a
-straightforward manner.  The rules are a little simpler than some
-dependent type systems \AI{such as?}  because there is no abstraction
-at the type level.
-
-% \QCsp以外の説明
-% We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
-% All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
-% \QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
-% The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
-% the results of applications are also equivalent.
-
-\begin{figure}
-	\begin{center}
-		\infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
-		\infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
-		\infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
-		\infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
-		\infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
-		\infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
-		\infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
-		\infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
-		\caption{Type Equivalence Rules.}
-		\label{fig:type-equivalence-rules}
-	\end{center}
-\end{figure}
-
-The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
-which means that terms $M$ and $N$ are equivalent as terms of type
-$\rho$ at stage $A$ under $\G$, is defined by the rules in
-Figure~\ref{fig:term-equivalence-rules}.  Most rules are
-straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
-\QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
-rules \QBeta, \QTBLTB, and \QLambda{} correspond to the reduction rules.
-\AI{Don't we give names to those reduction rules?}
-
-\begin{figure}
-	\begin{center}
-		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
-		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
-		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
-		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
-		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
-		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
-		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
-		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
-		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
-		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
-		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
-		\caption{Term Equivalence Rules.}
-		\label{fig:term-equivalence-rules}
-	\end{center}
-\end{figure}
-
-% \QPercentの説明
-The only rule that deserves elaboration is the last rule \QPercent.
-Intuitively, it means that the CSP operator applied to term $M$ can be
-removed if $M$ is also well typed at the next stage \(A\alpha\).
-For example, constants do not depend on the stage (see \TConst) and
-so \(\G\V \%_\alpha c \E c : \tau @ A\alpha\) holds but variables
-do depend on stages and so this rule does not apply.
-
-Interestingly, Hanada and Igarashi~\cite{} rejected the idea of
-reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
-in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and as we argue \AI{where?}
-it is practically significant.
-
-%%%%%%%%%%%%%%%%%%% SKIP FROM HERE %%%%%%%%%%%%%%%%%%%%
-$\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
-$\text{mulmat}$ takes two integers which are the size of the multiplicand matrix and generate a code.
-The last integer to decide the size of the multiplier matrix is given at runtime.
-You can generate code by applying two integers to $\text{mulmat}$.
-We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
-But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under a condition which is explained in the next paragraph.
-
-The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
-For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
-In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
-
-	% Example of QCsp (mulmat)
-	{
-		\begin{align*}
-			\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-			\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-			                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-		\end{align*}
-	}
-
-This kind of type equality is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
-We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
-because types of codes don't contain $\%_\alpha$ generally.
-
-%%%%%%%%%%%%%%%%%%% TO HERE %%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Staged Semantics}
-
-The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
-But we need to fix order of reduction when we implement an interpreter of \LMD and
-the order must be appropriate in terms of stages.
-
-We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
-In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
-$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
-
-\begin{definition}[Values]
-	The family $V^A$ of sets of values, ranged over by $v^A$ and 
-	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
-	are defined by following grammar. In the grammar $A \neq \epsilon$.
-	\begin{align*}
-		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
-		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                          & \\
-		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
-		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
-		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
-	\end{align*}
-\end{definition}
-
-Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
-The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
-This restriction means that the body of $Lambda$ abstraction must be evaluated before application of an $\epsilon$ stage.
-Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
-This is because $\TBL_\alpha v^\epsilon$ is a redex.
-
-\begin{definition}[Evaluation Context]
-	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
-	$A$ is nonempty. (Although $B,A'$ can be empty.)
-	$A \neq \epsilon$\\
-	\begin{align*}
-		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B     
-		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
-		\mid E^\epsilon_B\ \epsilon                                                                                                 \\
-		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
-		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
-		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
-		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B                                                   
-		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
-	\end{align*}
-\end{definition}
-
-We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.
-
-\begin{definition}[Staged Reduction]
-	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
-	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
-\end{definition}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
-			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
-			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
-		\end{align*}
-		\caption{Staged Reduction}
-		\label{fig:staged-reduction}
-	\end{center}
-\end{figure}
-
-\section{Properties of \LMD}
-
-In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
-unique decomposition of evaluation contexts, and progress.
-These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
-
-% Substitution Lemma
-
-Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
-because there are six types of judgment and two types of substitution in \LMD.
-Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
-typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
-
-\begin{lemma}[Substitution Lemma on Terms]
-	\begin{flalign*}
-		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
-	\end{flalign*}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Substitution Lemma on Stages]
-	\begin{flalign*}
-		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
-	\end{flalign*}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Inversion Lemma
-
-Following three Inversion Lemmas are needed in proving later theorems.
-Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
-They are composed of three part.
-The first part state that we can infer types of subterms.
-The second and third parts state 
-that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence.
-
-\begin{lemma}[Inversion Lemma for $\Pi$ type]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
-	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau @A$
-	\end{enumerate}
-	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\TW$ type]
-	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\Lambda$ type]
-	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Preservation
-
-Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
-Preservation ensure that any one step reduction preserves type.
-
-\begin{theorem}[Preservation]
-	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
-\end{theorem}
-
-\begin{proof}
-	First, there are three cases for $M \longrightarrow M'$.
-	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-% Strong Normalization
-
-Strong Normalization is also important property which guarantee that
-no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus.
-
-\begin{theorem}[Strong Normalization]
-	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
-	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
-\end{theorem}
-
-\begin{proof}
-	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
-	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
-\end{proof}
-
-Confluence is a property that any reduction sequences from one typed term converge.
-Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
-
-\begin{theorem}[Confluence]
-	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
-	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
-\end{theorem}
-
-\begin{proof}
-	Because we proved Strong Normalization of \LMD, 
-	we can use Newman's lemma to prove Confluence of \LMD.
-	Then, what we must show is Weak Church-Rosser Property now.
-	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
-	In short, they are never overlapped each other.
-	So, we can reduce one of them after we reduce another.
-\end{proof}
-
-Unique Decomposition ensure that
-,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it guarantee
-that the evaluation context decides a redex to reduce deterministically.
-Specifically speaking, this theorem guarantee that 
-when you write a interpreter using the evaluation context of \LMD,
-your interpreter works just as intended.
-
-\begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
-	\begin{enumerate}
-		\item $ M \in V^A$
-		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
-	\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
-Thanks to Unique Decomposition, we can prove this theorem easily.
-
-\begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-\section{Related Works}
-
-% 依存型の歴史
-
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
-
-% 依存型の応用
-
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
-
-% 多段階計算の歴史
-
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
-However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
-construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
-
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\epsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump the quoted code into an external file.
-
-% 他段階計算の機能拡張
-
-Combination of multi-stage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
-
-% 多段階計算の応用
-
-MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
-Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
-which include filtering in signal processing, matrix-vector product, and DSL compiler.
-
-% \begin{enumerate}
-% 	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
-
-% 	      CSPも入りました
-% 	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-% 	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-% 	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-% 	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
-% 	\item Done: Environment classifiers\cite{taha2003environment}
-% 	\item Done: A framework for defining logics\cite{harper1993framework}
-
-% 	      $\Sigma$ の使い方を確認した
-% 	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-% 	\item Done: Dependent types in practical programming\cite{xi1999dependent}
-
-% 	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-% 	\item Done: A dependently typed assembly language\cite{xi2001dependently}
-
-% 	      DTALの定義と制約solverを用いた型検査の定義
-% 	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
-% 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-% 	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
-% 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
-% 	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-% 	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
-% 	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
-% 	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
-% 	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
-% 	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
-% 	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-% \end{enumerate}
-
-\section{Conclusions}
-
-We proposed new multi-stage calculus \LMD, which can use dependent types.
-\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
-This extention prevent some bugs relating to generated functions with multi-stage programming,
-such as \verb|vadd| function for vectors of a fixed length.
-We proved properties of \LMD including preservation, confluence, 
-strong normalization for full reduction, and progress for staged reduction.
-The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
-We resolve this problem by ignoring $\%$ under some condition.
-
-Making algorithmic typing and equality rules for \LMD is a future work.
-They would be complicated but possible 
-because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
-
-% 2つの設計手法と今回採用した理由
-% Conclusion送りか?
-% When we design type equivalence rules of \LMD, there are two design choices.
-% One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-% Another is defining type equivalence directly by a combination of type equivalence rules.
-% We adopt the latter one because it is convenient to handle CSP in the type equivalence.
-
-% \section{First Section}
-% \subsection{A Subsection Sample}
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc. does not need an indent, either.
-% 
-% Subsequent paragraphs, however, are indented.
-% 
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-% 
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-% 
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-% 
-% 
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-% 
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-% 
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-% %
-% % the environments 'definition', 'lemma', 'proposition', 'corollary',
-% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
-% %
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\bibliographystyle{splncs04}
-\bibliography{main}
-%
-% \begin{thebibliography}{8}
-% \bibitem{ref_article1}
-% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-% 
-% \bibitem{ref_lncs1}
-% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-% 
-% \bibitem{ref_book1}
-% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-% Location (1999)
-% 
-% \bibitem{ref_proc1}
-% Author, A.-B.: Contribution title. In: 9th International Proceedings
-% on Proceedings, pp. 1--2. Publisher, Location (2010)
-% 
-% \bibitem{ref_url1}
-% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-% Oct 2017
-% \end{thebibliography}
-
-\section{Appendix}
-
-\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
-Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures.
-This category encompasses both theoretical and implementation (also known as system descriptions) papers.
-In either case, submissions should clearly identify what has been accomplished and why it is significant.
-Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity.
-System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design.
-In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
-\blue{Review Process
-	APLAS 2019 will use a lightweight double-blind reviewing process.
-Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper.
-The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
-	To facilitate this process, submitted papers must adhere to the following:
-	Author names and institutions must be omitted and
-	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
-	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
-Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas.
-For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure.
-Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would.
-For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
-\end{document}

### 2019-06-14 introduction.tex
Split main.tex.

--- 2019-06-13 main.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\newif\ifnotanonymous \notanonymousfalse
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bcprules, proof}
-\usepackage{fancybox}
-\usepackage{mathtools}
-\usepackage{float}
-\usepackage{xparse}
-\usepackage{lscape}
-\usepackage{mdframed}
-\usepackage{xspace}
-
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\newcommand{\red}[1]{\textcolor{red}{#1 }}
-\newcommand{\blue}[1]{\textcolor{blue}{#1 }}
-
-\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
-\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
-\newcommand{\LLF}{$\lambda\textrm{LF}$\xspace}
-
-\newcommand{\G}{\Gamma}
-\newcommand{\D}{\Delta}
-\newcommand{\V}{\vdash_\Sigma}
-\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
-\newcommand{\iskind}{\text{\ kind}}
-\newcommand{\TW}{{\mathop{\triangleright}}}
-\newcommand{\TWL}{{\mathop{\triangleleft}}}
-\newcommand{\F}{\forall}
-\newcommand{\TB}{{\mathop{\blacktriangleright}}}
-\newcommand{\TBL}{{\mathop{\blacktriangleleft}}}
-\newcommand{\E}{\equiv}
-\newcommand{\FV}{\text{FV}}
-\newcommand{\FTV}{\text{FSV}}
-
-\newcommand{\WStar}{\textsc{W-Star}}
-\newcommand{\WAbs}{\textsc{W-Abs}}
-\newcommand{\WCsp}{\textsc{W-Csp}}
-\newcommand{\WApp}{\textsc{W-App}}
-\newcommand{\WTW}{\textsc{W-$\TW$}}
-
-\newcommand{\KVar}{\textsc{K-Var}}
-\newcommand{\KAbs}{\textsc{K-Abs}}
-\newcommand{\KApp}{\textsc{K-App}}
-\newcommand{\KConv}{\textsc{K-Conv}}
-\newcommand{\KTW}{\textsc{K-$\TW$}}
-\newcommand{\KTWL}{\textsc{K-$\TWL$}}
-\newcommand{\KGen}{\textsc{K-Gen}}
-\newcommand{\KCsp}{\textsc{K-Csp}}
-
-\newcommand{\TConst}{\textsc{T-Const}}
-\newcommand{\TVar}{\textsc{T-Var}}
-\newcommand{\TAbs}{\textsc{T-Abs}}
-\newcommand{\TApp}{\textsc{T-App}}
-\newcommand{\TConv}{\textsc{T-Conv}}
-\newcommand{\TTB}{\textsc{T-$\TB$}}
-\newcommand{\TTBL}{\textsc{T-$\TBL$}}
-\newcommand{\TGen}{\textsc{T-Gen}}
-\newcommand{\TIns}{\textsc{T-Ins}}
-\newcommand{\TCsp}{\textsc{T-Csp}}
-
-\newcommand{\QKAbs}{\textsc{QK-Abs}}
-\newcommand{\QKCsp}{\textsc{QK-Csp}}
-\newcommand{\QKRefl}{\textsc{QK-Refl}}
-\newcommand{\QKSym}{\textsc{QK-Sym}}
-\newcommand{\QKTrans}{\textsc{QK-Trans}}
-
-\newcommand{\QTAbs}{\textsc{QT-Abs}}
-\newcommand{\QTApp}{\textsc{QT-App}}
-\newcommand{\QTTW}{\textsc{QT-$\TW$}}
-\newcommand{\QTGen}{\textsc{QT-Gen}}
-\newcommand{\QTCsp}{\textsc{QT-Csp}}
-\newcommand{\QTRefl}{\textsc{QT-Refl}}
-\newcommand{\QTSym}{\textsc{QT-Sym}}
-\newcommand{\QTTrans}{\textsc{QT-Trans}}
-
-\newcommand{\QAbs}{\textsc{Q-Abs}}
-\newcommand{\QApp}{\textsc{Q-App}}
-\newcommand{\QTB}{\textsc{Q-$\TB$}}
-\newcommand{\QTBL}{\textsc{Q-$\TBL$}}
-\newcommand{\QGen}{\textsc{Q-Gen}}
-\newcommand{\QIns}{\textsc{Q-Ins}}
-\newcommand{\QCsp}{\textsc{Q-Csp}}
-\newcommand{\QRefl}{\textsc{Q-Refl}}
-\newcommand{\QSym}{\textsc{Q-Sym}}
-\newcommand{\QTrans}{\textsc{Q-Trans}}
-\newcommand{\QBeta}{\textsc{Q-$\beta$}}
-\newcommand{\QEta}{\textsc{Q-$\eta$}}
-\newcommand{\QTBLTB}{\textsc{Q-$\TBL\TB$}}
-\newcommand{\QLambda}{\textsc{Q-$\Lambda$}}
-\newcommand{\QPercent}{\textsc{Q-\%}}
-
-\newcommand{\ID}[1]{\infer[]{#1}{\vdots}}
-\newcommand{\MD}[1]{\mathcal{D}_#1}
-
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\B}{\textrm{Bool}}
-\newcommand{\M}{\textrm{Mat}}
-
-\newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}
-
-\begin{document}
-%
-\title{A Dependently Typed Multi-Stage Calculus%
-	\ifnotanonymous\thanks{Supported by organization x.}\fi
-}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\ifnotanonymous
-	\author{Akira Kawata\inst{1} \and
-		Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
-	% %
-	\authorrunning{A. Kawata, A. Igarashi}
-	% % First names are abbreviated in the running head.
-	% % If there are more than two authors, 'et al.' is used.
-	% %
-	\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
-		\email{akira@fos.kuis.kyoto-u.ac.jp} \and
-		\email{igarashi@kuis.kyoto-u.ac.jp}
-	}
-\fi
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-
-	We study a dependently typed extension of a multi-stage programming
-	language \`a la MetaOCaml, which supports quasi-quotation and
-	cross-stage persistence for manipulation of code fragments as
-	first-class values and eval for execution of programs dynamically
-	generated by the code manipulation.  Dependent types are expected to
-	bring to multi-stage programming enforcement of strong
-	invariants---beyond simple type safety---on the behavior of
-	dynamically generated code.  An extension is, however, not trivial
-	because a type system would have to take stages---roughly speaking,
-	the number of surrounding quotations---of types into account.
-
-	To rigorously study properties of such an extension, we develop
-	\LMD, which is an extension of Hanada and Igarashi's typed calculus
-	\LTP with dependent types, and prove its properties including
-	preservation, confluence, strong normalization for full
-	reduction, and progress for staged reduction.  Motivated
-	by code generators such that the type of generated code depends on a
-	value from outside of quotations, we argue the significance of
-	cross-stage persistence in dependently typed multi-stage programming
-	and certain type equivalence that are not directly derived from
-	reduction rules.
-
-	% A multi-stage calculus enables us to generate and execute codes at runtime.
-	% It can improve the performance of programs by generating optimized codes for given inputs.
-	% Dependent types are types dependent on values. 
-	% A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
-	% In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
-	% You can make more efficient programs from existing dependent typed programs with \LMD.
-	% \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
-	% It also includes an evaluation context which satisfies unique decomposition.
-	% The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
-	% Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
-	% In this paper, we give reasonable equivalence rules to handle them.
-
-	\keywords{multi-stage programming, cross-stage persistence, dependent types}
-\end{abstract}
-
-\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
-\blue{コードとかはボールドを使ったほうが良いかもしれない。}
-\red{Suspicious senetences are colored red.}
-%
-%
-%
-\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}
-
 \section{Introduction}
@@
 \AI{``Related work'' and ``future work'' (they are uncountable).}
-
-\section{Informal Overview of \LMD}
-
-We designed \LMD, a multi-stage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP and
-we introduced dependent types based on \LTP\cite{attapl}.
-In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
-
-\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
-\subsection{\LTP}
-
-% quote and unquote
-
-\LTP\cite{Hanada2014} is a multi-stage calculus with CSP by Hanada and Igarashi.
-In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
-The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
-The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
-% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
-\begin{align*}
-	\TBL_\alpha (\TB_\alpha M) \longrightarrow M 
-\end{align*}
-It means escape cancels brackets.
-% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
-% \red{この文はここに来るべきなのか? LTPの説明ではないが}
-
-% transition variable and transition
-
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
-a sequence of transition variables is called \textit{transition}.
-The empty transition is represented by $\epsilon$.
-They are used to show the thickness of brackets.
-For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
-becomes $(\lambda x:\I.x+10)$ after it was run it twice.
-\red{run twiceは表現が微妙}
-
-% transition abstraction and application
-
-There are abstractions for transition variables and applications for transition abstraction in \LTP.
-They look like $\Lambda\alpha.M$ and $M A$, respectively.
-A transition abstraction binds a transition variable in a term.
-For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural there is a reduction rule for transition application in \LTP.
-The rule is the following.
-\begin{align*}
-	(\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
-\end{align*}
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
-
-% transition-related symbols disappear when the empty transition is substituted.
-% In short, about "run"
-
-Another important rule about a transition variable is 
-that symbols with transition variables disappear 
-when the empty transition $\epsilon$ is substituted to the transition variable.
-The purpose of this rule is express \verb|run| without any special symbol.
-In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
-For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.
-
-% transition in typing rules
-
-A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-A transition in a judgement represents where the judgement is true.
-For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
-term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
-Especially, terms without quoting exist at the empty transition $\epsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
-$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
-Terefore, transitions appear in typing rules, too.
-\begin{center}
-	\infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
-	\infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
-\end{center}
-\TTB, corresponding to brackets, means 
-if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
-\TTBL\ is converse of \TTB.
-
-% CSP
-
-CSP, cross-stage persistence, is an important feature of \LTP.
-It enables us to embed value at an outer transition into an inner transition.
-$\%$ is dedicated to CSP in \LTP.
-For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
-\red{inner / outer は適切か?}
-
-% Omitting Residualization
-% この段落は3章のM eのあとに、この制限の結果として...という形で入れる
-
-% There is another important feature called program residualization in \LTP.
-% It means that a generated code can be dumped into a file.
-% We can load the dumped file and run it.
-% The difficulty arises when program residualization is used with CSP.
-% Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
-
-\subsection{\LLF}
-
-% \LLF
-\LLF is a simple system of dependent types introduced in \cite{attapl}.
-\red{system / type system / calculus?}
-It is based on Edinburgh LF\cite{harper1993framework}.
-Therefore, all constants and base types are declared in the signature.
-The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.
-
-% Kind, Well-formed kind
-In addition to ordinary typing rules like simply typed lambda calculus,
-there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
-Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
-For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
-for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
-
-% Type Equality
-Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
-For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
-but they are not equivalent seemingly. Thus, we must define equivalence rules.
-In \LLF, equivalence is expressed with a symbol of $\E$.
-$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
-$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
-$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
-
-\subsection{Extending \LTP with Dependent Types}
-
-Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-From here, we use the word "stage" instead of "transition" 
-because we develop a multi-stage calculus, not a multi-transition calculus.
-\red{stageのほうが言葉としてふさわしいと言いたい}
-There are three technical points in the extension from \LTP to \LMD.
-
-\red{以下の3文をどこかに入れる必要がある}
-\red{, which is called a \textit{stage variable} in \LMD.}
-\red{ which is called a stage in \LMD.}
-\red{Although we can apply any transition to a transition abstraction in \LTP,
-	we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
-
-% Constants and Base Types
-
-First, the way of handling of constants and base types is the difference between \LMD and \LTP.
-We adopt a signature $\Sigma$ to handle constants and base types.
-This is because a signature simplifies kinding rules relating to type variables.
-A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
-For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
-\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}
-
-% Kidinding and Well-formed Kinding Rules
-
-Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
-It was lucky that almost all rules are determined easily.
-This is because multi-stage calculus and dependent types are almost orthogonal.
-\red{orthogonal は抽象的すぎるか?}
-Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
-attaching stage anotations to ones of \LLF.
-For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
-\begin{center}
-	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
-	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
-\end{center}
-
-% Equivalence Rules
-
-Third, we also need type equivalence rules in \LMD as a dependent type system.
-Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily.
-\red{design?}
-\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
-
-% Q-% rule
-
-The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
-The equivalence simple rule to handle CSP is \QCsp.
-\begin{center}
-	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
-\end{center}
-However, this rule isn't enough when the parameters of dependent types are cross-staed.
-We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
-\begin{center}
-	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-\end{center}
-\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
-
-\section{Formal Definition of \LMD}
-
-In this section, we give a formal definition of \LMD, including
-the syntax, full reduction, and type system.  In addition to full reduction,
-in which any redex at any stage can be reduced, we also give staged reduction,
-which models execution as programs.
-
-\subsection{Syntax}
-
-\AI{Rename ``type variables'' to ``type-level constants''. }
-We assume the denumerable set of type variables, ranged over by
-metavariables \(X, Y, Z\), the denumerable set of variables, ranged
-over by \(x,y,z\), the denumerable set of constants, ranged over by
-\(c\), and the denumerable set of stage variables, ranged over by
-\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
-sequences of stage variables; we write \(\varepsilon\) for the empty
-sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:
-
-\AI{``Transition'' is still used.}
-
-\begin{align*}
-    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
-    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
-    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
-    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
-    \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
-    \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
-%     \textrm{Constants}       &   &                          & c                                                                                                          \\
-    \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
-                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
-    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
-    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
-\end{align*}
-
-\AI{Add $M\,\alpha$ to terms.}
-
-\AI{Is $O$ used as a metavariable?}
-\AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
-
-% Description on meta variables
-
-% Kinds
-
-A kind, which is used to classify types, is either $*$, the kind of
-proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
-of type operators that takes $x$ as an argument of type $\tau$ and returns a type
-of kind $K$.
-% Types
-% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
-% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
-% \red{この段落は短いので型の段落と結合するか?}
-% Types
-A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
-$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
-An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
-if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
-A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
-An $\alpha$-closed type corresponds to a runnable code fragment.
-Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
-an application of a term to a dependent function type $\tau\ M$,
-a code type $\TW_{\alpha} \tau$,
-a dependent function type $\Pi x:\tau.\tau$, 
-an $\alpha$-closed type $\F\alpha.\tau$.
-Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
-
-% Terms
-
-Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
-whose type is declared in signature $\Sigma$, and the following five forms
-related to multi-stage programming:
-$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
-$\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
-$\%_\alpha M$ is an operator for cross-stage persistence.
-The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
-and applications are left-associative
-and two abstractions extends as far to the right as possible.
-For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
-
-% Signature
-
-We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
-are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
-\AI{Change Int to Bool.}
-
-% Free variables
-As usual, the variable $x$ is bound in $\lambda x:\tau.M$
-and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
-\AI{What about other binders such as $\Pi$?}
-We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
-We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
-
-% Contexts
-Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
-$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
-\AI{I'd prefer \textit{dom}.}
-The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
-$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.
-
-\AI{We should note that constants and type variables are not staged.}
-\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
-
-\subsection{Reduction}
-
-Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define two kinds of substitutions.
-Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
-$N$ for $x$ in $M$, and we omit its definition here.
-Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
-for stage variable $\alpha$ in $M$ is defined below.
-\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}
-
-\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
-\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
-
-\begin{align*}
-	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
-	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
-	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
-	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
-\end{align*}
-
-\begin{definition}[Reduction]
-  \AI{It's not clear what are defined here.  You are talking only about rules.
-    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
-	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
-	Congruence rules which are omitted from the definition.
-	\begin{align*}
-		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                       \\
-		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
-		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
-		 & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
-	\end{align*}
-	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
-\end{definition}
-
-The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
-$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
-where $\epsilon$ is substituted for the stage variable.
-Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
-There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
-% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
-
-\AI{A few examples are desirable.}
-
-\subsection{Type System}
-
-% 総論
-
-In this section, we define the type system of \LMD.
-% \LMD is little complicated because it contains dependent types.
-It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
-We list the judgments forms in Figure~\ref{fig:LMD-six-judgements}.
-\AI{equality vs. equivalence?}
-\AI{A few judgment forms do not match rules.}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			\G & \V M : \tau @ A   & \text{typing} \\
-			\G & \V \tau :: K @ A  & \text{kinding} \\
-			\G & \V K \iskind @ A  & \text{well-formed kinding} \\
-			\G & \V M \E N @ A     & \text{term equality} \\
-			\G & \V \tau \E \sigma & \text{type equality} \\
-			\G & \V K \E J @ A     & \text{kind equality}
-		\end{align*}
-		\caption{Six judgment forms of the type system of \LMD.}
-		\label{fig:LMD-six-judgements}
-	\end{center}
-\end{figure}
-
-\AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
-\begin{definition}[Typing]
-  The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
-  \AI{Precisely speaking, it cannot be defined independently of other judgments.
-  How is dependency between judgments?}
-\end{definition}
-
-\AI{``judgment'' vs. ``judgement''.}  We start from defining typing of
-\LMD.  Typing rules of \LMD are shown in Figure
-\ref{fig:typing-rules}.  The rule \TConst{} means any constants in the
-signature can appear at any stage.  \AI{This should be discussed
-  earlier.}  For example, if we have a signature $\Sigma$ which is
-$\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
-\textrm{bool}$, the derivation tree in
-Figure~\ref{fig:tconst-derivation-tree} is admissible.  \AI{Don't we
-  need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$
-  should be a well-formed type under ... what?}  The rules \TVar,
-\TAbs, and \TApp{} are almost the same as those in the simply typed
-lambda calculus.  \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}  Additional conditions are that subterms must be
-typed at the same stage (\TAbs{} and \TApp); the type
-annotation/declaration on a variable has to be a proper type of kind
-$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
-
-\begin{figure}
-	\begin{center}
-		\begin{minipage}{0.50\hsize}
-			\infer[\TConst]
-			{\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
-			{\textrm{true}:\textrm{bool} \in \Sigma \andalso
-				\ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
-			}
-			\caption{A derivation tree using \TConst}
-			\label{fig:tconst-derivation-tree}
-		\end{minipage}
-	\end{center}
-\end{figure}
-
-% \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is opposite.}
-As in standard dependent type systems, \TConv{} allows us to replace
-the type of a term with an equivalent one.  
-In a type system which includes dependent types, this kind of rule is essential
-because two types which have different shapes may be equivalent.
-For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
-
-% Typing rules for a multi-stage calculus
-\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-They are corresponding to brackets, escape, making a stage abstraction, 
-application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
-Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
-
-\begin{figure}
-	\begin{center}
-		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
-		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
-		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
-		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
-		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
-		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
-		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
-		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
-		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
-		\caption{Typing Rules.}
-		\label{fig:typing-rules}
-	\end{center}
-\end{figure}
-
-\subsubsection{Type and Term Equivalence}
-
-As usual in dependent type systems, type equivalence, used in \TConv,
-is important.  The type equivalence judgment of the form
-$\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
-are equivalent as types of kind $K$ at stage $A$ under $\G$.
-Figure~\ref{fig:type-equivalence-rules} shows the rules for type
-equivalence.  Type equivalence is basically the least congruence
-closed under term equivalence.  The rules for compatibility (closure
-under type formation) are derived from corresponding typing rules in a
-straightforward manner.  The rules are a little simpler than some
-dependent type systems \AI{such as?}  because there is no abstraction
-at the type level.
-
-% \QCsp以外の説明
-% We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
-% All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
-% \QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
-% The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
-% the results of applications are also equivalent.
-
-\begin{figure}
-	\begin{center}
-		\infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
-		\infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
-		\infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
-		\infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
-		\infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
-		\infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
-		\infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
-		\infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
-		\caption{Type Equivalence Rules.}
-		\label{fig:type-equivalence-rules}
-	\end{center}
-\end{figure}
-
-The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
-which means that terms $M$ and $N$ are equivalent as terms of type
-$\rho$ at stage $A$ under $\G$, is defined by the rules in
-Figure~\ref{fig:term-equivalence-rules}.  Most rules are
-straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
-\QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
-rules \QBeta, \QTBLTB, and \QLambda{} correspond to the reduction rules.
-\AI{Don't we give names to those reduction rules?}
-
-\begin{figure}
-	\begin{center}
-		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
-		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
-		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
-		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
-		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
-		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
-		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
-		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
-		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
-		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
-		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
-		\caption{Term Equivalence Rules.}
-		\label{fig:term-equivalence-rules}
-	\end{center}
-\end{figure}
-
-% \QPercentの説明
-The only rule that deserves elaboration is the last rule \QPercent.
-Intuitively, it means that the CSP operator applied to term $M$ can be
-removed if $M$ is also well typed at the next stage \(A\alpha\).
-For example, constants do not depend on the stage (see \TConst) and
-so \(\G\V \%_\alpha c \E c : \tau @ A\alpha\) holds but variables
-do depend on stages and so this rule does not apply.
-
-Interestingly, Hanada and Igarashi~\cite{} rejected the idea of
-reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
-in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and as we argue \AI{where?}
-it is practically significant.
-
-%%%%%%%%%%%%%%%%%%% SKIP FROM HERE %%%%%%%%%%%%%%%%%%%%
-$\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
-$\text{mulmat}$ takes two integers which are the size of the multiplicand matrix and generate a code.
-The last integer to decide the size of the multiplier matrix is given at runtime.
-You can generate code by applying two integers to $\text{mulmat}$.
-We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
-But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under a condition which is explained in the next paragraph.
-
-The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
-For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
-In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
-
-	% Example of QCsp (mulmat)
-	{
-		\begin{align*}
-			\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-			\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-			                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-		\end{align*}
-	}
-
-This kind of type equality is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
-We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
-because types of codes don't contain $\%_\alpha$ generally.
-
-%%%%%%%%%%%%%%%%%%% TO HERE %%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Staged Semantics}
-
-The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
-But we need to fix order of reduction when we implement an interpreter of \LMD and
-the order must be appropriate in terms of stages.
-
-We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
-In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
-$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
-
-\begin{definition}[Values]
-	The family $V^A$ of sets of values, ranged over by $v^A$ and 
-	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
-	are defined by following grammar. In the grammar $A \neq \epsilon$.
-	\begin{align*}
-		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
-		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                          & \\
-		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
-		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
-		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
-	\end{align*}
-\end{definition}
-
-Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
-The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
-This restriction means that the body of $Lambda$ abstraction must be evaluated before application of an $\epsilon$ stage.
-Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
-This is because $\TBL_\alpha v^\epsilon$ is a redex.
-
-\begin{definition}[Evaluation Context]
-	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
-	$A$ is nonempty. (Although $B,A'$ can be empty.)
-	$A \neq \epsilon$\\
-	\begin{align*}
-		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B     
-		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
-		\mid E^\epsilon_B\ \epsilon                                                                                                 \\
-		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
-		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
-		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
-		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B                                                   
-		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
-	\end{align*}
-\end{definition}
-
-We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.
-
-\begin{definition}[Staged Reduction]
-	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
-	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
-\end{definition}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
-			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
-			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
-		\end{align*}
-		\caption{Staged Reduction}
-		\label{fig:staged-reduction}
-	\end{center}
-\end{figure}
-
-\section{Properties of \LMD}
-
-In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
-unique decomposition of evaluation contexts, and progress.
-These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
-
-% Substitution Lemma
-
-Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
-because there are six types of judgment and two types of substitution in \LMD.
-Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
-typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
-
-\begin{lemma}[Substitution Lemma on Terms]
-	\begin{flalign*}
-		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
-	\end{flalign*}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Substitution Lemma on Stages]
-	\begin{flalign*}
-		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
-	\end{flalign*}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Inversion Lemma
-
-Following three Inversion Lemmas are needed in proving later theorems.
-Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
-They are composed of three part.
-The first part state that we can infer types of subterms.
-The second and third parts state 
-that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence.
-
-\begin{lemma}[Inversion Lemma for $\Pi$ type]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
-	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau @A$
-	\end{enumerate}
-	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\TW$ type]
-	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\Lambda$ type]
-	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Preservation
-
-Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
-Preservation ensure that any one step reduction preserves type.
-
-\begin{theorem}[Preservation]
-	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
-\end{theorem}
-
-\begin{proof}
-	First, there are three cases for $M \longrightarrow M'$.
-	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-% Strong Normalization
-
-Strong Normalization is also important property which guarantee that
-no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus.
-
-\begin{theorem}[Strong Normalization]
-	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
-	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
-\end{theorem}
-
-\begin{proof}
-	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
-	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
-\end{proof}
-
-Confluence is a property that any reduction sequences from one typed term converge.
-Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
-
-\begin{theorem}[Confluence]
-	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
-	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
-\end{theorem}
-
-\begin{proof}
-	Because we proved Strong Normalization of \LMD, 
-	we can use Newman's lemma to prove Confluence of \LMD.
-	Then, what we must show is Weak Church-Rosser Property now.
-	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
-	In short, they are never overlapped each other.
-	So, we can reduce one of them after we reduce another.
-\end{proof}
-
-Unique Decomposition ensure that
-,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it guarantee
-that the evaluation context decides a redex to reduce deterministically.
-Specifically speaking, this theorem guarantee that 
-when you write a interpreter using the evaluation context of \LMD,
-your interpreter works just as intended.
-
-\begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
-	\begin{enumerate}
-		\item $ M \in V^A$
-		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
-	\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
-Thanks to Unique Decomposition, we can prove this theorem easily.
-
-\begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-\section{Related Works}
-
-% 依存型の歴史
-
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
-
-% 依存型の応用
-
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
-
-% 多段階計算の歴史
-
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
-However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
-construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
-
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\epsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump the quoted code into an external file.
-
-% 他段階計算の機能拡張
-
-Combination of multi-stage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
-
-% 多段階計算の応用
-
-MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
-Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
-which include filtering in signal processing, matrix-vector product, and DSL compiler.
-
-% \begin{enumerate}
-% 	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
-
-% 	      CSPも入りました
-% 	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
-% 	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
-% 	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
-% 	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
-% 	\item Done: Environment classifiers\cite{taha2003environment}
-% 	\item Done: A framework for defining logics\cite{harper1993framework}
-
-% 	      $\Sigma$ の使い方を確認した
-% 	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
-% 	\item Done: Dependent types in practical programming\cite{xi1999dependent}
-
-% 	      Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。
-
-% 	\item Done: A dependently typed assembly language\cite{xi2001dependently}
-
-% 	      DTALの定義と制約solverを用いた型検査の定義
-% 	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
-% 	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
-% 	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
-% 	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
-% 	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
-% 	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
-% 	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
-% 	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
-% 	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
-% 	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
-% 	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
-% \end{enumerate}
-
-\section{Conclusions}
-
-We proposed new multi-stage calculus \LMD, which can use dependent types.
-\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
-This extention prevent some bugs relating to generated functions with multi-stage programming,
-such as \verb|vadd| function for vectors of a fixed length.
-We proved properties of \LMD including preservation, confluence, 
-strong normalization for full reduction, and progress for staged reduction.
-The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
-We resolve this problem by ignoring $\%$ under some condition.
-
-Making algorithmic typing and equality rules for \LMD is a future work.
-They would be complicated but possible 
-because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
-
-% 2つの設計手法と今回採用した理由
-% Conclusion送りか?
-% When we design type equivalence rules of \LMD, there are two design choices.
-% One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
-% Another is defining type equivalence directly by a combination of type equivalence rules.
-% We adopt the latter one because it is convenient to handle CSP in the type equivalence.
-
-% \section{First Section}
-% \subsection{A Subsection Sample}
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc. does not need an indent, either.
-% 
-% Subsequent paragraphs, however, are indented.
-% 
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-% 
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-% 
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-% 
-% 
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-% 
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-% 
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-% %
-% % the environments 'definition', 'lemma', 'proposition', 'corollary',
-% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
-% %
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\bibliographystyle{splncs04}
-\bibliography{main}
-%
-% \begin{thebibliography}{8}
-% \bibitem{ref_article1}
-% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-% 
-% \bibitem{ref_lncs1}
-% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-% 
-% \bibitem{ref_book1}
-% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-% Location (1999)
-% 
-% \bibitem{ref_proc1}
-% Author, A.-B.: Contribution title. In: 9th International Proceedings
-% on Proceedings, pp. 1--2. Publisher, Location (2010)
-% 
-% \bibitem{ref_url1}
-% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-% Oct 2017
-% \end{thebibliography}
-
-\section{Appendix}
-
-\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
-Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures.
-This category encompasses both theoretical and implementation (also known as system descriptions) papers.
-In either case, submissions should clearly identify what has been accomplished and why it is significant.
-Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity.
-System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design.
-In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
-\blue{Review Process
-	APLAS 2019 will use a lightweight double-blind reviewing process.
-Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper.
-The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
-	To facilitate this process, submitted papers must adhere to the following:
-	Author names and institutions must be omitted and
-	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
-	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
-Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas.
-For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure.
-Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would.
-For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
-\end{document}

### 2019-06-14 main.tex
Split main.tex.

--- 2019-06-13 main.tex
@@
 
-\section{Introduction}
+\input{introduction.tex}
 
-\subsection{Multi-stage Programming}
+\input{informal-overview.tex}
 
-% \subsubsection{多段階計算とは何か?}
+\input{formal-defnition.tex}
 
-Multi-stage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multi-stage programming, which are brackets, escape, and run.
-Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
-Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Escape, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, escape is supposed to use in a fragment of code, that is, escape cannot be used as an alternative of run.
-For example, the following MetaOCaml expression
+\input{properties.tex}
 
-\begin{verbatim}
-        let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
-\end{verbatim}
-evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
-\begin{verbatim}
-        run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
-\end{verbatim}
-is reduced to 3.
+\input{related-work.tex}
 
-% \subsubsection{CSPに関する補足説明}
-
-Cross-stage Persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
-This is an example of CSP.
-\begin{verbatim}
-        let plusone = fun x -> x + 1 in
-        let y = plusone 2 in  .< y >.
-\end{verbatim}
-This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
-This is because the variable \verb|y| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|y| is embedded after it was calculated.
-CSP is very important when we write practical programs 
-because CSP enables us to use library functions in code fragments as in \verb|.<List.combine [1;2] ['a';'b']>.|.
-
-% \subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}
-
-The main application of multi-stage calculi is program optimization.
-A famous example is power functions.
-Usual power functions take two arguments, which are the base and the exponent.
-We can make a specialized power function for given exponents with multi-stage programming and 
-optimize them by unrolling a loop in functions for given exponents.
-The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
-\verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
-Multi-stage programming can optimize functions which take more than two arguments 
-by generating a code fragment optimized to a given argument.
-
-% \subsubsection{ベクトル計算も高速化できる}
-
-Multi-stage programming can also optimize vector calculation.
-For example, \verb|vadd| function, which takes two vectors and return the sum of them,
-is implemented with a loop in many cases.
-We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
-\red{MetaOCamlで書いた長さ付きベクトルの例?}
-
-% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
-
-However, there is a sever problem in functions which are optimized by multi-stage programming.
-Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
-For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
-Otherwise, we will get a Segmentation Fault error.
-This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
-
-% We call this problem \red{Specialized Code Problem}.
-
-\subsection{Dependent Types}
-
-% \subsubsection{依存型とは何か?}
-
-Dependent types are types which is dependent on values.
-We can use dependent types for securer programming.
-For example, we can realize vectors with their sizes with them.
-\begin{verbatim}
-        Vector :: Int -> *
-\end{verbatim}
-\verb|Vector| is a type constor which takes the length of vectors, that is, 
-\verb|Vector 3| is a type for vectors whose lengths are 3.
-If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n|,
-we can confirm the two arguments of \verb|vadd| function has the same length.
-\red{secure programming? finer grained typing? とか}
-
-\subsection{Multi-stage Programming with Dependent Types}
-\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
-
-% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
-
-As we pointed out in the above section,
-functions optimized with multi-stage programming can take only restricted values as arguments.
-When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
-We introduce dependent types into a multi-stage calculus
-so that the type system can guarantee optimized functions are used properly.
-
-In this paper, we design new multi-stage calculus \LMD by 
-merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
-\LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming more safer with the power of dependent types.
-
-\subsection{Organization of the Paper}
-
-The organization of this paper is the following.
-Section 2 gives an informal overview of \LMD.
-Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
-Section 4 shows the properties of \LMD including Unique Decomposition.
-Section 5 discusses future works.
-Finally, Section 6 discusses related works.
-\AI{Use $\backslash$label and $\backslash$ref!}
-\AI{``Related work'' and ``future work'' (they are uncountable).}
-
-\section{Informal Overview of \LMD}
-
-We designed \LMD, a multi-stage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP and
-we introduced dependent types based on \LTP\cite{attapl}.
-In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
-
-\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
-\subsection{\LTP}
-
-% quote and unquote
-
-\LTP\cite{Hanada2014} is a multi-stage calculus with CSP by Hanada and Igarashi.
-In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
-The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
-The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
-% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
-\begin{align*}
-	\TBL_\alpha (\TB_\alpha M) \longrightarrow M 
-\end{align*}
-It means escape cancels brackets.
-% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
-% \red{この文はここに来るべきなのか? LTPの説明ではないが}
-
-% transition variable and transition
-
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
-a sequence of transition variables is called \textit{transition}.
-The empty transition is represented by $\epsilon$.
-They are used to show the thickness of brackets.
-For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
-becomes $(\lambda x:\I.x+10)$ after it was run it twice.
-\red{run twiceは表現が微妙}
-
-% transition abstraction and application
-
-There are abstractions for transition variables and applications for transition abstraction in \LTP.
-They look like $\Lambda\alpha.M$ and $M A$, respectively.
-A transition abstraction binds a transition variable in a term.
-For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural there is a reduction rule for transition application in \LTP.
-The rule is the following.
-\begin{align*}
-	(\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
-\end{align*}
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
-
-% transition-related symbols disappear when the empty transition is substituted.
-% In short, about "run"
-
-Another important rule about a transition variable is 
-that symbols with transition variables disappear 
-when the empty transition $\epsilon$ is substituted to the transition variable.
-The purpose of this rule is express \verb|run| without any special symbol.
-In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
-For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.
-
-% transition in typing rules
-
-A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-A transition in a judgement represents where the judgement is true.
-For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
-term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
-Especially, terms without quoting exist at the empty transition $\epsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
-$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
-Terefore, transitions appear in typing rules, too.
-\begin{center}
-	\infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
-	\infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
-\end{center}
-\TTB, corresponding to brackets, means 
-if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
-\TTBL\ is converse of \TTB.
-
-% CSP
-
-CSP, cross-stage persistence, is an important feature of \LTP.
-It enables us to embed value at an outer transition into an inner transition.
-$\%$ is dedicated to CSP in \LTP.
-For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
-\red{inner / outer は適切か?}
-
-% Omitting Residualization
-% この段落は3章のM eのあとに、この制限の結果として...という形で入れる
-
-% There is another important feature called program residualization in \LTP.
-% It means that a generated code can be dumped into a file.
-% We can load the dumped file and run it.
-% The difficulty arises when program residualization is used with CSP.
-% Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.
-
-\subsection{\LLF}
-
-% \LLF
-\LLF is a simple system of dependent types introduced in \cite{attapl}.
-\red{system / type system / calculus?}
-It is based on Edinburgh LF\cite{harper1993framework}.
-Therefore, all constants and base types are declared in the signature.
-The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.
-
-% Kind, Well-formed kind
-In addition to ordinary typing rules like simply typed lambda calculus,
-there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
-Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
-For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
-for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
-
-% Type Equality
-Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
-For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
-but they are not equivalent seemingly. Thus, we must define equivalence rules.
-In \LLF, equivalence is expressed with a symbol of $\E$.
-$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
-$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
-$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
-
-\subsection{Extending \LTP with Dependent Types}
-
-Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-From here, we use the word "stage" instead of "transition" 
-because we develop a multi-stage calculus, not a multi-transition calculus.
-\red{stageのほうが言葉としてふさわしいと言いたい}
-There are three technical points in the extension from \LTP to \LMD.
-
-\red{以下の3文をどこかに入れる必要がある}
-\red{, which is called a \textit{stage variable} in \LMD.}
-\red{ which is called a stage in \LMD.}
-\red{Although we can apply any transition to a transition abstraction in \LTP,
-	we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
-
-% Constants and Base Types
-
-First, the way of handling of constants and base types is the difference between \LMD and \LTP.
-We adopt a signature $\Sigma$ to handle constants and base types.
-This is because a signature simplifies kinding rules relating to type variables.
-A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
-For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
-\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}
-
-% Kidinding and Well-formed Kinding Rules
-
-Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
-It was lucky that almost all rules are determined easily.
-This is because multi-stage calculus and dependent types are almost orthogonal.
-\red{orthogonal は抽象的すぎるか?}
-Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
-attaching stage anotations to ones of \LLF.
-For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
-\begin{center}
-	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
-	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
-\end{center}
-
-% Equivalence Rules
-
-Third, we also need type equivalence rules in \LMD as a dependent type system.
-Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily.
-\red{design?}
-\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
-
-% Q-% rule
-
-The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
-The equivalence simple rule to handle CSP is \QCsp.
-\begin{center}
-	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
-\end{center}
-However, this rule isn't enough when the parameters of dependent types are cross-staed.
-We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
-\begin{center}
-	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-\end{center}
-\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
-
-\section{Formal Definition of \LMD}
-
-In this section, we give a formal definition of \LMD, including
-the syntax, full reduction, and type system.  In addition to full reduction,
-in which any redex at any stage can be reduced, we also give staged reduction,
-which models execution as programs.
-
-\subsection{Syntax}
-
-\AI{Rename ``type variables'' to ``type-level constants''. }
-We assume the denumerable set of type variables, ranged over by
-metavariables \(X, Y, Z\), the denumerable set of variables, ranged
-over by \(x,y,z\), the denumerable set of constants, ranged over by
-\(c\), and the denumerable set of stage variables, ranged over by
-\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
-sequences of stage variables; we write \(\varepsilon\) for the empty
-sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:
-
-\AI{``Transition'' is still used.}
-
-\begin{align*}
-    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
-    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
-    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
-    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
-    \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
-    \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
-%     \textrm{Constants}       &   &                          & c                                                                                                          \\
-    \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
-                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
-    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
-    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
-\end{align*}
-
-\AI{Add $M\,\alpha$ to terms.}
-
-\AI{Is $O$ used as a metavariable?}
-\AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
-
-% Description on meta variables
-
-% Kinds
-
-A kind, which is used to classify types, is either $*$, the kind of
-proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
-of type operators that takes $x$ as an argument of type $\tau$ and returns a type
-of kind $K$.
-% Types
-% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
-% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
-% \red{この段落は短いので型の段落と結合するか?}
-% Types
-A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
-$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
-An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
-if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
-A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
-An $\alpha$-closed type corresponds to a runnable code fragment.
-Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
-an application of a term to a dependent function type $\tau\ M$,
-a code type $\TW_{\alpha} \tau$,
-a dependent function type $\Pi x:\tau.\tau$, 
-an $\alpha$-closed type $\F\alpha.\tau$.
-Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
-
-% Terms
-
-Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
-whose type is declared in signature $\Sigma$, and the following five forms
-related to multi-stage programming:
-$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
-$\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
-$\%_\alpha M$ is an operator for cross-stage persistence.
-The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
-and applications are left-associative
-and two abstractions extends as far to the right as possible.
-For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
-
-% Signature
-
-We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
-are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
-\AI{Change Int to Bool.}
-
-% Free variables
-As usual, the variable $x$ is bound in $\lambda x:\tau.M$
-and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
-\AI{What about other binders such as $\Pi$?}
-We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
-We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
-
-% Contexts
-Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
-$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
-\AI{I'd prefer \textit{dom}.}
-The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
-$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.
-
-\AI{We should note that constants and type variables are not staged.}
-\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
-
-\subsection{Reduction}
-
-Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define two kinds of substitutions.
-Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
-$N$ for $x$ in $M$, and we omit its definition here.
-Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
-for stage variable $\alpha$ in $M$ is defined below.
-\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}
-
-\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
-\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
-
-\begin{align*}
-	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
-	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
-	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
-	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
-\end{align*}
-
-\begin{definition}[Reduction]
-  \AI{It's not clear what are defined here.  You are talking only about rules.
-    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
-	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
-	Congruence rules which are omitted from the definition.
-	\begin{align*}
-		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                       \\
-		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
-		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
-		 & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
-	\end{align*}
-	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
-\end{definition}
-
-The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
-$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
-where $\epsilon$ is substituted for the stage variable.
-Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
-There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
-% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
-
-\AI{A few examples are desirable.}
-
-\subsection{Type System}
-
-% 総論
-
-In this section, we define the type system of \LMD.
-% \LMD is little complicated because it contains dependent types.
-It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
-We list the judgments forms in Figure~\ref{fig:LMD-six-judgements}.
-\AI{equality vs. equivalence?}
-\AI{A few judgment forms do not match rules.}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			\G & \V M : \tau @ A   & \text{typing} \\
-			\G & \V \tau :: K @ A  & \text{kinding} \\
-			\G & \V K \iskind @ A  & \text{well-formed kinding} \\
-			\G & \V M \E N @ A     & \text{term equality} \\
-			\G & \V \tau \E \sigma & \text{type equality} \\
-			\G & \V K \E J @ A     & \text{kind equality}
-		\end{align*}
-		\caption{Six judgment forms of the type system of \LMD.}
-		\label{fig:LMD-six-judgements}
-	\end{center}
-\end{figure}
-
-\AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
-\begin{definition}[Typing]
-  The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
-  \AI{Precisely speaking, it cannot be defined independently of other judgments.
-  How is dependency between judgments?}
-\end{definition}
-
-\AI{``judgment'' vs. ``judgement''.}  We start from defining typing of
-\LMD.  Typing rules of \LMD are shown in Figure
-\ref{fig:typing-rules}.  The rule \TConst{} means any constants in the
-signature can appear at any stage.  \AI{This should be discussed
-  earlier.}  For example, if we have a signature $\Sigma$ which is
-$\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
-\textrm{bool}$, the derivation tree in
-Figure~\ref{fig:tconst-derivation-tree} is admissible.  \AI{Don't we
-  need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$
-  should be a well-formed type under ... what?}  The rules \TVar,
-\TAbs, and \TApp{} are almost the same as those in the simply typed
-lambda calculus.  \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}  Additional conditions are that subterms must be
-typed at the same stage (\TAbs{} and \TApp); the type
-annotation/declaration on a variable has to be a proper type of kind
-$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
-
-\begin{figure}
-	\begin{center}
-		\begin{minipage}{0.50\hsize}
-			\infer[\TConst]
-			{\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
-			{\textrm{true}:\textrm{bool} \in \Sigma \andalso
-				\ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
-			}
-			\caption{A derivation tree using \TConst}
-			\label{fig:tconst-derivation-tree}
-		\end{minipage}
-	\end{center}
-\end{figure}
-
-% \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is opposite.}
-As in standard dependent type systems, \TConv{} allows us to replace
-the type of a term with an equivalent one.  
-In a type system which includes dependent types, this kind of rule is essential
-because two types which have different shapes may be equivalent.
-For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
-
-% Typing rules for a multi-stage calculus
-\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-They are corresponding to brackets, escape, making a stage abstraction, 
-application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
-Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
-
-\begin{figure}
-	\begin{center}
-		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
-		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
-		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
-		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
-		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
-		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
-		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
-		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
-		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
-		\caption{Typing Rules.}
-		\label{fig:typing-rules}
-	\end{center}
-\end{figure}
-
-\subsubsection{Type and Term Equivalence}
-
-As usual in dependent type systems, type equivalence, used in \TConv,
-is important.  The type equivalence judgment of the form
-$\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
-are equivalent as types of kind $K$ at stage $A$ under $\G$.
-Figure~\ref{fig:type-equivalence-rules} shows the rules for type
-equivalence.  Type equivalence is basically the least congruence
-closed under term equivalence.  The rules for compatibility (closure
-under type formation) are derived from corresponding typing rules in a
-straightforward manner.  The rules are a little simpler than some
-dependent type systems \AI{such as?}  because there is no abstraction
-at the type level.
-
-% \QCsp以外の説明
-% We show type equivalence rules in Figure \ref{fig:type-equivalence-rules}.
-% All rules except \QTRefl, \QTSym, \QTTrans, and \QTApp\ are generated naturally from the typing rules.
-% \QTRefl, \QTSym, \QTTrans\ exist in order to make the type equivalence relation an equivalence relationship.
-% The rule \QTApp\ means that if there are two equivalent $\Pi$ type and two equivalent terms,
-% the results of applications are also equivalent.
-
-\begin{figure}
-	\begin{center}
-		\infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
-		\infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
-		\infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
-		\infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
-		\infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
-		\infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
-		\infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
-		\infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
-		\caption{Type Equivalence Rules.}
-		\label{fig:type-equivalence-rules}
-	\end{center}
-\end{figure}
-
-The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
-which means that terms $M$ and $N$ are equivalent as terms of type
-$\rho$ at stage $A$ under $\G$, is defined by the rules in
-Figure~\ref{fig:term-equivalence-rules}.  Most rules are
-straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
-\QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
-rules \QBeta, \QTBLTB, and \QLambda{} correspond to the reduction rules.
-\AI{Don't we give names to those reduction rules?}
-
-\begin{figure}
-	\begin{center}
-		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
-		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
-		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
-		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
-		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
-		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
-		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
-		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
-		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
-		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
-		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
-		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
-		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
-		\caption{Term Equivalence Rules.}
-		\label{fig:term-equivalence-rules}
-	\end{center}
-\end{figure}
-
-% \QPercentの説明
-The only rule that deserves elaboration is the last rule \QPercent.
-Intuitively, it means that the CSP operator applied to term $M$ can be
-removed if $M$ is also well typed at the next stage \(A\alpha\).
-For example, constants do not depend on the stage (see \TConst) and
-so \(\G\V \%_\alpha c \E c : \tau @ A\alpha\) holds but variables
-do depend on stages and so this rule does not apply.
-
-Interestingly, Hanada and Igarashi~\cite{} rejected the idea of
-reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
-in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and as we argue \AI{where?}
-it is practically significant.
-
-%%%%%%%%%%%%%%%%%%% SKIP FROM HERE %%%%%%%%%%%%%%%%%%%%
-$\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
-$\text{mulmat}$ takes two integers which are the size of the multiplicand matrix and generate a code.
-The last integer to decide the size of the multiplier matrix is given at runtime.
-You can generate code by applying two integers to $\text{mulmat}$.
-We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
-But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under a condition which is explained in the next paragraph.
-
-The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
-For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
-In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
-
-	% Example of QCsp (mulmat)
-	{
-		\begin{align*}
-			\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-			\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-			                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-		\end{align*}
-	}
-
-This kind of type equality is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
-We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
-because types of codes don't contain $\%_\alpha$ generally.
-
-%%%%%%%%%%%%%%%%%%% TO HERE %%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Staged Semantics}
-
-The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
-But we need to fix order of reduction when we implement an interpreter of \LMD and
-the order must be appropriate in terms of stages.
-
-We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
-In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
-$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
-
-\begin{definition}[Values]
-	The family $V^A$ of sets of values, ranged over by $v^A$ and 
-	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
-	are defined by following grammar. In the grammar $A \neq \epsilon$.
-	\begin{align*}
-		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
-		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                          & \\
-		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
-		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
-		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
-	\end{align*}
-\end{definition}
-
-Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
-The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
-This restriction means that the body of $Lambda$ abstraction must be evaluated before application of an $\epsilon$ stage.
-Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
-This is because $\TBL_\alpha v^\epsilon$ is a redex.
-
-\begin{definition}[Evaluation Context]
-	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
-	$A$ is nonempty. (Although $B,A'$ can be empty.)
-	$A \neq \epsilon$\\
-	\begin{align*}
-		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B     
-		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
-		\mid E^\epsilon_B\ \epsilon                                                                                                 \\
-		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
-		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
-		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
-		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B                                                   
-		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
-	\end{align*}
-\end{definition}
-
-We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.
-
-\begin{definition}[Staged Reduction]
-	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
-	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
-\end{definition}
-
-\begin{figure}
-	\begin{center}
-		\begin{align*}
-			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
-			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
-			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
-		\end{align*}
-		\caption{Staged Reduction}
-		\label{fig:staged-reduction}
-	\end{center}
-\end{figure}
-
-\section{Properties of \LMD}
-
-In this section, we prove some properties of \LMD: preservation, strong normalization, confluence,
-unique decomposition of evaluation contexts, and progress.
-These theorem show that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
-
-% Substitution Lemma
-
-Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
-because there are six types of judgment and two types of substitution in \LMD.
-Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
-typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
-
-\begin{lemma}[Substitution Lemma on Terms]
-	\begin{flalign*}
-		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
-	\end{flalign*}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Substitution Lemma on Stages]
-	\begin{flalign*}
-		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
-		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
-	\end{flalign*}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Inversion Lemma
-
-Following three Inversion Lemmas are needed in proving later theorems.
-Inversion Lemmas enable us to infer types of subterms of a term from the type of the term.
-They are composed of three part.
-The first part state that we can infer types of subterms.
-The second and third parts state 
-that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence.
-
-\begin{lemma}[Inversion Lemma for $\Pi$ type]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
-	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$
-		\item $\G ,x:\sigma@A\V M:\tau @A$
-	\end{enumerate}
-	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$
-		\item $\G \V \sigma \E \sigma' : K @A$
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\TW$ type]
-	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$
-		      \item $\G @A\V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-\begin{theorem}[Inversion Lemma for $\Lambda$ type]
-	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$
-		      \item $\G \V \tau \E \tau' : K @A$
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
-
-\begin{proof}
-	Straightforward induction on derivations.
-\end{proof}
-
-% Preservation
-
-Thanks to Substitution Lemmas and Inversion Lemma, we can prove Preservation easily.
-Preservation ensure that any one step reduction preserves type.
-
-\begin{theorem}[Preservation]
-	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
-\end{theorem}
-
-\begin{proof}
-	First, there are three cases for $M \longrightarrow M'$.
-	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-% Strong Normalization
-
-Strong Normalization is also important property which guarantee that
-no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus.
-
-\begin{theorem}[Strong Normalization]
-	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
-	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
-\end{theorem}
-
-\begin{proof}
-	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
-	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
-\end{proof}
-
-Confluence is a property that any reduction sequences from one typed term converge.
-Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
-
-\begin{theorem}[Confluence]
-	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
-	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
-\end{theorem}
-
-\begin{proof}
-	Because we proved Strong Normalization of \LMD, 
-	we can use Newman's lemma to prove Confluence of \LMD.
-	Then, what we must show is Weak Church-Rosser Property now.
-	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
-	In short, they are never overlapped each other.
-	So, we can reduce one of them after we reduce another.
-\end{proof}
-
-Unique Decomposition ensure that
-,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it guarantee
-that the evaluation context decides a redex to reduce deterministically.
-Specifically speaking, this theorem guarantee that 
-when you write a interpreter using the evaluation context of \LMD,
-your interpreter works just as intended.
-
-\begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
-	\begin{enumerate}
-		\item $ M \in V^A$
-		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
-	\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
-Thanks to Unique Decomposition, we can prove this theorem easily.
-
-\begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
-\end{theorem}
-
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
-
-\section{Related Works}
-
-% 依存型の歴史
-
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
-
-% 依存型の応用
-
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
-
-% 多段階計算の歴史
-
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
-However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
-construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
-
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\epsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump the quoted code into an external file.
-
-% 他段階計算の機能拡張
-
-Combination of multi-stage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
-
-% 多段階計算の応用
-
-MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
-Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
-which include filtering in signal processing, matrix-vector product, and DSL compiler.
+\input{conclusions.tex}
 
@@
 % \end{enumerate}
-
-\section{Conclusions}
-
-We proposed new multi-stage calculus \LMD, which can use dependent types.
-\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
-This extention prevent some bugs relating to generated functions with multi-stage programming,
-such as \verb|vadd| function for vectors of a fixed length.
-We proved properties of \LMD including preservation, confluence, 
-strong normalization for full reduction, and progress for staged reduction.
-The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
-We resolve this problem by ignoring $\%$ under some condition.
-
-Making algorithmic typing and equality rules for \LMD is a future work.
-They would be complicated but possible 
-because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
 

### 2019-06-14 properties.tex
Split main.tex.

\section{Properties of \LMD}

In this section, we prove \AI{use ``show'' because we omit proofs from the paper} basic properties of \LMD: preservation, strong normalization, confluence, and progress.
These theorem shows that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
\AI{In this setting, a simple type system is already sufficient to guarantee
  ``a well-typed term never goes wrong.''  If the language has
  case analysis that uses dependent types, then
  we could say more.
}

% Substitution Lemma

Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
because there are six types of judgment and two types of substitution in \LMD.
Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.

\begin{lemma}[Substitution Lemma on Terms]
	\begin{flalign*}
		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
	\end{flalign*}
\end{lemma}

\AI{Since the order of variable declarations is significant,
  we cannot assume $z$ is always declared at the end.}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}

\begin{theorem}[Substitution Lemma on Stages]
	\begin{flalign*}
		\text{If\ } \G \V M:\tau @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V \tau::K @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V K\iskind @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V M\E N : \tau @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V \tau\E \sigma : K @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V K\E J @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
	\end{flalign*}
\end{theorem}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}

% Inversion Lemma

The following three Inversion Lemmas are needed to prove main theorems.
As usual~\cite{TAPL}, Inversion Lemmas enable us to infer the types of subterms of a term from the type of the term.
They are composed of three parts.
The first part states that we can infer types of subterms.
The second and third parts state 
that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
We need both of the second and the third because of the reflexivity of the type equivalence. \AI{Symmetry?  We can omit the third one.}

\begin{lemma}[Inversion Lemma for $\Pi$-types]
	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
	\begin{enumerate}
		\item $\G \V \sigma \E \sigma'@A$ and
		\item $\G ,x:\sigma@A\V M:\tau @A$.
	\end{enumerate}
	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
	\begin{enumerate}
		\item $\rho = \Pi x:\sigma'.\tau'$,
		\item $\G \V \sigma \E \sigma' : K @A$, and
		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$.
	\end{enumerate}
	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
	\begin{enumerate}
		\item $\rho = \Pi x:\sigma'.\tau'$,
		\item $\G \V \sigma \E \sigma' : K @A$, and
		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$.
	\end{enumerate}
\end{lemma}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}

\begin{theorem}[Inversion Lemma for $\TW$-types]
	\begin{item}
	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
	      \begin{enumerate}
		      \item $\rho = \TW_\alpha \tau'$ and
		      \item $\G @A\V \tau \E \tau' : K @A$.
	      \end{enumerate}
	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
	      \begin{enumerate}
		      \item $\rho = \TW_\alpha \tau'$ and
		      \item $\G @A\V \tau \E \tau' : K @A$.
	      \end{enumerate}
	\end{item}
\end{theorem}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}

\begin{theorem}[Inversion Lemma for $\forall$-types]
	\begin{item}
	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
	      \begin{enumerate}
		      \item $\rho = \forall\alpha.\tau'$ and
		      \item $\G \V \tau \E \tau' : K @A$.
	      \end{enumerate}
	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
	      \begin{enumerate}
		      \item $\rho = \forall\alpha.\tau'$ and
		      \item $\G \V \tau \E \tau' : K @A$.
	      \end{enumerate}
	\end{item}
\end{theorem}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}

% Preservation

Thanks to Substitution Lemmas and Inversion Lemmas, we can prove Preservation easily.
Preservations ensure that any one step reduction preserves type.

\begin{theorem}[Preservation]
	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$.
\end{theorem}

\begin{proof}
	First, there are three cases for $M \longrightarrow M'$.
	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
	For each case, we can use straightforward induction on derivations.
	Difficult cases are \TApp, \TTBL, and \TIns.
	We need Inversion Lemmas for them.
\end{proof}

% Strong Normalization

Strong Normalization is also important property which guarantee that
no typed term has an infinite reduction sequence.
We prove this thorem by translating \LMD to the symply typed lambda calculus.

\begin{theorem}[Strong Normalization]
	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$.
\end{theorem}

\begin{proof}
	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
\end{proof}

Confluence is a property that any reduction sequences from one typed term converge.
Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.

\begin{theorem}[Confluence]
	For any term $M$, if $M \longrightarrow^* M'$ and $M \longrightarrow^* M''$ then
	there exists $M'''$ that satisfies $M' \longrightarrow^* M'''$ and $M'' \longrightarrow^* M'''$.
\end{theorem}

\begin{proof}
	Because we proved Strong Normalization of \LMD, 
	we can use Newman's lemma to prove Confluence of \LMD.
	Then, what we must show is Weak Church-Rosser Property now.
	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
	In short, they are never overlapped each other.
	So, we can reduce one of them after we reduce another.
\end{proof}

Unique Decomposition ensure that
,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
This theorem is important because it guarantee
that the evaluation context decides a redex to reduce deterministically.
Specifically speaking, this theorem guarantee that 
when you write a interpreter using the evaluation context of \LMD,
your interpreter works just as intended.

\begin{theorem}[Unique Decomposition]
	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then either
	\begin{enumerate}
		\item $ M \in V^A$, or
		\item there exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$ with $B = \epsilon$ or $B = \beta$ for some $\beta$.
	\end{enumerate}
\end{theorem}

\begin{proof}
	We can prove by straightforward induction on derivations.
	Difficult cases are \TApp, \TTBL, and \TIns.
	We need Inversion Lemmas for them.
\end{proof}

Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
Thanks to Unique Decomposition, we can prove this theorem easily.

\begin{theorem}[Progress]
	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
\end{theorem}

\begin{proof}
	We can prove by straightforward induction on derivations.
	Difficult cases are \TApp, \TTBL, and \TIns.
	We need Inversion Lemmas for them.
\end{proof}

\AI{Explain the condition on $\G$.}

### 2019-06-14 related-work.tex
Split main.tex.

\section{Related Work}

% 依存型の歴史

There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
In Advanced Topics in Types and Programming Languages\cite{attapl},
a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
We adopted \cite{attapl}-like dependent types for \LMD.

One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}

% 依存型の応用

Applications of dependent types for real problems were also researched.
In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
and succeeded in reducing the bounds checking of arrays.
In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
it is useful for spped up.
Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.

% 多段階計算の歴史

\red{Besides,} multi-stage calculi also have a long history of research.
Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
However, $\lambda^\circ$ don't have operators for run and CSP.
\red{runはboldか? Besidesより適切な接続詞はないのか?}
Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.

In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
show that run can be represented as application of $\epsilon$ to transition abstractions.
In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
which allows us to dump the quoted code into an external file.

% 他段階計算の機能拡張

Combination of multi-stage programming and another programming feature has been studied.
Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.

% 多段階計算の応用

MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
which include filtering in signal processing, matrix-vector product, and DSL compiler.

### 2019-06-14 text/informal-overview.tex
分割コンパイルが失敗する

--- 2019-06-14 informal-overview.tex
@@
+% !TEX root = ../main.tex
+
 \section{Informal Overview of \LMD}
@@
 
-\red{以下の3文をどこかに入れる必要がある}
-\red{, which is called a \textit{stage variable} in \LMD.}
-\red{ which is called a stage in \LMD.}
-\red{Although we can apply any transition to a transition abstraction in \LTP,
-	we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
-
 % Constants and Base Types
 
-First, the way of handling of constants and base types is the difference between \LMD and \LTP.
-We adopt a signature $\Sigma$ to handle constants and base types.
+First, the way of handling of constants and type-level constants is the difference between \LMD and \LTP.
+We adopt a signature $\Sigma$ to handle constants and type-level constants.
 This is because a signature simplifies kinding rules relating to type variables.
@@
 
-Third, we also need type equivalence rules in \LMD as a dependent type system.
+Third, we also need type equivalence rules in \LMD because its type system contains dependent types.
+For example, vadd function, which takes a length of vector and returns addition function for vectors with the length, is following.
+\newcommand{\M}{\textrm{M}}
+\newcommand{\I}{\textrm{Int}}
+\newcommand{\Vn}{\text{Vector}\ (\%_\alpha n)}
+\begin{align*}
+	  & \textbf{let}\ \text{vadd}_1 : \Pi n:\I.\TW_\alpha\Vn\to\TW_\alpha\Vn\to\TW_\alpha\Vn                 \\
+	  & \hspace{7mm} = \textbf{fix}\ f.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vn.\ \lambda v_2:\TW_\alpha\Vn. \\
+	  & \hspace{14mm} \textbf{if}\ n = 0                                                                     \\
+	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                    \\
+	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                            \\
+	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                        \\
+	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                        \\
+	  & \hspace{21mm} \text{cons}\ (\text{head}\ t_1 + \text{head}\ t_2) (\TBL_\alpha f\ (n-1)\ t_1\ t_2))   \\
+\end{align*}
+\begin{align*}
+	  & \textbf{let}\ \text{vadd}_\alpha : \Pi n:\I.\TW_\alpha(\Vn\to\Vn\to\Vn)                                                                      \\
+	  & \hspace{7mm} = \lambda n:\I.\TB_\alpha (\lambda v_1:\Vn.\ \lambda v_2:\Vn. \TBL_\alpha \text{vadd}_1\ n\ (\TB_\alpha v_1)\ (\TB_\alpha v_2)) \\
+\end{align*}
 Although there are new primitives relating to stages which aren't in \LLF,

### 2019-06-14 text/informal-overview.tex
Fix a bug.
Add the example of vadd function to Section 2.

@@
 Third, we also need type equivalence rules in \LMD because its type system contains dependent types.
-For example, vadd function, which takes a length of vector and returns addition function for vectors with the length, is following.
-\newcommand{\M}{\textrm{M}}
-\newcommand{\I}{\textrm{Int}}
-\newcommand{\Vn}{\text{Vector}\ (\%_\alpha n)}
+Although there are new primitives relating to stages which aren't in \LLF,
+we can design all rules except \QPercent\ easily from the syntax or the reductions of \LMD.
+
+\QPercent\ is different from other rules because it was designed from practical reason, not from the syntax or the reductions.
+For example, we discuss $\text{vadd}_\beta$ function,
+which takes a length of vector and returns addition function for vectors with the length.
+$\text{vadd}_1$ is a helper function to make $\text{vadd}$, 
+which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
+\newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
 \begin{align*}
-	  & \textbf{let}\ \text{vadd}_1 : \Pi n:\I.\TW_\alpha\Vn\to\TW_\alpha\Vn\to\TW_\alpha\Vn                 \\
-	  & \hspace{7mm} = \textbf{fix}\ f.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vn.\ \lambda v_2:\TW_\alpha\Vn. \\
+	  & \textbf{let}\ \text{vadd}_1 : \F\alpha.\Pi n:\I.\TW_\alpha\Vpn\to\TW_\alpha\Vpn\to\TW_\alpha\Vpn                 \\
+	  & \hspace{7mm} = \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn. \\
 	  & \hspace{14mm} \textbf{if}\ n = 0                                                                     \\
@@
 \end{align*}
+Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.
+This function takes the length of vectors and returns a quoted add function for vector of the given size.
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta n)}
 \begin{align*}
-	  & \textbf{let}\ \text{vadd}_\alpha : \Pi n:\I.\TW_\alpha(\Vn\to\Vn\to\Vn)                                                                      \\
-	  & \hspace{7mm} = \lambda n:\I.\TB_\alpha (\lambda v_1:\Vn.\ \lambda v_2:\Vn. \TBL_\alpha \text{vadd}_1\ n\ (\TB_\alpha v_1)\ (\TB_\alpha v_2)) \\
+	  & \textbf{let}\ \text{vadd}: \Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)          \\ 
+	  & \hspace{7mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
+	  & \hspace{63mm} \TBL_\beta \text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))      \\
 \end{align*}
-Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily.
-\red{design?}
-\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 10)}
+When we use this function, we need to instantiate $\text{vadd}$ with a length.
+If we instantiate it with a integer 10, we get function $\text{vadd10}$ whose type is \\
+$\text{vadd10}: \F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
+This function is difficult to use because its type contains $\Vpn$.
+In most cases, we have vectors of type $\text{Vector}\ 10$, not $\Vpn$.
+Therefore, we want to identify $\text{Vector}\ 10$ and $\Vpn$.
 
-% Q-% rule
-
-The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
-The equivalence simple rule to handle CSP is \QCsp.
-\begin{center}
-	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
-\end{center}
-However, this rule isn't enough when the parameters of dependent types are cross-staed.
-We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
+In order to resolve this problem, we introduced \QPercent into \LMD.
+\QPercent\ enables us to identify $\text{Vector}\ 10$ and $\Vpn$.
+This rule says that if term $M$ has the same type at stage $A\alpha$ and $A$,
+we can assume $\%_\alpha M \E M$ which roughly means $\%_\alpha M$ and $M$ are equivalent.
+With this rule, we can identify $10$ and $\%_\beta 10$ and use $\text{vadd}$ to many vectors.
 \begin{center}
@@
 \end{center}
-\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}

### 2019-06-14 text/informal-overview.tex
Wrote a note on n=0.

@@
 which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
+We assumed that type checker can know $n=0$ when process the $\textbf{then}$ clause.
 \newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
@@
 	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                                                   \\
-	  & \hspace{21mm} \text{cons}\ (\text{head}\ t_1 + \text{head}\ t_2) (\TBL_\alpha f\ (n-1)\ t_1\ t_2))   \\
+	  & \hspace{21mm} \text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2)) \\
 \end{align*}
@@
 
-In order to resolve this problem, we introduced \QPercent into \LMD.
+In order to resolve this problem, we introduced \QPercent\ into \LMD.
 \QPercent\ enables us to identify $\text{Vector}\ 10$ and $\Vpn$.

### 2019-06-14 text/formal-defnition.tex
分割コンパイルが失敗する
type variable -> type-level constant

--- 2019-06-14 formal-defnition.tex
@@
+% !TEX root = ../main.tex
+
 \section{Formal Definition of \LMD}
@@
 \AI{Rename ``type variables'' to ``type-level constants''. }
-We assume the denumerable set of type variables, ranged over by
+We assume the denumerable set of type-level constants, ranged over by
 metavariables \(X, Y, Z\), the denumerable set of variables, ranged
@@
 % Types
-A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
+A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
 an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
@@
 An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
-if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
+if type-level constant $\text{Vector}$ has the kind $\Pi x:\I.*$.
 A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
@@
 
-We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
+We adopt a \LLF-like system, where constants and type-level constants for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
 are a sequence of declarations of the form $c:\tau$ and $X:K$.
@@
 
-\AI{We should note that constants and type variables are not staged.}
+\AI{We should note that constants and type-level constants are not staged.}
 \paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}

### 2019-06-14 text/formal-defnition.tex
epsilon -> varepsilon.

@@
     \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
-                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
+                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \varepsilon \mid \%_\alpha M                          \\  
     \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
@@
 $\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
+$M\ \varepsilon$ is an application of $\varepsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
 $\%_\alpha M$ is an operator for cross-stage persistence.
@@
 $N$ for $x$ in $M$, and we omit its definition here.
-Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
+Substitution $M[\alpha \mapsto \varepsilon]$ of the empty stage
 for stage variable $\alpha$ in $M$ is defined below.
-\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}
+\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \varepsilon]$ and $K[\alpha \mapsto \varepsilon]$?}
 
@@
 	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
-	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
-	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
-	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
-	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
-	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
-	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
-	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
+	(\lambda x:\tau.M)[\alpha \mapsto \varepsilon] & = \lambda x:(\tau[\alpha \mapsto \varepsilon]).(M[\alpha \mapsto \varepsilon])                                  \\
+	(M\ N)[\alpha \mapsto \varepsilon]             & = (M[\alpha \mapsto \varepsilon])\ (N[\alpha \mapsto \varepsilon])                                          \\
+	(M\ \varepsilon)[\alpha \mapsto \varepsilon]      & = (M[\alpha \mapsto \varepsilon])\ \varepsilon                                                                \\
+	(\TB_\alpha M)[\alpha \mapsto \varepsilon]      & = M[\alpha \mapsto \varepsilon]                                                                          \\
+	(\TB_\beta M)[\alpha \mapsto \varepsilon]      & = \TB_\beta (M[\alpha \mapsto \varepsilon])                               & (\text{if } \alpha \neq \beta) \\
+	(\TBL_\alpha M)[\alpha \mapsto \varepsilon]     & =  M[\alpha \mapsto \varepsilon]                                        &                               \\
+	(\TBL_\beta M)[\alpha \mapsto \varepsilon]     & = \TBL_\beta (M[\alpha \mapsto \varepsilon])                              & (\text{if } \alpha \neq \beta) \\
+	(\Lambda\beta.M)[\alpha \mapsto \varepsilon]   & = \Lambda\beta.(M[\alpha \mapsto \varepsilon])                            & (\text{if } \alpha \neq \beta) \\
+	% (\Lambda\beta.M)[\alpha \mapsto \varepsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
+	(\%_\alpha M)[\alpha \mapsto \varepsilon]       & = M[\alpha \mapsto \varepsilon]                                         &                                  \\
+	(\%_\beta M)[\alpha \mapsto \varepsilon]       & = \%_{\beta[\alpha \mapsto \varepsilon]}(M[\alpha \mapsto \varepsilon])      & (\text{if } \alpha \neq \beta) \\
 \end{align*}
@@
 		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
-		 & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
+		 & (\Lambda \alpha.M)\ \varepsilon \longrightarrow_\Lambda M[\alpha \mapsto \varepsilon]
 	\end{align*}
@@
 $\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
-where $\epsilon$ is substituted for the stage variable.
-Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
+the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of abstraction
+where $\varepsilon$ is substituted for the stage variable.
+Application of a non-$\varepsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
 There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
+The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
 % $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
@@
 They are corresponding to brackets, escape, making a stage abstraction, 
-application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
+application of $\varepsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
 Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
@@
 		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
-		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
+		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \varepsilon:\tau[\alpha \mapsto \varepsilon]@A} \andalso
 		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
@@
 		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
-		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
+		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \varepsilon \E N\ \varepsilon : \tau[\alpha \mapsto \varepsilon]@A} \andalso
 		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
@@
 		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
-		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
+		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \varepsilon \E M[\alpha \mapsto \varepsilon] : \tau[\alpha \mapsto \varepsilon]@A} \\[2mm]
 		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
@@
 	The family $V^A$ of sets of values, ranged over by $v^A$,
-	is defined by following grammar.  In the grammar, $A \neq \epsilon$ is assumed.
+	is defined by following grammar.  In the grammar, $A \neq \varepsilon$ is assumed.
 	\begin{align*}
-		v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
-		v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
-		                         & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \epsilon)                          & \\
+		v^\varepsilon \in V^\varepsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\varepsilon                                       & \\
+		v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \varepsilon & \\
+		                         & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \varepsilon)                          & \\
                                           & \quad\   \mid\ \%_\alpha v^{A'} (\text{if } A = A'\alpha  \text{ for some } \alpha, A')
@@
 
-Values at $\epsilon$ stage are a $\lambda$-abstraction, a quoted code,
+Values at $\varepsilon$ stage are a $\lambda$-abstraction, a quoted code,
 or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
@@
   The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$,
-the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
+the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
 	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
 	\begin{align*}
-		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B     
-		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
-		\mid E^\epsilon_B\ \epsilon                                                                                                 \\
+		E^\varepsilon_B \in ECtx^\varepsilon_B & ::= \square\ (\text{if\ } B = \varepsilon) \mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B     
+		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\varepsilon_B
+		\mid E^\varepsilon_B\ \varepsilon                                                                                                 \\
 		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
-		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
+		\mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B
 		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
-		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B                                                   
-		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
+		                                 & \quad \mid \Lambda\alpha.E^\varepsilon_B                                                   
+		\mid E^A_B\ \varepsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
 \\
-		 R^\epsilon  & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
+		 R^\varepsilon  & ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon                                       & \\
 		 R^\alpha    & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\	\end{align*}
@@
 		\begin{align*}
-			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
-			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
+			E^A_\varepsilon [(\lambda x:\tau.M)\ v^\varepsilon]       & \longrightarrow_s E^A_\varepsilon[M[x\mapsto v^\varepsilon]]             \\
+			E^A_\varepsilon [(\Lambda\alpha.v^\varepsilon)\ \varepsilon] & \longrightarrow_s E^A_\varepsilon[v^\varepsilon[\alpha\mapsto \varepsilon]] \\
 			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\

### 2019-06-14 text/informal-overview.tex
type variable -> type-level constant
epsilon -> varepsilon.

@@
 a sequence of transition variables is called \textit{transition}.
-The empty transition is represented by $\epsilon$.
+The empty transition is represented by $\varepsilon$.
 They are used to show the thickness of brackets.
@@
 that symbols with transition variables disappear 
-when the empty transition $\epsilon$ is substituted to the transition variable.
+when the empty transition $\varepsilon$ is substituted to the transition variable.
 The purpose of this rule is express \verb|run| without any special symbol.
 In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
-For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.
+For example, $(\TB_\varepsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
+Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \varepsilon$ becomes $\lambda x:\I.x$
+In \LTP, \verb|run| is realized with application to the empty transition $\varepsilon$.
 
@@
 term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
-Especially, terms without quoting exist at the empty transition $\epsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
+Especially, terms without quoting exist at the empty transition $\varepsilon$.
+For example, $(\lambda x:\I.x)\ (1+2)$ is at $\varepsilon$ transition and 
 $\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
@@
 We adopt a signature $\Sigma$ to handle constants and type-level constants.
-This is because a signature simplifies kinding rules relating to type variables.
+This is because a signature simplifies kinding rules relating to type-level constants.
 A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.

### 2019-06-14 text/properties.tex
分割コンパイルが失敗する
epsilon -> varepsilon.

--- 2019-06-14 properties.tex
@@
+% !TEX root = ../main.tex
+
 \section{Properties of \LMD}
@@
 typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\epsilon]$.
+Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\varepsilon]$.
 
@@
 		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V M[\beta \mapsto \varepsilon]:\tau[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&\\
 		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V \tau[\beta \mapsto \varepsilon]::K[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&\\
 		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
+		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V K[\beta \mapsto \varepsilon] \iskind @A[\beta \mapsto \varepsilon].&\\
 		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
+		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V M[\beta \mapsto \varepsilon]\E N[\beta \mapsto \varepsilon] : \tau[\beta \mapsto \varepsilon]  @A[\beta \mapsto \varepsilon].&\\
 		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
+		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V \tau[\beta \mapsto \varepsilon]\E \sigma[\beta \mapsto \varepsilon] : K[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&\\
 		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
+		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V K[\beta \mapsto \varepsilon]\E J[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&
 	\end{flalign*}
@@
 \begin{theorem}[Unique Decomposition]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then either
+	If $x:\tau @\varepsilon \notin \G$ and $\G \V M : \tau @ A$ then either
 	\begin{enumerate}
 		\item $ M \in V^A$, or
-		\item there exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$ with $B = \epsilon$ or $B = \beta$ for some $\beta$.
+		\item there exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$ with $B = \varepsilon$ or $B = \beta$ for some $\beta$.
 	\end{enumerate}
@@
 \begin{theorem}[Progress]
-	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau  @ A$ then
+	If $x:\tau @\varepsilon \notin \G$ and $\G \V M : \tau  @ A$ then
 	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.

### 2019-06-14 text/related-work.tex
分割コンパイルが失敗する
epsilon -> varepsilon.

--- 2019-06-14 related-work.tex
@@
+% !TEX root = ../main.tex
+
 \section{Related Work}
@@
 In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\epsilon$ to transition abstractions.
+show that run can be represented as application of $\varepsilon$ to transition abstractions.
 In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 

### 2019-06-15 text/formal-defnition.tex
Revised until Section 3.1.

@@
 
-\AI{Rename ``type variables'' to ``type-level constants''. }
+% \AI{Rename ``type variables'' to ``type-level constants''. }
+% \AI{I prefer $\varepsilon$ for the nonempty sequence.}  
 We assume the denumerable set of type-level constants, ranged over by
@@
 sequences of stage variables; we write \(\varepsilon\) for the empty
-sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:
+sequence. \LMD is defined by the following grammar:
 
-\AI{``Transition'' is still used.}
+% \AI{``Transition'' is still used.}
 
@@
 	\textrm{Terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
-                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \varepsilon \mid \%_\alpha M                          \\  
+	                           &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
 	\textrm{Signature}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
-    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
+	\textrm{Type environments} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
 \end{align*}
 
-\AI{Add $M\,\alpha$ to terms.}
+% \AI{Add $M\,\alpha$ to terms.}
 
@@
 A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
-$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
-An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
+an application of a term to a type (operator) of $\Pi$-kind, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
+An application of a term to a type (operator) of $\Pi$-kind is, for example, $\text{Vector}\ 10$
 if type-level constant $\text{Vector}$ has the kind $\Pi x:\I.*$.
@@
 An $\alpha$-closed type corresponds to a runnable code fragment.
-Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
-an application of a term to a dependent function type $\tau\ M$,
-a code type $\TW_{\alpha} \tau$,
-a dependent function type $\Pi x:\tau.\tau$, 
-an $\alpha$-closed type $\F\alpha.\tau$.
+
+% Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
+An application of a term to a type (operator) of $\Pi$-kind: $\tau\ M$ connect tighter than
+the type constructor $\TW_{\alpha}$ and $\TW_{\alpha}$ connect tighter than
+$\Pi$ in dependent types such as $\Pi x:\tau.\tau$ and $\Pi$ connect tighter than
+$\F$ in types for stage abstraction such as $\F\alpha.\tau$.
 Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}
+$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$.
+% \AI{I don't understand this rule...}
 
@@
 $\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ \varepsilon$ is an application of $\varepsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
+$M\ A$ is an application of stage $A$ to a stage abstraction; and
 $\%_\alpha M$ is an operator for cross-stage persistence.
-The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
+The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ connect tighter than the two forms of applications
 and applications are left-associative
@@
 For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
+% \AI{I think the usage of ``application'' is wrong again}
 
@@
 
-We adopt a \LLF-like system, where constants and type-level constants for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
+We adopt a \LLF-like system, where constants and type-level constants are given in the signature $\Sigma$, which
 are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
-\AI{Change Int to Bool.}
+For example, when we use integers in \LMD, $\Sigma = \B :: *, true:\B, false:\B$.
+Please note that constants or type-level constants has no stage.
+This means that we can use them at any stage.
+% Type environments
+Type environments are sequences of triples of a variable, its type, and its stage.
+We define well-formed signature and well-formed type environments later
+in order to prove theorems.
 
 % Free variables
-As usual, the variable $x$ is bound in $\lambda x:\tau.M$
-and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
-\AI{What about other binders such as $\Pi$?}
+As usual, the variable $x$ is bound in $\lambda x:\tau.M$ or $\Pi x:\tau.\tau$ and
+and the stage variable $\alpha$ is bound in $\Lambda \alpha.M$ or $\F\alpha.\tau$.
+We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
+$x$ is not a free variable in $\tau_2$.
 We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
 We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
+% \AI{This should be mentioned after free variables are introduced.}
+% \AI{What about other binders such as $\Pi$?}
 
-% Contexts
-Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
-$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
-\AI{I'd prefer \textit{dom}.}
-The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
-$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.
-
-\AI{We should note that constants and type-level constants are not staged.}
+% \AI{We should note that constants and type-level constants are not staged.}
 \paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
@@
 where $\varepsilon$ is substituted for the stage variable.
-Application of a non-$\varepsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
 There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
@@
 It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
-We list the judgments forms in Figure~\ref{fig:LMD-six-judgements}.
+We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.
 \AI{equality vs. equivalence?}
@@
 			\G & \V K \iskind @ A      & \text{well-formed kinding} \\
-			\G & \V M \E N @ A     & \text{term equality} \\
-			\G & \V \tau \E \sigma & \text{type equality} \\
-			\G & \V K \E J @ A     & \text{kind equality}
+			\G & \V M \E N @ A         & \text{term equivalence}    \\
+			\G & \V \tau \E \sigma @ A & \text{type equivalence}    \\
+			\G & \V K \E J @ A         & \text{kind equivalence}
 		\end{align*}
 		\caption{Six judgment forms of the type system of \LMD.}
-		\label{fig:LMD-six-judgements}
+		\label{fig:LMD-six-judgments}
 	\end{center}
@@
 \AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
-\begin{definition}[Typing]
-  The typing relation $ \G \V M : \tau @ A $ is the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
-  \AI{Precisely speaking, it cannot be defined independently of other judgments.
-  How is dependency between judgments?}
+\begin{definition}[Typing, Kinding, Well-formed Kinding, Term Equivalence, Type Equivalence, Kind Equivalence]
+	The typing relation $ \G \V M : \tau @ A $,
+	the kinding relation $\G \V \tau :: K @ A$,
+	the well-formed kinding relation $\G \V K \iskind @ A$,
+	the term equivalence relation $\G \V M \E N @ A$,
+	the type equivalence relation $\G \V \tau \E \sigma @ A$,
+	the kind equivalence relation $\G \V K \E J @ A$,
+	are the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
 \end{definition}
+This definition is little complicated to define six relations at the same time.
+We canot define them one by one because they are dependent on each other.
 
-\AI{``judgment'' vs. ``judgement''.}  We start from defining typing of
+We introduce a well-formed signature and well-formed type environments.
+$\textit{dom}$ is a function from a content to a set of variables defined in the context.
+\begin{definition}[Well-formed Signature]
+	\begin{itemize}
+		\item $\emptyset$ is a well-formed signature.
+		\item if $\Sigma$ is a well-formed signature and $\V K :: * @ \varepsilon$ and $X\notin\textit{dom}(\Sigma)$ \\
+		      then $\Sigma,X::K$ is a well-formed signature.
+		\item if $\Sigma$ is a well-formed signature and $\V \tau :: K @ \varepsilon$ and $c\notin\textit{dom}(\Sigma)$ \\
+		      then $\Sigma,c:\tau$ is a well-formed signature.
+	\end{itemize}
+\end{definition}
+\begin{definition}[Well-formed Type Environments]
+	\begin{itemize}
+		\item $\emptyset$ are well-formed type environments.
+		\item if $\G$ are well-formed type environments and $x\not\in\textit{dom}(\G)$ and $x\not\in\textrm{FV}(\tau)$ \\
+			  then $\G,x:\tau@A$ are well-formed type environments.
+	\end{itemize}
+\end{definition}
+From here, we assume that all signature and type environments are well-formed.
+
+ We start from defining typing of
 \LMD.  Typing rules of \LMD are shown in Figure
@@
 They are corresponding to brackets, escape, making a stage abstraction,
-application of $\varepsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
+application of stage $A$ to a stage abstraction, and cross-stage persistence, respectively.
 Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
@@
 
-Interestingly, Hanada and Igarashi~\cite{} rejected the idea of
+Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
 reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
@@
 in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and as we argue \AI{where?}
+programs, the rule \QPercent makes sense and as we argue next
 it is practically significant.
@@
 		R^\varepsilon                          & ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon        & \\
-		 R^\alpha    & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\	\end{align*}
+		R^\alpha                               & ::=\ \TBL_\alpha \TB_\alpha M                                                                & \\\end{align*}
 \end{definition}
@@
 		E^A_\varepsilon [(\lambda x:\tau.M)\ v^\varepsilon] & \longrightarrow_s E^A_\varepsilon[M[x\mapsto v^\varepsilon]]      \\
-			E^A_\varepsilon [(\Lambda\alpha.v^\varepsilon)\ \varepsilon] & \longrightarrow_s E^A_\varepsilon[v^\varepsilon[\alpha\mapsto \varepsilon]] \\
+		E^A_\varepsilon [(\Lambda\alpha.v^\varepsilon)\ A]  & \longrightarrow_s E^A_\varepsilon[v^\varepsilon[\alpha\mapsto A]] \\
 		E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                            \\

### 2019-06-15 text/related-work.tex
Add high-level comments.

@@
 
+\AI{歴史をふりかえる部分もあってもいいけど，本論文との「関連」も議論す
+  る必要あり．特に Brady--Hammond との比較は必須．あと，例えば他の MSP
+  体系に依存型を入れるとしたらどうなりそうかの見込みを議論するとか． }
+
 % 依存型の歴史
 
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
+There are many papers on dependent types and most of them are affected by the pioneering work of Per Martin-L\"{o}f. \AI{citation?}
 $\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 

### 2019-06-15 text/formal-defnition.tex
Revised almost all comments.

@@
 \AI{Is $O$ used as a metavariable?}
-\AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
+% \AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
 
@@
 are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \B :: *, true:\B, false:\B$.
+For example, when we use integers in \LMD, $\Sigma = \B :: *, \textrm{true}:\B, \textrm{false}:\B$.
 Please note that constants or type-level constants has no stage.
@@
 Type environments are sequences of triples of a variable, its type, and its stage.
-We define well-formed signature and well-formed type environments later
-in order to prove theorems.
+We define well-formed signature and well-formed type environments later.
 
@@
 Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define two kinds of substitutions.
-Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
-$N$ for $x$ in $M$, and we omit its definition here.
-Substitution $M[\alpha \mapsto \varepsilon]$ of the empty stage
-for stage variable $\alpha$ in $M$ is defined below.
-\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \varepsilon]$ and $K[\alpha \mapsto \varepsilon]$?}
+Before giving the definition of reduction, we define six kinds of substitutions.
+Substitution $M[x\mapsto N], \tau[x \mapsto N]$ and $K[x \mapsto N]$ are 
+the ordinary capture-avoiding substitutions of
+term $N$ for $x$ in term $M$, type $\tau$, and kind $K$, respectively
+and we omit their definition here.
+Substitution $M[\alpha \mapsto A], \tau [\alpha \mapsto A], K[\alpha \mapsto A]$ and $B[\alpha\mapsto A]$ are 
+substitutions of stage $A$ for stage variable $\alpha$ in 
+term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$ respectively.
+We show replesentive cases below.
+% \AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \varepsilon]$ and $K[\alpha \mapsto \varepsilon]$?}
 
-\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
-\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
+% \AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
+% \AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
 
 \begin{align*}
-	% \newcommand{\SB}{}
-	(\lambda x:\tau.M)[\alpha \mapsto \varepsilon] & = \lambda x:(\tau[\alpha \mapsto \varepsilon]).(M[\alpha \mapsto \varepsilon])                                  \\
-	(M\ N)[\alpha \mapsto \varepsilon]             & = (M[\alpha \mapsto \varepsilon])\ (N[\alpha \mapsto \varepsilon])                                              \\
-	(M\ \varepsilon)[\alpha \mapsto \varepsilon]   & = (M[\alpha \mapsto \varepsilon])\ \varepsilon                                                                  \\
-	(\TB_\alpha M)[\alpha \mapsto \varepsilon]     & = M[\alpha \mapsto \varepsilon]                                                                                 \\
-	(\TB_\beta M)[\alpha \mapsto \varepsilon]      & = \TB_\beta (M[\alpha \mapsto \varepsilon])                                    & (\text{if } \alpha \neq \beta) \\
-	(\TBL_\alpha M)[\alpha \mapsto \varepsilon]    & =  M[\alpha \mapsto \varepsilon]                                               &                                \\
-	(\TBL_\beta M)[\alpha \mapsto \varepsilon]     & = \TBL_\beta (M[\alpha \mapsto \varepsilon])                                   & (\text{if } \alpha \neq \beta) \\
-	(\Lambda\beta.M)[\alpha \mapsto \varepsilon]   & = \Lambda\beta.(M[\alpha \mapsto \varepsilon])                                 & (\text{if } \alpha \neq \beta) \\
-	% (\Lambda\beta.M)[\alpha \mapsto \varepsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
-	(\%_\alpha M)[\alpha \mapsto \varepsilon]      & = M[\alpha \mapsto \varepsilon]                                                &                                \\
-	(\%_\beta M)[\alpha \mapsto \varepsilon]       & = \%_{\beta[\alpha \mapsto \varepsilon]}(M[\alpha \mapsto \varepsilon])        & (\text{if } \alpha \neq \beta) \\
+	(\lambda x:\tau.M)[\alpha \mapsto A] & = \lambda x:(\tau[\alpha \mapsto A]).(M[\alpha \mapsto A])                                  \\
+	(M\ B)[\alpha \mapsto A]             & = (M[\alpha \mapsto A])\ B[\alpha\mapsto A]                                                 \\
+	(\TB_\beta M)[\alpha \mapsto A]      & = \TB_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                          \\
+	(\TBL_\beta M)[\alpha \mapsto A]     & = \TBL_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                         \\
+	(\%_\beta M)[\alpha \mapsto A]       & = \%_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                           \\
+	(\beta B)[\alpha \mapsto A]          & = \beta (B[\alpha\mapsto A])                               & (\text{if } \alpha \neq \beta) \\
+	(\beta B)[\alpha \mapsto A]          & = A (B[\alpha\mapsto A])                                   & (\text{if } \alpha = \beta)
 \end{align*}
@@
 \begin{definition}[Reduction]
-	\AI{It's not clear what are defined here.  You are talking only about rules.
-		Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
-	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
+	The relations $M \longrightarrow_\beta N$, $M \longrightarrow_\blacklozenge N$, and $M \longrightarrow_\Lambda N$
+	are the least compatible relations closed under the rules below.
 	Congruence rules which are omitted from the definition.
@@
 		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                             \\
-		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
 		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                              \\
-		 & (\Lambda \alpha.M)\ \varepsilon \longrightarrow_\Lambda M[\alpha \mapsto \varepsilon]
+		 & (\Lambda \alpha.M)\ A \longrightarrow_\Lambda M[\alpha \mapsto A]
 	\end{align*}
-	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
+	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$ and
+	we call $\longrightarrow_\beta$, $\longrightarrow_\blacklozenge$, and $\longrightarrow_\Lambda$ $\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction, respectively.
 \end{definition}
@@
 We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.
-\AI{equality vs. equivalence?}
-\AI{A few judgment forms do not match rules.}
+% \AI{equality vs. equivalence?} \red{Select equivalence}
+% \AI{A few judgment forms do not match rules.}
 
@@
 
-\AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
+% \AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
 \begin{definition}[Typing, Kinding, Well-formed Kinding, Term Equivalence, Type Equivalence, Kind Equivalence]
@@
 We start from defining typing of
-\LMD.  Typing rules of \LMD are shown in Figure
-\ref{fig:typing-rules}.  The rule \TConst{} means any constants in the
-signature can appear at any stage.  \AI{This should be discussed
-	earlier.}  For example, if we have a signature $\Sigma$ which is
+\LMD.  Typing rules of \LMD are shown in Figure~\ref{fig:typing-rules}.
+The rule \TConst{} means any constants in the
+signature can appear at any stage.  \
+AI{This should be discussed earlier.}  
+For example, if we have a signature $\Sigma$ which is
 $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
 	\textrm{bool}$, the derivation tree in
-Figure~\ref{fig:tconst-derivation-tree} is admissible.  \AI{Don't we
-	need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$
-	should be a well-formed type under ... what?}  The rules \TVar,
-\TAbs, and \TApp{} are almost the same as those in the simply typed
-lambda calculus.  \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}  Additional conditions are that subterms must be
+Figure~\ref{fig:tconst-derivation-tree} is admissible.  
+The rules \TVar,\TAbs, and \TApp{} are almost the same as those in the simply typed
+lambda calculus or \LLF.  Additional conditions are that subterms must be
 typed at the same stage (\TAbs{} and \TApp); the type
@@
 $*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
+% \AI{Don't we need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$ should be a well-formed type under ... what?}
+% \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}
 
@@
 \QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
-rules \QBeta, \QTBLTB, and \QLambda{} correspond to the reduction rules.
-\AI{Don't we give names to those reduction rules?}
+rules \QBeta, \QTBLTB, and \QLambda{} correspond to 
+$\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction, respectively.
 
@@
 
-This kind of type equality is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
+This kind of type equivalence is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
 We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine

### 2019-06-15 text/formal-defnition.tex
Add a paragraph of Comparison with Hanada-Igarashi

@@
 % \AI{We should note that constants and type-level constants are not staged.}
-\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}
+% \paragraph{Remark:}  \AI{
+
+% Comparison with Hanada--Igarashi
+
+As the end of this subsection, we compare \LMD and \LTP.
+Terms of \LMD is the same with \LTP except constants.
+The difference between \LMD and \LTP is their types and kinds.
+First, \LMD contains $\Pi$ type instead of function type in \LTP.
+Second, there two kinds of $\F$ in \LTP in order to disscuss on program residualization
+although \LMD contains only one $\F$ type.
+Third, \LMD contains kinding and type equivalence rules to handle dependent types.
 

### 2019-06-15 text/formal-defnition.tex
Add an example of reduction sequence.
Revise Typing rules for a multi-stage calculus.

@@
 The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
+We show an example of reduction sequence below.
+Underlines show the redexes.
+\begin{align*}
+	 & \hspace{10mm} \underline{(\lambda i:\I\to\I.(\Lambda\alpha.\TB_\alpha (\%_\alpha i\ 1 + (\TBL_\alpha \TB_\alpha 3))\ \varepsilon))\ (\lambda x:\I.x)} \\
+	 & \longrightarrow_\blacklozenge (\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + (\underline{\TBL_\alpha \TB_\alpha 3})))\ \varepsilon        \\
+	 & \longrightarrow_\beta \underline{(\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + 3))\ \varepsilon}                                         \\
+	 & \longrightarrow_\Lambda \underline{(\lambda x:\I.x)\ 1} + 3                                                                                           \\
+	 & \longrightarrow_\beta 1 + 3                                                                                                                           \\
+	 & \longrightarrow^* 4
+\end{align*}
+
 % $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.
-
-\AI{A few examples are desirable.}
 
@@
 % Typing rules for a multi-stage calculus
-\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
+% \AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-They are corresponding to brackets, escape, making a stage abstraction,
-application of stage $A$ to a stage abstraction, and cross-stage persistence, respectively.
-Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.
+The rule \TTB{}, which corresponds to brackets, means that if term $M$ is of type $\tau$ at stage $A\alpha$,
+$\TB_\alpha M$ is of type $\TW_\alpha \tau$ at stage $A$.
+The rule \TTBL{}, which corresponds to escape, is the converse of \TTB.
+The rule \TGen{} is a rule for stage abstraction.
+The condition of $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensure that
+substitutions to $\alpha$ don't affect type environments or stages.
+The rule \TIns{} is for applications of stages to stage abstractions.
+The rule \TCsp is the rule for CSP, which means that 
+if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
 
@@
 		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
-		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \varepsilon:\tau[\alpha \mapsto \varepsilon]@A} \andalso
+		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ B:\tau[\alpha \mapsto B]@A} \andalso
 		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}

### 2019-06-15 text/formal-defnition.tex
Revised general description on staged semantics.

@@
 The reduction given above is full reduction and any redexes---even
-under quotation---can be reduced in an arbitrary order.  Following
-previous work~\cite{}, we introduce (small-step, call-by-value) staged
-semantics, where only redexes at stage $\varepsilon$\AI{not quite true
-	because of unquote--quote reduction} are reduced, modeling an
-implementation.
+under quotation---can be reduced in an arbitrary order.  
+Following previous work~\cite{Hanada2014}, 
+we introduce (small-step, call-by-value) staged semantics, 
+where only $\beta$-reduction or $\Lambda$-reduction at stage or the outer-most $\blacklozenge$-reduction are allowed, 
+modeling an implementation.
 
@@
 single quotation will splice the code value into the surrounding
-code).  See Hanada and Igarashi~\cite{} for details.
+code).  See Hanada and Igarashi~\cite{Hanada2014} for details.
 

### 2019-06-15 text/formal-defnition.tex
Fix the definition of Evaluation Context.

@@
 
-\begin{definition}[Evaluation Context and Redex]
-	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$,
-	the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
+\begin{definition}[Evaluation Context]
+	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$.
 	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
 	\begin{align*}
-		E^\varepsilon_B \in ECtx^\varepsilon_B & ::= \square\ (\text{if\ } B = \varepsilon) \mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B
-		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\varepsilon_B
-		\mid E^\varepsilon_B\ \varepsilon                                                                                                       \\
-		E^A_B \in ECtx^A_B                     & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B
-		\mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B
-		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                                \\
-		                                       & \quad \mid \Lambda\alpha.E^\varepsilon_B
-		\mid E^A_B\ \varepsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                         \\
-		\\
-		R^\varepsilon                          & ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon        & \\
-		R^\alpha                               & ::=\ \TBL_\alpha \TB_\alpha M                                                                & \\\end{align*}
+		 & E^\varepsilon_B \in ECtx^\varepsilon_B ::= \square\ (\text{if\ } B = \varepsilon)
+		\mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B \mid \TB_\alpha E^\alpha_B
+		\mid \Lambda\alpha.E^\varepsilon_B \mid E^\varepsilon_B\ A'                                                                       \\
+		 & E^A_B \in ECtx^A_B                     ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B \\
+		 & \hspace{25mm} \mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B \mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)      \\
+		 & \hspace{25mm} \mid \Lambda\alpha.E^\varepsilon_B \mid E^A_B\ B' \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)        \\
+	\end{align*}
+\end{definition}
+
+\begin{definition}[Redex]
+	the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
+	\begin{align*}
+		 & R^\varepsilon ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon \\
+		 & R^\alpha      ::=\ \TBL_\alpha \TB_\alpha M                                                         \\
+	\end{align*}
 \end{definition}

### 2019-06-15 text/formal-defnition.tex
Wrote a paragraph of evaluation context.

@@
 
+In order to define Staged Reduction, we define Redex and Evaluation Context.
+
+\begin{definition}[Redex]
+	the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
+	\begin{align*}
+		 & R^\varepsilon ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon \\
+		 & R^\alpha      ::=\ \TBL_\alpha \TB_\alpha M                                                         \\
+	\end{align*}
+\end{definition}
+
 \begin{definition}[Evaluation Context]
@@
 \end{definition}
-
-\begin{definition}[Redex]
-	the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
-	\begin{align*}
-		 & R^\varepsilon ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon \\
-		 & R^\alpha      ::=\ \TBL_\alpha \TB_\alpha M                                                         \\
-	\end{align*}
-\end{definition}
-
 \AI{some more explanation of the syntax of evaluation contexts.}
 
-We write $E^A_B[M]$ for the term obtained by filling the hole in $E^A_B$ by $M$
+We write $E^A_B[M]$ for the term obtained by filling the hole $\square$ in $E^A_B$ by $M$ 
 and define the staged reduction relation.
+Intuitively, $\square$ is the placefolder for redex.
+Examples of evaluation context is below.
+\red{Example of evaluation context}
+% \begin{align*}
+% \end{align*}
 
@@
 	the least relation closed under the rules below.
-	% \begin{figure}
-	% 	\begin{center}
 	\begin{align*}
@@
 	\end{align*}
-	%    	\caption{Staged Reduction}
-	%    	\label{fig:staged-reduction}
-	%    \end{center}
-	% \end{figure}
 \end{definition}
+
+This reduction relation reduces a typed term in a unique way 
+which is appropriate as call-by-value code generater.
+It means that terms in brackets is not evaluated until the terms are run
+and arguments of a function are evaluated before the application.
+\red{Example of staged reduction}

### 2019-06-15 text/formal-defnition.tex
Add examples.
Fix by grammarly.

@@
 % \AI{Rename ``type variables'' to ``type-level constants''. }
-% \AI{I prefer $\varepsilon$ for the nonempty sequence.}  
+% \AI{I prefer $\varepsilon$ for the non-empty sequence.}  
 We assume the denumerable set of type-level constants, ranged over by
@@
 
-% Description on meta variables
+% Description of meta variables
 
@@
 For example, when we use integers in \LMD, $\Sigma = \B :: *, \textrm{true}:\B, \textrm{false}:\B$.
-Please note that constants or type-level constants has no stage.
+Please note that constants or type-level constants have no stage.
 This means that we can use them at any stage.
@@
 As the end of this subsection, we compare \LMD and \LTP.
-Terms of \LMD is the same with \LTP except constants.
+Terms of \LMD are the same with \LTP except for constants.
 The difference between \LMD and \LTP is their types and kinds.
 First, \LMD contains $\Pi$ type instead of function type in \LTP.
-Second, there two kinds of $\F$ in \LTP in order to disscuss on program residualization
+Second, there two kinds of $\F$ in \LTP in order to discuss on program residualization
 although \LMD contains only one $\F$ type.
@@
 
-Next, we define full reduction for \LMD.
+Next, we define the full reduction for \LMD.
 Before giving the definition of reduction, we define six kinds of substitutions.
@@
 $\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of abstraction
+the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of the abstraction
 where $\varepsilon$ is substituted for the stage variable.
@@
 The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
-We show an example of reduction sequence below.
+We show an example of a reduction sequence below.
 Underlines show the redexes.
@@
 This definition is little complicated to define six relations at the same time.
-We canot define them one by one because they are dependent on each other.
+We can't define them one by one because they are dependent on each other.
 
@@
 % \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is opposite.}
+\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is the opposite.}
 As in standard dependent type systems, \TConv{} allows us to replace
@@
 % Typing rules for a multi-stage calculus
-% \AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
+% \AI{This paragraph is not very informative.  We shouldn't just refer readers to previous work.}
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
@@
 reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
+the reduction does not match the operational behavior of the CSP operator
 in implementation.  However, as an equational system for multi-stage
@@
 we introduce (small-step, call-by-value) staged semantics,
-where only $\beta$-reduction or $\Lambda$-reduction at stage or the outer-most $\blacklozenge$-reduction are allowed, 
+where only $\beta$-reduction or $\Lambda$-reduction at stage $\varepsilon$ or the outer-most $\blacklozenge$-reduction are allowed,
 modeling an implementation.
@@
     The family $V^A$ of sets of values, ranged over by $v^A$,
-	is defined by following grammar.  In the grammar, $A \neq \varepsilon$ is assumed.
+    is defined by the following grammar.  In the grammar, $A \neq \varepsilon$ is assumed.
     \begin{align*}
@@
 
-In order to define Staged Reduction, we define Redex and Evaluation Context.
+In order to define Staged Reduction, we define redex and evaluation context.
 
@@
 Examples of evaluation context is below.
-\red{Example of evaluation context}
-% \begin{align*}
-% \end{align*}
+\begin{align*}
+     & \square\ (\lambda x:\I.x) \in  ECtx^\varepsilon_\varepsilon            \\
+     & \Lambda\alpha.\square\ \epsilon \in ECtx^\varepsilon_\varepsilon       \\
+     & \TBL_\alpha \TB_\alpha \TBL_\alpha \square \in ECtx^\alpha_\varepsilon
+\end{align*}
 
@@
 This reduction relation reduces a typed term in a unique way
-which is appropriate as call-by-value code generater.
-It means that terms in brackets is not evaluated until the terms are run
+which is appropriate as call-by-value code generator.
+It means that terms in brackets are not evaluated until the terms are run
 and arguments of a function are evaluated before the application.
-\red{Example of staged reduction}
+We show an example of staged reduction.
+Underlines show the redexes.
+\begin{align*}
+     & \hspace{9mm} \Lambda\alpha.(\TB_\alpha \underline{\TBL_\alpha \TB_\alpha} (\lambda x:\I.x)\ 10)\ \varepsilon \\
+     & \longrightarrow_s \underline{\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x)\ 10)\ \varepsilon}                   \\
+     & \longrightarrow_s \underline{(\lambda x:\I.x)\ 10}                                                           \\
+     & \longrightarrow_s 10
+\end{align*}

### 2019-06-15 text/informal-overview.tex

@@
 We designed \LMD, a multi-stage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP and
+\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP, and
 we introduced dependent types based on \LTP\cite{attapl}.
@@
 \red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
+\AI{ないです．たしかにあんまりつけるとうるさいですね．2.1 の冒頭とかは文ごと不要なのでは？}
 \subsection{\LTP}
@@
 The empty transition is represented by $\varepsilon$.
-They are used to show the thickness of brackets.
+They are used to show the thickness of brackets. \AI{Perhaps ``thickness'' doesn't make sense.}
 For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
@@
 For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural there is a reduction rule for transition application in \LTP.
+It is only natural \AI{?} there is a reduction rule for transition application in \LTP.
 The rule is the following.
@@
 $\%$ is dedicated to CSP in \LTP.
+\AI{What should me mentioned here is that in MetaOCaml CSP is implicit but
+in \LTP it's explicit.}
 For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
 \red{inner / outer は適切か?}
+\AI{What is \(a\)?}
+\AI{Is this explanation enough to understand the rest of the section?}
 
@@
 It is based on Edinburgh LF\cite{harper1993framework}.
-Therefore, all constants and base types are declared in the signature.
+\AI{Can you remind me of differences between Edinburgh LF and \LLF?}
+Therefore, \AI{``Therefore'' is used to show a logical consequence.} all constants and base types are declared in the signature.
 The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.
+by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.  \AI{``dependent product'' vs. ``dependent function''.}
 
@@
 Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.
+introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.  \AI{Vect\ true may be a better example?}
 For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
@@
 Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily from the syntax or the reductions of \LMD.
+we can design all rules except \QPercent\ easily from the syntax or the reductions of \LMD.  \AI{Don't refer to a concrete rule name without showing it because we haven't introduced rules.}
+
+\AI{If there's space, we should have introduced the \LTP-version of vadd.}
 
@@
 \end{align*}
+\AI{I think we should state the types of cons, tail, and head.}
 Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.

### 2019-06-15 text/introduction.tex
分割コンパイルが失敗する

--- 2019-06-14 introduction.tex
@@
+% !TEX root = ../main.tex
+
 \section{Introduction}
@@
 Multi-stage programming enables us to generate and run fragments of code at runtime.
-MetaOCaml\cite{oleg2014} provide features for multi-stage programming, which are brackets, escape, and run.
+\AI{It sounds like the subject of ``generate and run'' is human being (``us'').
+Something like ``Multi-stage programming offers linguistic support for dynamic code generation and execution.''?}
+MetaOCaml~\cite{oleg2014} \AI{You need a space between a word and a citation.
+Taha's original MetaOCaml should be cited, too.} provides features for multi-stage programming, which are brackets, escape, and run.
+\AI{CSP?}
 Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
@@
 
-Cross-stage Persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
+Cross-stage persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
 This is an example of CSP.
@@
 Otherwise, we will get a Segmentation Fault error.
+\AI{Why SEGV?  MetaOCaml will raise an exception.}
 This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
@@
 % We call this problem \red{Specialized Code Problem}.
+
+\AI{このイントロ、各段落はまあまあよいのですが、全体の流れが、ふたつ目の文から MetaOCaml という特定の多段階プログラミング言語の話をして、それから応用と問題点の話になりますが、ここが多段階プログラミング一般の話なのか MetaOCaml 固有の話なのかがぶれているように思います。まずは、多段階プログラミング一般の話を応用も含めてする。(他の多段階計算ができるシステムを無視しない。)それから、MetaOCaml の紹介と、その型システムの問題点の話をすべきでしょう。MetaOCaml の型システムでできることもふれておいた方がよいでしょう。}
 
@@
 
-Dependent types are types which is dependent on values.
-We can use dependent types for securer programming.
+Dependent types are types which is \AI{are} dependent on values.
+We can use dependent types for securer programming. \AI{Cite Xi--Pfenning, for example?}
 For example, we can realize vectors with their sizes with them.
@@
 \end{verbatim}
-\verb|Vector| is a type constor which takes the length of vectors, that is, 
+\verb|Vector| is a type constructor which takes the length of vectors, that is, 
 \verb|Vector 3| is a type for vectors whose lengths are 3.
-If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n|,
+If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n| for any positive number \verb|n|,
 we can confirm the two arguments of \verb|vadd| function has the same length.
@@
 \red{このsubsectionは短いので上とくっつけてもいいかもしれない}
-
+\AI{くっつけましょう。Section 1 で指摘した問題を依存型で解決するというのは自然なアイデアだし。One natural idea to address this problem is the introduction of dependent types. みたいなこといって、依存型の導入をする。先行研究として Brady--Hammond にもふれる。}
 % \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
@@
 
-In this paper, we design new multi-stage calculus \LMD by 
+In this paper, we design a new multi-stage calculus \LMD by 
 merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
 \LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming more safer with the power of dependent types.
+\LMD makes multi-stage programming more safer \AI{remove ``more''} with the power of dependent types.
+
+\AI{Give a summary of our technical contribution as itemization.}
 
@@
 Section 2 gives an informal overview of \LMD.
-Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
-Section 4 shows the properties of \LMD including Unique Decomposition.
+Section 3 defines \LMD and
+Section 4 shows the properties of \LMD including Unique Decomposition \AI{There are more important properties that should be mentioned!  In fact, the properties should be mentioned earlier.}.
 Section 5 discusses future works.
@@
 \AI{``Related work'' and ``future work'' (they are uncountable).}
+\AI{Related work is discussed in Section 5?  Section 6 is the section for conclusion, which includes future work.}

### 2019-06-15 text/formal-defnition.tex
Wrote on vadd and composition.

@@
 
-%%%%%%%%%%%%%%%%%%% SKIP FROM HERE %%%%%%%%%%%%%%%%%%%%
-$\text{mulmat}$ function in the following code fragment generate code for matrix multiplication.
-$\text{mulmat}$ takes two integers which are the size of the multiplicand matrix and generate a code.
-The last integer to decide the size of the multiplier matrix is given at runtime.
-You can generate code by applying two integers to $\text{mulmat}$.
-We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
-But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
-\QPercent\ states that we can erase this $\%_\alpha$ under a condition which is explained in the next paragraph.
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
+As we discussed in Section 2, $\text{vadd}$ function, 
+which takes the length of vectors and returns a quoted add function for vector of the given size,
+has the type of $\Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
+When we use this function, we instansiate $\text{vadd}$ with some integer such as 5
+and get code of a optimzed $\text{vadd}$ function such as $\text{vadd5}$.
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 5)}
+Although $\text{vadd5}$ is of type $\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$,
+a code value of this type is difficult to combine with another code fragment.
+For example, if we want to composite $\text{vadd5}$ with reverse fucntion, 
+which is of type $\text{rev5}:\F\alpha.\TW_\alpha(\text{Vector}\ 5\to\text{Vector}\ 5)$,
+we write a program like following.
+\begin{align*}
+\Lambda\gamma.\TB_\gamma.\lambda v_1:(\text{Vector}\ 5).\lambda v_2:(\text{Vector}\ 5).\TBL_\gamma 
+(\text{rev5}\ \gamma)\ (\TBL_\gamma (\text{vadd5}\ \gamma)\ \TBL_\gamma v_1\ \TBL_\gamma v_2)
+\end{align*}
+However, this program cannot be typed without \QPercent{}
+because the type of $v_1$: $\text{Vector}\ 5$ isn't equivalent with the type of arguments of $\text{vadd5}$: $\text{Vector}\ \%_\gamma 5$.
 
+In order to resolve this problem, we introduce \QPercent{} into \LMD.
+\begin{center}
+\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
+\end{center}
+\QPercent\ states that we can erase this $\%_\alpha$ under a condition.
 The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
@@
 In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
-
-    % Example of QCsp (mulmat)
-    {
-        \begin{align*}
-            \text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
-            \text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
-                                & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
-        \end{align*}
-    }
-
-This kind of type equivalence is very useful when we combine $\text{mulmat}\ 3\ 5$ with another code.
-We cannot remove $\%_\alpha$ in the type without \QPercent and it makes very difficult to combine
-because types of codes don't contain $\%_\alpha$ generally.
-
-%%%%%%%%%%%%%%%%%%% TO HERE %%%%%%%%%%%%%%%%%%%%
+Thanks to \QPercent, we can identify $\text{Vector}\ 5$ and $\text{Vector}\ \%_\gamma 5$
+and compose code values of functions as we expected.
 

### 2019-06-16 text/formal-defnition.tex
Revise 3.1 and 3.2.

@@
 
-% \AI{Rename ``type variables'' to ``type-level constants''. }
-% \AI{I prefer $\varepsilon$ for the non-empty sequence.}  
-We assume the denumerable set of type-level constants, ranged over by
-metavariables \(X, Y, Z\), the denumerable set of variables, ranged
-over by \(x,y,z\), the denumerable set of constants, ranged over by
-\(c\), and the denumerable set of stage variables, ranged over by
+We assume the denumerable set of \emph{type-level constants}, ranged over by
+metavariables \(X, Y, Z\), the denumerable set of \emph{variables}, ranged
+over by \(x,y,z\), the denumerable set of \emph{constants}, ranged over by
+\(c\), and the denumerable set of \emph{stage variables}, ranged over by
 \(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
@@
     % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
-    \textrm{Kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
-    \textrm{Types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
+    \textrm{kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
+    \textrm{types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
     %     \textrm{Constants}       &   &                          & c                                                                                                          \\
-    \textrm{Terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
+    \textrm{terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
                                &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
-    \textrm{Signature}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
-    \textrm{Type environments} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
+    \textrm{signatures}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
+    \textrm{type environments} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
 \end{align*}
@@
 A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application of a term to a type (operator) of $\Pi$-kind, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-An application of a term to a type (operator) of $\Pi$-kind is, for example, $\text{Vector}\ 10$
+an application $\tau\ M$ of a type (operator) (of $\Pi$-kind) to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
+An application of a type (operator) of $\Pi$-kind to a term is, for example, $\text{Vector}\ 10$
 if type-level constant $\text{Vector}$ has the kind $\Pi x:\I.*$.
-A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
+A code type $\TW_\alpha \tau$ is for a code fragment of a term of type $\tau$.
 An $\alpha$-closed type corresponds to a runnable code fragment.
 
-% Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
-An application of a term to a type (operator) of $\Pi$-kind: $\tau\ M$ connect tighter than
-the type constructor $\TW_{\alpha}$ and $\TW_{\alpha}$ connect tighter than
-$\Pi$ in dependent types such as $\Pi x:\tau.\tau$ and $\Pi$ connect tighter than
-$\F$ in types for stage abstraction such as $\F\alpha.\tau$.
-Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
-$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$.
+% An application $\tau\ M$ of a type (operator) to a term connects tighter than
+% $\TW_{\alpha}$ connects tighter than
+% $\Pi$ in dependent types such as $\Pi x:\tau.\tau$ and $\Pi$ connect tighter than
+% $\F$ in types for stage abstraction such as $\F\alpha.\tau$.
+% Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
+% $\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$.
 % \AI{I don't understand this rule...}
@@
 $\%_\alpha M$ is an operator for cross-stage persistence.
-The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ connect tighter than the two forms of applications
-and applications are left-associative
-and two abstractions extends as far to the right as possible.
-For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
-% \AI{I think the usage of ``application'' is wrong again}
 
@@
 
-We adopt a \LLF-like system, where constants and type-level constants are given in the signature $\Sigma$, which
-are a sequence of declarations of the form $c:\tau$ and $X:K$.
-For example, when we use integers in \LMD, $\Sigma = \B :: *, \textrm{true}:\B, \textrm{false}:\B$.
-Please note that constants or type-level constants have no stage.
-This means that we can use them at any stage.
+We adopt the tradition of \LLF-like systems, where types of constants and kinds of type-level constants are globally declared in a signature $\Sigma$, which
+is a sequence of declarations of the form $c:\tau$ and $X:K$.
+For example, when we use Boolean in \LMD, $\Sigma$ includes $\B :: *, \textrm{true}:\B, \textrm{false}:\B$.
+Note that constants and type-level constants are not associated with stages;
+so, we can use them at any stage.
 % Type environments
@@
 
-% Free variables
-As usual, the variable $x$ is bound in $\lambda x:\tau.M$ or $\Pi x:\tau.\tau$ and
-and the stage variable $\alpha$ is bound in $\Lambda \alpha.M$ or $\F\alpha.\tau$.
+The variable $x$ is bound in $M$ of $\lambda x:\tau.M$ and in $\tau_2$
+of $\Pi x:\tau_1.\tau_2$, as usual; the stage variable $\alpha$ is
+bound in $M$ of $\Lambda \alpha.M$ and $\tau$ of $\F\alpha.\tau$.
+We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.  Similarly, $\FV(\tau)$, $\FTV(\tau)$,
+$\FV(K)$, and $\FTV(K)$ are defined.
 We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
 $x$ is not a free variable in $\tau_2$.
+% Free variables
 We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
-We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
 % \AI{This should be mentioned after free variables are introduced.}
@@
 
-% \AI{We should note that constants and type-level constants are not staged.}
-% \paragraph{Remark:}  \AI{
+The prefix operators $\TW_\alpha, \TB_\alpha, \TBL_\alpha$, and
+$\%_\alpha$ connect tighter than the three forms $\tau\ M$, $M\ N$,
+$M\ A$ of applications, which are left-associative; The binders $\Pi$,
+$\forall$, and $\lambda$ extend as far to the right as possible.
+Thus, $\F\alpha.\TW_{\alpha} (\Pi x:\I.\text{Vector}\ 5)$ is
+interpreted as
+$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$; and
+$\Lambda\alpha.\lambda x:\I.\TB_\alpha x\ y$ means
+$\Lambda\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
 
-% Comparison with Hanada--Igarashi
-
-As the end of this subsection, we compare \LMD and \LTP.
-Terms of \LMD are the same with \LTP except for constants.
-The difference between \LMD and \LTP is their types and kinds.
-First, \LMD contains $\Pi$ type instead of function type in \LTP.
-Second, there two kinds of $\F$ in \LTP in order to discuss on program residualization
-although \LMD contains only one $\F$ type.
-Third, \LMD contains kinding and type equivalence rules to handle dependent types.
+\paragraph{Remark:} Basically, we define \LMD to be an extension of
+\LTP with dependent types.  One notable difference is that \LMD has
+only one kind of \(\alpha\)-closed types, whereas \LTP has two kinds
+of \(\alpha\)-closed types \(\forall\alpha.\tau\) and
+\(\forall^\varepsilon\alpha.\tau\).  We have omitted the first kind,
+for simplicity, and dropped the superscript $\varepsilon$.  It would
+not be difficult to recover the distinction to show properties related
+to program residualization~\cite{Hanada2014}.
 
@@
 
-Next, we define the full reduction for \LMD.
+Next, we define full reduction for \LMD.
 Before giving the definition of reduction, we define six kinds of substitutions.
 Substitution $M[x\mapsto N], \tau[x \mapsto N]$ and $K[x \mapsto N]$ are
-the ordinary capture-avoiding substitutions of
-term $N$ for $x$ in term $M$, type $\tau$, and kind $K$, respectively
-and we omit their definition here.
+ordinary capture-avoiding substitution of
+term $N$ for $x$ in term $M$, type $\tau$, and kind $K$, respectively,
+and we omit their definitions here.
 Substitution $M[\alpha \mapsto A], \tau [\alpha \mapsto A], K[\alpha \mapsto A]$ and $B[\alpha\mapsto A]$ are
 substitutions of stage $A$ for stage variable $\alpha$ in
-term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$ respectively.
-We show replesentive cases below.
-% \AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \varepsilon]$ and $K[\alpha \mapsto \varepsilon]$?}
-
-% \AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
-% \AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
-
+term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$, respectively.
+We show representative cases below.
+%
 \begin{align*}
@@
 \end{align*}
+Here, $\TB_{\alpha_1\cdots\alpha_n} M$,
+$\TBL_{\alpha_1\cdots\alpha_n} M$, and $\%_{\alpha_1\cdots\alpha_n} M$
+$(n \geq 0)$ stand for $\TB_{\alpha_1} \cdots \TB_{\alpha_n} M$,
+$\TBL_{\alpha_1}\cdots \TBL_{\alpha_n} M$, and
+$\%_{\alpha_1}\cdots \%_{\alpha_n} M$, respectively.  In particular,
+$\TB_{\varepsilon} M = \TBL_{\varepsilon} M = \%_{\varepsilon} M = M$.
 
@@
     are the least compatible relations closed under the rules below.
-    Congruence rules which are omitted from the definition.
+%    Congruence rules are omitted from the definition.
     \begin{align*}
-         & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]         \\
-         & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M          \\
-         & (\Lambda \alpha.M)\ A \longrightarrow_\Lambda M[\alpha \mapsto A]
+         (\lambda x:\tau.M) N & \longrightarrow_\beta M[x \mapsto N]         \\
+         \TBL_\alpha \TB_\alpha M & \longrightarrow_\blacklozenge M          \\
+         (\Lambda \alpha.M)\ A & \longrightarrow_\Lambda M[\alpha \mapsto A]
     \end{align*}
-    We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$ and
-    we call $\longrightarrow_\beta$, $\longrightarrow_\blacklozenge$, and $\longrightarrow_\Lambda$ $\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction, respectively.
 \end{definition}
+We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$,
+$ M \longrightarrow_\blacklozenge M'$, or
+$ M \longrightarrow_\Lambda M'$ and we call $\longrightarrow_\beta$,
+$\longrightarrow_\blacklozenge$, and $\longrightarrow_\Lambda$
+$\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction,
+respectively.
+\AI{Don't we need to define $\longrightarrow^*$?}
 
-The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation
+The relation $\longrightarrow_\beta$ represents ordinary $\beta$-reduction in the \(\lambda\)-calculus; the relation
 $\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
-the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of the abstraction
-where $\varepsilon$ is substituted for the stage variable.
+the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to  stage $A$ reduces to the body of the abstraction
+where $A$ is substituted for the stage variable.
 There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
-The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
+The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted for $\alpha$.
 We show an example of a reduction sequence below.
@@
 
-% 総論
-
 In this section, we define the type system of \LMD.
-% \LMD is little complicated because it contains dependent types.
 It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
 We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.
-% \AI{equality vs. equivalence?} \red{Select equivalence}
-% \AI{A few judgment forms do not match rules.}
 
@@
 
-% \AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
 \begin{definition}[Typing, Kinding, Well-formed Kinding, Term Equivalence, Type Equivalence, Kind Equivalence]
@@
     the kind equivalence relation $\G \V K \E J @ A$,
-    are the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
+    are the least relation closed under the rules in Figure~\ref{fig:typing-rules}.  \AI{There are more rules!  Some of them are not even in the paper.}
 \end{definition}
@@
 We can't define them one by one because they are dependent on each other.
+\AI{I think well-formed signatures and type environments cannot be defined independently.}
 

### 2019-06-16 text/formal-defnition.tex
Add comments on Section 3.3.

@@
 For example, when we use Boolean in \LMD, $\Sigma$ includes $\B :: *, \textrm{true}:\B, \textrm{false}:\B$.
-Note that constants and type-level constants are not associated with stages;
+Type environments are sequences of triples of a variable, its type, and its stage.
+We write \(\textit{dom}(\Sigma)\) and \(\textit{dom}(\Gamma)\)
+for the set of (type-level) constants declared in \(\Sigma\) and \(\Gamma\), respectively.   As in other multi-stage calculi~\cite{Taha03,Tsukada,Hanada2014},
+a variable declaration is associated with a stage
+so that a variable can be referenced only at the declared stage.
+Constants and type-level constants are not associated with stages;
 so, we can use them at any stage.
-% Type environments
-Type environments are sequences of triples of a variable, its type, and its stage.
 We define well-formed signature and well-formed type environments later.
@@
 In this section, we define the type system of \LMD.
-It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
+It consists of eight judgment forms for signature well-formedness, type environment well-formedness, kind well-formedness, kinding, typing, term equivalence, type equivalence, and kind equivalence.
 We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.
+They are all defined in a mutual recursive manner.  We will discuss
+each judgment below.
 
@@
       \begin{align*}
+            \vdash & \Sigma            & \text{signature well-formedness} \\
+            \V & \G                & \text{type environment well-formedness} \\
+            \G & \V K \iskind @ A      & \text{kind well-formedness} \\
+            \G & \V \tau :: K @ A      & \text{kinding}             \\
             \G & \V M : \tau @ A       & \text{typing}              \\
-            \G & \V \tau :: K @ A      & \text{kinding}             \\
-            \G & \V K \iskind @ A      & \text{well-formed kinding} \\
-            \G & \V M \E N @ A         & \text{term equivalence}    \\
+            \G & \V K \E J @ A         & \text{kind equivalence}    \\
             \G & \V \tau \E \sigma @ A & \text{type equivalence}    \\
-            \G & \V K \E J @ A         & \text{kind equivalence}
+            \G & \V M \E N @ A         & \text{term equivalence}
         \end{align*}
-        \caption{Six judgment forms of the type system of \LMD.}
+        \caption{Eight judgment forms of the type system of \LMD.}
         \label{fig:LMD-six-judgments}
@@
 
-\begin{definition}[Typing, Kinding, Well-formed Kinding, Term Equivalence, Type Equivalence, Kind Equivalence]
-    The typing relation $ \G \V M : \tau @ A $,
-    the kinding relation $\G \V \tau :: K @ A$,
-    the well-formed kinding relation $\G \V K \iskind @ A$,
-    the term equivalence relation $\G \V M \E N @ A$,
-    the type equivalence relation $\G \V \tau \E \sigma @ A$,
-    the kind equivalence relation $\G \V K \E J @ A$,
-    are the least relation closed under the rules in Figure~\ref{fig:typing-rules}.  \AI{There are more rules!  Some of them are not even in the paper.}
-\end{definition}
-This definition is little complicated to define six relations at the same time.
-We can't define them one by one because they are dependent on each other.
-\AI{I think well-formed signatures and type environments cannot be defined independently.}
+\subsubsection{Signature and Type Environment Well-formedness.}
+The rules for Well-formed signatures and type environments are
+shown below:
+%
+{\small
+\begin{center}
+  \infrule{
+  }{
+    \vdash \emptyset
+  }
+  \hfil
+  \infrule{
+    \vdash \Sigma \andalso
+    \V K \iskind @ \varepsilon \\
+    X\notin\textit{dom}(\Sigma)
+  }{
+    \vdash \Sigma, X::K
+  }
+  \hfil
+  \infrule{
+    \vdash \Sigma \andalso
+    \V \tau :: * @ \varepsilon \\
+    c\notin\textit{dom}(\Sigma)
+  }{
+   \vdash \Sigma, c:\tau
+ }
+ \\[2mm]
+  \infrule{
+  }{
+    \V \emptyset
+  }
+  \hfil
+  \infrule{
+    \V \Gamma \andalso
+    \Gamma \V \tau :: * @ A \andalso
+    x\notin\textit{dom}(\Sigma)
+  }{
+   \V \Gamma, x:\tau@A
+ }
+\end{center}
+}
 
-We introduce a well-formed signature and well-formed type environments.
-$\textit{dom}$ is a function from a content to a set of variables defined in the context.
-\begin{definition}[Well-formed Signature]
-    \begin{itemize}
-        \item $\emptyset$ is a well-formed signature.
-        \item if $\Sigma$ is a well-formed signature and $\V K :: * @ \varepsilon$ and $X\notin\textit{dom}(\Sigma)$ \\
-              then $\Sigma,X::K$ is a well-formed signature.
-        \item if $\Sigma$ is a well-formed signature and $\V \tau :: K @ \varepsilon$ and $c\notin\textit{dom}(\Sigma)$ \\
-              then $\Sigma,c:\tau$ is a well-formed signature.
-    \end{itemize}
-\end{definition}
-\begin{definition}[Well-formed Type Environments]
-    \begin{itemize}
-        \item $\emptyset$ are well-formed type environments.
-        \item if $\G$ are well-formed type environments and $x\not\in\textit{dom}(\G)$ and $x\not\in\textrm{FV}(\tau)$ \\
-              then $\G,x:\tau@A$ are well-formed type environments.
-    \end{itemize}
-\end{definition}
-From here, we assume that all signature and type environments are well-formed.
+To add declarations to a signature, the kind/type of a (type-level)
+constant has to be well-formed at stage \(\varepsilon\) so that it is
+used at any stage. \AI{We should discuss implicit CSP at the type
+  level somewhere.}
 
-We start from defining typing of
-\LMD.  Typing rules of \LMD are shown in Figure~\ref{fig:typing-rules}.
-The rule \TConst{} means any constants in the
-signature can appear at any stage.  \
-AI{This should be discussed earlier.}
-For example, if we have a signature $\Sigma$ which is
-$\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
-    \textrm{bool}$, the derivation tree in
-Figure~\ref{fig:tconst-derivation-tree} is admissible.
-The rules \TVar,\TAbs, and \TApp{} are almost the same as those in the simply typed
-lambda calculus or \LLF.  Additional conditions are that subterms must be
-typed at the same stage (\TAbs{} and \TApp); the type
-annotation/declaration on a variable has to be a proper type of kind
-$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
-% \AI{Don't we need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$ should be a well-formed type under ... what?}
-% \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}
+In what follows, well-formedness is not explicitly mentioned but
+we assume that all signatures and type environments are well-formed.
 
+\subsubsection{Kind Wellformedness and Kinding.}
+
+The rules for kind wellformedness and kiding is straightforward
+adaptation from \LLF.  So, we omit them.
+
+\subsubsection{Typing.}
+
+\AI{The second premises of \TConst and \TVar are not needed?}
 \begin{figure}
     \begin{center}
-        \begin{minipage}{0.50\hsize}
-            \infer[\TConst]
-            {\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
-            {\textrm{true}:\textrm{bool} \in \Sigma \andalso
-                \ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
-            }
-            \caption{A derivation tree using \TConst}
-            \label{fig:tconst-derivation-tree}
-        \end{minipage}
-    \end{center}
-\end{figure}
-
-% \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is the opposite.}
-As in standard dependent type systems, \TConv{} allows us to replace
-the type of a term with an equivalent one.
-In a type system which includes dependent types, this kind of rule is essential
-because two types which have different shapes may be equivalent.
-For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.
-
-% Typing rules for a multi-stage calculus
-% \AI{This paragraph is not very informative.  We shouldn't just refer readers to previous work.}
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-The rule \TTB{}, which corresponds to brackets, means that if term $M$ is of type $\tau$ at stage $A\alpha$,
-$\TB_\alpha M$ is of type $\TW_\alpha \tau$ at stage $A$.
-The rule \TTBL{}, which corresponds to escape, is the converse of \TTB.
-The rule \TGen{} is a rule for stage abstraction.
-The condition of $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensure that
-substitutions to $\alpha$ don't affect type environments or stages.
-The rule \TIns{} is for applications of stages to stage abstractions.
-The rule \TCsp is the rule for CSP, which means that
-if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
-
-\begin{figure}
-    \begin{center}
-        \infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
+        \infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \hfil
         \infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
@@
 
-\subsubsection{Type and Term Equivalence}
+Typing rules of \LMD are shown in Figure~\ref{fig:typing-rules}.
+The rule \TConst{} means that a constant can appear at any stage.
+% For example, if we have a signature $\Sigma$ which is
+% $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}:
+%     \textrm{bool}$, the derivation tree in
+% Figure~\ref{fig:tconst-derivation-tree} is admissible.
+The rules \TVar,\TAbs, and \TApp{} are almost the same as those in the simply typed
+lambda calculus or \LLF.  Additional conditions are that subterms must be
+typed at the same stage (\TAbs{} and \TApp); the type
+annotation/declaration on a variable has to be a proper type of kind
+$*$ (\TAbs) at the stage where it is declared (\TVar{} and \TAbs).
+% \AI{Don't we need signature well formedness?  If $c:\tau \in \Sigma$, then $\tau$ should be a well-formed type under ... what?}
+% \AI{... or \(\lambda\)LF?  We are working in a dependently type system...}
 
-As usual in dependent type systems, type equivalence, used in \TConv,
-is important.  The type equivalence judgment of the form
-$\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
-are equivalent as types of kind $K$ at stage $A$ under $\G$.
-Figure~\ref{fig:type-equivalence-rules} shows the rules for type
-equivalence.  Type equivalence is basically the least congruence
-closed under term equivalence.  The rules for compatibility (closure
-under type formation) are derived from corresponding typing rules in a
-straightforward manner.  The rules are a little simpler than some
-dependent type systems \AI{such as?}  because there is no abstraction
-at the type level.
+% \begin{figure}
+%     \begin{center}
+%         \begin{minipage}{0.50\hsize}
+%             \infer[\TConst]
+%             {\G \V \textrm{true}:\textrm{bool}@\alpha\beta}
+%             {\textrm{true}:\textrm{bool} \in \Sigma \andalso
+%                 \ID{\G\V\textrm{bool}::*@\alpha\beta} \andalso
+%             }
+%             \caption{A derivation tree using \TConst}
+%             \label{fig:tconst-derivation-tree}
+%         \end{minipage}
+%     \end{center}
+% \end{figure}
+
+% \TConv
+\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is the opposite.}
+As in standard dependent type systems, \TConv{} allows us to replace
+the type of a term with an equivalent one.
+In a type system with dependent types, this kind of rule is essential
+because \AI{?} two types which have different shapes may be equivalent.
+For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
+$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not syntactically equivalent.
+
+% Typing rules for a multi-stage calculus
+% \AI{This paragraph is not very informative.  We shouldn't just refer readers to previous work.}
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
+The rule \TTB{}, which corresponds to brackets \AI{Sounds like the rule corresponds to brackets.  What corresponds to brackets is $\TB$}, means that if term $M$ is of type $\tau$ at stage $A\alpha$,
+$\TB_\alpha M$ is of type $\TW_\alpha \tau$ at stage $A$.
+The rule \TTBL{}, which corresponds to escape, is the converse of \TTB.
+The rule \TGen{} for stage abstraction is straightforward.
+The condition $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that
+the scope of $\alpha$ is in $M$.
+The rule \TIns{} is for applications of stages to stage abstractions.
+\AI{Any comments?}
+The rule \TCsp is the rule for CSP, which means that
+if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.  \AI{This does not explain what this rule means.
+  It just gives how the rule is read.}
+
+\subsubsection{Kind, Type and Term Equivalence.}
+
+Since the syntax of kinds, types, and terms is mutually recursive,
+corresponding notions of equivalence are also mutually recursive.
+They are congruences closed under a few axioms for term equivalence.
+So, the rules for kind and type equivalences are not very interesting
+except implict CSP is allowed.
+We show a few representative rules below.
+
+{\small
+\begin{center}
+\infrule[\textsc{QK-Csp}]{%
+  \G\V K \E J @ A
+}{
+  \G\V K \E J @ A\alpha
+}
+\hfil
+\infrule[\QTCsp]{
+  \G\V \tau \E \sigma :: K@A
+}{
+  \G\V \tau \E \sigma :: K@{A\alpha}
+}
+\\[2mm]
+\infrule[\QTApp]{%
+  \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
+  \G\V M \E N : \rho @A
+}{
+  \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
+}
+\end{center}
+}
+
+% The type equivalence judgment of the form
+% $\G \V \tau \E \sigma : K @ A$ means that types $\tau$ and $\sigma$
+% are equivalent as types of kind $K$ at stage $A$ under $\G$.
+% Figure~\ref{fig:type-equivalence-rules} shows the rules for type
+% equivalence.  Type equivalence is basically the least congruence
+% closed under term equivalence.  The rules for compatibility (closure
+% under type formation) are derived from corresponding typing rules in a
+% straightforward manner.  The rules are a little simpler than some
+% dependent type systems \AI{such as?}  because there is no abstraction
+% at the type level.
 
@@
 
-\begin{figure}
-    \begin{center}
-        \infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
-        \infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
-        \infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
-        \infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
-        \infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
-        \infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
-        \infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
-        \infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
-        \caption{Type Equivalence Rules.}
-        \label{fig:type-equivalence-rules}
-    \end{center}
-\end{figure}
+% \begin{figure}
+%     \begin{center}
+%         \infrule[{\QTAbs }]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A} \\[2mm]
+%         \infrule[\QTApp]{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A} \\[2mm]
+%         \infrule[\textsc{QT-$\TW$}]{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}\andalso
+%         \infrule[\QTCsp]{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}} \\[2mm]
+%         \infrule[\QTGen]{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A} \\[2mm]
+%         \infrule[\QTRefl]{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A} \andalso
+%         \infrule[\QTSym]{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A} \\[2mm]
+%         \infrule[\QTTrans]{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}
+%         \caption{Type Equivalence Rules.}
+%         \label{fig:type-equivalence-rules}
+%     \end{center}
+% \end{figure}
 
-The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
-which means that terms $M$ and $N$ are equivalent as terms of type
-$\rho$ at stage $A$ under $\G$, is defined by the rules in
-Figure~\ref{fig:term-equivalence-rules}.  Most rules are
-straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
-\QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence; the
-rules \QBeta, \QTBLTB, and \QLambda{} correspond to
+% The term equivalence judgment of the form $\G \V M \E N : \rho @ A$,
+% which means that terms $M$ and $N$ are equivalent as terms of type
+% $\rho$ at stage $A$ under $\G$, is defined by the rules in
+We show the rules for term equivalence are shown in 
+Figure~\ref{fig:term-equivalence-rules}, omitting
+straightforward rules for reflexivity, symmetry, transitivity,
+and compatibility.
+% Most rules are
+% straightforward.  The rules \QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns,
+% \QCsp, \QRefl, \QSym, and \QTrans{} make the relation congruence;
+The rules \QBeta, \QTBLTB, and \QLambda{} correspond to
 $\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction, respectively.
@@
     \begin{center}
-        \infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
-        \infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
-        \infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
-        \infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
-        \infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
-        \infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \varepsilon \E N\ \varepsilon : \tau[\alpha \mapsto \varepsilon]@A} \andalso
-        \infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
-        \infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
-        \infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
-        \infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
+        % \infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
+        % \infrule[\QApp]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
+        % \infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
+        % \infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
+        % \infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
+        % \infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \varepsilon \E N\ \varepsilon : \tau[\alpha \mapsto \varepsilon]@A} \andalso
+        % \infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
+        % \infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
+        % \infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
+        % \infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
         \infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
@@
 Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
-reduction to remove $\%_\alpha$ when they developed \LTP{}, as such
-the reduction does not match the operational behavior of the CSP operator
+reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
+reduction does not match the operational behavior of the CSP operator
 in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and as we argue next
+programs, the rule \QPercent makes sense and, as we argue next,
 it is practically significant.
 
+\AI{This paragraph should be polished later.}
 \renewcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
@@
 
-\subsubsection{Staged Semantics}
+\subsubsection{Staged Semantics.}
 
@@
 
-In order to define Staged Reduction, we define redex and evaluation context.
+In order to define staged reduction, we define redex and evaluation contexts.
 
 \begin{definition}[Redex]
-    the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
+    The sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
     \begin{align*}
@@
 \begin{definition}[Evaluation Context]
-    The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$.
-    In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
+  Let $B$ be either \(\varepsilon\) or a transition variable \(\beta\).
+  The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar (in which $A'$ stands for a non-empty stage).
+%  $A$ is assumed to be nonempty (but $B,A'$ can be empty).
     \begin{align*}
-         & E^\varepsilon_B \in ECtx^\varepsilon_B ::= \square\ (\text{if\ } B = \varepsilon)
-        \mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B \mid \TB_\alpha E^\alpha_B
-        \mid \Lambda\alpha.E^\varepsilon_B \mid E^\varepsilon_B\ A'                                                                       \\
-         & E^A_B \in ECtx^A_B                     ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B \\
-         & \hspace{25mm} \mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B \mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)      \\
-         & \hspace{25mm} \mid \Lambda\alpha.E^\varepsilon_B \mid E^A_B\ B' \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)        \\
+         E^\varepsilon_B \in ECtx^\varepsilon_B & ::= \square\ (\text{if\ } B = \varepsilon)
+        \mid E^\varepsilon_B\ M \mid v^\varepsilon\ E^\varepsilon_B \mid \TB_\alpha E^\alpha_B
+        \mid \Lambda\alpha.E^\varepsilon_B \mid E^\varepsilon_B\ A \\
+         E^{A'}_B \in ECtx^{A'}_B  & ::= \square\ (\text{if } A' = B) \mid \lambda x:\tau.E^{A'}_B \mid E^{A'}_B\ M \mid v^{A'}\ E^{A'}_B \\
+         & \mid \TB_\alpha E^{A'\alpha}_B \mid \TBL_\alpha E^{A}_B \ (\text{where } A\alpha = A')      \\
+         & \mid \Lambda\alpha.E^{A'}_B \mid E^{A'}_B\ A \mid \%_\alpha\ E^{A'}_B \ (\text{where } A\alpha = A')
     \end{align*}
@@
 
-We write $E^A_B[M]$ for the term obtained by filling the hole $\square$ in $E^A_B$ by $M$
-and define the staged reduction relation.
-Intuitively, $\square$ is the placefolder for redex.
-Examples of evaluation context is below.
+The subscripts $A$ and $B$ in $E^A_B$ stand for the stage of the evaluation context and of the hole, respectively.
+The grammer represents that staged reduction is left-to-right and call-by-value and terms under \(\Lambda\) is reduced.
+A few examples of evaluation context are shown below:
 \begin{align*}
-     & \square\ (\lambda x:\I.x) \in  ECtx^\varepsilon_\varepsilon            \\
-     & \Lambda\alpha.\square\ \epsilon \in ECtx^\varepsilon_\varepsilon       \\
-     & \TBL_\alpha \TB_\alpha \TBL_\alpha \square \in ECtx^\alpha_\varepsilon
+     \square\ (\lambda x:\I.x) & \in  ECtx^\varepsilon_\varepsilon            \\
+     \Lambda\alpha.\square\ \epsilon & \in ECtx^\varepsilon_\varepsilon       \\
+     \TBL_\alpha \TB_\alpha \TBL_\alpha \square & \in ECtx^\alpha_\varepsilon
 \end{align*}
+%
+We write $E^A_B[M]$ for the term obtained by filling the hole $\square$ in $E^A_B$ by $M$.
+
+Now we define staged reduction using the redex and evaluation contexts.
 
@@
 
-This reduction relation reduces a typed term in a unique way
-which is appropriate as call-by-value code generator.
-It means that terms in brackets are not evaluated until the terms are run
+This reduction relation represents a term reduces in a deterministic,
+left-to-right, call-by-value manner.  An application of an abstraction
+is executed only at stage \(\varepsilon\) and only a quotation at
+stage \(\varepsilon\) is spiliced into the surrounding code---notice
+that, if \(\TB_\alpha v^\alpha\) is at stage \(\varepsilon\), then the
+redex \(\TBL_\alpha \TB_\alpha v^\alpha\) is at stage \(\alpha\).
+In other words, terms in brackets are not evaluated until the terms are run
 and arguments of a function are evaluated before the application.
@@
 \begin{align*}
-     & \hspace{9mm} \Lambda\alpha.(\TB_\alpha \underline{\TBL_\alpha \TB_\alpha} (\lambda x:\I.x)\ 10)\ \varepsilon \\
-     & \longrightarrow_s \underline{\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x)\ 10)\ \varepsilon}                   \\
-     & \longrightarrow_s \underline{(\lambda x:\I.x)\ 10}                                                           \\
-     & \longrightarrow_s 10
+     & (\Lambda\alpha.(\TB_\alpha \underline{\TBL_\alpha \TB_\alpha ((\lambda x:\I.x)\ 10))})\ \varepsilon \\
+      \longrightarrow_s & \underline{(\Lambda\alpha.(\TB_\alpha ((\lambda x:\I.x)\ 10)))\ \varepsilon}                   \\
+      \longrightarrow_s & \underline{(\lambda x:\I.x)\ 10}                                                           \\
+      \longrightarrow_s & 10
 \end{align*}

### 2019-06-17 text/properties.tex
Revised Section 4.

@@
 
-In this section, we prove \AI{use ``show'' because we omit proofs from the paper} basic properties of \LMD: preservation, strong normalization, confluence, and progress.
-These theorem shows that the type system of \LMD is strong enough to ensure a typed term of \LMD never go wrong.
-\AI{In this setting, a simple type system is already sufficient to guarantee
-  ``a well-typed term never goes wrong.''  If the language has
-  case analysis that uses dependent types, then
-  we could say more.
-}
+In this section, we show basic properties of \LMD: preservation, strong normalization, confluence, and progress.
 
@@
 typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto\varepsilon]$.
+Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto A]$.
+\red{2つの代入補題を指してSubstitution Lemmasということが出来るのか?}
+
+In order to write Substitution Lemma briefly, we write $\G\V J@A$ for an arbitary judgment
+amongst $\G\V M:\tau@A$, $\G\V \tau::K@A$, $\G\V K \iskind @A$, $\G\V M \E N : \tau @ A$, 
+$\G\V \tau \E \sigma @ A$, and $\G \V K \E J @ A$.
 
 \begin{lemma}[Substitution Lemma on Terms]
-	\begin{flalign*}
-		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
-		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
-		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
-		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
-	\end{flalign*}
+	If $\G, z:\xi@B, \D \V J @ A$ and $\G\V P:\xi @B$ then $\G, \D[z \mapsto P] \V J[z \mapsto P] @ A$.
 \end{lemma}
 
-\AI{Since the order of variable declarations is significant,
-  we cannot assume $z$ is always declared at the end.}
+\red{TODO: Fix the proof.}
+\red{$\G\V J@A$における代入を定義する必要があるか?}
 
@@
 
-\begin{theorem}[Substitution Lemma on Stages]
-	\begin{flalign*}
-		\text{If\ } \G \V M:\tau @A
-		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V M[\beta \mapsto \varepsilon]:\tau[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&\\
-		\text{If\ } \G \V \tau::K @A
-		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V \tau[\beta \mapsto \varepsilon]::K[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&\\
-		\text{If\ } \G \V K\iskind @A
-		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V K[\beta \mapsto \varepsilon] \iskind @A[\beta \mapsto \varepsilon].&\\
-		\text{If\ } \G \V M\E N : \tau @A
-		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V M[\beta \mapsto \varepsilon]\E N[\beta \mapsto \varepsilon] : \tau[\beta \mapsto \varepsilon]  @A[\beta \mapsto \varepsilon].&\\
-		\text{If\ } \G \V \tau\E \sigma : K @A
-		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V \tau[\beta \mapsto \varepsilon]\E \sigma[\beta \mapsto \varepsilon] : K[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&\\
-		\text{If\ } \G \V K\E J @A
-		&\text{\ then\ } \G[\beta \mapsto \varepsilon]\V K[\beta \mapsto \varepsilon]\E J[\beta \mapsto \varepsilon] @A[\beta \mapsto \varepsilon].&
-	\end{flalign*}
-\end{theorem}
+\begin{lemma}[Substitution Lemma on Stages]
+	If $\G \V J @ A$ then $\G[\beta\mapsto B] \V J[\beta\mapsto B] @ A[\beta\mapsto B]$.
+\end{lemma}
 
@@
 As usual~\cite{TAPL}, Inversion Lemmas enable us to infer the types of subterms of a term from the type of the term.
-They are composed of three parts.
-The first part states that we can infer types of subterms.
-The second and third parts state 
-that when we have a type equivalence, we can infer the shape of type from the left to the right, and vice versa.
-We need both of the second and the third because of the reflexivity of the type equivalence. \AI{Symmetry?  We can omit the third one.}
 
 \begin{lemma}[Inversion Lemma for $\Pi$-types]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
-	\begin{enumerate}
-		\item $\G \V \sigma \E \sigma'@A$ and
-		\item $\G ,x:\sigma@A\V M:\tau @A$.
-	\end{enumerate}
-	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$,
-		\item $\G \V \sigma \E \sigma' : K @A$, and
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$.
-	\end{enumerate}
-	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
-	\begin{enumerate}
-		\item $\rho = \Pi x:\sigma'.\tau'$,
-		\item $\G \V \sigma \E \sigma' : K @A$, and
-		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$.
-	\end{enumerate}
+	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$
+	then $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma@A\V M:\tau @A$.
 \end{lemma}
@@
 \begin{proof}
-	Straightforward induction on derivations.
+	First, we generalize this theorem by adding statements about $\Pi$-types in equivalence relation in order to use induction.
+	After that, we can prove with straightforward induction on derivations.
 \end{proof}
 
-\begin{theorem}[Inversion Lemma for $\TW$-types]
-	\begin{item}
-	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$ and
-		      \item $\G @A\V \tau \E \tau' : K @A$.
-	      \end{enumerate}
-	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
-	      \begin{enumerate}
-		      \item $\rho = \TW_\alpha \tau'$ and
-		      \item $\G @A\V \tau \E \tau' : K @A$.
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
+\begin{lemma}[Inversion Lemma for $\TW$-types]
+	If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
+\end{lemma}
 
 \begin{proof}
-	Straightforward induction on derivations.
+	Prove as with Inversion Lemma for $\Pi$-types.
 \end{proof}
 
-\begin{theorem}[Inversion Lemma for $\forall$-types]
-	\begin{item}
-	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$ and
-		      \item $\G \V \tau \E \tau' : K @A$.
-	      \end{enumerate}
-	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
-	      \begin{enumerate}
-		      \item $\rho = \forall\alpha.\tau'$ and
-		      \item $\G \V \tau \E \tau' : K @A$.
-	      \end{enumerate}
-	\end{item}
-\end{theorem}
+\begin{lemma}[Inversion Lemma for $\forall$-types]
+	If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
+\end{lemma}
 
 \begin{proof}
-	Straightforward induction on derivations.
+	Prove as with Inversion Lemma for $\Pi$-types.
 \end{proof}
@@
 
-Unique Decomposition ensure that
-,for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
+Unique Decomposition ensure that,
+for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
 This theorem is important because it guarantee
@@
 your interpreter works just as intended.
+Although, in ordinary calculi, there is a condition that $\G$ is $\emptyset$,
+the condition is relaxed because variables at non-$\varepsilon$ stages are values in \LMD.
 
 \begin{theorem}[Unique Decomposition]
-	If $x:\tau @\varepsilon \notin \G$ and $\G \V M : \tau @ A$ then either
+	If $\G$ does not have any variable declared at stage $\varepsilon$ 
+	and $\G \V M : \tau @ A$ then either
 	\begin{enumerate}
@@
 \begin{theorem}[Progress]
-	If $x:\tau @\varepsilon \notin \G$ and $\G \V M : \tau  @ A$ then
+	If $\G$ does not have any variable declared at stage $\varepsilon$ and $\G \V M : \tau  @ A$ then
 	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
@@
 \end{proof}
-
-\AI{Explain the condition on $\G$.}

### 2019-06-18 text/related-work.tex
Revised related work.

--- 2019-06-14 text/related-work.tex
@@
 
-% 依存型の歴史
-
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
-
-% 依存型の応用
-
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
-
 % 多段階計算の歴史
 
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
+Multi-stage calculi also have a long history of research.
+Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$ \cite{davies1996temporal}.
 However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
 Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
 Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
+Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$ \cite{taha2003environment} and 
 construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
 
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
+In $\lambda^\TW$ \cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
 show that run can be represented as application of $\varepsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
+In \LTP \cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
 which allows us to dump the quoted code into an external file.
@@
 which include filtering in signal processing, matrix-vector product, and DSL compiler.
+
+% 依存型の歴史
+
+There are many papers on dependent types and most of them are affected by the pioneering work of Per Martin-L\"{o}f \cite{martin1973intuitionstic}.
+$\lambda^\Pi$ \cite{Meyer1986}, Calculus of Constructions \cite{coquand:inria-00076024}, 
+and Harper, Honsell and Plotkin \cite{harper1993framework} are famous papers on dependent types.
+In Advanced Topics in Types and Programming Languages \cite{attapl},
+a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
+We adopted \cite{attapl}-like dependent types for \LMD.
+
+% 依存型の応用
+
+Applications of dependent types for real problems were also researched.
+One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
+interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
+In Xi and Pfenning \cite{Xi98}, they extended SML with restricted dependent types
+and succeeded in reducing the bounds checking of arrays.
+In Xi and Robert \cite{xi2001dependently}, they design a type system for an assembly language and
+it is useful for spped up.
+Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
+
+% 関連研究との比較
+
+Brady and Hammond \cite{brady2006dependently} extended a dependent type system 
+with Taha's staging technique \cite{taha2007gentle} in order to implement a staged interpreter.
+However, they focused on implementation and there is no theoritical discussion in their paper.
+
+% 他の方法としてどのようなものが考えられたか
+
+Although we define type equivalence of \LMD with composition of equivalence rules,
+there is another candiate to define,
+which gives reduction on types and compare the results of reduction such as \cite{sorensen2006lectures}.
+This method is better than one of \LMD because equivalence rules become simple.
+However, we reject it because it cannot handle CSP flexibly.

### 2019-06-18 text/properties.tex
Revise Section 4.

@@
 
-In this section, we show basic properties of \LMD: preservation, strong normalization, confluence, and progress.
+In this section, we show basic properties of \LMD: preservation, strong normalization, confluence for full reduction, and progress for staged reduction.
 
@@
 
-Substitution Lemma in \LMD\ is little more complicated than an ordinary one 
-because there are six types of judgment and two types of substitution in \LMD.
-Substitution Lemma on Terms states that term substitution $[z \mapsto P]$ preserves
-typing, kinding, well-formed kinding, term equivalence, type equivalence, and king equivalence.
-Substitution Lemma on Terms states the same for stage substitution $[\beta\mapsto A]$.
-\red{2つの代入補題を指してSubstitution Lemmasということが出来るのか?}
+Substitution Lemma in \LMD{} is little more complicated than usual
+because there are eight judgment forms and two kinds of substitution.
+Term Substitution Lemma states that term substitution $[z \mapsto M]$
+preserves derivability of judgments and Stage Substitution Lemma
+states similarly for stage substitution $[\alpha\mapsto A]$.
 
-In order to write Substitution Lemma briefly, we write $\G\V J@A$ for an arbitary judgment
-amongst $\G\V M:\tau@A$, $\G\V \tau::K@A$, $\G\V K \iskind @A$, $\G\V M \E N : \tau @ A$, 
-$\G\V \tau \E \sigma @ A$, and $\G \V K \E J @ A$.
+We let $\mathcal{J}$ stand for judgments $K \iskind @A$, $\tau::K@A$,
+$M:\tau@A$, $K \E J @ A$, $\tau \E \sigma @ A$, and
+$M \E N : \tau @ A$.  Substitutions $\mathcal{J}[z \mapsto M]$ and
+$\mathcal{J}[\alpha \mapsto A]$ are defined in a straightforward
+manner.  Using these notations, the two substitution lemmas are stated as follows:
+\AI{Did we define $\Delta [x \mapsto N]$?}
 
-\begin{lemma}[Substitution Lemma on Terms]
-	If $\G, z:\xi@B, \D \V J @ A$ and $\G\V P:\xi @B$ then $\G, \D[z \mapsto P] \V J[z \mapsto P] @ A$.
+\begin{lemma}[Term Substitution]
+  If $\G, z:\xi@B, \D \V \mathcal{J}$ and $\G\V P:\xi @B$, then $\G, \D[z \mapsto P] \V \mathcal{J}[z \mapsto P]$.  Similarly, if $\V \G, z:\xi@B, \D$ and
+  $\G\V P:\xi @B$, then $\V \G, \D[z \mapsto P]$.
 \end{lemma}
@@
 \begin{proof}
-	Straightforward induction on derivations.
+  By simultaneous induction on derivations.
+ \qed
 \end{proof}
 
-\begin{lemma}[Substitution Lemma on Stages]
-	If $\G \V J @ A$ then $\G[\beta\mapsto B] \V J[\beta\mapsto B] @ A[\beta\mapsto B]$.
+\begin{lemma}[Stage Substitution]
+	If $\G \V \mathcal{J}$, then $\G[\beta\mapsto B] \V \mathcal{J}[\beta\mapsto B]$.  Similarly, if $\G \V \mathcal{J}$, then $\V \G[\beta\mapsto B]$.
 \end{lemma}
@@
 \begin{proof}
-	Straightforward induction on derivations.
+  By simultaneous induction on derivations.
+  \qed
 \end{proof}
@@
 
-The following three Inversion Lemmas are needed to prove main theorems.
-As usual~\cite{TAPL}, Inversion Lemmas enable us to infer the types of subterms of a term from the type of the term.
+The following Inversion Lemma is needed to prove main theorems.
+As usual~\cite{TAPL}, Inversion Lemma enables us to infer the types of subterms of a term from the type of the term.
 
-\begin{lemma}[Inversion Lemma for $\Pi$-types]
-	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$
+\begin{lemma}[Inversion]\ 
+  \begin{enumerate}
+  \item If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$,
     then $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma@A\V M:\tau @A$.
+  \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
+  \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
+  \end{enumerate}
 \end{lemma}
@@
 \begin{proof}
-	First, we generalize this theorem by adding statements about $\Pi$-types in equivalence relation in order to use induction.
-	After that, we can prove with straightforward induction on derivations.
-\end{proof}
+  Each item is strengthen by statements about type equivalence.
+  For example, the first statement is augmented by
+  \begin{quotation}
+    If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$, then there exist
+    $\sigma'$ and $\tau'$ such that $\rho = \Pi x:\sigma'.\tau'$ and
+    $\G \V \sigma \E \sigma' : K @A$ and
+    $\G, x:\sigma@A\V \tau \E \tau' : J @A$.
+  \end{quotation}
+  and its symmetric version.  Then, they are proved simultaneously by induction on derivations.
 
-\begin{lemma}[Inversion Lemma for $\TW$-types]
-	If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-\end{lemma}
-
-\begin{proof}
-	Prove as with Inversion Lemma for $\Pi$-types.
-\end{proof}
-
-\begin{lemma}[Inversion Lemma for $\forall$-types]
-	If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
-\end{lemma}
-
-\begin{proof}
-	Prove as with Inversion Lemma for $\Pi$-types.
+  Similarly for the others.
+ \qed
 \end{proof}
@@
 Thanks to Substitution Lemmas and Inversion Lemmas, we can prove Preservation easily.
-Preservations ensure that any one step reduction preserves type.
 
@@
 	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations.
+	For each case, we can use straightforward induction on derivations. \AI{何の derivation?}
 	Difficult cases are \TApp, \TTBL, and \TIns.
@@
 
-Strong Normalization is also important property which guarantee that
+Strong Normalization is also an important property, which guarantees that
 no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus.
+We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{Tsukada} \AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
 
 \begin{theorem}[Strong Normalization]
-	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
+	If $\G\V M_1:\tau@A$ then there is no infinite sequence $(M_i)_{i\ge1}$ of terms such that
 	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$.
@@
 \begin{proof}
-	In order prove this theorem, we define a translation $\natural$ from \LMD\ to the symply typed lambda calculus.
-	Second, we prove $\natural$ preserves typing and $\beta$-reductions.
-	Then, we can prove Strong Normalization of \LMD\ from Strong Normalization of the symply typed lambda calculus.
+	In order to prove this theorem, we define a translation $(\cdot)^\natural$ from \LMD\ to the symply typed lambda calculus.
+	Second, we prove the $\natural$-translation preserves typing and reduction.
+	Then, we can prove Strong Normalization of \LMD from Strong Normalization of the symply typed lambda calculus.
 \end{proof}
@@
 Confluence is a property that any reduction sequences from one typed term converge.
-Because we have proved Strong Normalization, we can use Newman's Lemma to prove Confluence.
+Since we have proved Strong Normalization, we can use Newman's Lemma~\cite{} to prove Confluence.
 
@@
 \begin{proof}
-	Because we proved Strong Normalization of \LMD, 
-	we can use Newman's lemma to prove Confluence of \LMD.
-	Then, what we must show is Weak Church-Rosser Property now.
-	When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
-	In short, they are never overlapped each other.
-	So, we can reduce one of them after we reduce another.
+  We can easily show Weak Church-Rosser.  Use Newman's Lemma.
+	% Because we proved Strong Normalization of \LMD, 
+	% we can use Newman's lemma to prove Confluence of \LMD.
+	% Then, what we must show is Weak Church-Rosser Property now.
+	% When we consider two different redexes in a \LMD term, they can only be disjoint, or one is a part of the other.
+	% In short, they are never overlapped each other.
+	% So, we can reduce one of them after we reduce another.
 \end{proof}
 
-Unique Decomposition ensure that,
-for every typed term, we can find just one redex to reduce by the evaluation context or it is a value.
-This theorem is important because it guarantee
-that the evaluation context decides a redex to reduce deterministically.
-Specifically speaking, this theorem guarantee that 
-when you write a interpreter using the evaluation context of \LMD,
-your interpreter works just as intended.
-Although, in ordinary calculi, there is a condition that $\G$ is $\emptyset$,
-the condition is relaxed because variables at non-$\varepsilon$ stages are values in \LMD.
+Now, we turn our attention to proving Progress for staged semantics.
+The following lemma Unique Decomposition ensures that, every typed
+term is either a value or can be uniquely decomposed to an evaluation
+context and a redex, ensuring that a well typed term is not
+immediately stuck and the staged semantics is deterministic.
 
@@
   If $\G$ does not have any variable declared at stage $\varepsilon$ 
-	and $\G \V M : \tau @ A$ then either
+  and $\G \V M : \tau @ A$, then either
   \begin{enumerate}
   \item $ M \in V^A$, or
-		\item there exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$ with $B = \varepsilon$ or $B = \beta$ for some $\beta$.
+  \item there uniquely exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$.
   \end{enumerate}
@@
 \begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
+  We can prove by straightforward induction on typing derivations.
+  Main cases are \TApp, \TTBL, and \TIns.
   We need Inversion Lemmas for them.
@@
 
-Progress states $\longrightarrow_s$ defines appropriate reduction for typed terms of \LMD.
-Thanks to Unique Decomposition, we can prove this theorem easily.
+In a usual setting, the type environment $\G$ has to be empty, namely
+the term has to be closed.  The condition is relaxed here because
+variables at stages higher than \(\varepsilon\) are considered
+symbols.  In fact, this relaxation is required for proof by induction
+to work.
 
-\begin{theorem}[Progress]
+% This theorem is important because it guarantees
+% that the evaluation context decides a redex to reduce deterministically.
+% Specifically speaking, this theorem guarantee that 
+% when you write a interpreter using the evaluation context of \LMD,
+% your interpreter works just as intended.
+
+Progress is a collorary of Unique Decomposition.
+
+\begin{corollary}[Progress]
 	If $\G$ does not have any variable declared at stage $\varepsilon$ and $\G \V M : \tau  @ A$ then
 	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
-\end{theorem}
+\end{corollary}
 
-\begin{proof}
-	We can prove by straightforward induction on derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
-\end{proof}
+\AI{Don't we prove $\longrightarrow_s$ is a subrelation of $\longrightarrow$?}

### 2019-06-18 text/properties.tex
Minor revision.

@@
 
-Now, we turn our attention to proving Progress for staged semantics.
-The following lemma Unique Decomposition ensures that, every typed
+Now, we turn our attention to staged semantics.  First, the staged
+reduction relation is a subrelation of full reduction, so Subject
+Reduction holds also for the staged reduction.
+
+\begin{theorem}
+  If $M \longrightarrow_s M'$, then $M \longrightarrow M'$.
+\end{theorem}
+\begin{proof}
+  Easy.
+ \qed
+\end{proof}
+
+The following theorem Unique Decomposition ensures that, every typed
 term is either a value or can be uniquely decomposed to an evaluation
@@
   \item $ M \in V^A$, or
-  \item there uniquely exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$.
+  \item $M$ can be uniquely decomposed into an evaluation context and a redex, that is, there uniquely exist $B, E^A_B$, and $R^B$ such that $M = E^A_B[R^B]$.
   \end{enumerate}
@@
   We can prove by straightforward induction on typing derivations.
-  Main cases are \TApp, \TTBL, and \TIns.
-  We need Inversion Lemmas for them.
+  Main cases are \TApp, \TTBL, and \TIns, where we use Inversion.
+  \qed
 \end{proof}
 
-In a usual setting, the type environment $\G$ has to be empty, namely
-the term has to be closed.  The condition is relaxed here because
-variables at stages higher than \(\varepsilon\) are considered
+The type environment $\G$ in the statement usually has to be empty;
+in other words, the term has to be closed.  The condition is relaxed here
+because variables at stages higher than \(\varepsilon\) are considered
 symbols.  In fact, this relaxation is required for proof by induction
@@
 \begin{corollary}[Progress]
-	If $\G$ does not have any variable declared at stage $\varepsilon$ and $\G \V M : \tau  @ A$ then
+	If $\G$ does not have any variable declared at stage $\varepsilon$ and $\G \V M : \tau  @ A$, then
 	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.

### 2019-06-18 text/introduction.tex
Fix the latter half of introduction.

@@
 
-\subsection{Dependent Types}
+\subsection{Multi-stage Programming with Dependent Types}
 
-% \subsubsection{依存型とは何か?}
+% 依存型とは何か?
 
-Dependent types are types which is \AI{are} dependent on values.
-We can use dependent types for securer programming. \AI{Cite Xi--Pfenning, for example?}
+One natural idea to address this problem is the introduction of dependent types.
+Dependent types are types which are dependent on values.
+We can use dependent types for securer programming like Xi and Pfenning \cite{Xi98}.
 For example, we can realize vectors with their sizes with them.
@@
 we can confirm the two arguments of \verb|vadd| function has the same length.
-\red{secure programming? finer grained typing? とか}
-
-\subsection{Multi-stage Programming with Dependent Types}
-\red{このsubsectionは短いので上とくっつけてもいいかもしれない}
-\AI{くっつけましょう。Section 1 で指摘した問題を依存型で解決するというのは自然なアイデアだし。One natural idea to address this problem is the introduction of dependent types. みたいなこといって、依存型の導入をする。先行研究として Brady--Hammond にもふれる。}
-% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}
+% \red{secure programming? finer grained typing? とか}
 
@@
 \LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming more safer \AI{remove ``more''} with the power of dependent types.
-
-\AI{Give a summary of our technical contribution as itemization.}
+\LMD makes multi-stage programming safer with the power of dependent types.
+Our technical contribution are summarized as follows:
+\begin{itemize}
+        \item we give the formal definition of \LMD with its syntax, 
+        type system which contains type equivalence, full, reduction, and staged reduction;
+        \item for the full reduction, we prove subject reduction, strong normalization, and confluence
+        \item fot the staged reduction, we prove unique decomposition and progress.
+\end{itemize}
 

### 2019-06-18 text/introduction.tex
FInish revising Seciton 1.

@@
 
-Multi-stage programming enables us to generate and run fragments of code at runtime.
-\AI{It sounds like the subject of ``generate and run'' is human being (``us'').
-Something like ``Multi-stage programming offers linguistic support for dynamic code generation and execution.''?}
-MetaOCaml~\cite{oleg2014} \AI{You need a space between a word and a citation.
-Taha's original MetaOCaml should be cited, too.} provides features for multi-stage programming, which are brackets, escape, and run.
-\AI{CSP?}
+Multi-stage programming enables programmers to generate and run fragments of code at runtime.
+We can treat a piece of code as a value with multi-stage programming.
+It means code fragments can be substituted into variables, combined and run at runtime.
+Multi-stage programming improves the performance of programs by generating optimized code for a given input at runtime. \cite{taha2007gentle}
+% MetaOCamlを例に挙げて多段階計算について説明する
+
+MetaOCaml~\cite{calcagno2003implementing}\cite{oleg2014} provides features for multi-stage programming, which are brackets, escape, run, and CSP.
 Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
@@
 
-% \subsubsection{ベクトル計算も高速化できる}
+% 多段階計算の型理論の既存研究の紹介
+
+Existing type systems for multi-stage calculi ensure that
+the generated code is well-typed and code generation and evaluation are performed in the intended order.
+For example, the type system of MetaOCaml~\cite{taha1999multi} classify expressions in a program
+with the depth of brackets in order to handle them appropriately.
+In $\lambda^\triangleright$ by Tsukada and Igarashi~\cite{Tsukada},
+they use environment classifier to classify and 
+succeeded in recognizing code values which are run safely at type-checking time.
+
+% ベクトル計算も高速化できる
 
@@
 We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
-\red{MetaOCamlで書いた長さ付きベクトルの例?}
 
-% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
+% 多段階計算で生成したコードは特殊化されているが故に問題も多い
 
@@
 For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
-Otherwise, we will get a Segmentation Fault error.
-\AI{Why SEGV?  MetaOCaml will raise an exception.}
+Otherwise, we will get a exception.
 This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
-
-% We call this problem \red{Specialized Code Problem}.
-
-\AI{このイントロ、各段落はまあまあよいのですが、全体の流れが、ふたつ目の文から MetaOCaml という特定の多段階プログラミング言語の話をして、それから応用と問題点の話になりますが、ここが多段階プログラミング一般の話なのか MetaOCaml 固有の話なのかがぶれているように思います。まずは、多段階プログラミング一般の話を応用も含めてする。(他の多段階計算ができるシステムを無視しない。)それから、MetaOCaml の紹介と、その型システムの問題点の話をすべきでしょう。MetaOCaml の型システムでできることもふれておいた方がよいでしょう。}
 
@@
 so that the type system can guarantee optimized functions are used properly.
+Although there is a trial to combine multi-stage programming and dependent type by Brady and Hammond~\cite{brady2006dependently},
+they didn't give a formal definition and properties for the calculus.
 
@@
         type system which contains type equivalence, full, reduction, and staged reduction;
-        \item for the full reduction, we prove subject reduction, strong normalization, and confluence
+        \item for the full reduction, we prove preservation, strong normalization, and confluence
         \item fot the staged reduction, we prove unique decomposition and progress.
@@
 The organization of this paper is the following.
-Section 2 gives an informal overview of \LMD.
-Section 3 defines \LMD and
-Section 4 shows the properties of \LMD including Unique Decomposition \AI{There are more important properties that should be mentioned!  In fact, the properties should be mentioned earlier.}.
-Section 5 discusses future works.
-Finally, Section 6 discusses related works.
-\AI{Use $\backslash$label and $\backslash$ref!}
-\AI{``Related work'' and ``future work'' (they are uncountable).}
-\AI{Related work is discussed in Section 5?  Section 6 is the section for conclusion, which includes future work.}
+Section \ref{sec:informal-overview} gives an informal overview of \LMD.
+Section \ref{sec:formal-definition} defines \LMD and
+Section \ref{sec:properties} shows the properties of \LMD including preservation, strong normalization, confluence, and progress.
+Section \ref{sec:related-work} discusses related work.
+Finally, we conclude this paper in Section \ref{sec:conclusion} and discusses future work.

### 2019-06-18 text/informal-overview.tex
FInish revising Seciton 1.
Reivised for easy comments.

@@
 
-\section{Informal Overview of \LMD}
+\section{Informal Overview of \LMD \label{sec:informal-overview}}
 
@@
 
-\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
-\AI{ないです．たしかにあんまりつけるとうるさいですね．2.1 の冒頭とかは文ごと不要なのでは？}
+% \red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
+% \AI{ないです．たしかにあんまりつけるとうるさいですね．2.1 の冒頭とかは文ごと不要なのでは？}
 \subsection{\LTP}
@@
 
-\LTP\cite{Hanada2014} is a multi-stage calculus with CSP by Hanada and Igarashi.
 In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
@@
 
-% transition variable and transition
+% stage variable and stage
 
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
-a sequence of transition variables is called \textit{transition}.
-The empty transition is represented by $\varepsilon$.
+The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{stage variable}
+\footnote{In the original \LTP paper, this is called a \textit{transition variable}. 
+However, we call it a \textit{stage variable} in this paper.} and
+a sequence of stage variables is called \textit{stage}.
+The empty stage is represented by $\varepsilon$.
 They are used to show the thickness of brackets. \AI{Perhaps ``thickness'' doesn't make sense.}
@@
 
-% transition abstraction and application
+% stage abstraction and application
 
-There are abstractions for transition variables and applications for transition abstraction in \LTP.
+There are abstractions for stage variables and applications for stage abstraction in \LTP.
 They look like $\Lambda\alpha.M$ and $M A$, respectively.
-A transition abstraction binds a transition variable in a term.
+A stage abstraction binds a stage variable in a term.
 For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-It is only natural \AI{?} there is a reduction rule for transition application in \LTP.
+There is a reduction rule for stage application in \LTP.
 The rule is the following.
@@
 
-% transition-related symbols disappear when the empty transition is substituted.
+% stage-related symbols disappear when the empty stage is substituted.
 % In short, about "run"
 
-Another important rule about a transition variable is 
-that symbols with transition variables disappear 
-when the empty transition $\varepsilon$ is substituted to the transition variable.
+Another important rule about a stage variable is 
+that symbols with stage variables disappear 
+when the empty stage $\varepsilon$ is substituted to the stage variable.
 The purpose of this rule is express \verb|run| without any special symbol.
@@
 Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \varepsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty transition $\varepsilon$.
+In \LTP, \verb|run| is realized with application to the empty stage $\varepsilon$.
 
-% transition in typing rules
+% stage in typing rules
 
 A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-A transition in a judgement represents where the judgement is true.
+A stage in a judgement represents where the judgement is true.
 For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
-term $\lambda x:\I.x$ has type $\I \to \I$ at transition $\alpha$.
-Especially, terms without quoting exist at the empty transition $\varepsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\varepsilon$ transition and 
-$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.
-Terefore, transitions appear in typing rules, too.
+term $\lambda x:\I.x$ has type $\I \to \I$ at stage $\alpha$.
+Especially, terms without quoting exist at the empty stage $\varepsilon$.
+For example, $(\lambda x:\I.x)\ (1+2)$ is at $\varepsilon$ stage and 
+$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ stage.
+Terefore, stages appear in typing rules, too.
 \begin{center}
@@
 \TTB, corresponding to brackets, means 
-if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
+if $M$ is typed $\tau$ at stage $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
 \TTBL\ is converse of \TTB.
@@
 CSP, cross-stage persistence, is an important feature of \LTP.
-It enables us to embed value at an outer transition into an inner transition.
+It enables us to embed value at an outer stage into an inner stage.
 $\%$ is dedicated to CSP in \LTP.
@@
 Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-From here, we use the word "stage" instead of "transition" 
-because we develop a multi-stage calculus, not a multi-transition calculus.
-\red{stageのほうが言葉としてふさわしいと言いたい}
 There are three technical points in the extension from \LTP to \LMD.

### 2019-06-18 text/informal-overview.tex
Revising.

@@
 It enables us to embed value at an outer stage into an inner stage.
-$\%$ is dedicated to CSP in \LTP.
-\AI{What should me mentioned here is that in MetaOCaml CSP is implicit but
-in \LTP it's explicit.}
+In \LTP, CSP is written explicitly and $\%$ is a symbol dedicated to CSP
+although MetaOCaml CSP is implicit and there is no symbol for CSP.
 For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
@@
 The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.  \AI{``dependent product'' vs. ``dependent function''.}
+by replacing the function type $\tau\to\sigma$ with the dependent function type $\Pi x:\tau.\sigma$.
 
@@
 Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.  \AI{Vect\ true may be a better example?}
+introduced in order to prohibit making illegal types such as $\textrm{Vector}\ \textrm{true}$.
 For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
@@
 Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
-For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
+For example, $\textrm{Vector}\ 7$ should be equivalent to $\textrm{Vector}\ (3+4)$
 but they are not equivalent seemingly. Thus, we must define equivalence rules.

### 2019-06-19 text/introduction.tex
Revise -- getting close to the final form.

--- 2019-06-18 text/introduction.tex
@@
 
-\subsection{Multi-stage Programming}
+\subsection{Multi-stage Programming and MetaOCaml}
 
@@
 
-Multi-stage programming enables us to generate and run fragments of code at runtime.
-\AI{It sounds like the subject of ``generate and run'' is human being (``us'').
-Something like ``Multi-stage programming offers linguistic support for dynamic code generation and execution.''?}
-MetaOCaml~\cite{oleg2014} \AI{You need a space between a word and a citation.
-Taha's original MetaOCaml should be cited, too.} provides features for multi-stage programming, which are brackets, escape, and run.
-\AI{CSP?}
-Brackets, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
-Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
-Escape, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
-Unlike run, escape is supposed to use in a fragment of code, that is, escape cannot be used as an alternative of run.
-For example, the following MetaOCaml expression
+\AI{前の版は，まだ MetaOCaml specific な話と，MSP 一般の話が交互に出てきて
+わかりづらかったと思います．}
 
+Multi-stage programming makes it easier for programmers to implement
+generation and execution of code at run time by providing language
+constructs for composing and running pieces of code as first-class
+values.  A promising application of multi-stage programming is
+(run-time) code specialization, which is to generate program code
+specialized to partial inputs to the program and such applications are
+studied in the literature~\cite{taha2007gentle}  \AI{We should list
+applications of multi-stage programming, not necessarily of MetaOCaml.}
+
+MetaOCaml~\cite{calcagno2003implementing,oleg2014} is an extension of
+OCaml\footnote{\url{http://ocaml.org}} with constructs for multi-stage
+programming, including brackets, escape, run, and cross-stage
+persistence (CSP) .  Brackets, written \verb|.< e >.| in MetaOCaml,
+makes a value that represents the code (or abstract syntax tree) of
+expression \verb|e|; and escape, written \verb|.~ e| and is supposed
+to appear inside brackets, evaluates \verb|e| to a code value and
+expands the code into the surrounding code.
+For example,
 \begin{verbatim}
@@
 \end{verbatim}
-evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
+evaluates to \verb|.< (fun x -> x + 1) 2 >.|.  
+Run, written \verb|run e|, evaluates \verb|e| to a code value
+and executes it.  For example,
 \begin{verbatim}
@@
 \end{verbatim}
-is reduced to 3.
-
-% \subsubsection{CSPに関する補足説明}
-
-Cross-stage persistence (CSP) is another primitive of multi-stage programming, which enable us to embed computed values into a code value.
-This is an example of CSP.
+yields \verb|3| (here, escape connects tighter than application).
+Finally, CSP is a primitive to embed values (not necessarily code
+values) into a code value.  In MetaOCaml, CSP is implicitly applied to
+occurrences of variables defined outside brackets.  For example,
 \begin{verbatim}
    let plusone = fun x -> x + 1 in
-        let y = plusone 2 in  .< y >.
+   let y = plusone 2 in  .< y * 2 >.
 \end{verbatim}
-This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
-This is because the variable \verb|y| is introduced into a code fragment using CSP.
-Therefore, the variable \verb|y| is embedded after it was calculated.
-CSP is very important when we write practical programs 
-because CSP enables us to use library functions in code fragments as in \verb|.<List.combine [1;2] ['a';'b']>.|.
+evaluates to \verb|.< 3 * 2 >.|, not \verb|.< plusone 2 * 2 >.|.
+This is because the variable \verb|y| is bound to an integer \verb|3|
+before \verb|.<y>.| is evaluated and the value of \verb|y| is embedded
+into the code value.
+In MetaOCaml, CSP can be applied to (variables of) any type.
+CSP is practically important because it enables us to use library functions in brackets, e.g., \verb|.<List.combine [1;2] ['a';'b']>.|.
 
@@
 
-The main application of multi-stage calculi is program optimization. 
-A famous example is power functions.
-Usual power functions take two arguments, which are the base and the exponent.
-We can make a specialized power function for given exponents with multi-stage programming and 
-optimize them by unrolling a loop in functions for given exponents.
-The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
-\verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
-Multi-stage programming can optimize functions which take more than two arguments 
-by generating a code fragment optimized to a given argument.
+% As we mentioned earlier, a main application of multi-stage
+% calculi is program optimization. 
+% A famous example is power functions.
+% Usual power functions take two arguments, which are the base and the exponent.
+% We can make a specialized power function for given exponents with multi-stage programming and 
+% optimize them by unrolling a loop in functions for given exponents.
+% The optimized power function for the exponent of \verb|3| looks like \verb|power3 = fun x -> x * x * x|.
+% \verb|power3| is faster than ordinary \verb|power| function because it contains no loop.
+% Multi-stage programming can optimize functions which take more than two arguments 
+% by generating a code fragment optimized to a given argument.
 
-% \subsubsection{ベクトル計算も高速化できる}
+% 多段階計算の型理論の既存研究の紹介
 
-Multi-stage programming can also optimize vector calculation.
-For example, \verb|vadd| function, which takes two vectors and return the sum of them,
-is implemented with a loop in many cases.
-We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
-\red{MetaOCamlで書いた長さ付きベクトルの例?}
+MetaOCaml is also equipped with a type system for safe code generation
+and execution.  The notion of code types is introduced to prevent code
+values that represent ill-typed expressions from being generated.  For
+example,
+\begin{verbatim}
+   let plusone = .< fun x -> x + 1 >. in .< .~plusone "foo" >.
+\end{verbatim}
+is rejected by the MetaOCaml typechecker as \verb|plusone| is given
+type \verb|(int -> int)| \verb|code| but it is used in the code context that
+requires a function from \verb|string| is expected.  Ensuring safety
+for \verb|run| is more challenging because basic code types do not
+guarantee code values to be closed.  Taha and
+Nielsen~\cite{taha2003environment} introduced the notion of
+environment classifiers to address the problem and developed a type
+system to ensure not only type-safe composition but also type-safe
+execution of code values with a type soundness theorem.
 
-% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
-% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}
+However, the type system, which is based on Hindley--Milner
+polymorphism~\cite{}, is not strong enough to guarantee invariants
+beyond simple types.  For example, Kiselyov~\cite{} demonstrates
+specialization of vector/matrix computation with respect to the sizes
+of vectors and matrices but such specialized functions can be applied
+to vectors and matrices of different sizes.
 
-However, there is a sever problem in functions which are optimized by multi-stage programming.
-Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
-For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
-Otherwise, we will get a Segmentation Fault error.
-\AI{Why SEGV?  MetaOCaml will raise an exception.}
-This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
+% Multi-stage programming can also optimize vector calculation.
+% For example, \verb|vadd| function, which takes two vectors and return the sum of them,
+% is implemented with a loop in many cases.
+% We can unroll \verb|vadd| function for a given vector length and optimize it with multi-stage programming.
 
-% We call this problem \red{Specialized Code Problem}.
+% % 多段階計算で生成したコードは特殊化されているが故に問題も多い
 
-\AI{このイントロ、各段落はまあまあよいのですが、全体の流れが、ふたつ目の文から MetaOCaml という特定の多段階プログラミング言語の話をして、それから応用と問題点の話になりますが、ここが多段階プログラミング一般の話なのか MetaOCaml 固有の話なのかがぶれているように思います。まずは、多段階プログラミング一般の話を応用も含めてする。(他の多段階計算ができるシステムを無視しない。)それから、MetaOCaml の紹介と、その型システムの問題点の話をすべきでしょう。MetaOCaml の型システムでできることもふれておいた方がよいでしょう。}
+% However, there is a sever problem in functions which are optimized by multi-stage programming.
+% Although unrolled \verb|vadd| function is optimized, we cannot use it for different vector length.
+% For example, when you optimize for the length of 5, you shouldn't use it for vectors of 3 lengths.
+% Otherwise, we will get a exception.
+% This problem is serious but existing type systems for multi-stage calculi cannot prevent it.
 
@@
 
-One natural idea to address this problem is the introduction of dependent types.
-Dependent types are types which are dependent on values.
-We can use dependent types for securer programming like Xi and Pfenning \cite{Xi98}.
-For example, we can realize vectors with their sizes with them.
+One natural idea to address this problem is the introduction of dependent types
+to express the size of data structure in static types~\cite{Xi98}.
+% Dependent types are types which are dependent on values.
+% We can use dependent types for securer programming like Xi and Pfenning
+For example, we could declare vector types indexed by the size of
+vectors as follows.
 \begin{verbatim}
@@
 \end{verbatim}
-\verb|Vector| is a type constructor which takes the length of vectors, that is, 
-\verb|Vector 3| is a type for vectors whose lengths are 3.
-If \verb|vadd| function has the type of \verb|Vector n -> Vector n -> Vector n| for any positive number \verb|n|,
-we can confirm the two arguments of \verb|vadd| function has the same length.
-% \red{secure programming? finer grained typing? とか}
+\verb|Vector| is a type constructor that takes an integer (which
+represents the length of vectors): for example, \verb|Vector 3| is the
+type for vectors whose lengths are 3.  Then, our hope is to specialize
+vector/matrix functions with respect to their size and get a piece of
+function code, whose type respects the given size, \emph{provided at
+  specilization time}.  For example, we would like to specialize a
+function to add two vectors with respect to the size of vectors, that
+is, to implement a code generator that takes an integer $n$ as an
+input and generates a piece of function code of type
+\verb|(Vector |$n$\verb| -> Vector|$n$\verb| -> Vector |$n$\verb|) code|.
 
-As we pointed out in the above section,
-functions optimized with multi-stage programming can take only restricted values as arguments.
-When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
-We introduce dependent types into a multi-stage calculus
-so that the type system can guarantee optimized functions are used properly.
+% As we pointed out in the above section,
+% functions optimized with multi-stage programming can take only restricted values as arguments.
+% When you optimize \verb|vadd| function for the length of 5, you should it only for 5 length vectors.
+% We introduce dependent types into a multi-stage calculus
+% so that the type system can guarantee optimized functions are used properly.
+% Although there is a trial to combine multi-stage programming and dependent type by Brady and Hammond~\cite{brady2006dependently},
+% they didn't give a formal definition and properties for the calculus.
 
-In this paper, we design a new multi-stage calculus \LMD by 
-merging dependent types into existing multi-stage calculus \LTP\cite{Hanada2014}.
-\LMD is multi-stage calculus which contains dependent types.
-\LMD makes multi-stage programming safer with the power of dependent types.
-Our technical contribution are summarized as follows:
+In this paper, we develop a new multi-stage calculus \LMD by extending
+the existing multi-stage calculus \LTP\cite{Hanada2014}---which
+formalizes the four constructs of MetaOCaml in a way slightly
+different from MetaOCaml---with dependent types and study its
+properties.  We base our work on \LTP because its type system and
+semantics are arguably simpler than
+\(\lambda^\alpha\)~\cite{taha2003environment}, which is more faithful
+to the design of MetaOCaml.  Our technical contribution are summarized
+as follows:
 \begin{itemize}
-        \item we give the formal definition of \LMD with its syntax, 
-        type system which contains type equivalence, full, reduction, and staged reduction;
-        \item for the full reduction, we prove subject reduction, strong normalization, and confluence
-        \item fot the staged reduction, we prove unique decomposition and progress.
+\item We give the formal definition of \LMD with its syntax, 
+  type system and two kinds of reduction---full and staged reduction.
+\item We show preservation, strong normalization, and confluence for
+  full reduction; and show unique decomposition (and progress as its
+  corollary) for staged reduction, which formalizes program execution.
 \end{itemize}
+The combination of multi-stage programming and dependent types has
+been discussed by Brady and Hammond~\cite{brady2006dependently} but,
+to our knowledge, our work is a first formal calculus of dependently
+typed multi-stage programming.
 
@@
 
-The organization of this paper is the following.
-Section 2 gives an informal overview of \LMD.
-Section 3 defines \LMD and
-Section 4 shows the properties of \LMD including Unique Decomposition \AI{There are more important properties that should be mentioned!  In fact, the properties should be mentioned earlier.}.
-Section 5 discusses future works.
-Finally, Section 6 discusses related works.
-\AI{Use $\backslash$label and $\backslash$ref!}
-\AI{``Related work'' and ``future work'' (they are uncountable).}
-\AI{Related work is discussed in Section 5?  Section 6 is the section for conclusion, which includes future work.}
+The organization of this paper is as follows.
+Section~\ref{sec:informal-overview} gives an informal overview of
+\LMD.  Section~\ref{sec:formal-definition} defines \LMD and
+Section~\ref{sec:properties} shows properties of \LMD.  Section
+\ref{sec:related-work} discusses related work and Section
+\ref{sec:conclusion} concludes the paper with discussion of future
+work.

### 2019-06-19 text/introduction.tex
Small changes.
Further revision

@@
 
+\subsection{Our Work}
 In this paper, we develop a new multi-stage calculus \LMD by extending
-the existing multi-stage calculus \LTP\cite{Hanada2014}---which
-formalizes the four constructs of MetaOCaml in a way slightly
-different from MetaOCaml---with dependent types and study its
-properties.  We base our work on \LTP because its type system and
-semantics are arguably simpler than
-\(\lambda^\alpha\)~\cite{taha2003environment}, which is more faithful
-to the design of MetaOCaml.  Our technical contribution are summarized
-as follows:
+the existing multi-stage calculus \LTP\cite{Hanada2014} with dependent
+types and study its properties.  We base our work on \LTP, in which
+the four multi-stage constructs are handled slightly differently from
+MetaOCaml, because its type system and semantics are arguably simpler
+than \(\lambda^\alpha\)~\cite{taha2003environment}, another calculus,
+which formalizes the design of MetaOCaml more faithfully.  Our
+technical contribution are summarized as follows:
 \begin{itemize}
@@
 
-\subsection{Organization of the Paper}
+\AI{Informal discussion on how important CSP is?}
+\AI{Comments on Appendix required.}
+
+\subsubsection{Organization of the Paper.}
 

### 2019-06-19 text/formal-defnition.tex
Promote the section on staged semantics to subsection.
Fix judgments.
FInish revising Seciton 1.
Revised Section 2.

@@
 
-\section{Formal Definition of \LMD}
+\section{Formal Definition of \LMD \label{sec:formal-definition}}
 
@@
       \G     & \V K \E J @ A              & \text{kind equivalence}                 \\
-            \G & \V \tau \E \sigma @ A & \text{type equivalence}    \\
-            \G & \V M \E N @ A         & \text{term equivalence}
+      \G     & \V \tau \E \sigma :: K @ A & \text{type equivalence}                 \\
+      \G     & \V M \E N : \tau @ A       & \text{term equivalence}
     \end{align*}
@@
 
+\QPercent\ is different from other rules because it was designed from practical reason, not from the syntax or the reductions.
+For example, we discuss $\text{vadd}_\beta$ function,
+which takes a length of vector and returns addition function for vectors with the length.
+$\text{vadd}_1$ is a helper function to make $\text{vadd}$, 
+which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
+We assumed that type checker can know $n=0$ when process the $\textbf{then}$ clause.
+\newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
+\begin{align*}
+	  & \textbf{let}\ \text{vadd}_1 : \F\alpha.\Pi n:\I.\TW_\alpha\Vpn\to\TW_\alpha\Vpn\to\TW_\alpha\Vpn                                \\
+	  & \hspace{7mm} = \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn.            \\
+	  & \hspace{14mm} \textbf{if}\ n = 0                                                                                                \\
+	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                                               \\
+	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                                                       \\
+	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                                                   \\
+	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                                                   \\
+	  & \hspace{21mm} \text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2)) \\
+\end{align*}
+\AI{I think we should state the types of cons, tail, and head.}
+Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.
+This function takes the length of vectors and returns a quoted add function for vector of the given size.
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta n)}
+\begin{align*}
+	  & \textbf{let}\ \text{vadd}: \Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)                \\ 
+	  & \hspace{7mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
+	  & \hspace{63mm} \TBL_\beta \text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))    \\
+\end{align*}
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 10)}
+When we use this function, we need to instantiate $\text{vadd}$ with a length.
+If we instantiate it with a integer 10, we get function $\text{vadd10}$ whose type is \\
+$\text{vadd10}: \F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
+This function is difficult to use because its type contains $\Vpn$.
+In most cases, we have vectors of type $\text{Vector}\ 10$, not $\Vpn$.
+Therefore, we want to identify $\text{Vector}\ 10$ and $\Vpn$.
+
+In order to resolve this problem, we introduced \QPercent\ into \LMD.
+\QPercent\ enables us to identify $\text{Vector}\ 10$ and $\Vpn$.
+This rule says that if term $M$ has the same type at stage $A\alpha$ and $A$,
+we can assume $\%_\alpha M \E M$ which roughly means $\%_\alpha M$ and $M$ are equivalent.
+With this rule, we can identify $10$ and $\%_\beta 10$ and use $\text{vadd}$ to many vectors.
+\begin{center}
+	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
+\end{center}
+
 \AI{This paragraph should be polished later.}
@@
 
-\subsubsection{Staged Semantics.}
+\subsection{Staged Semantics}
 

### 2019-06-19 text/informal-overview.tex
Revised Section 2.

@@
 The empty stage is represented by $\varepsilon$.
-They are used to show the thickness of brackets. \AI{Perhaps ``thickness'' doesn't make sense.}
+They are used to show the depth of brackets.
 For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
@@
 becomes $(\lambda x:\I.x+10)$ after it was run it twice.
-\red{run twiceは表現が微妙}
 
@@
 although MetaOCaml CSP is implicit and there is no symbol for CSP.
-For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
-\red{inner / outer は適切か?}
-\AI{What is \(a\)?}
-\AI{Is this explanation enough to understand the rest of the section?}
+For example, the variable $x$ is cross-staged into a code value in the following expression.
+\[\lambda x:\I.(\Lambda\alpha.(\TB_\alpha (\lambda y:\I.y+\%_\alpha x))\ \varepsilon)\ 10\]
 
@@
 \LLF is a simple system of dependent types introduced in \cite{attapl}.
-\red{system / type system / calculus?}
-It is based on Edinburgh LF\cite{harper1993framework}.
-\AI{Can you remind me of differences between Edinburgh LF and \LLF?}
-Therefore, \AI{``Therefore'' is used to show a logical consequence.} all constants and base types are declared in the signature.
+It is made from Edinburgh LF\cite{harper1993framework} by omitting signatures and include declarative equality judgements.
+Hence, all constants and base types are declared in the signature.
 The \LLF type theory generalizes simply typed lambda calculus
@@
 For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
-\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}
 
@@
 This is because multi-stage calculus and dependent types are almost orthogonal.
-\red{orthogonal は抽象的すぎるか?}
 Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
@@
 Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules except \QPercent\ easily from the syntax or the reductions of \LMD.  \AI{Don't refer to a concrete rule name without showing it because we haven't introduced rules.}
-
-\AI{If there's space, we should have introduced the \LTP-version of vadd.}
-
-\QPercent\ is different from other rules because it was designed from practical reason, not from the syntax or the reductions.
-For example, we discuss $\text{vadd}_\beta$ function,
-which takes a length of vector and returns addition function for vectors with the length.
-$\text{vadd}_1$ is a helper function to make $\text{vadd}$, 
-which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
-We assumed that type checker can know $n=0$ when process the $\textbf{then}$ clause.
-\newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
-\begin{align*}
-	  & \textbf{let}\ \text{vadd}_1 : \F\alpha.\Pi n:\I.\TW_\alpha\Vpn\to\TW_\alpha\Vpn\to\TW_\alpha\Vpn                                \\
-	  & \hspace{7mm} = \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn.            \\
-	  & \hspace{14mm} \textbf{if}\ n = 0                                                                                                \\
-	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                                               \\
-	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                                                       \\
-	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                                                   \\
-	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                                                   \\
-	  & \hspace{21mm} \text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2)) \\
-\end{align*}
-\AI{I think we should state the types of cons, tail, and head.}
-Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.
-This function takes the length of vectors and returns a quoted add function for vector of the given size.
-\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta n)}
-\begin{align*}
-	  & \textbf{let}\ \text{vadd}: \Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)                \\ 
-	  & \hspace{7mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
-	  & \hspace{63mm} \TBL_\beta \text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))    \\
-\end{align*}
-\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 10)}
-When we use this function, we need to instantiate $\text{vadd}$ with a length.
-If we instantiate it with a integer 10, we get function $\text{vadd10}$ whose type is \\
-$\text{vadd10}: \F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
-This function is difficult to use because its type contains $\Vpn$.
-In most cases, we have vectors of type $\text{Vector}\ 10$, not $\Vpn$.
-Therefore, we want to identify $\text{Vector}\ 10$ and $\Vpn$.
-
-In order to resolve this problem, we introduced \QPercent\ into \LMD.
-\QPercent\ enables us to identify $\text{Vector}\ 10$ and $\Vpn$.
-This rule says that if term $M$ has the same type at stage $A\alpha$ and $A$,
-we can assume $\%_\alpha M \E M$ which roughly means $\%_\alpha M$ and $M$ are equivalent.
-With this rule, we can identify $10$ and $\%_\beta 10$ and use $\text{vadd}$ to many vectors.
-\begin{center}
-	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-\end{center}
+we can design all rules easily from the syntax or the reductions of \LMD except one equivalence rule about CSP..

### 2019-06-19 text/formal-defnition.tex
Revising Section 3.

@@
 respectively.
-\AI{Don't we need to define $\longrightarrow^*$?}
+$M \longrightarrow^* N$ means that there is a sequence of reduction $\longrightarrow$ whose length is greater than or equal to 0.
 
@@
   level somewhere.}
+\red{Conclusionに入れます}
 
@@
 \AI{The second premises of \TConst and \TVar are not needed?}
+\red{Removed. TODO: Fix proofs.}
 \begin{figure}
   \begin{center}
-    \infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \hfil
-    \infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
+    \infrule[\TConst]{c:\tau \in \Sigma}{\G \V c:\tau @A} \hfil
+    \infrule[\TVar]{x:\tau @A \in \G}{\G \V x:\tau @A} \\[2mm]
     \infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
@@
 % \TConv
-\AI{Looks like a paper is written for those who know multi-stage calculi fairly well but don't know dependent type systems.  The reality is the opposite.}
 As in standard dependent type systems, \TConv{} allows us to replace

### 2019-06-20 text/formal-defnition.tex
Revising Section 3.
Wrote a pagraph of typing rules for a multi-stage calculus.

@@
 sequence. \LMD is defined by the following grammar:
-
-% \AI{``Transition'' is still used.}
 
@@
 % \TConv
-As in standard dependent type systems, \TConv{} allows us to replace
-the type of a term with an equivalent one.
-In a type system with dependent types, this kind of rule is essential
-because \AI{?} two types which have different shapes may be equivalent.
+As in standard dependent type systems, \TConv{} allows us to replace the type of a term with an equivalent one.
 For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not syntactically equivalent.
+a value of type $\textrm{Vector}\ (4+1)$ can also has type $\textrm{Vector}\ 5$ because of \TConv{}.
 
 % Typing rules for a multi-stage calculus
-% \AI{This paragraph is not very informative.  We shouldn't just refer readers to previous work.}
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-The rule \TTB{}, which corresponds to brackets \AI{Sounds like the rule corresponds to brackets.  What corresponds to brackets is $\TB$}, means that if term $M$ is of type $\tau$ at stage $A\alpha$,
-$\TB_\alpha M$ is of type $\TW_\alpha \tau$ at stage $A$.
-The rule \TTBL{}, which corresponds to escape, is the converse of \TTB.
+\TTB and \TTBL are the same with \LTP as we explained in Section \ref{sec:informal-overview}.
 The rule \TGen{} for stage abstraction is straightforward.
-The condition $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that
-the scope of $\alpha$ is in $M$.
+The condition $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that the scope of $\alpha$ is in $M$.
 The rule \TIns{} is for applications of stages to stage abstractions.
-\AI{Any comments?}
-The rule \TCsp is the rule for CSP, which means that
-if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.  \AI{This does not explain what this rule means.
-  It just gives how the rule is read.}
+\TIns{} is mainly used when we run a code value or rename a stage variable in the body of an abstraction.
+The rule \TCsp{} is the rule for CSP, which means that
+if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
+This rule enable to embed computed values into a fragment of code.
 
@@
 it is practically significant.
+
+\red{ここがやばい}
 
@@
 \begin{definition}[Evaluation Context]
-  Let $B$ be either \(\varepsilon\) or a transition variable \(\beta\).
+  Let $B$ be either \(\varepsilon\) or a stage variable \(\beta\).
   The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar (in which $A'$ stands for a non-empty stage).
@@
 \end{definition}
-\AI{some more explanation of the syntax of evaluation contexts.}
 

### 2019-06-20 text/formal-defnition.tex
Revised Section 3.

@@
 
-\red{ここがやばい}
+\red{$\text{head}: \text{Vector}\ n \to \I$としているが
+$\text{head}: \Pi n:\I.\text{Vector}\ n \to \I$のほうが良いか? tail, consも同様}
 
@@
 For example, we discuss $\text{vadd}_\beta$ function,
-which takes a length of vector and returns addition function for vectors with the length.
+which takes a length of integer vectors and returns addition function for vectors with the length.
 $\text{vadd}_1$ is a helper function to make $\text{vadd}$, 
 which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
-We assumed that type checker can know $n=0$ when process the $\textbf{then}$ clause.
+We assumed that type checker can know $n=0$ when process the $\textbf{then}$ clause,
+$\text{head}$ is of type $\text{Vector}\ n \to \I$,
+$\text{tail}$ is of type $(\text{Vector}\ n) \to (\text{Vector}\ (n-1))$, 
+and  $\text{cons}$ is of type $\I \to (\text{Vector}\ n) \to (\text{Vector}\ (n+1))$, 
 \newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
@@
 \end{align*}
-\AI{I think we should state the types of cons, tail, and head.}
 Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.
@@
 \renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 10)}
-When we use this function, we need to instantiate $\text{vadd}$ with a length.
-If we instantiate it with a integer 10, we get function $\text{vadd10}$ whose type is \\
-$\text{vadd10}: \F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
-This function is difficult to use because its type contains $\Vpn$.
-In most cases, we have vectors of type $\text{Vector}\ 10$, not $\Vpn$.
-Therefore, we want to identify $\text{Vector}\ 10$ and $\Vpn$.
 
-In order to resolve this problem, we introduced \QPercent\ into \LMD.
-\QPercent\ enables us to identify $\text{Vector}\ 10$ and $\Vpn$.
-This rule says that if term $M$ has the same type at stage $A\alpha$ and $A$,
-we can assume $\%_\alpha M \E M$ which roughly means $\%_\alpha M$ and $M$ are equivalent.
-With this rule, we can identify $10$ and $\%_\beta 10$ and use $\text{vadd}$ to many vectors.
-\begin{center}
-	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
-\end{center}
-
-\AI{This paragraph should be polished later.}
 \renewcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
-As we discussed in Section 2, $\text{vadd}$ function,
-which takes the length of vectors and returns a quoted add function for vector of the given size,
-has the type of $\Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
-When we use this function, we instansiate $\text{vadd}$ with some integer such as 5
+$\text{vadd}$ function has the type of $\Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$ and
+when we use this function, we instansiate $\text{vadd}$ with some integer such as 5
 and get code of a optimzed $\text{vadd}$ function such as $\text{vadd5}$.
@@
 a code value of this type is difficult to combine with another code fragment.
-For example, if we want to composite $\text{vadd5}$ with reverse fucntion,
+For example, if we want to composite $\text{vadd5}$ with code of reverse fucntion,
 which is of type $\text{rev5}:\F\alpha.\TW_\alpha(\text{Vector}\ 5\to\text{Vector}\ 5)$,
@@
 Thanks to \QPercent, we can identify $\text{Vector}\ 5$ and $\text{Vector}\ \%_\gamma 5$
-and compose code values of functions as we expected.
+and compose the code values of functions as we expected.
 

### 2019-06-21 text/properties.tex
Remove a comment.
FInish revising Seciton 1.
Substitutions in type environment.
Finish revising Section 4.

@@
 
-\section{Properties of \LMD}
+\section{Properties of \LMD \label{sec:properties}}
 
@@
 manner.  Using these notations, the two substitution lemmas are stated as follows:
-\AI{Did we define $\Delta [x \mapsto N]$?}
 
@@
 	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
-	For each case, we can use straightforward induction on derivations. \AI{何の derivation?}
+	For each case, we can use straightforward induction on typing derivations.
 	Difficult cases are \TApp, \TTBL, and \TIns.
@@
 no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{Tsukada} \AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
+We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{harper1993framework}.
+\AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
+\red{とりあえずA Framework for Defining Logicsを引用しました。}
 
@@
 \end{corollary}
-
-\AI{Don't we prove $\longrightarrow_s$ is a subrelation of $\longrightarrow$?}

### 2019-06-21 text/introduction.tex
Shorten the introduction.

@@
 \subsection{Multi-stage Programming and MetaOCaml}
-
-% \subsubsection{多段階計算とは何か?}
-
-\AI{前の版は，まだ MetaOCaml specific な話と，MSP 一般の話が交互に出てきて
-わかりづらかったと思います．}
 
@@
 MetaOCaml~\cite{calcagno2003implementing,oleg2014} is an extension of
-OCaml\footnote{\url{http://ocaml.org}} with constructs for multi-stage
-programming, including brackets, escape, run, and cross-stage
-persistence (CSP) .  Brackets, written \verb|.< e >.| in MetaOCaml,
-makes a value that represents the code (or abstract syntax tree) of
-expression \verb|e|; and escape, written \verb|.~ e| and is supposed
-to appear inside brackets, evaluates \verb|e| to a code value and
-expands the code into the surrounding code.
-For example,
-\begin{verbatim}
-   let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
-\end{verbatim}
-evaluates to \verb|.< (fun x -> x + 1) 2 >.|.  
-Run, written \verb|run e|, evaluates \verb|e| to a code value
-and executes it.  For example,
-\begin{verbatim}
-   run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
-\end{verbatim}
-yields \verb|3| (here, escape connects tighter than application).
-Finally, CSP is a primitive to embed values (not necessarily code
-values) into a code value.  In MetaOCaml, CSP is implicitly applied to
-occurrences of variables defined outside brackets.  For example,
-\begin{verbatim}
-   let plusone = fun x -> x + 1 in
-   let y = plusone 2 in  .< y * 2 >.
-\end{verbatim}
-evaluates to \verb|.< 3 * 2 >.|, not \verb|.< plusone 2 * 2 >.|.
-This is because the variable \verb|y| is bound to an integer \verb|3|
-before \verb|.<y>.| is evaluated and the value of \verb|y| is embedded
-into the code value.
+OCaml\footnote{\url{http://ocaml.org}} with special constructs for
+multi-stage programming, including brackets and espace, which are
+(hygienic) quasi-quotation, and \texttt{run}, which is similar to
+\texttt{eval} in Lisp, and cross-stage persistence
+(CSP)~\cite{MetaML}.  Programmers can easily write code generators by
+using these features.  Moreover, MetaOCaml is equipped with a powerful
+type system for safe code generation and execution.  The notion of
+code types is introduced to prevent code values that represent
+ill-typed expressions from being generated.  For example, a quotation
+of expression \texttt{1 + 1} is given type \texttt{int code}; a
+quotation of \texttt{abs} is given type \texttt{(int -> int) code};
+and a code-generating function, which takes a code value \(c\) as an
+argument and returns \(c \texttt{ + } c\), is given type \texttt{int
+  code -> int code} so that it cannot be applied to, say, a quotation
+of \texttt{"Hello"}, which is given type \texttt{string
+  code}.  Ensuring safety for \verb|run| is more challenging because
+basic code types do not guarantee that execution of code values never
+results in unbound variable errors.  Taha and
+Nielsen~\cite{taha2003environment} introduced the notion of
+environment classifiers to address the problem and developed a type
+system to ensure not only type-safe composition but also type-safe
+execution of code values with a type soundness theorem (for a pure
+subset of MetaOCaml).
+
+% rackets, written \verb|.< e >.| in
+% MetaOCaml, makes a value that represents the code (or abstract syntax
+% tree) of expression \verb|e|; and escape, written \verb|.~ e| and is
+% supposed to appear inside brackets, evaluates \verb|e| to a code value
+% and expands the code into the surrounding code.  For example,
+% \begin{verbatim}
+%    let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
+% \end{verbatim}
+% evaluates to \verb|.< (fun x -> x + 1) 2 >.|.  
+% Run, written \verb|run e|, evaluates \verb|e| to a code value
+% and executes it.  For example,
+% \begin{verbatim}
+%    run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
+% \end{verbatim}
+% yields \verb|3| (here, escape connects tighter than application).
+% Finally, CSP is a primitive to embed values (not necessarily code
+% values) into a code value.  In MetaOCaml, CSP is implicitly applied to
+% occurrences of variables defined outside brackets.  For example,
+% \begin{verbatim}
+%    let plusone = fun x -> x + 1 in
+%    let y = plusone 2 in  .< y * 2 >.
+% \end{verbatim}
+% evaluates to \verb|.< 3 * 2 >.|, not \verb|.< plusone 2 * 2 >.|.
+% This is because the variable \verb|y| is bound to an integer \verb|3|
+% before \verb|.<y>.| is evaluated and the value of \verb|y| is embedded
+% into the code value.
 In MetaOCaml, CSP can be applied to (variables of) any type.
@@
 
-MetaOCaml is also equipped with a type system for safe code generation
-and execution.  The notion of code types is introduced to prevent code
-values that represent ill-typed expressions from being generated.  For
-example,
-\begin{verbatim}
-   let plusone = .< fun x -> x + 1 >. in .< .~plusone "foo" >.
-\end{verbatim}
-is rejected by the MetaOCaml typechecker as \verb|plusone| is given
-type \verb|(int -> int)| \verb|code| but it is used in the code context that
-requires a function from \verb|string| is expected.  Ensuring safety
-for \verb|run| is more challenging because basic code types do not
-guarantee code values to be closed.  Taha and
-Nielsen~\cite{taha2003environment} introduced the notion of
-environment classifiers to address the problem and developed a type
-system to ensure not only type-safe composition but also type-safe
-execution of code values with a type soundness theorem.
-
-However, the type system, which is based on Hindley--Milner
-polymorphism~\cite{}, is not strong enough to guarantee invariants
-beyond simple types.  For example, Kiselyov~\cite{} demonstrates
-specialization of vector/matrix computation with respect to the sizes
-of vectors and matrices but such specialized functions can be applied
-to vectors and matrices of different sizes.
+However, the type system, which is based on the Hindley--Milner
+polymorphism~\cite{Milner78JCSS}, is not strong enough to guarantee
+invariants beyond simple types.  For example, Kiselyov~\cite{8384206}
+demonstrates specialization of vector/matrix computation with respect
+to the sizes of vectors and matrices in MetaOCaml but the type system
+cannot prevent such specialized functions from being applied to
+vectors and matrices of different sizes.
 
@@
 input and generates a piece of function code of type
-\verb|(Vector |$n$\verb| -> Vector|$n$\verb| -> Vector |$n$\verb|) code|.
+\verb|(Vector |$n$\verb| -> Vector |$n$\verb| -> Vector |$n$\verb|) code|.
 

### 2019-06-21 text/informal-overview.tex
[WIP] revising overview.

@@
 
-We designed \LMD, a multi-stage calculus with dependent type.
-\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multi-stage calculus with CSP, and
-we introduced dependent types based on \LTP\cite{attapl}.
-In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.
+We describe our calculus \LMD informally.  \LMD is based on
+\LTP~\cite{Hanada2014} by Hanada and Igarashi and we introduce
+dependent types based on \LLF~\cite{attapl}.  We start with a review of 
+\LTP.
 
@@
 
-In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
-The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
-The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
-% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
-In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
+In \LTP, brackets (quasi-quotation) and escape (unquote) are written
+$\TB_\alpha M$ and $\TBL_\alpha M$, respectively.  For example,
+$\TB_\alpha (1 + 1)$ represents code of expression $1 + 1$ and thus
+evaluates to itself.  Escape $\TBL_\alpha M$ may appear under
+$\TB_\alpha$; it evaluates $M$ to a code value and splice it into the
+surrounding code fragment.  Such splicing is expressed by the
+following reduction rule:
 \begin{align*}
@@
 \end{align*}
-It means escape cancels brackets.
-% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
-% \red{この文はここに来るべきなのか? LTPの説明ではないが}
+The type of
+$\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$; the type
+of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
 
-% stage variable and stage
-
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{stage variable}
-\footnote{In the original \LTP paper, this is called a \textit{transition variable}. 
-However, we call it a \textit{stage variable} in this paper.} and
+The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{stage variable}\footnote{%
+  In Hanada and Igarash~\cite{Hanada2014}, it was called a \textit{transition variable}, which is derived from correspondence to modal logic, studied by Tsukada and Igarashi~\cite{Tsukada}.} and
 a sequence of stage variables is called \textit{stage}.
-The empty stage is represented by $\varepsilon$.
-They are used to show the depth of brackets.
-For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
-$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
-becomes $(\lambda x:\I.x+10)$ after it was run it twice.
-
-% stage abstraction and application
-
-There are abstractions for stage variables and applications for stage abstraction in \LTP.
-They look like $\Lambda\alpha.M$ and $M A$, respectively.
-A stage abstraction binds a stage variable in a term.
-For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
-There is a reduction rule for stage application in \LTP.
-The rule is the following.
+Intuitively, they represent the depth of nested brackets.
+Stage variables can be abstracted by $\Lambda\alpha.M$ and instantiated by
+an application $M\ A$ to stages.
+For example, $\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10) 5)$ is a code value, where \(\alpha\)
+is abstracted.  If it is applied to \(\varepsilon\), which is the empty sequence standing for zero,
+\(\TB_\alpha\) becomes \(\TB_\varepsilon\), which stands for zero brackets,
+and so \(\TB_\alpha\) disappears.  As a result, the application reduces to (unquoted) \((\lambda x:\I.x+10) 5\) and to 15.  If \(\alpha\) is instantiated with, say, \(\beta\gamma\), then
+\(\TB_\alpha\) becomes nested brackets \(\TB_{\beta} \TB_\gamma\).  These are expressed by
+the following reduction rule:
 \begin{align*}
@@
 \end{align*}
-For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
+where stage substitution \([\alpha \mapsto A]\) manipulates nesting of
+\(\TB\) and \(\TBL\) (and also \(\%_\alpha\) as we see later).  As we
+show above, application to $\varepsilon$ corresponds to \texttt{run}.
 
-% stage-related symbols disappear when the empty stage is substituted.
-% In short, about "run"
+Cross-stage persistence (CSP), which is an important feature of \LTP,
+is a primitive to embed values (not necessarily code values) into a
+code value.
+For example,
+\begin{verbatim}
+   let y = 1 + 2 in
+   .< y * 2 >.    (* .< e >. stands for brackets *)
+\end{verbatim}
+evaluates to \verb|.< 3 * 2 >.|, not \verb|.< plusone 2 * 2 >.|.
+Here, CSP is implicitly applied to the occurrence of \texttt{y}
+and embeds its value \texttt{3} into the code.
+In \LTP, CSP is written explicitly and $\%$ is a symbol for CSP.
+For example, the above MetaOCaml expression can be expressed
+in \LTP as follows:
+\[
+  (\lambda x:\I.\Lambda\alpha.(\TB_\alpha ((\%_\alpha y) * 2)))\ (1 + 2)
+\]
+It evaluates to \(\Lambda\alpha.(\TB_\alpha ((\%_\alpha 3) * 2))\), in
+which $\%_\alpha 3$ means that it waits for the surrounding code to be
+run (by an application to $\varepsilon$).  If it is applied to
+\(\varepsilon\), substitution of \(\varepsilon\) for \(\alpha\)
+eliminates \(\TB_\alpha\) and \(\%_\alpha\) and so \(3 * 2\) is
+obtained.
 
-Another important rule about a stage variable is 
-that symbols with stage variables disappear 
-when the empty stage $\varepsilon$ is substituted to the stage variable.
-The purpose of this rule is express \verb|run| without any special symbol.
-In multi-stage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
-For example, $(\TB_\varepsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
-Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \varepsilon$ becomes $\lambda x:\I.x$
-In \LTP, \verb|run| is realized with application to the empty stage $\varepsilon$.
-
-% stage in typing rules
-
-A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
-A stage in a judgement represents where the judgement is true.
-For example, $\G \vdash (\lambda x:\I.x) : \I \to \I @ \alpha$ means 
-term $\lambda x:\I.x$ has type $\I \to \I$ at stage $\alpha$.
-Especially, terms without quoting exist at the empty stage $\varepsilon$.
-For example, $(\lambda x:\I.x)\ (1+2)$ is at $\varepsilon$ stage and 
-$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ stage.
-Terefore, stages appear in typing rules, too.
+The type system of \LTP uses code types---the type of code of type
+\(\tau\) is written \(\TW_\alpha \tau\)---for typing \(\TB_\alpha\),
+\(\TBL_\alpha\) and \(\%_\alpha\).  It takes stages into account: A
+variable declaration in a type environment is associated with its
+declared stage as well as its type and a type judgement of \LTP is of
+the form $\G \vdash M : \tau @ A$, in which $A$ stands for the stage
+of term $M$.  For example,
+$y:\I@\alpha \vdash (\lambda x:\I.y) : \I \to \I @ \alpha$ holds, but
+$y:\I@\alpha \vdash (\lambda x:\I.y) : \I \to \I @ \varepsilon$ does
+not because the latter uses $y$ at stage \(\varepsilon\) but $y$ is
+declared at $\alpha$.  Quotation \(\TB_\alpha M\) is given type
+\(\TW_\alpha \tau\) at stage \(A\) if \(M\) is given type \(\tau\) at
+stage \(A\alpha\) and  unquote \(\TBL_\alpha M\) is given type
+\(\tau\) at stage \(A\alpha\) if \(M\) is given type \(\TW_\alpha \tau\) at
+stage \(A\alpha\), represented by the following rules.
 \begin{center}
@@
 \end{center}
-\TTB, corresponding to brackets, means 
-if $M$ is typed $\tau$ at stage $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
-\TTBL\ is converse of \TTB.
+% \TTB, corresponding to brackets, means 
+% if $M$ is typed $\tau$ at stage $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
+% \TTBL\ is converse of \TTB.
 
 % CSP
-
-CSP, cross-stage persistence, is an important feature of \LTP.
-It enables us to embed value at an outer stage into an inner stage.
-In \LTP, CSP is written explicitly and $\%$ is a symbol dedicated to CSP
-although MetaOCaml CSP is implicit and there is no symbol for CSP.
-For example, the variable $x$ is cross-staged into a code value in the following expression.
-\[\lambda x:\I.(\Lambda\alpha.(\TB_\alpha (\lambda y:\I.y+\%_\alpha x))\ \varepsilon)\ 10\]
 
@@
 
+\AI{We should discuss conceptual points, not technical points!}
+
 Next, we develop \LMD by extending \LTP with \LLF-like dependent types.

### 2019-06-22 text/informal-overview.tex
Rewrite Sections 1 and 2.

@@
 
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{stage variable}\footnote{%
-  In Hanada and Igarash~\cite{Hanada2014}, it was called a \textit{transition variable}, which is derived from correspondence to modal logic, studied by Tsukada and Igarashi~\cite{Tsukada}.} and
-a sequence of stage variables is called \textit{stage}.
-Intuitively, they represent the depth of nested brackets.
-Stage variables can be abstracted by $\Lambda\alpha.M$ and instantiated by
-an application $M\ A$ to stages.
-For example, $\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10) 5)$ is a code value, where \(\alpha\)
-is abstracted.  If it is applied to \(\varepsilon\), which is the empty sequence standing for zero,
-\(\TB_\alpha\) becomes \(\TB_\varepsilon\), which stands for zero brackets,
-and so \(\TB_\alpha\) disappears.  As a result, the application reduces to (unquoted) \((\lambda x:\I.x+10) 5\) and to 15.  If \(\alpha\) is instantiated with, say, \(\beta\gamma\), then
-\(\TB_\alpha\) becomes nested brackets \(\TB_{\beta} \TB_\gamma\).  These are expressed by
-the following reduction rule:
+The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{stage
+  variable}\footnote{%
+  In Hanada and Igarash~\cite{Hanada2014}, it was called a
+  \textit{transition variable}, which is derived from correspondence
+  to modal logic, studied by Tsukada and Igarashi~\cite{Tsukada}.} and
+a sequence of stage variables is called \textit{stage}.  Intuitively,
+they represent the depth of nested brackets.  Stage variables can be
+abstracted by $\Lambda\alpha.M$ and instantiated by an application
+$M\ A$ to stages.  For example,
+$\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10) 5)$ is a code value,
+where \(\alpha\) is abstracted.  If it is applied to \(\varepsilon\),
+which is the empty sequence standing for zero, \(\TB_\alpha\) becomes
+\(\TB_\varepsilon\), which stands for zero brackets, and so, in fact,
+\(\TB_\alpha\) disappears.  As a result, the application reduces to
+(unquoted) \((\lambda x:\I.x+10) 5\) and to 15.  So, application of a
+\(\Lambda\)-abstraction to $\varepsilon$ corresponds to \texttt{run}.
+If \(\alpha\) is instantiated with, say, \(\beta\gamma\), then
+\(\TB_\alpha\) becomes nested brackets \(\TB_{\beta} \TB_\gamma\).
+These are expressed by the following reduction rule:
 \begin{align*}
@@
 where stage substitution \([\alpha \mapsto A]\) manipulates nesting of
-\(\TB\) and \(\TBL\) (and also \(\%_\alpha\) as we see later).  As we
-show above, application to $\varepsilon$ corresponds to \texttt{run}.
+\(\TB\) and \(\TBL\) (and also \(\%_\alpha\) as we see later).
 
@@
 is a primitive to embed values (not necessarily code values) into a
-code value.
-For example,
-\begin{verbatim}
-   let y = 1 + 2 in
-   .< y * 2 >.    (* .< e >. stands for brackets *)
-\end{verbatim}
-evaluates to \verb|.< 3 * 2 >.|, not \verb|.< plusone 2 * 2 >.|.
-Here, CSP is implicitly applied to the occurrence of \texttt{y}
-and embeds its value \texttt{3} into the code.
-In \LTP, CSP is written explicitly and $\%$ is a symbol for CSP.
-For example, the above MetaOCaml expression can be expressed
-in \LTP as follows:
+code value.  For example, a \LTP-term
 \[
-  (\lambda x:\I.\Lambda\alpha.(\TB_\alpha ((\%_\alpha y) * 2)))\ (1 + 2)
+  M_1 = \lambda x:\I.\Lambda\alpha.(\TB_\alpha ((\%_\alpha x) * 2))
 \]
-It evaluates to \(\Lambda\alpha.(\TB_\alpha ((\%_\alpha 3) * 2))\), in
-which $\%_\alpha 3$ means that it waits for the surrounding code to be
-run (by an application to $\varepsilon$).  If it is applied to
-\(\varepsilon\), substitution of \(\varepsilon\) for \(\alpha\)
-eliminates \(\TB_\alpha\) and \(\%_\alpha\) and so \(3 * 2\) is
-obtained.
+takes an integer \(x\) as an input and returns the code value into
+which \(x\) is embedded.  CSP is practically important because
+one can call library functions from inside quotations.  If the above
+\(\lambda\)-abstraction is applied to $1 + 2$ as in
+\[
+  M_2 = (\lambda x:\I.\Lambda\alpha.(\TB_\alpha ((\%_\alpha x) * 2)))\ (38 + 4)
+\]
+it evaluates to
+\(M_3 = \Lambda\alpha.(\TB_\alpha ((\%_\alpha 42) * 2))\).  According
+to the semantics of \LTP, the subterm $\%_\alpha 42$ means that it
+waits for the surrounding code to be run (by an application to
+$\varepsilon$) and so it does not reduce further.  If \(M_3\) is run
+by application to \(\varepsilon\), substitution of \(\varepsilon\) for
+\(\alpha\) eliminates \(\TB_\alpha\) and \(\%_\alpha\) and so
+\(42 * 2\) is obtained.
 
@@
 \(\TW_\alpha \tau\) at stage \(A\) if \(M\) is given type \(\tau\) at
-stage \(A\alpha\) and  unquote \(\TBL_\alpha M\) is given type
-\(\tau\) at stage \(A\alpha\) if \(M\) is given type \(\TW_\alpha \tau\) at
-stage \(A\alpha\), represented by the following rules.
+stage \(A\alpha\); unquote \(\TBL_\alpha M\) is given type \(\tau\)
+at stage \(A\alpha\) if \(M\) is given type \(\TW_\alpha \tau\) at
+stage \(A\alpha\); and CSP \(\%_\alpha M\) is give type \(\tau\)
+at stage \(A\alpha\) if \(M\) is given type \(\tau\) at \(A\).
+These are expressed by the following inference rules:
 \begin{center}
-	\infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
-	\infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
+	\infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A} \hfil
+	\infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}} \hfil
+	\infrule{\G\vdash M: \tau @A}{\G\vdash \%_{\alpha}M:\tau @{A\alpha}}
 \end{center}
@@
 
-\AI{We should discuss conceptual points, not technical points!}
+In this paper, we add a simple form of dependent types---{\`a} la
+Edinburgh LF~\cite{} and \LLF~\cite{}---to \LTP and develop \LMD.
+Types can be indexed by terms as in \texttt{Vector} in
+Section~\ref{sec:intro} and \(\lambda\)-abstractions can be given
+dependent function types of the form \(\Pi x:\tau. \sigma\) but we do
+not consider type operators (such as $\texttt{list } \tau$) or
+abstraction over type variables.  We introduce kinds to classify
+well-formed types and equivalences for kinds, types, and terms---as
+in other dependent type systems---but we have to address a question
+how the notion of stage (should) interact with kinds and types.
 
-Next, we develop \LMD by extending \LTP with \LLF-like dependent types.
-There are three technical points in the extension from \LTP to \LMD.
+On the one hand, base types such as \(\I\) should be able to be used
+at every stage as in \LTP so that
+\(\lambda x:\I.\Lambda \alpha. \TB_\alpha \lambda y:\I.M\) is a valid
+term (here, \(\I\) is used at \(\varepsilon\) and \(\alpha\)).
+Similarly for indexed types such as Vector 4.  On the other hand, it
+is not clear how a type indexed by a variable, which can be used only
+at a declared stage, can be used.  For example,
+consider
+\[\TB_\alpha (\lambda x:\I. (\TBL_\alpha (\lambda y:\text{Vector
+  }x.M)N) )
+  \text{ and }
+  \lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M).
+\]
+Is Vector\ \(x\) a legitimate type at \(\varepsilon\) (or \(\alpha\),
+resp.)  even if \(x:\I\) is declared at stage \(\alpha\) (or
+\(\varepsilon\), resp.)?  We give our answer to this question in two
+steps.
 
-% Constants and Base Types
+First, type-level constants such as \(\I\) and Vector can be used at
+every stage in \LMD.  Technically, we introduce a signature that
+declares kinds of type-level constants and types of constants.  For
+example, a signature for the Boolean type and constans is given as
+follows $\B::*, \text{true}:\B, \text{false}:\B$ (where $*$ is the
+kind of proper types).  Declarations in a siganature are not
+associated to particular stages and so they are used at every stage.
 
-First, the way of handling of constants and type-level constants is the difference between \LMD and \LTP.
-We adopt a signature $\Sigma$ to handle constants and type-level constants.
-This is because a signature simplifies kinding rules relating to type-level constants.
-A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
-For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
+Second, an indexed type such as Vector\ 3 or Vector\ $x$ is well
+formed only at the stage(s) where the index term is well typed.  Since
+constant \(3\) is well typed at every stage (if it is declared in the
+signature), so Vector\ 3 is a well-formed type at every stage, too.
+However, Vector\ $M$ is well formed only at the stage where index term
+$M$ is typed.  Thus, the kinding judgment
+of \LMD takes the form \(\G\V \tau :: K @ A\), where stage $A$ stands for
+where \(\tau\) is well formed.  For example,
+given \(\text{Vector}:: \I \rightarrow *\) in the signature \(\Sigma\),
+\(x:\I@\varepsilon \V \text{Vector }x :: * @\varepsilon\) can be
+derived but
+neither
+\(x:\I@\alpha \V \text{Vector }x :: * @\varepsilon\)
+nor 
+\(x:\I@\epsilon \V \text{Vector }x :: * @\alpha\)
+can be.
 
-% Kidinding and Well-formed Kinding Rules
+At first, the restriction above sounds too severe, because a term like
+\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M) \), which
+models a typical code generator which takes the size $x$ and returns
+code for vector manipulation specialized to the given size.  It seems
+crucial for \(y\) to be given a type indexed by $x$.  We can address
+this problem by CSP---In fact,
+$\text{Vector }x$ is not well formed at $\alpha$ under $x:\I@\epsilon$
+but $\text{Vector }(\%_\alpha x)$ is!  So, we can still write
+\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)
+for the typical code generator.
 
-Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
-It was lucky that almost all rules are determined easily.
-This is because multi-stage calculus and dependent types are almost orthogonal.
-Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
-attaching stage anotations to ones of \LLF.
-For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
-\begin{center}
-	\infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
-	\infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
-\end{center}
-
-% Equivalence Rules
-
-Third, we also need type equivalence rules in \LMD because its type system contains dependent types.
-Although there are new primitives relating to stages which aren't in \LLF,
-we can design all rules easily from the syntax or the reductions of \LMD except one equivalence rule about CSP..
+Our decision that wellformedness of types takes stages of index terms
+into account will lead to the introduction of CSP at the type level
+and special equivalence rules, as we will see later.

### 2019-06-22 text/formal-defnition.tex
Substitutions in type environment.
[WIP] revise.

@@
 
-\AI{Is $O$ used as a metavariable?}
 % \AI{Domain and FV are not defined (yet).  I think we should introduce the notion of well-formed type environments by prose below and assume every type environment is well formed.}
@@
 term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$, respectively.
+We also define substitutions of a stage or a term for variables in type environment $\G$.
 We show representative cases below.
@@
 constant has to be well-formed at stage \(\varepsilon\) so that it is
-used at any stage. \AI{We should discuss implicit CSP at the type
-  level somewhere.}
-\red{Conclusionに入れます}
+used at any stage.
 
@@
 The rules for kind wellformedness and kiding is straightforward
-adaptation from \LLF.  So, we omit them.
+adaptation from \LLF and \LTP, except for the rule for type-level CSP.
+\begin{center}
+  \infrule[K-Csp]{
+    \G \V \tau :: * @ A
+  }{
+    \G \V \tau :: * @ A\alpha
+  }
+\end{center}
+Unlike the term level, type-level CSP is implicit.
 
@@
 
-\AI{The second premises of \TConst and \TVar are not needed?}
-\red{Removed. TODO: Fix proofs.}
 \begin{figure}
@@
 if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
-This rule enable to embed computed values into a fragment of code.
+Note that CSP is also applied to the type \(\tau\) (although it is implicit) in the conclusion.  Thanks to implicit CSP, the typing rule is the same as \LTP.
 

### 2019-06-22 text/formal-defnition.tex
Revise Section 3.

@@
 
-Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
-reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
-in implementation.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense and, as we argue next,
-it is practically significant.
+This rule is motivated by a practical consideration.  We will discuss
+the motivation through an example of specializing a vector addition
+function with respect to the size of vectors.  The following function
+vadd (with an auxilirary function vadd$_1$) implements a code
+generator in a hypothetical language based on \LTP.  This language
+provides definitions by \textbf{let}, recursive functions (represented
+by \textbf{fix}), \textbf{if}-expressions, and primitives cons, head,
+and tail to maniputlate vectors.
+We assume that
+$\text{cons}$ is of type $\I \to (\text{Vector}\ n) \to (\text{Vector}\ (n+1))$, 
+$\text{head}$ is of type $\text{Vector}\ n \to \I$, and
+$\text{tail}$ is of type $(\text{Vector}\ n) \to (\text{Vector}\ (n-1))$ for any integer $n$.
 
-\red{$\text{head}: \text{Vector}\ n \to \I$としているが
-$\text{head}: \Pi n:\I.\text{Vector}\ n \to \I$のほうが良いか? tail, consも同様}
+% type checker can know $n=0$ when process the $\textbf{then}$ clause,
 
-\QPercent\ is different from other rules because it was designed from practical reason, not from the syntax or the reductions.
-For example, we discuss $\text{vadd}_\beta$ function,
-which takes a length of integer vectors and returns addition function for vectors with the length.
-$\text{vadd}_1$ is a helper function to make $\text{vadd}$, 
-which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
-We assumed that type checker can know $n=0$ when process the $\textbf{then}$ clause,
-$\text{head}$ is of type $\text{Vector}\ n \to \I$,
-$\text{tail}$ is of type $(\text{Vector}\ n) \to (\text{Vector}\ (n-1))$, 
-and  $\text{cons}$ is of type $\I \to (\text{Vector}\ n) \to (\text{Vector}\ (n+1))$, 
+The helper function vadd$_1$ takes a stage, the length $n$ of vectors, and two quoted vectors and returns code that computes the addition of the given two vectors:
+%
 \newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
@@
 	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                                                   \\
-	  & \hspace{21mm} \text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2)) \\
+	  & \hspace{21mm} \text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2))
 \end{align*}
-Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.
-This function takes the length of vectors and returns a quoted add function for vector of the given size.
+(Here, we assume that the type system can know whether $n=0$ when
+\textbf{then}- and \textbf{else}-branches are typechecked so that
+both branches can be given type \(\TW_\alpha \text{Vector }n\).)
+
+The main function vadd below takes the length $n$ and returns
+($\beta$-closed) code of a function that takes two vectors and returns
+their addition using vadd$_1$.
 \renewcommand{\Vpn}{\text{Vector}\ (\%_\beta n)}
@@
 	  & \hspace{7mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
-	  & \hspace{63mm} \TBL_\beta \text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))    \\
+	  & \hspace{63mm} \TBL_\beta (\text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))) 
 \end{align*}
-\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 10)}
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 5)}
+If this function is applied to a concrete
+(nonnegative) integer, say 5, it returns function code for adding
+two vectors of size 5.  The type of vadd\ 5, obtained by
+substituting 5 for $n$, is
+$\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
+\renewcommand{\Vpn}{\text{Vector}\ 5}
+If the obtained code is run by applying to \(\varepsilon\),
+the type of vadd\ 5\ $\varepsilon$ is
+\(\Vpn\to\Vpn\to\Vpn\) as expected.
+Without \QPercent, however, it would not be possible
+to compose this function code with another piece of code
+$v$ of type, say, \(\TW_\gamma \text{Vector }5\) because
+\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are
+syntactically different types.
+% : \(\TB_\gamma (\TBL_\gamma (\text{vadd}\ 5\ \gamma)\ v\ v)\).
 
-\renewcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
-$\text{vadd}$ function has the type of $\Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$ and
-when we use this function, we instansiate $\text{vadd}$ with some integer such as 5
-and get code of a optimzed $\text{vadd}$ function such as $\text{vadd5}$.
-\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 5)}
-Although $\text{vadd5}$ is of type $\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$,
-a code value of this type is difficult to combine with another code fragment.
-For example, if we want to composite $\text{vadd5}$ with code of reverse fucntion,
-which is of type $\text{rev5}:\F\alpha.\TW_\alpha(\text{Vector}\ 5\to\text{Vector}\ 5)$,
-we write a program like following.
-\begin{align*}
-  \Lambda\gamma.\TB_\gamma.\lambda v_1:(\text{Vector}\ 5).\lambda v_2:(\text{Vector}\ 5).\TBL_\gamma
-  (\text{rev5}\ \gamma)\ (\TBL_\gamma (\text{vadd5}\ \gamma)\ \TBL_\gamma v_1\ \TBL_\gamma v_2)
-\end{align*}
-However, this program cannot be typed without \QPercent{}
-because the type of $v_1$: $\text{Vector}\ 5$ isn't equivalent with the type of arguments of $\text{vadd5}$: $\text{Vector}\ \%_\gamma 5$.
+Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
+reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
+reduction does not match the operational behavior of the CSP operator
+in implementation.  However, as an equational system for multi-stage
+programs, the rule \QPercent makes sense.
 
-In order to resolve this problem, we introduce \QPercent{} into \LMD.
-\begin{center}
-  \infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
-\end{center}
-\QPercent\ states that we can erase this $\%_\alpha$ under a condition.
-The condition is that a CSPed value equals to the original value when it has the same type in the original stage.
-For example, $\V \%_\alpha 5 \E 5 @ \alpha$ because $ \V 5 : \I @ \alpha $ from \TConst\ and  $ \V \%_\alpha 5 : \I @ \alpha$.
-In other words, we can remove a $\%_\alpha$ symbol of a value when it doesn't change the type.
-Thanks to \QPercent, we can identify $\text{Vector}\ 5$ and $\text{Vector}\ \%_\gamma 5$
-and compose the code values of functions as we expected.
+\renewcommand{\Vpn}{\text{Vector}\ n}
+\paragraph{Remark:} By using implicit type-level CSP, the type of vadd
+could have been written
+\(\Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)\).  In this type,
+Vector\ $n$ is given kind at stage \(\varepsilon\) and type-level CSP
+implicitly lifts it to stage \(\beta\).  However, if a type-level
+constant takes two or more arguments from different stages, term-level
+CSP is necessary.  A matrix type (indexed by the numbers of columns
+and rows) is such an example.
 

### 2019-06-22 text/formal-defnition.tex
Reduce the number of pages.

@@
 
+{\small
 \begin{align*}
@@
 \end{align*}
-
+}
 % \AI{Add $M\,\alpha$ to terms.}
@@
 %
+{\small
 \begin{align*}
@@
 \end{align*}
+}
 Here, $\TB_{\alpha_1\cdots\alpha_n} M$,
@@
 %    Congruence rules are omitted from the definition.
+{\small
     \begin{align*}
@@
     \end{align*}
+  }    
 \end{definition}
@@
 
-\begin{figure}
+\begin{figure}[tbp]
   \begin{center}
@@
 the motivation through an example of specializing a vector addition
-function with respect to the size of vectors.  The following function
-vadd (with an auxilirary function vadd$_1$) implements a code
+function with respect to the size of vectors.  The function
+vadd (with an auxilirary function vadd$_1$) below implements a code
 generator in a hypothetical language based on \LTP.  This language
@@
 We assume that
-$\text{cons}$ is of type $\I \to (\text{Vector}\ n) \to (\text{Vector}\ (n+1))$, 
-$\text{head}$ is of type $\text{Vector}\ n \to \I$, and
-$\text{tail}$ is of type $(\text{Vector}\ n) \to (\text{Vector}\ (n-1))$ for any integer $n$.
-
-% type checker can know $n=0$ when process the $\textbf{then}$ clause,
+$\text{cons}$ is of type $\Pi n:\I.\I \to \text{Vector}\ n \to \text{Vector}\ (n+1)$, 
+$\text{head}$ is of type $\Pi n:\I.\text{Vector}\ (n+1) \to \I$, and
+$\text{tail}$ is of type $\Pi n:\I.\text{Vector}\ (n+1) \to (\text{Vector}\ n)$.
 
@@
 \newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
+{\small
 \begin{align*}
@@
 	  & \hspace{7mm} = \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn.            \\
-	  & \hspace{14mm} \textbf{if}\ n = 0                                                                                                \\
-	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                                               \\
+	  & \hspace{14mm} \textbf{if}\ n = 0 \ \textbf{then}\ \TB_\alpha \text{nil}                                                                               \\
 	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                                                       \\
@@
 \end{align*}
+}
 (Here, we assume that the type system can know whether $n=0$ when

### 2019-06-22 text/informal-overview.tex
Reduce the number of pages.

@@
 
-\subsection{\LLF}
+% \subsection{\LLF}
 
-% \LLF
-\LLF is a simple system of dependent types introduced in \cite{attapl}.
-It is made from Edinburgh LF\cite{harper1993framework} by omitting signatures and include declarative equality judgements.
-Hence, all constants and base types are declared in the signature.
-The \LLF type theory generalizes simply typed lambda calculus
-by replacing the function type $\tau\to\sigma$ with the dependent function type $\Pi x:\tau.\sigma$.
+% % \LLF
+% \LLF is a simple system of dependent types introduced in \cite{attapl}.
+% It is made from Edinburgh LF\cite{harper1993framework} by omitting signatures and include declarative equality judgements.
+% Hence, all constants and base types are declared in the signature.
+% The \LLF type theory generalizes simply typed lambda calculus
+% by replacing the function type $\tau\to\sigma$ with the dependent function type $\Pi x:\tau.\sigma$.
 
-% Kind, Well-formed kind
-In addition to ordinary typing rules like simply typed lambda calculus,
-there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
-Kinding rules and well-formed kinding rules are 
-introduced in order to prohibit making illegal types such as $\textrm{Vector}\ \textrm{true}$.
-For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
-for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
+% % Kind, Well-formed kind
+% In addition to ordinary typing rules like simply typed lambda calculus,
+% there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
+% Kinding rules and well-formed kinding rules are 
+% introduced in order to prohibit making illegal types such as $\textrm{Vector}\ \textrm{true}$.
+% For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
+% for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.
 
-% Type Equality
-Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
-For example, $\textrm{Vector}\ 7$ should be equivalent to $\textrm{Vector}\ (3+4)$
-but they are not equivalent seemingly. Thus, we must define equivalence rules.
-In \LLF, equivalence is expressed with a symbol of $\E$.
-$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
-$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
-$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
+% % Type Equality
+% Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
+% For example, $\textrm{Vector}\ 7$ should be equivalent to $\textrm{Vector}\ (3+4)$
+% but they are not equivalent seemingly. Thus, we must define equivalence rules.
+% In \LLF, equivalence is expressed with a symbol of $\E$.
+% $\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
+% $\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
+% $\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
 

### 2019-06-22 text/introduction.tex
Rewrite Sections 1 and 2.
Add MetaOCaml/

@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 specialized to partial inputs to the program and such applications are
-studied in the literature~\cite{taha2007gentle}  \AI{We should list
+studied in the literature~\cite{8384206,taha2007gentle}  \AI{We should list
 applications of multi-stage programming, not necessarily of MetaOCaml.}

### 2019-06-22 text/conclusion.tex
FInish revising Seciton 1.
Revise.

--- 2019-06-14 conclusions.tex
@@
-\section{Conclusions}
+% !TEX root = ../main.tex
 
-We proposed new multi-stage calculus \LMD, which can use dependent types.
-\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
-This extention prevent some bugs relating to generated functions with multi-stage programming,
+\section{Conclusion \label{sec:conclusion}}
+
+We have proposed a new multi-stage calculus \LMD with dependent types.
+\LMD enables finer-grained typing of multi-stage programming comparing to existing type systems.
+This extention prevents some bugs relating to generated functions with multi-stage programming,
 such as \verb|vadd| function for vectors of a fixed length.
@@
 
-Making algorithmic typing and equality rules for \LMD is a future work.
+Developing a typechecking algorithmic for \LMD is left for future work.
 They would be complicated but possible 

### 2019-06-22 text/related-work.tex
FInish revising Seciton 1.
Revise.

--- 2019-06-14 text/related-work.tex
@@
 
-\section{Related Work}
+\section{Related Work \label{sec:related-work}}
+
+MetaOCaml is a programming language with quoting, unquoting, run, and
+CSP.  Kiselyov give many applications of MetaOCaml in \cite{8384206},
+which includes filtering in signal processing, matrix-vector product,
+and DSL compiler.
+
+% 多段階計算の歴史
+
+Theoretical studies on multi-stage programming owe a lot to seminal
+work by Davies and Pfenning~\cite{DaviesPfenning01JACM} and
+Davies~\cite{davies1996temporal}, which found Curry-Howard
+correspondence between multi-stage calculi and modal logic.  In
+particular, Davies' $\lambda^\circ$~\cite{davies1996temporal} has been
+a basis for multi-stage calculi with quasi-quotation.  $\lambda^\circ$
+did not have operators for run and CSP; a few
+studies~\cite{benaissa1999logical,MoggiTahaBenaissaSheard99ESOP}
+enhanced and improved $\lambda^\circ$ towards the development of a
+type-safe multi-stage calculus with quasi-quotation, run, and CSP,
+which were proposed by Taha and Sheard as constructs for multi-stage
+programming~\cite{MetaML}.
+% Benaissa et al.~\cite{benaissa1999logical} study the relationship between a multi-stage calculus and category theory or modal logic.
+% Taha and Sheard introduced run and CSP to a multi-stage calculus in 
+Finally, Taha and Nielsen invented the concept of environment
+classifiers~\cite{taha2003environment} and developed a typed calculus
+$\lambda^\alpha$, which was equipped with all the features above in a
+type sound manner and formed a basis of earlier versions of MetaOCaml.
+A different approach to type-safe multi-stage programming with
+different semantics for quasi-quotations has been studied by Kim, Yi,
+and Calcagno~\cite{DBLP:conf/popl/KimYC06}.
+
+Later, Tsukada and Igarashi~\cite{Tsukada} found correspondence
+between a variant of \(\lambda^\alpha\) called $\lambda^\TW$
+and modal logic and showed that run could be represented as a special
+case of application of a transition abstraction ($\Lambda\alpha$) to
+the empty sequence $\varepsilon$.  Hanada and
+Igarashi~\cite{Hanada2014} developed \LTP as an extension
+$\lambda^\TW$ with CSP.
+% and discuss code residualization which
+% allows us to dump the quoted code into an external file.
+
+% 他段階計算の機能拡張
+
+% 多段階計算の応用
 
@@
 
-There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
-$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
-and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
-In Advanced Topics in Types and Programming Languages\cite{attapl},
-a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
-We adopted \cite{attapl}-like dependent types for \LMD.
-
-One can use dependent types in programming languages such as Idris\cite{brady2013idris} or
-interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
-\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}
+There is much work on dependent types and most of them are affected by
+the pioneering work by Martin-L\"{o}f~\cite{martin1973intuitionstic}.
+Among many dependent type systems such as
+$\lambda^\Pi$~\cite{Meyer1986}, Calculus of
+Constructions~\cite{coquand:inria-00076024}, and Edinburgh
+LF~\cite{harper1993framework}, we base our work on \LLF~\cite{attapl}
+(which is quite close to $\lambda^\Pi$ and Edinburgh LF) due to its
+simplicity.  It has been well known that dependent types are useful to
+express detailed properties of data structure at the type level such
+as the size of data structures~\cite{Xi98} and typed abstract syntax
+trees~\cite{DBLP:conf/dsl/LeijenM99,DBLP:conf/popl/XiCC03}.  The
+vector addition discussed in Section~\ref{sec:formal} is also such an
+example.
 
@@
 
-Applications of dependent types for real problems were also researched.
-In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
-and succeeded in reducing the bounds checking of arrays.
-In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
-it is useful for spped up.
-Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
+% Practical applications of dependent types have been also studied.
+% One can use dependent types in programming languages such as Idris~\cite{brady2013idris} or
+% interactive theorem provers such as Coq~\cite{09thecoq} based on \cite{coquand:inria-00076024}.
+% In Xi and Pfenning~\cite{Xi98}, they extended SML with restricted dependent types
+% and succeeded in reducing the bounds checking of arrays.
+% In Xi and Harper~\cite{xi2001dependently}, they design a type system for an assembly language and
+% it is useful for speed up.
+% Xi also gave dead code elimination and loop unrolling as applications
+%  of dependent types~\cite{xi1999dependent}.
 
-% 多段階計算の歴史
+% 関連研究との比較
 
-\red{Besides,} multi-stage calculi also have a long history of research.
-Davis revealed there is Curry-Howard correspondence between a multi-stage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
-However, $\lambda^\circ$ don't have operators for run and CSP.
-\red{runはboldか? Besidesより適切な接続詞はないのか?}
-Benaissa, et al. \cite{benaissa1999logical} study the relationship between multi-stage calculus and category theory or modal logic.
-Taha and Sheard introduced run and CSP to a multi-stage calculus in \cite{MetaML}.
-Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
-construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
+Although there are studies on combinations of multi-stage programming and other programming features such as mutable cells~\cite{kiselyov2016refined},
+control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging},
+a combination with dependent types has been little studied.
+One exception is Brady and Hammond~\cite{brady2006dependently},
+who have discussed a
+combination of dependently typeed programming with staging in the
+style of MetaOCaml to implement a staged interpreter, which is
+statically guaranteed to generate well typed code.  However, they
+focused on concrete programming examples and there is no theoretical investigation
+of the programming language they used.
 
-In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multi-stage calculus with environment classifiers and
-show that run can be represented as application of $\varepsilon$ to transition abstractions.
-In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
-which allows us to dump the quoted code into an external file.
+% 他の方法としてどのようなものが考えられたか
 
-% 他段階計算の機能拡張
-
-Combination of multi-stage programming and another programming feature has been studied.
-Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multi-stage programming with mutable cells and
-Oishi and Kameyama\cite{oishi2017staging} extended a multi-stage calculus so that it can handle control operators such as shift and reset.
-
-% 多段階計算の応用
-
-MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
-Oleg gave many examples of application of MetaOCaml in \cite{8384206}, 
-which include filtering in signal processing, matrix-vector product, and DSL compiler.
+% Although we define type equivalence of \LMD with composition of equivalence rules,
+% there is another candiate to define,
+% which gives reduction on types and compare the results of reduction such as~\cite{sorensen2006lectures}.
+% This method is better than one of \LMD because equivalence rules become simple.
+% However, we reject it because it cannot handle CSP flexibly.

### 2019-06-22 text/formal-defnition.tex
Revise.
Minor edits.

@@
 \section{Formal Definition of \LMD \label{sec:formal-definition}}
+\label{sec:formal}
 
@@
 
-{\small
+{%\small
 \begin{align*}
@@
     \textrm{signatures}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
-    \textrm{type environments} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
+    \textrm{type env.} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
 \end{align*}
@@
 We write \(\textit{dom}(\Sigma)\) and \(\textit{dom}(\Gamma)\)
-for the set of (type-level) constants declared in \(\Sigma\) and \(\Gamma\), respectively.   As in other multi-stage calculi~\cite{Taha03,Tsukada,Hanada2014},
+for the set of (type-level) constants declared in \(\Sigma\) and \(\Gamma\), respectively.   As in other multi-stage calculi~\cite{taha2003environment,Tsukada,Hanada2014},
 a variable declaration is associated with a stage
@@
 %
-{\small
+{%\small
 \begin{align*}
@@
 %    Congruence rules are omitted from the definition.
-{\small
+{%\small
     \begin{align*}
@@
 \newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
-{\small
 \begin{align*}
@@
 \end{align*}
-}
 (Here, we assume that the type system can know whether $n=0$ when

### 2019-06-22 text/conclusion.tex
Spellcheck (except proof.tex)

@@
 \LMD enables finer-grained typing of multi-stage programming comparing to existing type systems.
-This extention prevents some bugs relating to generated functions with multi-stage programming,
+This extension prevents some bugs relating to generated functions with multi-stage programming,
 such as \verb|vadd| function for vectors of a fixed length.
@@
 strong normalization for full reduction, and progress for staged reduction.
-The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
+The technical difficulty of extension is how to deal with the symbol of CSP $\%$ in the equation rules.
 We resolve this problem by ignoring $\%$ under some condition.

### 2019-06-22 text/formal-defnition.tex
Spellcheck (except proof.tex)

@@
 
-The rules for kind wellformedness and kiding is straightforward
+The rules for kind wellformedness and kinding is straightforward
 adaptation from \LLF and \LTP, except for the rule for type-level CSP.
@@
 So, the rules for kind and type equivalences are not very interesting
-except implict CSP is allowed.
+except implicit CSP is allowed.
 We show a few representative rules below.
@@
 function with respect to the size of vectors.  The function
-vadd (with an auxilirary function vadd$_1$) below implements a code
+vadd (with an auxiliary function vadd$_1$) below implements a code
 generator in a hypothetical language based on \LTP.  This language
@@
 by \textbf{fix}), \textbf{if}-expressions, and primitives cons, head,
-and tail to maniputlate vectors.
+and tail to manipulate vectors.
 We assume that
@@
 The subscripts $A$ and $B$ in $E^A_B$ stand for the stage of the evaluation context and of the hole, respectively.
-The grammer represents that staged reduction is left-to-right and call-by-value and terms under \(\Lambda\) is reduced.
+The grammar represents that staged reduction is left-to-right and call-by-value and terms under \(\Lambda\) is reduced.
 A few examples of evaluation context are shown below:
@@
 is executed only at stage \(\varepsilon\) and only a quotation at
-stage \(\varepsilon\) is spiliced into the surrounding code---notice
+stage \(\varepsilon\) is spliced into the surrounding code---notice
 that, if \(\TB_\alpha v^\alpha\) is at stage \(\varepsilon\), then the

### 2019-06-22 text/introduction.tex
Revise.
Minor edits.
Spellcheck (except proof.tex)

@@
 function code, whose type respects the given size, \emph{provided at
-  specilization time}.  For example, we would like to specialize a
+  specialization time}.  For example, we would like to specialize a
 function to add two vectors with respect to the size of vectors, that
@@
 
-\AI{Informal discussion on how important CSP is?}
-\AI{Comments on Appendix required.}
-
 \subsubsection{Organization of the Paper.}
@@
 \ref{sec:conclusion} concludes the paper with discussion of future
-work.
+work.  For reference, we give the full definition of \LMD
+\AI{and proofs of properties}.

### 2019-06-22 text/properties.tex
Reduce the number of pages.
Spellcheck (except proof.tex)

@@
 \end{lemma}
-
-\red{TODO: Fix the proof.}
-\red{$\G\V J@A$における代入を定義する必要があるか?}
 
@@
 no typed term has an infinite reduction sequence.
-We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{harper1993framework}.
-\AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
-\red{とりあえずA Framework for Defining Logicsを引用しました。}
+We prove this theorem by translating \LMD to the simply typed lambda calculus~\cite{harper1993framework}.
 
@@
 \begin{proof}
-	In order to prove this theorem, we define a translation $(\cdot)^\natural$ from \LMD\ to the symply typed lambda calculus.
+	In order to prove this theorem, we define a translation $(\cdot)^\natural$ from \LMD\ to the simply typed lambda calculus.
 	Second, we prove the $\natural$-translation preserves typing and reduction.
-	Then, we can prove Strong Normalization of \LMD from Strong Normalization of the symply typed lambda calculus.
+	Then, we can prove Strong Normalization of \LMD from Strong Normalization of the simply typed lambda calculus.
 \end{proof}
@@
 
-Progress is a collorary of Unique Decomposition.
+Progress is a corollary of Unique Decomposition.
 

### 2019-06-22 text/related-work.tex
Spellcheck (except proof.tex)

@@
 There is much work on dependent types and most of them are affected by
-the pioneering work by Martin-L\"{o}f~\cite{martin1973intuitionstic}.
+the pioneering work by Martin-L\"{o}f~\cite{martin1973intuitionistic}.
 Among many dependent type systems such as
@@
 who have discussed a
-combination of dependently typeed programming with staging in the
+combination of dependently typed programming with staging in the
 style of MetaOCaml to implement a staged interpreter, which is
@@
 % Although we define type equivalence of \LMD with composition of equivalence rules,
-% there is another candiate to define,
+% there is another candidate to define,
 % which gives reduction on types and compare the results of reduction such as~\cite{sorensen2006lectures}.

### 2019-06-22 text/conclusion.tex
Rewrite conclusion.

@@
 
-We have proposed a new multi-stage calculus \LMD with dependent types.
-\LMD enables finer-grained typing of multi-stage programming comparing to existing type systems.
-This extension prevents some bugs relating to generated functions with multi-stage programming,
-such as \verb|vadd| function for vectors of a fixed length.
-We proved properties of \LMD including preservation, confluence, 
-strong normalization for full reduction, and progress for staged reduction.
-The technical difficulty of extension is how to deal with the symbol of CSP $\%$ in the equation rules.
-We resolve this problem by ignoring $\%$ under some condition.
+We have proposed a new multi-stage calculus \LMD with dependent types,
+which make it possible for programmers to express finer-grained
+properties about the behavior of code values.  The combination leads
+to augmentation of almost all judgments in the type system with stage
+information.  CSP and type equivalence specially tailored for it are
+keys to expressing dependently typed practical code generators.  We
+have proved basic properties of \LMD, including preservation,
+confluence, strong normalization for full reduction, and progress for
+staged reduction.
 
-Developing a typechecking algorithmic for \LMD is left for future work.
-They would be complicated but possible 
-because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
+Developing a typechecking algorithmic for \LMD is left for future
+work.  We expect that most of the development is straigtforward,
+except for implicit CSP at the type-level and \%-erasing equivalence
+rules.

### 2019-06-23 text/properties.tex
Fix the proof of Inversion Lemma for $\Pi$ type.
Revise the proof of Inversion Lemma for $\TW$ type.

--- 2019-06-21 text/properties.tex
@@
 
-\red{TODO: Fix the proof.}
-\red{$\G\V J@A$における代入を定義する必要があるか?}
-
 \begin{proof}
@@
 	\begin{enumerate}
-  \item If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$,
-    then $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma@A\V M:\tau @A$.
-  \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
+		\item If $\G \V (\lambda x:\sigma.M) : \rho$ then there are $\sigma'$ and $\tau'$ such that
+		      $\rho = \Pi x:\sigma'.\tau'$, $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma'@A\V M:\tau'@A$.
+		\item If $\G \V \TB_\alpha M : \tau@A$ then 
+		      there is $\sigma$ such that $\tau = \TW_\alpha \sigma$ and $\G \V M : \sigma@A$.
 		\item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
@@
 We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{harper1993framework}.
-\AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
-\red{とりあえずA Framework for Defining Logicsを引用しました。}
 

### 2019-06-23 text/informal-overview.tex

@@
   variable}\footnote{%
-  In Hanada and Igarash~\cite{Hanada2014}, it was called a
+  In Hanada and Igarashi~\cite{Hanada2014}, it was called a
   \textit{transition variable}, which is derived from correspondence
@@
 declares kinds of type-level constants and types of constants.  For
-example, a signature for the Boolean type and constans is given as
+example, a signature for the Boolean type and constants is given as
 follows $\B::*, \text{true}:\B, \text{false}:\B$ (where $*$ is the
-kind of proper types).  Declarations in a siganature are not
+kind of proper types).  Declarations in a signature are not
 associated to particular stages and so they are used at every stage.

### 2019-06-23 text/properties.tex
Inversion for $\Lambda$ type

--- 2019-06-22 text/properties.tex
@@
 	\begin{enumerate}
-  \item If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$,
-    then $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma@A\V M:\tau @A$.
-  \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
-  \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
+		\item If $\G \V (\lambda x:\sigma.M) : \rho$ then there are $\sigma'$ and $\tau'$ such that
+		      $\rho = \Pi x:\sigma'.\tau'$, $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma'@A\V M:\tau'@A$.
+		\item If $\G \V \TB_\alpha M : \tau@A$ then 
+		      there is $\sigma$ such that $\tau = \TW_\alpha \sigma$ and $\G \V M : \sigma@A$.
+		  \item If $\G \V \Lambda\alpha.M : \tau$ then 
+		  there is $\sigma$ such that $\sigma = \forall\alpha.\sigma$ and $\G \V M : \sigma@A$.% and $\alpha \notin \FTV(\G) \cup \FV(A)$.
 	\end{enumerate}

### 2019-06-23 text/related-work.tex

@@
 
-\section{Related Work \label{sec:related-work}}
+\section{Related Work}
+\label{sec:related-work}
 
@@
 type sound manner and formed a basis of earlier versions of MetaOCaml.
-A different approach to type-safe multi-stage programming with
-different semantics for quasi-quotations has been studied by Kim, Yi,
-and Calcagno~\cite{DBLP:conf/popl/KimYC06}.
+Different approaches to type-safe multi-stage programming with
+slightly different constructs for composing and running code values have been studied by Kim, Yi,
+and Calcagno~\cite{DBLP:conf/popl/KimYC06} and Nanevski and Pfenning~\cite{DBLP:journals/jfp/NanevskiP05}.
 

### 2019-06-23 text/informal-overview.tex
Revise Section 1.
Revise Section 2.

@@
 We describe our calculus \LMD informally.  \LMD is based on
-\LTP~\cite{Hanada2014} by Hanada and Igarashi and we introduce
-dependent types based on \LLF~\cite{attapl}.  We start with a review of 
+\LTP~\cite{Hanada2014} by Hanada and Igarashi and so we start with a review of 
 \LTP.
@@
 \begin{align*}
-	\TBL_\alpha (\TB_\alpha M) \longrightarrow M 
+	\TBL_\alpha (\TB_\alpha M) \longrightarrow M .
 \end{align*}
-The type of
-$\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$; the type
-of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
+% Using the type constructor $\TW_\alpha$ for code values, the type of
+% $\TB_\alpha M$ is given $\TW_\alpha \tau$ if $M$ has type $\tau$; the type
+% of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
 
-The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{stage
+The subscript $\alpha$ in $\TB_\alpha$ and $\TBL_\alpha$ is a \textit{stage
   variable}\footnote{%
@@
 $M\ A$ to stages.  For example,
-$\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10) 5)$ is a code value,
-where \(\alpha\) is abstracted.  If it is applied to \(\varepsilon\),
-which is the empty sequence standing for zero, \(\TB_\alpha\) becomes
-\(\TB_\varepsilon\), which stands for zero brackets, and so, in fact,
-\(\TB_\alpha\) disappears.  As a result, the application reduces to
-(unquoted) \((\lambda x:\I.x+10) 5\) and to 15.  So, application of a
+$\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10)\ 5)$ is a code value,
+where \(\alpha\) is abstracted.  If it is applied to \(\alpha_1 \cdots \alpha_n\), \(\TB_\alpha\) becomes \(\TB_{\alpha_1} \cdots \TB_{\alpha_n}\); in particular,
+if \(n = 0\), \(\TB_\alpha\) disappears.  So, an
+application of $\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10)\ 5)$
+to the empty sequence \(\varepsilon\) reduces to
+(unquoted) \((\lambda x:\I.x+10)\ 5\) and to 15.  In other words, application of of
 \(\Lambda\)-abstraction to $\varepsilon$ corresponds to \texttt{run}.
-If \(\alpha\) is instantiated with, say, \(\beta\gamma\), then
-\(\TB_\alpha\) becomes nested brackets \(\TB_{\beta} \TB_\gamma\).
-These are expressed by the following reduction rule:
+% If \(\alpha\) is instantiated with, say, \(\beta\gamma\), then
+% \(\TB_\alpha\) becomes nested brackets \(\TB_{\beta} \TB_\gamma\).
+This is expressed by the following reduction rule:
 \begin{align*}
@@
 where stage substitution \([\alpha \mapsto A]\) manipulates nesting of
-\(\TB\) and \(\TBL\) (and also \(\%_\alpha\) as we see later).
+\(\TB_\alpha\) and \(\TBL_\alpha\) (and also \(\%_\alpha\) as we see later).
 
@@
 \]
-takes an integer \(x\) as an input and returns the code value into
-which \(x\) is embedded.  CSP is practically important because
-one can call library functions from inside quotations.  If the above
-\(\lambda\)-abstraction is applied to $1 + 2$ as in
+takes an integer \(x\) as an input and returns a code value, into
+which \(x\) is embedded.  If $M_1$ is applied to $38 + 4$ as in
 \[
-  M_2 = (\lambda x:\I.\Lambda\alpha.(\TB_\alpha ((\%_\alpha x) * 2)))\ (38 + 4)
+  M_2 = (\lambda x:\I.\Lambda\alpha.(\TB_\alpha ((\%_\alpha x) * 2)))\ (38 + 4),
 \]
-it evaluates to
+then it evaluates to
 \(M_3 = \Lambda\alpha.(\TB_\alpha ((\%_\alpha 42) * 2))\).  According
@@
 \(\alpha\) eliminates \(\TB_\alpha\) and \(\%_\alpha\) and so
-\(42 * 2\) is obtained.
+\(42 * 2\), which reduces to 84, is obtained.
+CSP is practically important because
+one can call library functions from inside quotations.
 
@@
 \(\TBL_\alpha\) and \(\%_\alpha\).  It takes stages into account: A
-variable declaration in a type environment is associated with its
-declared stage as well as its type and a type judgement of \LTP is of
-the form $\G \vdash M : \tau @ A$, in which $A$ stands for the stage
-of term $M$.  For example,
+variable declaration (written $x:\tau@A$) in a type environment is associated with its
+declared stage $A$ as well as its type $\tau$ and the type judgement of \LTP is of
+the form $\G \vdash M : \tau@A$, in which $A$ stands for the stage
+of term $M$.\footnote{%
+  In Hanada and Igarashi~\cite{Hanada2014}, it is written
+  $\G \vdash^A M : \tau$.
+  }
+For example,
 $y:\I@\alpha \vdash (\lambda x:\I.y) : \I \to \I @ \alpha$ holds, but
@@
 at stage \(A\alpha\) if \(M\) is given type \(\tau\) at \(A\).
-These are expressed by the following inference rules:
+These are expressed by the following typing rules.
 \begin{center}
@@
 In this paper, we add a simple form of dependent types---{\`a} la
-Edinburgh LF~\cite{} and \LLF~\cite{}---to \LTP and develop \LMD.
+Edinburgh LF~\cite{harper1993framework} and \LLF~\cite{attapl}---to \LTP.
 Types can be indexed by terms as in \texttt{Vector} in
@@
 \]
-Is Vector\ \(x\) a legitimate type at \(\varepsilon\) (or \(\alpha\),
-resp.)  even if \(x:\I\) is declared at stage \(\alpha\) (or
-\(\varepsilon\), resp.)?  We give our answer to this question in two
+Is Vector\ \(x\) a legitimate type at \(\varepsilon\) (and \(\alpha\),
+resp.)  even if \(x:\I\) is declared at stage \(\alpha\) (and
+\(\varepsilon\), resp.)?  We will give our answer to this question in two
 steps.
@@
 kind of proper types).  Declarations in a signature are not
-associated to particular stages and so they are used at every stage.
+associated to particular stages; so they can be used at every stage.
 
@@
 \(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)
-for the typical code generator.
+for the typical sort of code generators.
 
-Our decision that wellformedness of types takes stages of index terms
+Our decision that well-formedness of types takes stages of index terms
 into account will lead to the introduction of CSP at the type level

### 2019-06-23 text/formal-defnition.tex
Revise Section 3.

@@
 In this section, we give a formal definition of \LMD, including
-the syntax, full reduction, and type system.  In addition to full reduction,
+the syntax, full reduction, and type system.  In addition to the full reduction,
 in which any redex at any stage can be reduced, we also give staged reduction,
-which models execution as programs.
+which models program execution (at \(\varepsilon\)-stage).
 
@@
 % Types
-A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
-an application $\tau\ M$ of a type (operator) (of $\Pi$-kind) to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
-An application of a type (operator) of $\Pi$-kind to a term is, for example, $\text{Vector}\ 10$
-if type-level constant $\text{Vector}$ has the kind $\Pi x:\I.*$.
+A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau.\sigma$,
+an application $\tau\ M$ of a type (operator of $\Pi$-kind) to a term, a code type $\TW_\alpha \tau$, or an $\alpha$-closed type $\F\alpha.\tau$.
+An example of an application of a type (operator) of $\Pi$-kind to a term is $\text{Vector}\ 10$; it is well kinded
+if, say, type-level constant $\text{Vector}$ has kind $\Pi x:\I.*$.
 A code type $\TW_\alpha \tau$ is for a code fragment of a term of type $\tau$.
-An $\alpha$-closed type corresponds to a runnable code fragment.
+An $\alpha$-closed type, when used with $\TW_\alpha$, represents runnable code.
 
@@
 Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
-whose type is declared in signature $\Sigma$, and the following five forms
+whose types are declared in signature $\Sigma$, and the following five forms
 related to multi-stage programming:
-$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
+$\TB_\alpha M$ represents a code fragment; $\TBL_\alpha M$ represents escape;
 $\Lambda\alpha.M$ is a stage variable abstraction;
-$M\ A$ is an application of stage $A$ to a stage abstraction; and
+$M\ A$ is an application of stage $A$ to a stage abstraction $M$; and
 $\%_\alpha M$ is an operator for cross-stage persistence.
@@
 We adopt the tradition of \LLF-like systems, where types of constants and kinds of type-level constants are globally declared in a signature $\Sigma$, which
-is a sequence of declarations of the form $c:\tau$ and $X:K$.
+is a sequence of declarations of the form $c:\tau$ and $X::K$.
 For example, when we use Boolean in \LMD, $\Sigma$ includes $\B :: *, \textrm{true}:\B, \textrm{false}:\B$.
@@
 We write \(\textit{dom}(\Sigma)\) and \(\textit{dom}(\Gamma)\)
-for the set of (type-level) constants declared in \(\Sigma\) and \(\Gamma\), respectively.   As in other multi-stage calculi~\cite{taha2003environment,Tsukada,Hanada2014},
+for the set of (type-level) constants and variables declared in \(\Sigma\) and \(\Gamma\), respectively.   As in other multi-stage calculi~\cite{taha2003environment,Tsukada,Hanada2014},
 a variable declaration is associated with a stage
 so that a variable can be referenced only at the declared stage.
-Constants and type-level constants are not associated with stages;
-so, we can use them at any stage.
+On the contrary, constants and type-level constants are \emph{not} associated with stages;
+so, they can appear at any stage.
 We define well-formed signature and well-formed type environments later.
 
-The variable $x$ is bound in $M$ of $\lambda x:\tau.M$ and in $\tau_2$
-of $\Pi x:\tau_1.\tau_2$, as usual; the stage variable $\alpha$ is
+The variable $x$ is bound in $M$ of $\lambda x:\tau.M$ and in $\sigma$
+of $\Pi x:\tau.\sigma$, as usual; the stage variable $\alpha$ is
 bound in $M$ of $\Lambda \alpha.M$ and $\tau$ of $\F\alpha.\tau$.
+The notion of free variables is defined in a standard manner.
 We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.  Similarly, $\FV(\tau)$, $\FTV(\tau)$,
@@
 We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
-$x$ is not a free variable in $\tau_2$.
+$x$ is not a free variable of $\tau_2$.
 % Free variables
@@
 \(\forall^\varepsilon\alpha.\tau\).  We have omitted the first kind,
-for simplicity, and dropped the superscript $\varepsilon$.  It would
+for simplicity, and dropped the superscript $\varepsilon$ from the second.  It would
 not be difficult to recover the distinction to show properties related
@@
 Next, we define full reduction for \LMD.
-Before giving the definition of reduction, we define six kinds of substitutions.
+Before giving the definition of reduction, we define two kinds of substitutions.
 Substitution $M[x\mapsto N], \tau[x \mapsto N]$ and $K[x \mapsto N]$ are
@@
 term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$, respectively.
-We also define substitutions of a stage or a term for variables in type environment $\G$.
 We show representative cases below.
@@
 $\TB_{\varepsilon} M = \TBL_{\varepsilon} M = \%_{\varepsilon} M = M$.
+We also define substitutions of a stage or a term for variables in type environment $\G$.
 
@@
 In this section, we define the type system of \LMD.
-It consists of eight judgment forms for signature well-formedness, type environment well-formedness, kind well-formedness, kinding, typing, term equivalence, type equivalence, and kind equivalence.
+It consists of eight judgment forms for signature well-formedness, type environment well-formedness, kind well-formedness, kinding, typing, kind equivalence, type equivalence, and term equivalence.
 We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.
@@
 constant has to be well-formed at stage \(\varepsilon\) so that it is
-used at any stage.
-
-In what follows, well-formedness is not explicitly mentioned but
-we assume that all signatures and type environments are well-formed.
+used at any stage.  In what follows, well-formedness is not explicitly
+mentioned but we assume that all signatures and type environments are
+well-formed.
 
@@
 
-The rules for kind wellformedness and kinding is straightforward
-adaptation from \LLF and \LTP, except for the rule for type-level CSP.
+The rules for kind wellformedness and kinding is a straightforward
+adaptation from \LLF and \LTP, except for the following rule for type-level CSP.
 \begin{center}
@@
 As in standard dependent type systems, \TConv{} allows us to replace the type of a term with an equivalent one.
-For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
-a value of type $\textrm{Vector}\ (4+1)$ can also has type $\textrm{Vector}\ 5$ because of \TConv{}.
+For example, assuming integers and arithmetic, a value of type $\textrm{Vector}\ (4+1)$ can also has type $\textrm{Vector}\ 5$ because of \TConv{}.
 
 % Typing rules for a multi-stage calculus
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
-\TTB and \TTBL are the same with \LTP as we explained in Section \ref{sec:informal-overview}.
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for multi-stage progarmming.
+\TTB{} and \TTBL{} are the same as \LTP, as we explained in Section \ref{sec:informal-overview}.
 The rule \TGen{} for stage abstraction is straightforward.
@@
 The rule \TIns{} is for applications of stages to stage abstractions.
-\TIns{} is mainly used when we run a code value or rename a stage variable in the body of an abstraction.
-The rule \TCsp{} is the rule for CSP, which means that
-if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
+% \TIns{} is mainly used when we run a code value or rename a stage variable in the body of an abstraction.
+The rule \TCsp{} is for CSP, which means that,
+if term $M$ is of type $\tau$ at stage $A$, then $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
 Note that CSP is also applied to the type \(\tau\) (although it is implicit) in the conclusion.  Thanks to implicit CSP, the typing rule is the same as \LTP.
@@
 % $\rho$ at stage $A$ under $\G$, is defined by the rules in
-We show the rules for term equivalence are shown in
+We show the rules for term equivalence  in
 Figure~\ref{fig:term-equivalence-rules}, omitting
@@
 \newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
-\begin{align*}
-	  & \textbf{let}\ \text{vadd}_1 : \F\alpha.\Pi n:\I.\TW_\alpha\Vpn\to\TW_\alpha\Vpn\to\TW_\alpha\Vpn                                \\
-	  & \hspace{7mm} = \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn.            \\
-	  & \hspace{14mm} \textbf{if}\ n = 0 \ \textbf{then}\ \TB_\alpha \text{nil}                                                                               \\
-	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                                                       \\
-	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                                                   \\
-	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                                                   \\
-	  & \hspace{21mm} \text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2))
-\end{align*}
+\begin{tabbing}
+	  $\textbf{let}\ \text{vadd}_1 : \F\alpha.\Pi n:\I.\TW_\alpha\Vpn\to\TW_\alpha\Vpn\to\TW_\alpha\Vpn$                                \\
+	  \hspace{6mm} \= $= \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn.$            \\
+	  \> \hspace{6mm} \= $\textbf{if}\ n = 0 \ \textbf{then}\ \TB_\alpha \text{nil}$ \\
+	  \>\> $\textbf{else}\ \TB_\alpha ($ \= $\textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}$ \\
+	  \>\>\> $\textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}$ \\
+          \>\>\> $\text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2))$
+\end{tabbing}
 (Here, we assume that the type system can know whether $n=0$ when
@@
 	  & \textbf{let}\ \text{vadd}: \Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)                \\ 
-	  & \hspace{7mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
+	  & \hspace{6mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
 	  & \hspace{63mm} \TBL_\beta (\text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))) 
 \end{align*}
-\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 5)}
-If this function is applied to a concrete
-(nonnegative) integer, say 5, it returns function code for adding
+\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 5)}%
+If this function is applied to a
+(nonnegative) integer constant, say 5, it returns function code for adding
 two vectors of size 5.  The type of vadd\ 5, obtained by
@@
 CSP is necessary.  A matrix type (indexed by the numbers of columns
-and rows) is such an example.
+and rows) would be such an example.
 
@@
 The reduction given above is full reduction and any redexes---even
-under quotation---can be reduced in an arbitrary order.
+under $\TB_\alpha$---can be reduced in an arbitrary order.
 Following previous work~\cite{Hanada2014},
@@
 Values at $\varepsilon$ stage are a $\lambda$-abstraction, a quoted code,
-or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
+or a $\Lambda$-abstraction.  The body of a $\lambda$-abstraction can
 be any term but the body of $\Lambda$-abstraction has to a value.  It
@@
 \begin{definition}[Staged Reduction]
-  The staged reduction relation, written $M \longrightarrow_s M'$, is defined by
+  The staged reduction relation, written $M \longrightarrow_s N$, is defined by
   the least relation closed under the rules below.

### 2019-06-23 text/introduction.tex
Revise

@@
 ill-typed expressions from being generated.  For example, a quotation
-of expression \texttt{1 + 1} is given type \texttt{int code}; a
-quotation of \texttt{abs} is given type \texttt{(int -> int) code};
+of expression \texttt{1 + 1} is given type \texttt{int code}
 and a code-generating function, which takes a code value \(c\) as an
@@
   code}.  Ensuring safety for \verb|run| is more challenging because
-basic code types do not guarantee that execution of code values never
+code types per by themselves do not guarantee that the execution of code values never
 results in unbound variable errors.  Taha and
 Nielsen~\cite{taha2003environment} introduced the notion of
-environment classifiers to address the problem and developed a type
+environment classifiers to address the problem, developed a type
 system to ensure not only type-safe composition but also type-safe
-execution of code values with a type soundness theorem (for a pure
-subset of MetaOCaml).
+execution of code values, and proved a type soundness theorem (for a formal calculus \(\lambda^\alpha\) modeling a pure subset of MetaOCaml).
 
@@
 to the sizes of vectors and matrices in MetaOCaml but the type system
-cannot prevent such specialized functions from being applied to
+of MetaOCaml cannot prevent such specialized functions from being applied to
 vectors and matrices of different sizes.
@@
 function to add two vectors with respect to the size of vectors, that
-is, to implement a code generator that takes an integer $n$ as an
+is, to implement a code generator that takes a (nonnegative) integer $n$ as an
 input and generates a piece of function code of type
@@
 MetaOCaml, because its type system and semantics are arguably simpler
-than \(\lambda^\alpha\)~\cite{taha2003environment}, another calculus,
-which formalizes the design of MetaOCaml more faithfully.  Our
-technical contribution are summarized as follows:
+than \(\lambda^\alpha\)~\cite{taha2003environment}, which formalizes
+the design of MetaOCaml more faithfully.  Dependent types are based on
+\LLF~\cite{attapl}, which has one of the simplest form of dependent
+types.  Our technical contribution are summarized as follows:
 \begin{itemize}
-\item We give the formal definition of \LMD with its syntax, 
+\item We give a formal definition of \LMD with its syntax, 
   type system and two kinds of reduction---full and staged reduction.
@@
 \LMD.  Section~\ref{sec:formal-definition} defines \LMD and
-Section~\ref{sec:properties} shows properties of \LMD.  Section
-\ref{sec:related-work} discusses related work and Section
+Section~\ref{sec:properties} shows properties of \LMD.
+Section~\ref{sec:related-work} discusses related work and Section
 \ref{sec:conclusion} concludes the paper with discussion of future
-work.  For reference, we give the full definition of \LMD
-\AI{and proofs of properties}.
+work.  For reference, we give the full definition of \LMD \AI{and
+  proofs of properties} in Appendix.

### 2019-06-23 text/properties.tex

@@
 
-Substitution Lemma in \LMD{} is little more complicated than usual
+Substitution Lemma in \LMD{} is a little more complicated than usual
 because there are eight judgment forms and two kinds of substitution.
@@
 
-We let $\mathcal{J}$ stand for judgments $K \iskind @A$, $\tau::K@A$,
+We let $\mathcal{J}$ stand for the judgments $K \iskind @A$, $\tau::K@A$,
 $M:\tau@A$, $K \E J @ A$, $\tau \E \sigma @ A$, and
@@
 \begin{lemma}[Term Substitution]
-  If $\G, z:\xi@B, \D \V \mathcal{J}$ and $\G\V P:\xi @B$, then $\G, \D[z \mapsto P] \V \mathcal{J}[z \mapsto P]$.  Similarly, if $\V \G, z:\xi@B, \D$ and
-  $\G\V P:\xi @B$, then $\V \G, \D[z \mapsto P]$.
+  If $\G, z:\xi@B, \D \V \mathcal{J}$ and $\G\V P:\xi @B$, then $\G, (\D[z \mapsto P]) \V \mathcal{J}[z \mapsto P]$.  Similarly, if $\V \G, z:\xi@B, \D$ and
+  $\G\V P:\xi @B$, then $\V \G, (\D[z \mapsto P])$.
 \end{lemma}
@@
   and its symmetric version.  Then, they are proved simultaneously by induction on derivations.
-
   Similarly for the others.
@@
 
-Thanks to Substitution Lemmas and Inversion Lemmas, we can prove Preservation easily.
+Thanks to Term/Stage Substitution and Inversion, we can prove Preservation easily.
 
@@
 	For each case, we can use straightforward induction on typing derivations.
-	Difficult cases are \TApp, \TTBL, and \TIns.
-	We need Inversion Lemmas for them.
+	% Difficult cases are \TApp, \TTBL, and \TIns.
+	% We need Inversion Lemmas for them.
 \end{proof}
@@
 no typed term has an infinite reduction sequence.
-We prove this theorem by translating \LMD to the simply typed lambda calculus~\cite{harper1993framework}.
+Following standard proofs (see, e.g., \cite{harper1993framework}), we prove this theorem by translating \LMD to the simply typed lambda calculus.
 
@@
 Confluence is a property that any reduction sequences from one typed term converge.
-Since we have proved Strong Normalization, we can use Newman's Lemma~\cite{} to prove Confluence.
+Since we have proved Strong Normalization, we can use Newman's Lemma~\cite{DBLP:books/daglib/0092409} to prove Confluence.
 
@@
   We can prove by straightforward induction on typing derivations.
-  Main cases are \TApp, \TTBL, and \TIns, where we use Inversion.
+%  Main cases are \TApp, \TTBL, and \TIns, where we use Inversion.
   \qed

### 2019-06-23 text/related-work.tex

@@
 MetaOCaml is a programming language with quoting, unquoting, run, and
-CSP.  Kiselyov give many applications of MetaOCaml in \cite{8384206},
-which includes filtering in signal processing, matrix-vector product,
+CSP.  Kiselyov~\cite{8384206} describes many applications of MetaOCaml, including filtering in signal processing, matrix-vector product,
 and DSL compiler.
@@
 work by Davies and Pfenning~\cite{DaviesPfenning01JACM} and
-Davies~\cite{davies1996temporal}, which found Curry-Howard
+Davies~\cite{davies1996temporal}, who found Curry-Howard
 correspondence between multi-stage calculi and modal logic.  In
 particular, Davies' $\lambda^\circ$~\cite{davies1996temporal} has been
-a basis for multi-stage calculi with quasi-quotation.  $\lambda^\circ$
+a basis for several multi-stage calculi with quasi-quotation.  $\lambda^\circ$
 did not have operators for run and CSP; a few
@@
 and modal logic and showed that run could be represented as a special
-case of application of a transition abstraction ($\Lambda\alpha$) to
+case of application of a transition abstraction ($\Lambda\alpha.M$) to
 the empty sequence $\varepsilon$.  Hanada and
@@
 Among many dependent type systems such as
-$\lambda^\Pi$~\cite{Meyer1986}, Calculus of
+$\lambda^\Pi$~\cite{Meyer1986}, The Calculus of
 Constructions~\cite{coquand:inria-00076024}, and Edinburgh

### 2019-06-24 main.tex
分割コンパイルが失敗する
Fix a bug.
Move proofs to a separate file and share with main.tex.
Add the example of vadd function to Section 2.
Add some comments on the writing style for proofs.
Move full definition to text/fulldefinition.tex and tidy up.
FInish revising Seciton 1.
Shorten the introduction.
Spellcheck (except proof.tex)
Tidy up Weakening.
Fixing proofs.

@@
 \newif\ifnotanonymous \notanonymousfalse
+\newif\iffullversion \fullversiontrue
 \documentclass[runningheads]{llncs}
@@
 \usepackage{lscape}
-\usepackage{mdframed}
 \usepackage{xspace}
+\usepackage{url}
 
@@
 \newcommand{\KVar}{\textsc{K-Var}}
+\newcommand{\KTConst}{\textsc{K-TConst}}
 \newcommand{\KAbs}{\textsc{K-Abs}}
@@
 \newcommand{\M}{\textrm{Mat}}
+
+\newcommand{\rulefbox}[1]{\fbox{\ensuremath{#1}} \hspace{1mm}}
 
@@
 
-\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
-\blue{コードとかはボールドを使ったほうが良いかもしれない。}
-\red{Suspicious senetences are colored red.}
-%
-%
-%
-\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}
+\input{text/introduction.tex}
 
-\input{introduction.tex}
+\input{text/informal-overview.tex}
 
-\input{informal-overview.tex}
+\input{text/formal-defnition.tex}
 
-\input{formal-defnition.tex}
+\input{text/properties.tex}
 
-\input{properties.tex}
+\input{text/related-work.tex}
 
-\input{related-work.tex}
-
-\input{conclusions.tex}
+\input{text/conclusion.tex}
 
@@
 
-\section{Appendix}
+\iffullversion
+\appendix
 
-\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
+%\newtheorem{thm}{Theorem}
+\newtheorem{dfn}{Definition}
+\newtheorem{ex}{Example}
+\newtheorem{cm}{Comment}
+\newcommand{\figheader}[2]{
+  \begin{flushleft}
+    #2 {\bf \normalsize #1}
+\end{flushleft}}
+
+\newpage
+\section{Full Definition of \LMD}
+\input{text/fulldefinitions}
+
+\section{Proofs}
+\input{text/proofs}
+
+\fi
+% \section{Appendix}
+
+% \blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies.
 Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures.
@@
 In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
-\blue{Review Process
-	APLAS 2019 will use a lightweight double-blind reviewing process.
+% \blue{Review Process
+% 	APLAS 2019 will use a lightweight double-blind reviewing process.
 Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper.
 The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
-	To facilitate this process, submitted papers must adhere to the following:
-	Author names and institutions must be omitted and
-	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
-	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
+% 	To facilitate this process, submitted papers must adhere to the following:
+% 	Author names and institutions must be omitted and
+% 	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
+% 	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try.
 Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas.

### 2019-06-24 text/introduction.tex
Remove comments in introduction.

@@
 specialized to partial inputs to the program and such applications are
-studied in the literature~\cite{8384206,taha2007gentle}  \AI{We should list
-applications of multi-stage programming, not necessarily of MetaOCaml.}
+studied in the literature~\cite{8384206,taha2007gentle}  
+% \AI{We should list applications of multi-stage programming, not necessarily of MetaOCaml.}
 
@@
 \ref{sec:conclusion} concludes the paper with discussion of future
-work.  For reference, we give the full definition of \LMD \AI{and
-  proofs of properties} in Appendix.
+work.  For reference, we give the full definition of \LMD and
+ proofs of properties in Appendix.

### 2019-06-24 text/introduction.tex
Fix order.

@@
 specialized to partial inputs to the program and such applications are
-studied in the literature~\cite{8384206,taha2007gentle}  
+studied in the literature~\cite{8384206,mainland2012metahaskell,taha2007gentle}.
 % \AI{We should list applications of multi-stage programming, not necessarily of MetaOCaml.}

### 2019-06-25 text/conclusion.tex
Fix typo.

@@
 to augmentation of almost all judgments in the type system with stage
-information.  CSP and type equivalence specially tailored for it are
+information.  CSP and type equivalence (specially tailored for CSP) are
 keys to expressing dependently typed practical code generators.  We
@@
 
-Developing a typechecking algorithmic for \LMD is left for future
+Developing a typechecking algorithm for \LMD is left for future
 work.  We expect that most of the development is straigtforward,

### 2019-06-25 text/formal-defnition.tex
Fixing proofs.
Reflect comments from John.

@@
 
-The variable $x$ is bound in $M$ of $\lambda x:\tau.M$ and in $\sigma$
-of $\Pi x:\tau.\sigma$, as usual; the stage variable $\alpha$ is
-bound in $M$ of $\Lambda \alpha.M$ and $\tau$ of $\F\alpha.\tau$.
+The variable $x$ is bound in $M$ by $\lambda x:\tau.M$ and in $\sigma$
+by $\Pi x:\tau.\sigma$, as usual; the stage variable $\alpha$ is
+bound in $M$ by $\Lambda \alpha.M$ and $\tau$ by $\F\alpha.\tau$.
 The notion of free variables is defined in a standard manner.
@@
       \infrule[\QTCsp]{
-        \G\V \tau \E \sigma :: K@A
+        \G\V \tau \E \sigma :: *@A
       }{
-        \G\V \tau \E \sigma :: K@{A\alpha}
+        \G\V \tau \E \sigma :: *@{A\alpha}
       }
@@
 \end{tabbing}
-(Here, we assume that the type system can know whether $n=0$ when
+(Here, we assume that the type system can determine whether $n=0$ when
 \textbf{then}- and \textbf{else}-branches are typechecked so that
@@
 The subscripts $A$ and $B$ in $E^A_B$ stand for the stage of the evaluation context and of the hole, respectively.
-The grammar represents that staged reduction is left-to-right and call-by-value and terms under \(\Lambda\) is reduced.
+The grammar represents that staged reduction is left-to-right and call-by-value and terms under \(\Lambda\) are reduced.
 A few examples of evaluation context are shown below:

### 2019-06-25 text/informal-overview.tex
Reflect comments from John.

@@
 evaluates to itself.  Escape $\TBL_\alpha M$ may appear under
-$\TB_\alpha$; it evaluates $M$ to a code value and splice it into the
+$\TB_\alpha$; it evaluates $M$ to a code value and splices it into the
 surrounding code fragment.  Such splicing is expressed by the
@@
   to modal logic, studied by Tsukada and Igarashi~\cite{Tsukada}.} and
-a sequence of stage variables is called \textit{stage}.  Intuitively,
+a sequence of stage variables is called a \textit{stage}.  Intuitively,
 they represent the depth of nested brackets.  Stage variables can be
@@
 constant \(3\) is well typed at every stage (if it is declared in the
-signature), so Vector\ 3 is a well-formed type at every stage, too.
+signature), Vector\ 3 is a well-formed type at every stage, too.
 However, Vector\ $M$ is well formed only at the stage where index term

### 2019-06-25 text/introduction.tex
Reflect comments from John.

--- 2019-06-24 text/introduction.tex
@@
 values.  A promising application of multi-stage programming is
-(run-time) code specialization, which is to generate program code
+(run-time) code specialization, which generates program code
 specialized to partial inputs to the program and such applications are
-studied in the literature~\cite{8384206,taha2007gentle}  
+studied in the literature~\cite{8384206,mainland2012metahaskell,taha2007gentle}.
 % \AI{We should list applications of multi-stage programming, not necessarily of MetaOCaml.}
@@
 \LLF~\cite{attapl}, which has one of the simplest form of dependent
-types.  Our technical contribution are summarized as follows:
+types.  Our technical contributions are summarized as follows:
 \begin{itemize}

### 2019-06-26 text/formal-defnition.tex
Found a bug in the defnition of values.

@@
     v^\varepsilon \in V^\varepsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\varepsilon                                       & \\
-    v^A \in V^A                     & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \varepsilon & \\
+    v^A \in V^A                     & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ B & \\
                                     & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \varepsilon)             & \\

### 2019-07-30 reply-for-review.txt
Add a draft for reply.

Dear Reviewers,
Thank you for your detailed and valuable comments.

We will incorporate the comments as much as possible to a final version of the paper is accepted.  We will focus below on a few important comments (by Reviewers 1 and 2) we think we should address here.

------------------ Reviewer 1 -------------------------

Comment on the last sentence of the abstract:
This sentence refers to the "vadd" example and handling of the symbol of CSP in the type equivalence relation. We think they are an important part of this paper. We'll try to improve but probably will not remove it.

Comment on the last sentence before Section 3.2:
This statement is a conjecture but we think it is not difficult to prove.  We'll make it clear.

Comment on design choice to make type-level CSP:
Because we don't have staged semantics for types, explicit type-level CSP just makes the system more complicated.

Comment on the proof of Strong Normalisation:
Yes, SN for a calculus with pattern-matching can be proved as suggested.  We are not sure how the progress property contributes to the discussion here, though: what we would like to prove is a simulation property, which assumes one-step (successful) reduction in the source calculus and so the progress is not used.  (Are we missing anything?)

------------------ Reviewer 2 -------------------------

Comment on "A metaprogramming framework for formal verification" (by Ebner et al.) and "Ur: Statically-Typed Metaprogramming with Type-Level Record Computation" (by Chlipala):
The first paper is loosely related in the sense that they are interested in (automated) construction of well-typed terms but, in the MSP setting, the presence of eval (which it does not care) often complicates the problem a lot. The second paper is also loosely related because it focuses on practical use and does not contain a theory for metaprogramming.

Comment on "Program Logics for Homogeneous Generative Run-Time Meta-Programming"
(by Berger and Tratt): Although this paper takes a different approach from ours, its main purpose is similar to ours. The main difference is that their language is based on lambda-Box, which can manipulate only closed code, whereas ours can deal with open code.

### 2019-07-30 reply-for-review.txt
Reflected comments from John.

@@
-Dear Reviewers,
 Thank you for your detailed and valuable comments.
 
-We will incorporate the comments as much as possible to a final version of the paper is accepted.
-We will focus below on a few important comments (by Reviewers 1 and 2) we think we should address here.
+We will incorporate all feedback and comments, including those not addressed
+here. We will now respond to some of the key comments and questsions from each
+reviewer.
 
@@
 Comment on the last sentence of the abstract:
-This sentence refers to the "vadd" example and handling of the symbol of CSP in the type equivalence relation.
-We think they are an important part of this paper.
-We'll try to improve but probably will not remove it.
+This sentence refers to the "vadd" example and handling of the symbol of CSP in
+the type equivalence relation. We think they are an important part of this
+paper. We'll try to improve but probably will not remove it.
 
 Comment on the last sentence before Section 3.2:
-This statement is a conjecture but we think it is not difficult to prove.  We'll make it clear.
+This statement is a conjecture but we think it is not difficult to prove.
+We will clarify this point.
 
 Comment on design choice to make type-level CSP:
-Because we don't have staged semantics for types, explicit type-level CSP just makes the system more complicated.
+As we don't have staged semantics for types, explicit type-level CSP ultimately
+complicates the system.
 
 Comment on the proof of Strong Normalisation:
-Yes, SN for a calculus with pattern-matching can be proved as suggested.
-We are not sure how the progress property contributes to the discussion here, though: what we would like to prove is a simulation property, which assumes one-step (successful) reduction in the source calculus and so the progress is not used.
-(Are we missing anything?)
+Yes, SN for a calculus with pattern-matching can be proved as suggested.  We
+are not sure how the progress property contributes to the discussion here,
+though: what we would like to prove is a simulation property, which assumes
+one-step (successful) reduction in the source calculus and so the progress is
+not used.  (Are we missing anything?)
 
@@
 
-Comment on "A metaprogramming framework for formal verification" (by Ebner et al.) and "Ur: Statically-Typed Metaprogramming with Type-Level Record Computation" (by Chlipala):
-The first paper is loosely related in the sense that they are interested in (automated) construction of well-typed terms but, in the MSP setting, the presence of eval (which it does not care) often complicates the problem a lot.
-The second paper is also loosely related because it focuses on practical use and does not contain a theory for metaprogramming.
+Comment on "A metaprogramming framework for formal verification" (by Ebner et
+        al.) and "Ur: Statically-Typed Metaprogramming with Type-Level Record
+        Computation" (by Chlipala):
+The first paper is loosely related in the sense that they are interested in
+(automated) construction of well-typed terms but, in the MSP setting, the
+presence of eval (which it does not care) often complicates the problem a lot.
+We will include this discussion in the Related work section.
+The second paper is also loosely related because it focuses on practical use
+and does not contain a theory for metaprogramming.
 
 Comment on "Program Logics for Homogeneous Generative Run-Time Meta-Programming"
-(by Berger and Tratt): Although this paper takes a different approach from ours, its main purpose is similar to ours.
-The main difference is that their language is based on lambda-Box, which can manipulate only closed code, whereas ours can deal with open code.
+    (by Berger and Tratt): 
+Although this paper takes a different approach from ours, its main purpose is
+similar to ours. The main difference is that their language is based on
+lambda-Box, which can manipulate only closed code, whereas ours can deal
+with open code.
+
+------------------ Reviewer 3 -------------------------

### 2019-07-30 reply-for-review.txt
Improve.

@@
 We will incorporate all feedback and comments, including those not addressed
-here. We will now respond to some of the key comments and questsions from each
+here. We will now respond to some of the key comments and questions from each
 reviewer.
@@
 the type equivalence relation. We think they are an important part of this
-paper. We'll try to improve but probably will not remove it.
+paper.
 
@@
 
+Comment on the ability of this calculus as a model for a practical language
+such as MetaOCaml:
+Because it is easy to extend this calculus to include recursion, we think it is
+able to use as a model of a practical language.
+
 Comment on "Program Logics for Homogeneous Generative Run-Time Meta-Programming"
@@
 ------------------ Reviewer 3 -------------------------
+
+Comment on the type checking algorithm:
+We will construct the algorithm by extending an algorithm for dependent type
+system.

### 2019-08-14 main.tex
Improving proof styles.
Add Acknowledgments.
small edit
Reflected comments on typing from reviwer 1,

@@
 %
-\newif\ifnotanonymous \notanonymousfalse
+\newif\ifnotanonymous \notanonymoustrue
 \newif\iffullversion \fullversiontrue
@@
 \usepackage{url}
+\usepackage{bcpproof}
 
@@
 \title{A Dependently Typed Multi-Stage Calculus%
-	\ifnotanonymous\thanks{Supported by organization x.}\fi
+	% \ifnotanonymous\thanks{Supported by organization x.}\fi
 }
@@
 	\author{Akira Kawata\inst{1} \and
-		Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
+		Atsushi Igarashi\inst{1}\orcidID{0000-0002-5143-9764}}
 	% %
@@
 	\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
-		\email{akira@fos.kuis.kyoto-u.ac.jp} \and
+          \email{akira@fos.kuis.kyoto-u.ac.jp} \\
           \email{igarashi@kuis.kyoto-u.ac.jp}
@@
 
-	We study a dependently typed extension of a multi-stage programming
-	language \`a la MetaOCaml, which supports quasi-quotation and
-	cross-stage persistence for manipulation of code fragments as
-	first-class values and eval for execution of programs dynamically
-	generated by the code manipulation.  Dependent types are expected to
-	bring to multi-stage programming enforcement of strong
-	invariants---beyond simple type safety---on the behavior of
-	dynamically generated code.  An extension is, however, not trivial
-	because a type system would have to take stages---roughly speaking,
+	We study a dependently typed extension of a multi-stage programming language
+\`a la MetaOCaml, which supports quasi-quotation and cross-stage persistence
+for manipulation of code fragments as first-class values and an evaluation
+construct for execution of programs dynamically generated by this code
+manipulation. Dependent types are expected to bring to multi-stage
+programming enforcement of strong invariants---beyond simple type safety---on
+the behavior of dynamically generated code. An extension is, however, not
+trivial because a type system would have to take stages---roughly speaking,
 the number of surrounding quotations---of types into account.
 
-	To rigorously study properties of such an extension, we develop
-	\LMD, which is an extension of Hanada and Igarashi's typed calculus
-	\LTP with dependent types, and prove its properties including
-	preservation, confluence, strong normalization for full
-	reduction, and progress for staged reduction.  Motivated
-	by code generators such that the type of generated code depends on a
-	value from outside of quotations, we argue the significance of
-	cross-stage persistence in dependently typed multi-stage programming
-	and certain type equivalence that are not directly derived from
-	reduction rules.
+To rigorously study properties of such an extension, we develop \LMD, which
+is an extension of Hanada and Igarashi's typed calculus \LTP with dependent
+types, and prove its properties including preservation, confluence, strong
+normalization for full reduction, and progress for staged reduction.
+Motivated by code generators such that the type of generated code depends on
+a value from outside of quotations, we argue the significance of cross-stage
+persistence in dependently typed multi-stage programming and certain type
+equivalence that are not directly derived from reduction rules.
 
@@
 \input{text/conclusion.tex}
+
+\input{text/acknowledgments.tex}
 

### 2019-08-14 text/formal-defnition.tex
Found a bug in the defnition of Redex.
Reflected comments on typing from reviwer 1,

@@
 An example of an application of a type (operator) of $\Pi$-kind to a term is $\text{Vector}\ 10$; it is well kinded
-if, say, type-level constant $\text{Vector}$ has kind $\Pi x:\I.*$.
+if, say, the type-level constant $\text{Vector}$ has kind $\Pi x:\I.*$.
 A code type $\TW_\alpha \tau$ is for a code fragment of a term of type $\tau$.
@@
 
-We adopt the tradition of \LLF-like systems, where types of constants and kinds of type-level constants are globally declared in a signature $\Sigma$, which
-is a sequence of declarations of the form $c:\tau$ and $X::K$.
-For example, when we use Boolean in \LMD, $\Sigma$ includes $\B :: *, \textrm{true}:\B, \textrm{false}:\B$.
-Type environments are sequences of triples of a variable, its type, and its stage.
-We write \(\textit{dom}(\Sigma)\) and \(\textit{dom}(\Gamma)\)
-for the set of (type-level) constants and variables declared in \(\Sigma\) and \(\Gamma\), respectively.   As in other multi-stage calculi~\cite{taha2003environment,Tsukada,Hanada2014},
-a variable declaration is associated with a stage
-so that a variable can be referenced only at the declared stage.
-On the contrary, constants and type-level constants are \emph{not} associated with stages;
-so, they can appear at any stage.
-We define well-formed signature and well-formed type environments later.
+We adopt the tradition of \LLF-like systems, where types of constants and
+kinds of type-level constants are globally declared in a signature $\Sigma$,
+which is a sequence of declarations of the form $c:\tau$ and $X::K$. For
+example, when we use Boolean in \LMD, $\Sigma$ includes $\B :: *,
+\textrm{true}:\B, \textrm{false}:\B$. Type environments are sequences of
+triples of a variable, its type, and its stage. We write
+\(\textit{dom}(\Sigma)\) and \(\textit{dom}(\Gamma)\) for the set of
+(type-level) constants and variables declared in \(\Sigma\) and \(\Gamma\),
+respectively. As in other multi-stage
+calculi~\cite{taha2003environment,Tsukada,Hanada2014}, a variable declaration
+is associated with a stage so that a variable can be referenced only at the
+declared stage. On the contrary, constants and type-level constants are
+\emph{not} associated with stages; so, they can appear at any stage. We
+define well-formed signatures and well-formed type environments later.
 
@@
      & \hspace{10mm} \underline{(\lambda i:\I\to\I.(\Lambda\alpha.\TB_\alpha (\%_\alpha i\ 1 + (\TBL_\alpha \TB_\alpha 3))\ \varepsilon))\ (\lambda x:\I.x)} \\
-     & \longrightarrow_\blacklozenge (\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + (\underline{\TBL_\alpha \TB_\alpha 3})))\ \varepsilon        \\
-     & \longrightarrow_\beta \underline{(\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + 3))\ \varepsilon}                                         \\
+     & \longrightarrow_\beta (\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + (\underline{\TBL_\alpha \TB_\alpha 3})))\ \varepsilon        \\
+     & \longrightarrow_\blacklozenge \underline{(\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + 3))\ \varepsilon}                                         \\
      & \longrightarrow_\Lambda \underline{(\lambda x:\I.x)\ 1} + 3                                                                                           \\
@@
 
-Typing rules of \LMD are shown in Figure~\ref{fig:typing-rules}.
+The typing rules of \LMD are shown in Figure~\ref{fig:typing-rules}.
 The rule \TConst{} means that a constant can appear at any stage.
@@
 Since the syntax of kinds, types, and terms is mutually recursive,
-corresponding notions of equivalence are also mutually recursive.
+the corresponding notions of equivalence are also mutually recursive.
 They are congruences closed under a few axioms for term equivalence.
-So, the rules for kind and type equivalences are not very interesting
-except implicit CSP is allowed.
+So, the rules for kind and type equivalences are not very interesting, 
+except that implicit CSP is allowed.
 We show a few representative rules below.
@@
 reduction does not match the operational behavior of the CSP operator
-in implementation.  However, as an equational system for multi-stage
+in implementations.  However, as an equational system for multi-stage
 programs, the rule \QPercent makes sense.
@@
      & R^\varepsilon ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon \\
-     & R^\alpha      ::=\ \TBL_\alpha \TB_\alpha M                                                         \\
+     & R^\alpha      ::=\ \TBL_\alpha \TB_\alpha v^\alpha                                                         \\
   \end{align*}
@@
                                            & \mid \TB_\alpha E^{A'\alpha}_B \mid \TBL_\alpha E^{A}_B \ (\text{where } A\alpha = A')               \\
-                                           & \mid \Lambda\alpha.E^{A'}_B \mid E^{A'}_B\ A \mid \%_\alpha\ E^{A'}_B \ (\text{where } A\alpha = A')
+                                           & \mid \Lambda\alpha.E^{A'}_B \mid E^{A'}_B\ A \mid \%_\alpha\ E^{A}_B \ (\text{where } A\alpha = A')
   \end{align*}

### 2019-08-14 text/informal-overview.tex
Reflected comments on typing from reviwer 1,

@@
 \end{align*}
-where stage substitution \([\alpha \mapsto A]\) manipulates nesting of
+where stage substitution \([\alpha \mapsto A]\) manipulates the nesting of
 \(\TB_\alpha\) and \(\TBL_\alpha\) (and also \(\%_\alpha\) as we see later).
@@
 \(\tau\) is written \(\TW_\alpha \tau\)---for typing \(\TB_\alpha\),
-\(\TBL_\alpha\) and \(\%_\alpha\).  It takes stages into account: A
+\(\TBL_\alpha\) and \(\%_\alpha\).  It takes stages into account: a
 variable declaration (written $x:\tau@A$) in a type environment is associated with its
@@
 nor 
-\(x:\I@\epsilon \V \text{Vector }x :: * @\alpha\)
+\(x:\I@\varepsilon \V \text{Vector }x :: * @\alpha\)
 can be.
@@
 this problem by CSP---In fact,
-$\text{Vector }x$ is not well formed at $\alpha$ under $x:\I@\epsilon$
+$\text{Vector }x$ is not well formed at $\alpha$ under $x:\I@\varepsilon$
 but $\text{Vector }(\%_\alpha x)$ is!  So, we can still write

### 2019-08-14 text/introduction.tex
Reflected comments on typing from reviwer 1,

@@
 OCaml\footnote{\url{http://ocaml.org}} with special constructs for
-multi-stage programming, including brackets and espace, which are
+multi-stage programming, including brackets and escape, which are
 (hygienic) quasi-quotation, and \texttt{run}, which is similar to
@@
 work.  For reference, we give the full definition of \LMD and
- proofs of properties in Appendix.
+ proofs of properties in the Appendix.

### 2019-08-14 text/properties.tex
Fixing proofs.
Reflect comments from John.
Reflected comments on typing from reviwer 1,

@@
 
-In this section, we show basic properties of \LMD: preservation, strong normalization, confluence for full reduction, and progress for staged reduction.
+In this section, we show the basic properties of \LMD: preservation, strong
+normalization, confluence for full reduction, and progress for staged
+reduction.
 
@@
 
-Substitution Lemma in \LMD{} is a little more complicated than usual
+The Substitution Lemma in \LMD{} is a little more complicated than usual
 because there are eight judgment forms and two kinds of substitution.
-Term Substitution Lemma states that term substitution $[z \mapsto M]$
-preserves derivability of judgments and Stage Substitution Lemma
+The Term Substitution Lemma states that term substitution $[z \mapsto M]$
+preserves derivability of judgments. The Stage Substitution Lemma
 states similarly for stage substitution $[\alpha\mapsto A]$.
@@
 \begin{lemma}[Stage Substitution]
-	If $\G \V \mathcal{J}$, then $\G[\beta\mapsto B] \V \mathcal{J}[\beta\mapsto B]$.  Similarly, if $\G \V \mathcal{J}$, then $\V \G[\beta\mapsto B]$.
+	If $\G \V \mathcal{J}$, then $\G[\beta\mapsto B] \V \mathcal{J}[\beta\mapsto B]$.  Similarly, if $\V \G$, then $\V \G[\beta\mapsto B]$.
 \end{lemma}
@@
 
-The following Inversion Lemma is needed to prove main theorems.
+The following Inversion Lemma is needed to prove the main theorems.
 As usual~\cite{TAPL}, Inversion Lemma enables us to infer the types of subterms of a term from the type of the term.
@@
 \begin{proof}
-  Each item is strengthen by statements about type equivalence.
+  Each item is strengthened by statements about type equivalence.
   For example, the first statement is augmented by

### 2019-08-14 main.tex
Fix typos of reviewer 2.

@@
 the behavior of dynamically generated code. An extension is, however, not
-trivial because a type system would have to take stages---roughly speaking,
-the number of surrounding quotations---of types into account.
+trivial because such a type system would have to take stages of types ---roughly speaking,
+the number of surrounding quotations---into account.
 
@@
 normalization for full reduction, and progress for staged reduction.
-Motivated by code generators such that the type of generated code depends on
-a value from outside of quotations, we argue the significance of cross-stage
+Motivated by code generators that generate code whose type depends on
+a value from outside of the quotations, we argue the significance of cross-stage
 persistence in dependently typed multi-stage programming and certain type

### 2019-08-17 main.tex
Reflects all easy comments.

@@
 persistence in dependently typed multi-stage programming and certain type
-equivalence that are not directly derived from reduction rules.
+equivalences that are not directly derived from reduction rules.
 

### 2019-08-17 text/formal-defnition.tex
Reflects all easy comments.

@@
 $\%_\alpha$ connect tighter than the three forms $\tau\ M$, $M\ N$,
-$M\ A$ of applications, which are left-associative; The binders $\Pi$,
+$M\ A$ of applications, which are left-associative. The binders $\Pi$,
 $\forall$, and $\lambda$ extend as far to the right as possible.
@@
 
-\subsubsection{Kind Wellformedness and Kinding.}
+\subsubsection{Kind Well-formedness and Kinding.}
 
-The rules for kind wellformedness and kinding is a straightforward
+The rules for kind well-formedness and kinding is a straightforward
 adaptation from \LLF and \LTP, except for the following rule for type-level CSP.
@@
 % \TConv
-As in standard dependent type systems, \TConv{} allows us to replace the type of a term with an equivalent one.
-For example, assuming integers and arithmetic, a value of type $\textrm{Vector}\ (4+1)$ can also has type $\textrm{Vector}\ 5$ because of \TConv{}.
+As in standard dependent type systems, \TConv{} allows us to replace the type
+of a term with an equivalent one. For example, assuming integers and
+arithmetic, a value of type $\textrm{Vector}\ (4+1)$ can also have type
+$\textrm{Vector}\ 5$ because of \TConv{}.
 
@@
 Intuitively, it means that the CSP operator applied to term $M$ can be
-removed if $M$ is also well typed at the next stage \(A\alpha\).
+removed if $M$ is also well-typed at the next stage \(A\alpha\).
 For example, constants do not depend on the stage (see \TConst) and

### 2019-08-17 text/informal-overview.tex
Reflects all easy comments.

@@
 to the empty sequence \(\varepsilon\) reduces to
-(unquoted) \((\lambda x:\I.x+10)\ 5\) and to 15.  In other words, application of of
+(unquoted) \((\lambda x:\I.x+10)\ 5\) and to 15.  In other words, application of
 \(\Lambda\)-abstraction to $\varepsilon$ corresponds to \texttt{run}.
@@
 Second, an indexed type such as Vector\ 3 or Vector\ $x$ is well
-formed only at the stage(s) where the index term is well typed.  Since
-constant \(3\) is well typed at every stage (if it is declared in the
+formed only at the stage(s) where the index term is well-typed.  Since
+constant \(3\) is well-typed at every stage (if it is declared in the
 signature), Vector\ 3 is a well-formed type at every stage, too.
-However, Vector\ $M$ is well formed only at the stage where index term
+However, Vector\ $M$ is well-formed only at the stage where index term
 $M$ is typed.  Thus, the kinding judgment
 of \LMD takes the form \(\G\V \tau :: K @ A\), where stage $A$ stands for
-where \(\tau\) is well formed.  For example,
+where \(\tau\) is well-formed.  For example,
 given \(\text{Vector}:: \I \rightarrow *\) in the signature \(\Sigma\),

### 2019-08-17 text/introduction.tex
Reflects all easy comments.

@@
   code}.  Ensuring safety for \verb|run| is more challenging because
-code types per by themselves do not guarantee that the execution of code values never
+code types by themselves do not guarantee that the execution of code values never
 results in unbound variable errors.  Taha and
@@
 One natural idea to address this problem is the introduction of dependent types
-to express the size of data structure in static types~\cite{Xi98}.
+to express the size of data structures in static types~\cite{Xi98}.
 % Dependent types are types which are dependent on values.
@@
 the design of MetaOCaml more faithfully.  Dependent types are based on
-\LLF~\cite{attapl}, which has one of the simplest form of dependent
+\LLF~\cite{attapl}, which has one of the simplest forms of dependent
 types.  Our technical contributions are summarized as follows:

### 2019-08-17 text/properties.tex
Reflects all easy comments.

@@
 
+We proved the next two leammas by simultaneous induction on derivations.
+
 \begin{lemma}[Term Substitution]
@@
 
-\begin{proof}
-  By simultaneous induction on derivations.
- \qed
-\end{proof}
-
 \begin{lemma}[Stage Substitution]
@@
 \end{lemma}
-
-\begin{proof}
-  By simultaneous induction on derivations.
-  \qed
-\end{proof}
 
@@
 term is either a value or can be uniquely decomposed to an evaluation
-context and a redex, ensuring that a well typed term is not
+context and a redex, ensuring that a well-typed term is not
 immediately stuck and the staged semantics is deterministic.
@@
 	If $\G$ does not have any variable declared at stage $\varepsilon$ and $\G \V M : \tau  @ A$, then
-	$ M \in V^A $ or $M'$ exists such that $M \longrightarrow_s M'$.
+	$ M \in V^A $ or there exists $M'$ such that $M \longrightarrow_s M'$.
 \end{corollary}

### 2019-08-17 text/related-work.tex
Reflect comments from John.
Reflects all easy comments.

@@
 CSP.  Kiselyov~\cite{8384206} describes many applications of MetaOCaml, including filtering in signal processing, matrix-vector product,
-and DSL compiler.
+and a DSL compiler.
 
@@
 
-There is much work on dependent types and most of them are affected by
+There is much work on dependent types and most of it are affected by
 the pioneering work by Martin-L\"{o}f~\cite{martin1973intuitionistic}.
@@
 (which is quite close to $\lambda^\Pi$ and Edinburgh LF) due to its
-simplicity.  It has been well known that dependent types are useful to
-express detailed properties of data structure at the type level such
+simplicity.  It is well known that dependent types are useful to
+express detailed properties of data structures at the type level such
 as the size of data structures~\cite{Xi98} and typed abstract syntax
@@
 
-Although there are studies on combinations of multi-stage programming and other programming features such as mutable cells~\cite{kiselyov2016refined},
-control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging},
-a combination with dependent types has been little studied.
-One exception is Brady and Hammond~\cite{brady2006dependently},
-who have discussed a
-combination of dependently typed programming with staging in the
-style of MetaOCaml to implement a staged interpreter, which is
-statically guaranteed to generate well typed code.  However, they
-focused on concrete programming examples and there is no theoretical investigation
-of the programming language they used.
+Although there are studies on combinations of multi-stage programming and
+other programming features such as mutable cells~\cite{kiselyov2016refined} and
+control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
+combination with dependent types has been little studied. One exception is
+Brady and Hammond~\cite{brady2006dependently}, who have discussed a
+combination of dependently typed programming with staging in the style of
+MetaOCaml to implement a staged interpreter, which is statically guaranteed
+to generate well-typed code. However, they focused on concrete programming
+examples and there is no theoretical investigation of the programming
+language they used.
 

### 2019-08-22 text/introduction.tex
Difference between full  and stage reduction

@@
 \begin{itemize}
-\item We give a formal definition of \LMD with its syntax, 
-  type system and two kinds of reduction---full and staged reduction.
+\item We give a formal definition of \LMD with its syntax, type system and
+two kinds of reduction. Full reduction, allowing reduction of any redex,
+including under $\lambda$-abstraction and quotation, and staged reduction, a
+small-step call-by-value operational semantics that is closer to the intended
+multi-stage implementation. \AK{This sentence looks too long as an item.}
 \item We show preservation, strong normalization, and confluence for

### 2019-08-22 text/formal-defnition.tex
Status of properties on program residualization
Justification for type-level implicit CSP.

@@
 \(\forall^\varepsilon\alpha.\tau\).  We have omitted the first kind,
-for simplicity, and dropped the superscript $\varepsilon$ from the second.  It would
-not be difficult to recover the distinction to show properties related
-to program residualization~\cite{Hanada2014}.
+for simplicity, and dropped the superscript $\varepsilon$ from the second. It
+would not be difficult to recover the distinction to show properties related
+to program residualization~\cite{Hanada2014}, although they are still
+conjecture.
 
@@
 \end{center}
-Unlike the term level, type-level CSP is implicit.
+Unlike the term level, type-level CSP is implicit because there is no staged
+semantics for types. \AK{This reason may not be enough for justification.}
 

### 2019-08-23 text/informal-overview.tex
Fix an imcomplete sentence.

@@
 At first, the restriction above sounds too severe, because a term like
-\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M) \), which
-models a typical code generator which takes the size $x$ and returns
-code for vector manipulation specialized to the given size.  It seems
-crucial for \(y\) to be given a type indexed by $x$.  We can address
-this problem by CSP---In fact,
-$\text{Vector }x$ is not well formed at $\alpha$ under $x:\I@\varepsilon$
-but $\text{Vector }(\%_\alpha x)$ is!  So, we can still write
-\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)
+\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M) \), which models a
+typical code generator which takes the size $x$ and returns code for vector
+manipulation specialized to the given size, frequently appears. It seems crucial
+for \(y\) to be given a type indexed by $x$. We can address this problem by
+CSP---In fact, $\text{Vector }x$ is not well formed at $\alpha$ under
+$x:\I@\varepsilon$ but $\text{Vector }(\%_\alpha x)$ is! So, we can still
+write \(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)
 for the typical sort of code generators.

### 2019-08-24 text/formal-defnition.tex
Change the style of syntax.
Fix "Typing rules for a multi-stage calculus"

@@
     \textrm{kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
-    \textrm{types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
+    \textrm{types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
     %     \textrm{Constants}       &   &                          & c                                                                                                          \\
-    \textrm{terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
+    \textrm{terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ N \mid \TB_\alpha M                   \\
                                &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
@@
 % Typing rules for a multi-stage calculus
-The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for multi-stage progarmming.
-\TTB{} and \TTBL{} are the same as \LTP, as we explained in Section \ref{sec:informal-overview}.
-The rule \TGen{} for stage abstraction is straightforward.
-The condition $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that the scope of $\alpha$ is in $M$.
-The rule \TIns{} is for applications of stages to stage abstractions.
-% \TIns{} is mainly used when we run a code value or rename a stage variable in the body of an abstraction.
-The rule \TCsp{} is for CSP, which means that,
-if term $M$ is of type $\tau$ at stage $A$, then $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.
-Note that CSP is also applied to the type \(\tau\) (although it is implicit) in the conclusion.  Thanks to implicit CSP, the typing rule is the same as \LTP.
+The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for
+multi-stage progarmming. \TTB{} and \TTBL{} are the same as \LTP, as we
+explained in Section \ref{sec:informal-overview}. The rule \TGen{} for stage
+abstraction is straightforward. The condition
+$\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensures that the scope of $\alpha$
+is in $M$, and avoids capturing variables in the rest of the judgments. The
+rule \TIns{} is for applications of stages to stage abstractions. The rule
+\TCsp{} is for CSP, which means that, if term $M$ is of type $\tau$ at stage
+$A$, then $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$. Note that CSP
+is also applied to the type \(\tau\) (although it is implicit) in the
+conclusion. Thanks to implicit CSP, the typing rules are the same as in \LTP.
 

### 2019-08-24 text/formal-defnition.tex
Add explanation of vadd example.

@@
 
-This rule is motivated by a practical consideration.  We will discuss
-the motivation through an example of specializing a vector addition
-function with respect to the size of vectors.  The function
-vadd (with an auxiliary function vadd$_1$) below implements a code
-generator in a hypothetical language based on \LTP.  This language
-provides definitions by \textbf{let}, recursive functions (represented
-by \textbf{fix}), \textbf{if}-expressions, and primitives cons, head,
-and tail to manipulate vectors.
+This rule is motivated by a practical consideration. We have potentially many
+pairs of vectors of the fixed length in some fields, for example, computer
+graphics and the same function such as vector addition is applied to all of
+them. We will discuss the motivation through an example of specializing a
+vector addition function with respect to the size of vectors. The function
+vadd (with an auxiliary function vadd$_1$) below implements a code generator
+in a hypothetical language based on \LTP. This language provides definitions
+by \textbf{let}, recursive functions (represented by \textbf{fix}),
+\textbf{if}-expressions, and primitives cons, head, and tail to manipulate
+vectors.
 We assume that

### 2019-08-24 text/formal-defnition.tex
Add an explanation on evaluation context.
Make consistent usage of A and A'.

@@
   The family $V^A$ of sets of values, ranged over by $v^A$,
-  is defined by the following grammar.  In the grammar, $A \neq \varepsilon$ is assumed.
+  is defined by the following grammar.  In the grammar, $A' \neq \varepsilon$ is assumed.
   \begin{align*}
     v^\varepsilon \in V^\varepsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\varepsilon                                             & \\
-    v^A \in V^A                     & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ B & \\
-                                    & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \varepsilon)             & \\
-                                    & \quad\   \mid\ \%_\alpha v^{A'} (\text{if } A = A'\alpha  \text{ for some } \alpha, A')
+    v^{A'} \in V^{A'}               & ::= x \mid \lambda x:\tau.v^{A'} \mid v^{A'}\ v^{A'} \mid\ \TB_\alpha v^{A'\alpha} \mid \Lambda\alpha.v^{A'} \mid v^{A'}\ B & \\
+                                    & \quad\   \mid\ \TBL_\alpha v^{A''} (\text{if } A' = A''\alpha \text{ for some } \alpha, A'' \neq \varepsilon)               & \\
+                                    & \quad\   \mid\ \%_\alpha v^{A''} (\text{if } A' = A''\alpha)
   \end{align*}
@@
                                            & \mid \TB_\alpha E^{A'\alpha}_B \mid \TBL_\alpha E^{A}_B \ (\text{where } A\alpha = A')               \\
-                                           & \mid \Lambda\alpha.E^{A'}_B \mid E^{A'}_B\ A \mid \%_\alpha\ E^{A}_B \ (\text{where } A\alpha = A')
+                                           & \mid \Lambda\alpha.E^{A'}_B \mid E^{A'}_B\ A \mid \%_\alpha\ E^{A'}_B \ (\text{where } A\alpha = A')
   \end{align*}
@@
 
-The subscripts $A$ and $B$ in $E^A_B$ stand for the stage of the evaluation context and of the hole, respectively.
-The grammar represents that staged reduction is left-to-right and call-by-value and terms under \(\Lambda\) are reduced.
-A few examples of evaluation context are shown below:
+The subscripts $A$ and $B$ in $E^A_B$ stand for the stage of the evaluation
+context and of the hole, respectively. The grammar represents that staged
+reduction is left-to-right and call-by-value and terms under \(\Lambda\) are
+reduced. Terms at non-$\varepsilon$ stages are not reduced as long as they do
+not contain a term such as \(\TBL_\alpha \TB_\alpha M\). A few examples of
+evaluation context are shown below:
 \begin{align*}

### 2019-08-25 text/related-work.tex
Add a description for Ur.

@@
 
-MetaOCaml is a programming language with quoting, unquoting, run, and
-CSP.  Kiselyov~\cite{8384206} describes many applications of MetaOCaml, including filtering in signal processing, matrix-vector product,
-and a DSL compiler.
+% Practical research on multi-stage programming
+
+MetaOCaml is a programming language with quoting, unquoting, run, and CSP.
+Kiselyov~\cite{8384206} describes many applications of MetaOCaml, including
+filtering in signal processing, matrix-vector product, and a DSL compiler.
+Ur\cite{chlipala2010ur} is a programming language with metaprogramming, which
+is focused on Web applications.
 
@@
 examples and there is no theoretical investigation of the programming
-language they used.
+language they used. In order to make safer multi-stage programming language, 
+Martin and Laurence~\cite{martin2015HGRTMP} gave program logic for
+\(\text{Mini-ML}^\square_e\)~\cite{DaviesPfenning01JACM} but
+it cannot manipulate open code which ours can deal with.
 

### 2019-08-26 text/formal-defnition.tex
Add some comments.

@@
 graphics and the same function such as vector addition is applied to all of
-them. We will discuss the motivation through an example of specializing a
-vector addition function with respect to the size of vectors. The function
-vadd (with an auxiliary function vadd$_1$) below implements a code generator
-in a hypothetical language based on \LTP. This language provides definitions
-by \textbf{let}, recursive functions (represented by \textbf{fix}),
-\textbf{if}-expressions, and primitives cons, head, and tail to manipulate
-vectors.
-We assume that
+them. \AK{I strenghened this example by adding concrete situation. Do we need
+more reinforcements such as comparision with other method?} We will discuss
+the motivation through an example of specializing a vector addition function
+with respect to the size of vectors. The function vadd (with an auxiliary
+function vadd$_1$) below implements a code generator in a hypothetical
+language based on \LTP. This language provides definitions by \textbf{let},
+recursive functions (represented by \textbf{fix}), \textbf{if}-expressions,
+and primitives cons, head, and tail to manipulate vectors. We assume that
 $\text{cons}$ is of type $\Pi n:\I.\I \to \text{Vector}\ n \to \text{Vector}\ (n+1)$, 

### 2019-08-28 text/related-work.tex
Add some comments.
Reflecting taha's comment.

@@
 
-% 多段階計算の歴史
+% The history of multi-stage programming
 
-Theoretical studies on multi-stage programming owe a lot to seminal
-work by Davies and Pfenning~\cite{DaviesPfenning01JACM} and
-Davies~\cite{davies1996temporal}, who found Curry-Howard
-correspondence between multi-stage calculi and modal logic.  In
-particular, Davies' $\lambda^\circ$~\cite{davies1996temporal} has been
-a basis for several multi-stage calculi with quasi-quotation.  $\lambda^\circ$
-did not have operators for run and CSP; a few
-studies~\cite{benaissa1999logical,MoggiTahaBenaissaSheard99ESOP}
-enhanced and improved $\lambda^\circ$ towards the development of a
-type-safe multi-stage calculus with quasi-quotation, run, and CSP,
-which were proposed by Taha and Sheard as constructs for multi-stage
-programming~\cite{MetaML}.
-% Benaissa et al.~\cite{benaissa1999logical} study the relationship between a multi-stage calculus and category theory or modal logic.
-% Taha and Sheard introduced run and CSP to a multi-stage calculus in 
+Theoretical studies on multi-stage programming owe a lot to seminal work by
+Davies and Pfenning~\cite{DaviesPfenning01JACM} and
+Davies~\cite{davies1996temporal}, who found Curry-Howard correspondence
+between multi-stage calculi and modal logic. In particular, Davies'
+$\lambda^\circ$~\cite{davies1996temporal} has been a basis for several
+multi-stage calculi with quasi-quotation. $\lambda^\circ$ did not have
+operators for run and CSP; a few
+studies~\cite{benaissa1999logical,MoggiTahaBenaissaSheard99ESOP} enhanced and
+improved $\lambda^\circ$ towards the development of a type-safe multi-stage
+calculus with quasi-quotation, run, and CSP, which were proposed by Taha and
+Sheard as constructs for multi-stage programming~\cite{MetaML}.
+
 Finally, Taha and Nielsen invented the concept of environment
 classifiers~\cite{taha2003environment} and developed a typed calculus
-$\lambda^\alpha$, which was equipped with all the features above in a
-type sound manner and formed a basis of earlier versions of MetaOCaml.
-Different approaches to type-safe multi-stage programming with
-slightly different constructs for composing and running code values have been studied by Kim, Yi,
-and Calcagno~\cite{DBLP:conf/popl/KimYC06} and Nanevski and Pfenning~\cite{DBLP:journals/jfp/NanevskiP05}.
+$\lambda^\alpha$, which was equipped with all the features above in a type
+sound manner and formed a basis of earlier versions of MetaOCaml. Different
+approaches to type-safe multi-stage programming with slightly different
+constructs for composing and running code values have been studied by Kim,
+Yi, and Calcagno~\cite{DBLP:conf/popl/KimYC06} and Nanevski and
+Pfenning~\cite{DBLP:journals/jfp/NanevskiP05}.
 
@@
 
-% 他段階計算の機能拡張
-
-% 多段階計算の応用
-
-% 依存型の歴史
+% The history of dependent types
 
@@
 
-% 依存型の応用
+% Applications of dependent types
 
-% Practical applications of dependent types have been also studied.
-% One can use dependent types in programming languages such as Idris~\cite{brady2013idris} or
-% interactive theorem provers such as Coq~\cite{09thecoq} based on \cite{coquand:inria-00076024}.
-% In Xi and Pfenning~\cite{Xi98}, they extended SML with restricted dependent types
-% and succeeded in reducing the bounds checking of arrays.
-% In Xi and Harper~\cite{xi2001dependently}, they design a type system for an assembly language and
-% it is useful for speed up.
-% Xi also gave dead code elimination and loop unrolling as applications
-%  of dependent types~\cite{xi1999dependent}.
+% Practical applications of dependent types have been also studied. One can use
+% dependent types in programming languages such as Idris~\cite{brady2013idris}
+% or interactive theorem provers such as Coq~\cite{09thecoq} based on
+% \cite{coquand:inria-00076024}. In Xi and Pfenning~\cite{Xi98}, they extended
+% SML with restricted dependent types and succeeded in reducing the bounds
+% checking of arrays. In Xi and Harper~\cite{xi2001dependently}, they design a
+% type system for an assembly language and it is useful for speed up. Xi also
+% gave dead code elimination and loop unrolling as applications of dependent
+% types~\cite{xi1999dependent}.
 
-% 関連研究との比較
+% Comparison with other works
 
@@
 control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
-combination with dependent types has been little studied. One exception is
-Brady and Hammond~\cite{brady2006dependently}, who have discussed a
+combination with dependent types has been little studied.
+
+Brady and Hammond~\cite{brady2006dependently} have discussed a
 combination of dependently typed programming with staging in the style of
@@
 examples and there is no theoretical investigation of the programming
-language they used. In order to make safer multi-stage programming language, 
+language they used.
+
+Pasalic and Taha~\cite{pasalic2002tagless} designed \(\lambda_{H\circ}\) by
+introducing the concept of stage into an existing dependent type system
+\(\lambda_H\)~\cite{zhong2002certified}. However, there are not eval and CSP
+in \(\lambda_{H\circ}\) because it was designed before the invention of
+environment classifiers.
+
+In Forgarty, Pasalic, Siek and Taha~\cite{fogarty2007concoqtion}
+
+In order to make safer multi-stage programming language, 
 Martin and Laurence~\cite{martin2015HGRTMP} gave program logic for
 \(\text{Mini-ML}^\square_e\)~\cite{DaviesPfenning01JACM} but
-it cannot manipulate open code which ours can deal with.
+it cannot manipulate open code which ours can deal with. \AK{Is the place of
+this sentence is appropriate?}
 
@@
 
-% Although we define type equivalence of \LMD with composition of equivalence rules,
-% there is another candidate to define,
-% which gives reduction on types and compare the results of reduction such as~\cite{sorensen2006lectures}.
-% This method is better than one of \LMD because equivalence rules become simple.
-% However, we reject it because it cannot handle CSP flexibly.
+Although we define type equivalence of \LMD with composition of equivalence
+rules, there is another candidate to define, which gives reduction on types
+and compare the results of reduction such as~\cite{sorensen2006lectures}.
+This method is better than one of \LMD because equivalence rules become
+simple. However, we reject it because it cannot handle CSP flexibly.

### 2019-08-28 text/related-work.tex
Relect all commments from Taha.

@@
 calculus with quasi-quotation, run, and CSP, which were proposed by Taha and
-Sheard as constructs for multi-stage programming~\cite{MetaML}.
+Sheard as constructs for multi-stage programming~\cite{MetaML}. Chen and
+Xi~\cite{chen2003meta} introduce a code type with types of free variables in
+the code in order to prevent free variable evaluation. \AK{Is here
+appropriate? Although this paper using the concept of dependent types, the
+purpose is avoid open code problem. Therefore, I cite this paper here.}
 
@@
 Although there are studies on combinations of multi-stage programming and
-other programming features such as mutable cells~\cite{kiselyov2016refined} and
-control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
-combination with dependent types has been little studied.
-
-Brady and Hammond~\cite{brady2006dependently} have discussed a
-combination of dependently typed programming with staging in the style of
-MetaOCaml to implement a staged interpreter, which is statically guaranteed
-to generate well-typed code. However, they focused on concrete programming
-examples and there is no theoretical investigation of the programming
-language they used.
-
+other programming features such as mutable cells~\cite{kiselyov2016refined}
+and control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
+combination with dependent types has been little studied. \AK{little?} Brady
+and Hammond~\cite{brady2006dependently} have discussed a combination of
+dependently typed programming with staging in the style of MetaOCaml to
+implement a staged interpreter, which is statically guaranteed to generate
+well-typed code. However, they focused on concrete programming examples and
+there is no theoretical investigation of the programming language they used.
 Pasalic and Taha~\cite{pasalic2002tagless} designed \(\lambda_{H\circ}\) by
@@
 in \(\lambda_{H\circ}\) because it was designed before the invention of
-environment classifiers.
-
-In Forgarty, Pasalic, Siek and Taha~\cite{fogarty2007concoqtion}
+environment classifiers. In Forgarty, Pasalic, Siek and
+Taha~\cite{fogarty2007concoqtion}, they extended the type system of MetaOCaml
+with indexed types. With this extension, types can be indexed with a Coq term.
 
@@
 
-Although we define type equivalence of \LMD with composition of equivalence
-rules, there is another candidate to define, which gives reduction on types
-and compare the results of reduction such as~\cite{sorensen2006lectures}.
-This method is better than one of \LMD because equivalence rules become
-simple. However, we reject it because it cannot handle CSP flexibly.
+% Although we define type equivalence of \LMD with composition of equivalence
+% rules, there is another candidate to define, which gives reduction on types
+% and compare the results of reduction such as~\cite{sorensen2006lectures}.
+% This method is better than one of \LMD because equivalence rules become
+% simple. However, we reject it because it cannot handle CSP flexibly.

### 2019-08-29 text/introduction.tex
Fix.

@@
 \end{itemize}
-The combination of multi-stage programming and dependent types has
-been discussed by Brady and Hammond~\cite{brady2006dependently} but,
-to our knowledge, our work is a first formal calculus of dependently
-typed multi-stage programming.
+The combination of multi-stage programming and dependent types has been
+discussed by Brady and Hammond~\cite{brady2006dependently} \AK{Should we
+include Meta-D~\cite{pasalic2002tagless}?}, to our knowledge, our work is a
+first formal calculus of dependently typed multi-stage programming.
 

### 2019-08-29 text/formal-defnition.tex
Towards the camera ready version.

@@
 The prefix operators $\TW_\alpha, \TB_\alpha, \TBL_\alpha$, and
-$\%_\alpha$ connect tighter than the three forms $\tau\ M$, $M\ N$,
+$\%_\alpha$ are given higher precedence over the three forms $\tau\ M$, $M\ N$,
 $M\ A$ of applications, which are left-associative. The binders $\Pi$,
@@
 would not be difficult to recover the distinction to show properties related
-to program residualization~\cite{Hanada2014}, although they are still
-conjecture.
+to program residualization~\cite{Hanada2014}, although they are left as 
+conjectures.
 
@@
 Substitution $M[\alpha \mapsto A], \tau [\alpha \mapsto A], K[\alpha \mapsto A]$ and $B[\alpha\mapsto A]$ are
-substitutions of stage $A$ for stage variable $\alpha$ in
-term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$, respectively.
+substitutions of stage $A$ for stage variable $\alpha$ in term $M$, type $\tau$, kind $K$, and stage $B$, respectively.
 We show representative cases below.
@@
 Unlike the term level, type-level CSP is implicit because there is no staged
-semantics for types. \AK{This reason may not be enough for justification.}
+semantics for types.
 
@@
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for
-multi-stage progarmming. \TTB{} and \TTBL{} are the same as \LTP, as we
+multi-stage progarmming. \TTB{} and \TTBL{} are the same as in \LTP, as we
 explained in Section \ref{sec:informal-overview}. The rule \TGen{} for stage
@@
 
-This rule is motivated by a practical consideration. We have potentially many
-pairs of vectors of the fixed length in some fields, for example, computer
-graphics and the same function such as vector addition is applied to all of
-them. \AK{I strenghened this example by adding concrete situation. Do we need
-more reinforcements such as comparision with other method?} We will discuss
-the motivation through an example of specializing a vector addition function
-with respect to the size of vectors. The function vadd (with an auxiliary
-function vadd$_1$) below implements a code generator in a hypothetical
-language based on \LTP. This language provides definitions by \textbf{let},
+\subsubsection{Example.}
+
+We show an example of a dependently typed code generator in a
+hypothetical language based on \LTP.  
+% This rule is motivated by a practical consideration.
+Let's consider an application, for example, in computer graphics, in
+which we have potentially many pairs of vectors of the fixed (but
+statically unkown) length and a function---such as vector
+addition---to be applied to all of them.
+
+\AI{Some more description about what we'd like to do.}
+\AI{Brief comparison with other ways (somewhere else)?}
+% \AK{I strenghened this example by adding concrete situation. Do we need
+% more reinforcements such as comparision with other method?} We will discuss
+% the motivation through an example of specializing a vector addition function
+% with respect to the size of vectors.
+
+The function vadd (with an auxiliary
+function vadd$_1$) below implements a code generator.
+This language provides definitions by \textbf{let},
 recursive functions (represented by \textbf{fix}), \textbf{if}-expressions,
@@
 \(\Vpn\to\Vpn\to\Vpn\) as expected.
+
+\AI{Comparison?}
+
+\paragraph{Remark:}
+\AI{Comments on \QPercent}
 Without \QPercent, however, it would not be possible
@@
 % : \(\TB_\gamma (\TBL_\gamma (\text{vadd}\ 5\ \gamma)\ v\ v)\).
-
 Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
@@
 reduction is left-to-right and call-by-value and terms under \(\Lambda\) are
-reduced. Terms at non-$\varepsilon$ stages are not reduced as long as they do
-not contain a term such as \(\TBL_\alpha \TB_\alpha M\). A few examples of
-evaluation context are shown below:
+reduced. Terms at non-$\varepsilon$ stages are not reduced, except
+redexes of the form \(\TBL_\alpha \TB_\alpha M\) at stage \(\alpha\).
+A few examples of
+evaluation contexts are shown below:
 \begin{align*}
   \square\ (\lambda x:\I.x)                  & \in  ECtx^\varepsilon_\varepsilon \\
-  \Lambda\alpha.\square\ \epsilon            & \in ECtx^\varepsilon_\varepsilon  \\
+  \Lambda\alpha.\square\ \varepsilon            & \in ECtx^\varepsilon_\varepsilon  \\
   \TBL_\alpha \TB_\alpha \TBL_\alpha \square & \in ECtx^\alpha_\varepsilon
@@
 
-This reduction relation represents a term reduces in a deterministic,
+This reduction relation reduces a term in a deterministic,
 left-to-right, call-by-value manner.  An application of an abstraction

### 2019-08-29 text/informal-overview.tex
Towards the camera ready version.

@@
 typical code generator which takes the size $x$ and returns code for vector
-manipulation specialized to the given size, frequently appears. It seems crucial
+manipulation specialized to the given size, will be rejected. It seems crucial
 for \(y\) to be given a type indexed by $x$. We can address this problem by

### 2019-08-29 text/introduction.tex
Towards the camera ready version.

--- 2019-08-17 text/introduction.tex
@@
 \begin{itemize}
-\item We give a formal definition of \LMD with its syntax, 
-  type system and two kinds of reduction---full and staged reduction.
+\item We give a formal definition of \LMD with its syntax, type system and
+two kinds of reduction: full reduction, allowing reduction of any redex,
+including one under $\lambda$-abstraction and quotation, and staged reduction, a
+small-step call-by-value operational semantics that is closer to the intended
+multi-stage implementation.
 \item We show preservation, strong normalization, and confluence for
@@
 The combination of multi-stage programming and dependent types has
-been discussed by Brady and Hammond~\cite{brady2006dependently} but,
-to our knowledge, our work is a first formal calculus of dependently
-typed multi-stage programming.
+been discussed by Pasalic, Taha, and Sheard~\cite{pasalic2002tagless}
+and Brady and Hammond~\cite{brady2006dependently} but, to our
+knowledge, our work is a first formal calculus of dependently typed
+multi-stage programming with all the key constructs~\cite{MetaML}.
 

### 2019-08-29 text/related-work.tex
Fix.
Towards the camera ready version.

@@
 filtering in signal processing, matrix-vector product, and a DSL compiler.
-Ur\cite{chlipala2010ur} is a programming language with metaprogramming, which
-is focused on Web applications.
 
@@
 calculus with quasi-quotation, run, and CSP, which were proposed by Taha and
-Sheard as constructs for multi-stage programming~\cite{MetaML}. Chen and
-Xi~\cite{chen2003meta} introduce a code type with types of free variables in
-the code in order to prevent free variable evaluation. \AK{Is here
-appropriate? Although this paper using the concept of dependent types, the
-purpose is avoid open code problem. Therefore, I cite this paper here.}
-
+Sheard as constructs for multi-stage programming~\cite{MetaML}. 
 Finally, Taha and Nielsen invented the concept of environment
@@
 
-Although there are studies on combinations of multi-stage programming and
-other programming features such as mutable cells~\cite{kiselyov2016refined}
-and control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
-combination with dependent types has been little studied. \AK{little?} Brady
-and Hammond~\cite{brady2006dependently} have discussed a combination of
-dependently typed programming with staging in the style of MetaOCaml to
-implement a staged interpreter, which is statically guaranteed to generate
-well-typed code. However, they focused on concrete programming examples and
-there is no theoretical investigation of the programming language they used.
-Pasalic and Taha~\cite{pasalic2002tagless} designed \(\lambda_{H\circ}\) by
-introducing the concept of stage into an existing dependent type system
-\(\lambda_H\)~\cite{zhong2002certified}. However, there are not eval and CSP
-in \(\lambda_{H\circ}\) because it was designed before the invention of
-environment classifiers. In Forgarty, Pasalic, Siek and
-Taha~\cite{fogarty2007concoqtion}, they extended the type system of MetaOCaml
-with indexed types. With this extension, types can be indexed with a Coq term.
+% Although there are studies on combinations of multi-stage programming and
+% other programming features such as mutable cells~\cite{kiselyov2016refined}
+% and control operators~\cite{KameyamaKiselyovShan09PEPM,oishi2017staging}, a
+% combination with dependent types has been little studied.
 
-In order to make safer multi-stage programming language, 
-Martin and Laurence~\cite{martin2015HGRTMP} gave program logic for
-\(\text{Mini-ML}^\square_e\)~\cite{DaviesPfenning01JACM} but
-it cannot manipulate open code which ours can deal with. \AK{Is the place of
-this sentence is appropriate?}
+%%%%%% dependent types for (compile-time) code generation
+
+The use of dependent types for code generation is argued by
+Chlipala~\cite{chlipala2010ur} and Ebner et
+al.~\cite{DBLP:journals/pacmpl/EbnerURAM17}.  They use inductive types
+to guarantee well-formedness of generated code.  Aside from the lack
+of quasi-quotation, their systems are for heterogeneous
+meta-programming and compile-time code generation and they do not
+support features for run-time code generation such as run and CSP, as \LMD{} does.
+
+%%%% index/dependent types for MSP
+
+We discuss earlier attempts at incorporating dependent types into
+multi-stage programming.  Pasalic and Taha~\cite{pasalic2002tagless}
+designed \(\lambda_{H\circ}\) by introducing the concept of stage into
+an existing dependent type system
+\(\lambda_H\)~\cite{zhong2002certified}.  However,
+\(\lambda_{H\circ}\) is equipped with neither run nor CSP.  Forgarty,
+Pasalic, Siek and Taha~\cite{fogarty2007concoqtion} extended the type
+system of MetaOCaml with indexed types.  With this extension, types
+can be indexed with a Coq term.  Chen and Xi~\cite{chen2003meta}
+introduce code types augmented with information on types of free
+variables in the code in order to prevent code with free variables
+from being evaluated.  These systems separate the language of type
+indices from the term language.  As a result, they do not enjoy
+full-spectrum dependent types but are technically simpler because
+there is no need to take stage of types into account.  Brady and
+Hammond~\cite{brady2006dependently} have discussed a combination of
+(full-spectrum) dependently typed programming with staging in the
+style of MetaOCaml to implement a staged interpreter, which is
+statically guaranteed to generate well-typed code.  However, they
+focused on concrete programming examples and there is no theoretical
+investigation of the programming language they used.
+
+Berger and Tratt~\cite{martin2015HGRTMP} gave program logic for
+\(\text{Mini-ML}^\square_e\)~\cite{DaviesPfenning01JACM}, which would
+allow fine-grained reasoning about the behavior of code generators.
+However, it cannot manipulate open code which ours can deal with.
 

### 2019-08-29 text/formal-defnition.tex
Fix Remark on QPercent.

@@
 \paragraph{Remark:}
-\AI{Comments on \QPercent}
-Without \QPercent, however, it would not be possible
-to compose this function code with another piece of code
-$v$ of type, say, \(\TW_\gamma \text{Vector }5\) because
-\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are
-syntactically different types.
-% : \(\TB_\gamma (\TBL_\gamma (\text{vadd}\ 5\ \gamma)\ v\ v)\).
+When this function is composed with another piece of code $v$ of type, say,
+\(\TW_\gamma \text{Vector }5\), \QPercent plays an essential role; that is,
+\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are syntactically
+different types but \QPercent enables to equate one with another.
 Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
 reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
-reduction does not match the operational behavior of the CSP operator
-in implementations.  However, as an equational system for multi-stage
-programs, the rule \QPercent makes sense.
+reduction does not match the operational behavior of the CSP operator in
+implementations. However, as an equational system for multi-stage programs,
+the rule \QPercent makes sense.
 

### 2019-08-29 text/formal-defnition.tex
Comparision with other method.

@@
 
-\AI{Comparison?}
+There are other ways to realize the vector addition function for fixed-length
+lists: determining statically the length of all the vectors and use tuples
+instead of lists or checking dynamically the dimensions of every pair of
+lists. However, our method is better than there two methods in two points.
+First, our function, $\text{vadd}_1$ can generate function for arbitrary
+length vectors unlike ones using tuples. Second, $\text{vadd}_1$ has an
+advantage in speed over ones using dynamic checking because it can generate
+optimized function for a given length.
 
@@
 When this function is composed with another piece of code $v$ of type, say,
-\(\TW_\gamma \text{Vector }5\), \QPercent plays an essential role; that is,
+\(\TW_\gamma \text{Vector }5\), \QPercent{} plays an essential role; that is,
 \(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are syntactically
-different types but \QPercent enables to equate one with another.
+different types but \QPercent{} enables to equate one with another.
 Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
@@
 implementations. However, as an equational system for multi-stage programs,
-the rule \QPercent makes sense.
+the rule \QPercent{} makes sense.
 

### 2019-08-29 text/formal-defnition.tex
Describe the motivation more precisely.
Revise the vadd example.

--- 2019-08-29 text/formal-defnition.tex
@@
 % This rule is motivated by a practical consideration.
-Let's consider an application, for example, in computer graphics, in
-which we have potentially many pairs of vectors of the fixed (but
-statically unkown) length and a function---such as vector
-addition---to be applied to all of them.
-
-\AI{Some more description about what we'd like to do.}
-\AI{Brief comparison with other ways (somewhere else)?}
-% \AK{I strenghened this example by adding concrete situation. Do we need
-% more reinforcements such as comparision with other method?} We will discuss
-% the motivation through an example of specializing a vector addition function
-% with respect to the size of vectors.
-
-The function vadd (with an auxiliary
-function vadd$_1$) below implements a code generator.
 This language provides definitions by \textbf{let},
@@
 
-The helper function vadd$_1$ takes a stage, the length $n$ of vectors, and two quoted vectors and returns code that computes the addition of the given two vectors:
+Let's consider an application, for example, in computer graphics, in which we
+have potentially many pairs of vectors of the fixed (but statically unkown)
+length and a function---such as vector addition---to be applied to
+them. This function should be fast because it is applied many times and be
+safe because just one runtime error may ruin the whole long-running calculation.
+
+% \AK{I strenghened this example by adding concrete situation. Do we need
+% more reinforcements such as comparision with other method?} We will discuss
+% the motivation through an example of specializing a vector addition function
+% with respect to the size of vectors.
+
+\newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
+
+Our goal is to define the function vadd of type
+\[
+  \Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn).
+\]
+\renewcommand{\Vpn}{\text{Vector}\ n}
+It takes the length $n$ and returns ($\beta$-closed) code of a
+function to add two vectors of length $n$.  The generated
+code is run by applying it to \(\varepsilon\) to obtain
+a function of type \(\Vpn\to\Vpn\to\Vpn\) as expected.
+
+We start with the helper function vadd$_1$, which takes a stage, the length $n$ of vectors, and two quoted vectors and returns code that computes the addition of the given two vectors:
 %
-\newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
 \begin{tabbing}
@@
 	  \>\>\> $\textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}$ \\
-          \>\>\> $\text{cons}\ (\text{head}\ (\TBL_\alpha v_1) + \text{head}\ (\TBL_\alpha v_2))\ (\TBL_\alpha f\ (n-1)\ t_1\ t_2))$
+          \>\>\> $\text{cons}\ $\= $(\text{head}\ (\TBL_\alpha v_1) + \text{head} \ (\TBL_\alpha v_2))$ \\
+          \>\>\>\> $(\TBL_\alpha f\ (n-1)\ (\TB_\alpha t_1)\ (\TB_\alpha t_2)))$
 \end{tabbing}
+Note that the generated code will not contain branching on $n$ or recursion.
 (Here, we assume that the type system can determine whether $n=0$ when
@@
 
-The main function vadd below takes the length $n$ and returns
-($\beta$-closed) code of a function that takes two vectors and returns
-their addition using vadd$_1$.
+Using vadd$_1$, the main function vadd can be defined as follows:
 \renewcommand{\Vpn}{\text{Vector}\ (\%_\beta n)}
@@
 \renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 5)}%
-If this function is applied to a
+The auxiliary function vadd$_1$ generates code to compute addition of
+the formal arguments $v_1$ and $v_2$ without branching on $n$ or recursion.
+As we mentioned already, if this function is applied to a
 (nonnegative) integer constant, say 5, it returns function code for adding
@@
 
-\AI{Comparison?}
+There are other ways to implement the vector addition function for
+lists of fixed length: by using tuples instead of lists if the length
+for all the vectors is statically known or by checking dynamically the
+lengths of lists for every pair.  However, our method is better than
+these two methods in two points.  First, our function, $\text{vadd}_1$
+can generate functions for vectors of arbitrary length unlike the one
+using tuples.  Second, $\text{vadd}_1$ has an advantage in speed over
+the one using dynamic checking because it can generate an optimized
+function for a given length.
 
-\paragraph{Remark:}
-When this function is composed with another piece of code $v$ of type, say,
-\(\TW_\gamma \text{Vector }5\), \QPercent plays an essential role; that is,
-\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are syntactically
-different types but \QPercent enables to equate one with another.
+We make two technical remarks before proceeding:
+\begin{enumerate}
+\item If the generated function code is composed with another piece of code of type, say,
+\(\TW_\gamma \text{Vector }5\), \QPercent{} plays an essential role; that is,
+\(\text{Vector }5\) and \(\text{Vector }(\%_\gamma 5)\), which would occur
+by applying the generated code to \(\gamma\) (instead of \(\varepsilon\)), are syntactically
+different types but \QPercent{} enables to equate them.
 Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
@@
 implementations. However, as an equational system for multi-stage programs,
-the rule \QPercent makes sense.
-
-\renewcommand{\Vpn}{\text{Vector}\ n}
-\paragraph{Remark:} By using implicit type-level CSP, the type of vadd
+the rule \QPercent{} makes sense.
+\item \renewcommand{\Vpn}{\text{Vector}\ n}
+By using implicit type-level CSP, the type of vadd
 could have been written
@@
 and rows) would be such an example.
+\end{enumerate}
 

### 2019-08-30 main.tex
Difference between full  and stage reduction
Add some comments.
Spell checked.

@@
 \newif\ifnotanonymous \notanonymoustrue
-\newif\iffullversion \fullversiontrue
+\newif\iffullversion \fullversionfalse
 \documentclass[runningheads]{llncs}
@@
 \newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}
+\newcommand{\AK}[1]{\textcolor{blue}{[#1 -- AK]}}
 
@@
 manipulation. Dependent types are expected to bring to multi-stage
-programming enforcement of strong invariants---beyond simple type safety---on
+programming enforcement of strong invariant---beyond simple type safety---on
 the behavior of dynamically generated code. An extension is, however, not

### 2019-08-30 text/formal-defnition.tex
Correct paranthesis
Spell checked.

@@
 The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are constructs for
-multi-stage progarmming. \TTB{} and \TTBL{} are the same as in \LTP, as we
+multi-stage programming. \TTB{} and \TTBL{} are the same as in \LTP, as we
 explained in Section \ref{sec:informal-overview}. The rule \TGen{} for stage
@@
 Let's consider an application, for example, in computer graphics, in which we
-have potentially many pairs of vectors of the fixed (but statically unkown)
+have potentially many pairs of vectors of the fixed (but statically unknown)
 length and a function---such as vector addition---to be applied to
@@
           \>\>\> $\text{cons}\ $\= $(\text{head}\ (\TBL_\alpha v_1) + \text{head} \ (\TBL_\alpha v_2))$ \\
-          \>\>\>\> $(\TBL_\alpha f\ (n-1)\ (\TB_\alpha t_1)\ (\TB_\alpha t_2)))$
+          \>\>\>\> $\TBL_\alpha (f\ (n-1)\ (\TB_\alpha t_1)\ (\TB_\alpha t_2)))$
 \end{tabbing}

### 2019-08-30 text/introduction.tex
Spell checked.

@@
 polymorphism~\cite{Milner78JCSS}, is not strong enough to guarantee
-invariants beyond simple types.  For example, Kiselyov~\cite{8384206}
+invariant beyond simple types.  For example, Kiselyov~\cite{8384206}
 demonstrates specialization of vector/matrix computation with respect

### 2019-08-30 main.tex
Final round of polishing.

@@
 % to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{cite}
+\usepackage{hyperref}
+\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 the behavior of dynamically generated code. An extension is, however, not
-trivial because such a type system would have to take stages of types ---roughly speaking,
+trivial because such a type system would have to take stages of types---roughly speaking,
 the number of surrounding quotations---into account.

### 2019-08-30 text/informal-overview.tex
Fix.
Final round of polishing.

@@
 a sequence of stage variables is called a \textit{stage}.  Intuitively,
-they represent the depth of nested brackets.  Stage variables can be
+a stage represents the depth of nested brackets.  Stage variables can be
 abstracted by $\Lambda\alpha.M$ and instantiated by an application
@@
 $\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10)\ 5)$ is a code value,
-where \(\alpha\) is abstracted.  If it is applied to \(\alpha_1 \cdots \alpha_n\), \(\TB_\alpha\) becomes \(\TB_{\alpha_1} \cdots \TB_{\alpha_n}\); in particular,
+where \(\alpha\) is abstracted.  If it is applied to \(A = \alpha_1 \cdots \alpha_n\), \(\TB_\alpha\) becomes \(\TB_{\alpha_1} \cdots \TB_{\alpha_n}\); in particular,
 if \(n = 0\), \(\TB_\alpha\) disappears.  So, an
 application of $\Lambda\alpha.\TB_\alpha ((\lambda x:\I.x+10)\ 5)$
-to the empty sequence \(\varepsilon\) reduces to
-(unquoted) \((\lambda x:\I.x+10)\ 5\) and to 15.  In other words, application of
+pto the empty sequence \(\varepsilon\) reduces to
+(unquoted) \((\lambda x:\I.x+10)\ 5\) and to 15.  In other words, application of a
 \(\Lambda\)-abstraction to $\varepsilon$ corresponds to \texttt{run}.
@@
 Similarly for indexed types such as Vector 4.  On the other hand, it
-is not clear how a type indexed by a variable, which can be used only
+is not immediately clear how a type indexed by a variable, which can be used only
 at a declared stage, can be used.  For example,
@@
 
-At first, the restriction above sounds too severe, because a term like
+Apparently, the restriction above sounds too severe, because a term like
 \(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M) \), which models a
@@
 CSP---In fact, $\text{Vector }x$ is not well formed at $\alpha$ under
-$x:\I@\varepsilon$ but $\text{Vector }(\%_\alpha x)$ is! So, we can still
+$x:\I@\varepsilon$ but $\text{Vector }(\%_\alpha x)$ is!  Thus, we can still
 write \(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)

### 2019-08-30 text/introduction.tex
For arxiv.

@@
   full reduction; and show unique decomposition (and progress as its
-  corollary) for staged reduction, which formalizes program execution.
+  corollary) for staged reduction.
 \end{itemize}
@@
 and Brady and Hammond~\cite{brady2006dependently} but, to our
-knowledge, our work is a first formal calculus of dependently typed
-multi-stage programming with all the key constructs~\cite{MetaML}.
+knowledge, our work is a first formal calculus of full-spectrum dependently typed
+multi-stage programming with all the key constructs mentioned above.
 

### 2019-11-20 slides/main.tex
Start making second draft.

\documentclass[dvipdfmx,aspectratio=169, 20pt]{beamer}
\usepackage[absolute,overlay]{textpos}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ascmac}
\usepackage[backend=biber, style=numeric]{biblatex}
\usepackage{color}
\usepackage{mathtools}
\usepackage{url}
\usepackage{bcprules, proof}
\usepackage{xparse}
\usepackage{xspace}
\usepackage{fancybox}
\usepackage{float}
\usepackage{bcprules}
\usepackage{ebproof}
\usepackage{lscape}
\usepackage{pgfpages}

% beamer cheat sheet
% http://www.cpt.univ-mrs.fr/~masson/latex/Beamer-appearance-cheat-sheet.pdf

% Make note pages suer simple.
% \setbeamertemplate{note page}[plain]

% This option generate pdf files showing notes on the right hand side of each
% pages. But this optionn has some bugs. I recommend you tou do not use this
% option.
% \setbeameroption{show notes on second screen=right}

% Note options
% \setbeameroption{show notes}
% \setbeameroption{hide notes}
% \setbeameroption{show only notes}

% Show grid for debug
% \setbeamertemplate{background}[grid][step=1cm]

% Use default design theme. I quit to use this theme because it has no boxed
% environments.
% \usetheme{default}
\usetheme{Boadilla}

% Add page numbers to footnotes. This line does not work for Boadilla theme.
% \setbeamertemplate{footline}[frame number]

% So, I use some hack in
% https://tex.stackexchange.com/questions/66995/modify-footer-of-slides.
% \makeatother and \makeatletter enable us to change internal package things.
\makeatother
\setbeamertemplate{footline}
{
    \leavevmode
    \hbox{
        \setbeamercolor{coloredboxstuff}{fg=black,bg=white}
        \hskip0.85\paperwidth
        \begin{beamercolorbox}[wd=0.10\paperwidth,ht=2.25ex,dp=1ex,right]{coloredboxstuff}
            {\textbf{\insertframenumber{} / \inserttotalframenumber}}
        \end{beamercolorbox}}
    \vskip0pt
}
\makeatletter

% Remove all navigation symbols
\setbeamertemplate{navigation symbols}{}
% using non standard fonts for beamer
\usefonttheme{professionalfonts}
% Set the font size of titles
% See other font category at
% https://tex.stackexchange.com/questions/183052/what-are-all-the-possible-first-arguments-to-setbeamerfont
\setbeamerfont{title}{size=\normalsize}
\setbeamerfont{frametitle}{size=\normalsize}
\setbeamerfont{normal text}{size=\small}
\setbeamerfont{itemize/enumerate body}{size=\footnotesize}
\setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
\setbeamerfont{frametitle continuation}{size=\small}
\setbeamerfont{framesubtitle}{size=\small}
\setbeamerfont{abstract}{size=\small}
\setbeamerfont{projected text}{size=\small}
\setbeamerfont{block title}{size=\small}
\setbeamerfont{footline}{size=\tiny}

% You need this line in order to enforce normal text font setting.
% https://tex.stackexchange.com/questions/320223/how-to-enforce-a-font-series-in-beamer-for-normal-default-text
\AtBeginDocument{\usebeamerfont{normal text}}

\setbeamertemplate{bibliography item}{\insertbiblabel}
% \setbeamertemplate{blocks}[default]
\setbeamertemplate{blocks}[rounded]
\setbeamertemplate{theorems}[normal font]

% \bibliography{main}{}
\addbibresource{main.bib}
\DeclareSortingScheme{mysorting}{\sort{\citeorder}}
\ExecuteBibliographyOptions{sorting=mysorting}

\setlength\intextsep{0pt}
\setlength\textfloatsep{0pt}

\newcommand{\rulefbox}[1]{\fbox{\ensuremath{#1}} \hspace{1mm}}
\newcommand{\figheader}[2]{
  \begin{flushleft}
    #2 {\bf \normalsize #1}
\end{flushleft}}

\newcommand{\toc}[0]{
  \begin{frame}{Contents}
  \tableofcontents[currentsection]
  \end{frame}
}

\defbeamertemplate{description item}{align left}{\insertdescriptionitem\hfill}

% Load symbol macros
\input{symboldef.tex}

\title{Dependently Typed Multi-stage Calculus}
\author{\underline{Akira Kawata} and Atsushi Igarashi}
\institute{Gradudate School of Informatics, Kyoto University}
\date{Dec 2, 2019}

\begin{document}
\maketitle

% Output the outline slide
% \begin{frame}{Contents}
%   \tableofcontents
%   \note{
%   }
% \end{frame}

\section{Introduction to Multistage programming}

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm enables
    \begin{itemize}
        \item Generation of code at runtime
        \item Evaluation of code at runtime
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using runtime information
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Styles of Multi-stage Programming}
    \begin{itemize}
        \item Strings
            \begin{itemize}
                    \item Ruby, Perl, etc.
            \end{itemize}
        \item ASTs
            \begin{itemize}
                    \item Lisp
            \end{itemize}
        \item ASTs and code types
            \begin{itemize}
                    \item MetaOCaml
            \end{itemize}
    \end{itemize}
    \note{
        There are three kinds of multi-stage Programming.
    }
\end{frame}

\begin{frame}[fragile]{Example of Multi-stage Programming in MetaOCaml}
    \begin{center}
        \begin{verbatim}
     # let a = .< 1 + 2 >.;;
     val a : int code = .< 1 + 2 >.
     # Runcode.run a;;
     - : int = 3

     # let b = .<.~a + .~a>.;;
     val b : int code = .<(1 + 2) + (1 + 2)>. 
     # Runcode.run b;;
     - : int = 6
        \end{verbatim}
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
    Generate efficient vector addition functions for given length vectors.
    \renewcommand{\V}{\text{Vec}}
    \begin{tabbing}
        \( \text{vadd-gen} : \I \to \TW_\alpha (\V \to \V \to \V) \) \\
        (* \( \TW_\alpha \) is corresponding to code in MetaOCaml.*) \\[2mm]
        \( \textbf{let}\ \text{vadd3} = \textbf{run}\ (\text{vadd-gen}\ 3);; \) \\
        \( \text{val}\ \text{vadd3} : \V \to \V \to \V \) \\[2mm]
        \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
        \( - : \V = [5;7;9] \)
    \end{tabbing}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \renewcommand{\V}{\text{Vec}}
    \begin{tabbing}
        \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
        \( \longrightarrow \textbf{RUNTIME ERROR!} \)
    \end{tabbing}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Dependent Types}
    Types dependent on values
    \begin{itemize}
            \item Can give more fine restriction on terms.
    \end{itemize}
    \renewcommand{\V}{\text{Vec}\ }
    \begin{tabbing}
        \( [1;2;3]:\ (\V 3) \) \\
        \( [1;2;3;4]:\ (\V 4) \) \\
        \( \text{vadd3}:\ (\V 3) \to (\V 3) \to (\V 3) \)
    \end{tabbing}

    \note{
        By the way, we can write types dependent on values using dependent types.
    }
\end{frame}

\begin{frame}[fragile]{Our Approach: \LMD}
    Introduce dependent types into \LTP [Hanada\&Igarashi'14].
    \begin{itemize}
        \item Features of multi-stage programming
            \begin{itemize}
                \item Code type
                \item Type safe {\bf{run}}
                \item Cross Stage Persistence(CSP)
            \end{itemize}
        \item Features of dependent types
            \begin{itemize}
                \item Typing, Kinding, Well-formed kind rules with stages
                \item Equivalence rules including CSP
            \end{itemize}
    \end{itemize}
    \note{
        Our approach to the problem of multi-stage programming is introducing dependent types into a multi-stage calculus by Hanada and Igarashi.
        We call our multi-stage calculus as \LMD.
    }
\end{frame}

\begin{frame}[fragile]{vadd-gen in \LMD}
    Type tells us the length of vector.
    \newcommand{\Vn}{\text{Vec}\ n}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \begin{tabbing}
        \( \text{vadd-gen} : \Pi n:\I \to \TW_\alpha (\Vn \to \Vn \to \Vn) \) \\[2mm]
        \( \textbf{let}\ \text{vadd3} = \textbf{run}\ (\text{vadd-gen}\ 3);; \) \\
        \( \text{val}\ \text{vadd3} : \Vt \to \Vt \to \Vt \) \\[2mm]
    \end{tabbing}
    Now, vadd3 takes only vectors of 3 length.
    \note{
        vadd-gen is changed as follows in \LMD.
        Thanks to dependent types ...
    }
\end{frame}

\begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
    Type system prevents illegal use of generated function.
    \renewcommand{\V}{\text{Vec}}
    \begin{tabbing}
        \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
        \( - : \V = [5;7;9] \) \\[2mm]
        \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
        \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
    \end{tabbing}
    \note{
        Type of generated functions by vadd-gen in \LMD have the length information in their types.
    }
\end{frame}

\begin{frame}[fragile]{Terms of \LMD}
    \begin{block}{Terms}
        \( M ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M \mid \textbf{run}\ M \mid \TBL_\alpha M \)
    \end{block}
    \begin{itemize}
        \item \( c \): constants
            \begin{itemize}
                    \item true, false, etc.
            \end{itemize}
        \item \( \TB_\alpha M \): code value
        \item \( \textbf{run}\ M \): run a code value \( M \)
            \begin{itemize}
                \item \( \textbf{run }(\text{vadd-gen }3)\)
            \end{itemize}
    \end{itemize}
    \note{
        Then, let me explain details of \LMD. \\
        \( \TBL_\alpha M \) is not needed?
    }
\end{frame}

\begin{frame}[fragile]{Types of \LMD}
    \begin{block}{Types}
    \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
    \end{block}
    \begin{itemize}
        \item \( X \): type-level constants 
            \begin{itemize}
                \item \( \text{Vec} \), \( \text{Int} \).
            \end{itemize}
        \item \( \Pi x:\tau.\sigma \): dependent type.
        \item \( \tau\ M \): Application of term to dependent type.
            \begin{itemize}
                \item \( \text{Vec } 3 \)
            \end{itemize}
        \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
            \begin{itemize}
                \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Kinds of \LMD}
    \begin{block}{Kinds}
        \( K ::= * \mid \Pi x:\tau.K \)
    \end{block}
    \begin{itemize}
        \item \( * \): kind of proper type
            \begin{itemize}
                \item \( \text{Int} :: * \)
            \end{itemize}
        \item \( \Pi x:\tau.K \): kind dependent on term.
            \begin{itemize}
                \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Judgements of \LMD}
    \begin{itemize}
        \item \( \G \V K @ A \)
            \begin{itemize}
                \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
            \end{itemize}
        \item \( \G \V \tau :: K @ A \)
            \begin{itemize}
                \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
            \end{itemize}
        \item \( \G \V M : \tau @ A \)
        \item \( \G \V K \E K' @ A \)
            \begin{itemize}
                \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
            \end{itemize}
        \item \( \G \V \tau \E \tau' @ A \)
        \item \( \G \V M \E M' @ A \)
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{What is stage\ \( A \)\ ?}
    % I copied this underwrite macro from
    % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
    % \underwrite[<thickness>]{<numerator>}{<denominator>}
    \newcommand{\underwrite}[3][]{
        \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
    }

    Level of nested brankets
    \begin{block}{Stages}
        \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
    \end{block}
    \begin{center}
        \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
    \end{center}
    \note{
        Stage is a sequence of stage variables which appended to each brack triangles.
        \( \varepsilon \) means the empty sequence

        The wholes expression is a term on stage \( \varepsilon \),
        But subexpression in the brack triangle is a term on stage \( \alpha \).
    }
\end{frame}

\begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
    Signature \( \Sigma \) is a sequence of type-level constants and constant values.
    \begin{itemize}
        \item For example,
            \begin{itemize}
                \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
            \end{itemize}
        \item Elements of \( \Sigma \) can be used at any stages.
    \end{itemize}
    \note{
        自然数が無限個あるというツッコミを誘発する気がする。
        後者関数が存在することにするか?
    }
\end{frame}

\begin{frame}[fragile]{Typing Rules of \LMD}
    \begin{center}
        \infrule[{\TTB}]{
            \G\V M:\tau@{A\alpha}
        }{
            \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
        } \\[2mm]
        \infrule[{\textsc{T-App}}]{
            \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
            \G\V N:\sigma@A
        }{
            \G\V M\ N : \tau[x\mapsto N]@A
        } \\[2mm]
        \infrule[{\TConst}]{
            c:\tau \in \Sigma \andalso
        }{
            \G \V c:\tau@A
        }
    \end{center}
    \begin{itemize}
        \item Terms are stage sensitive so cannot ignore stages.
        \item Constants in \( \Sigma \) can be used at any stages.
    \end{itemize}
    \note{
        Let's have a look on some typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Kinding Rules of \LMD}
    \begin{center}
        \infrule[{\KTW}]{
            \G\V \tau::*@A\alpha
        }{
            \G\V\TW_\alpha \tau::*@A
        }\\[2mm]
        \infrule[{\KApp}]{
            \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
        }{
            \G\V \sigma\ M::K[x\mapsto M]@A
        }
        \infrule[{\KTConst}]{
            X::K \in \Sigma
        }{
            \G \V X::K@A
        }
    \end{center}
    \begin{itemize}
        \item Types are also stage sensitive.
        \item Type-level constants in \( \Sigma \) can be used at any stages.
    \end{itemize}
    \note{
        Kinding rules have something in common with typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Example of Kinding Derivation}
    \renewcommand{\Vec}{\text{Vec}}
    \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
    \pause
    \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
    \begin{center}
        \footnotesize
        \begin{minipage}{0.7\hsize}
            \infer[\KTW]
            {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
            {
                \infer[\KApp]
                {\V \Vec\ 3 :: * @ \alpha}
                {
                    \infer[\KTConst]
                    {\V \Vec :: \Pi x:\I.* @ \alpha}
                    {\Vec :: \Pi x:\I.* \in \Sigma}
                    \andalso
                    \infer[\TConst]
                    {\V 3 : \I @ \alpha}
                    {3 : \I \in \Sigma}
                }
            }
        \end{minipage}
    \end{center}
    We can use \Vec\ and integers at any stages.
    \note{
        The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
        but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
    }
\end{frame}

\begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
    \begin{center}
        \footnotesize{
            \infrule[{\QTApp}]{
                \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
                \G\V M \E N : \rho @A
            }{
                \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
            } \\[2mm]
            \infrule[{\QBeta}]{
                \G,x:\sigma@A\V M:\tau@A \andalso
                \G\V N:\sigma@A
            }{
                \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
            } \\[2mm]
            \infrule[{\QPercent}]{
                \G\V M:\tau@{A\alpha} \andalso
                \G\V M:\tau@A
            }{
                \G\V\%_\alpha M \E M : \tau@{A\alpha}
            } \\[2mm]
            \infrule[{\textsc{T-Conv}}]{
                \G\V M:\tau@A \andalso
                \G\V \tau\equiv \sigma :: K@A
            }{
                \G\V M:\sigma@A
            }
        }
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Examples of Type Equality}
    \renewcommand{\V}{\text{Vec}}
    \begin{itemize}
        \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
            \begin{itemize}
                \item From \QBeta.
            \end{itemize}
        \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
            \begin{itemize}
                \item From \QTApp and \QBeta.
            \end{itemize}
        \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
            \begin{itemize}
                \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
            \end{itemize}
    \end{itemize}
    \note{
        Shold I show complete derivation tree?
    }
\end{frame}

\begin{frame}[fragile]{Propaties}
    \begin{itemize}
        \item Subject Reduction
        \item Strong Normalization
        \item Confluence
        \item Progress
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Conclusion \& Future Works}
    \begin{block}{Conclusion}
        We introduced dependent types into muti-stage programming.
        \begin{itemize}
            \item Define typing, kinding, well-formed kinding rules including stages.
            \item Define equality rules.
            \item Prove type soundness.
        \end{itemize}
    \end{block}
    \begin{block}{Future Works}
        \begin{itemize}
            \item Algorithmic Typing
        \end{itemize}
    \end{block}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Related Works}
    \begin{itemize}
        \item \LTP [Hanada\&Igarashi'14]
            \begin{itemize}
                \item Multi-stage programming including explicit CSP
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

\end{document}

### 2019-11-20 slides/main.tex
Making vadd-gen page.

@@
 % Show grid for debug
-% \setbeamertemplate{background}[grid][step=1cm]
+\setbeamertemplate{background}[grid][step=1cm]
 
@@
 \begin{frame}[fragile]{What is Multi-stage Programming}
-    A programming paradigm enables
+    A programming paradigm enables that
     \begin{itemize}
@@
 
-\begin{frame}[fragile]{Styles of Multi-stage Programming}
-    \begin{itemize}
-        \item Strings
-            \begin{itemize}
-                    \item Ruby, Perl, etc.
-            \end{itemize}
-        \item ASTs
-            \begin{itemize}
-                    \item Lisp
-            \end{itemize}
-        \item ASTs and code types
-            \begin{itemize}
-                    \item MetaOCaml
-            \end{itemize}
-    \end{itemize}
-    \note{
-        There are three kinds of multi-stage Programming.
-    }
-\end{frame}
+% \begin{frame}[fragile]{Styles of Multi-stage Programming}
+%     \begin{itemize}
+%         \item Strings
+%             \begin{itemize}
+%                     \item Ruby, Perl, etc.
+%             \end{itemize}
+%         \item ASTs
+%             \begin{itemize}
+%                     \item Lisp
+%             \end{itemize}
+%         \item ASTs and code types
+%             \begin{itemize}
+%                     \item MetaOCaml
+%             \end{itemize}
+%     \end{itemize}
+%     \note{
+%         There are three kinds of multi-stage Programming.
+%     }
+% \end{frame}
 
@@
         \begin{verbatim}
-     # let a = .< 1 + 2 >.;;
-     val a : int code = .< 1 + 2 >.
-     # Runcode.run a;;
+     # let a = .< (1 + 2) >.;;
+     val a : int code = .< (1 + 2) >.
+     # run a;;
      - : int = 3
 
-     # let b = .<.~a + .~a>.;;
-     val b : int code = .<(1 + 2) + (1 + 2)>. 
-     # Runcode.run b;;
+     # let b = .<(.~a) + (.~a)>.;;
+     val b : int code = .< ((1 + 2) + (1 + 2)) >. 
+     # run b;;
      - : int = 6
@@
     Generate efficient vector addition functions for given length vectors.
-    \renewcommand{\V}{\text{Vec}}
-    \begin{tabbing}
-        \( \text{vadd-gen} : \I \to \TW_\alpha (\V \to \V \to \V) \) \\
-        (* \( \TW_\alpha \) is corresponding to code in MetaOCaml.*) \\[2mm]
-        \( \textbf{let}\ \text{vadd3} = \textbf{run}\ (\text{vadd-gen}\ 3);; \) \\
-        \( \text{val}\ \text{vadd3} : \V \to \V \to \V \) \\[2mm]
-        \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
-        \( - : \V = [5;7;9] \)
-    \end{tabbing}
+    \begin{verbatim}
+ val vadd-gen : Int -> (Vec -> Vec -> Vec) code
+ let vadd3 = vadd-gen 3;;
+ val vadd : (Vec -> Vec -> Vec) code
+ (run vadd3) [1;2;3] [4;5;6];;
+  - : Vec = [5;7;9]
+    \end{verbatim}
     \note{

### 2019-11-20 slides/main.tex
Finished until page6.

@@
 \setbeamerfont{normal text}{size=\small}
-\setbeamerfont{itemize/enumerate body}{size=\footnotesize}
+\setbeamerfont{itemize/enumerate body}{size=\small}
 \setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
@@
 \begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
-    Generate efficient vector addition functions for given length vectors.
+    Generate efficient vector addition functions for given length.
+
     \begin{verbatim}
  val vadd-gen : Int -> (Vec -> Vec -> Vec) code
- let vadd3 = vadd-gen 3;;
- val vadd : (Vec -> Vec -> Vec) code
- (run vadd3) [1;2;3] [4;5;6];;
+ # let vadd3 = vadd-gen 3;;
+ (* vadd3 v w =                             *)
+ (*   let (v, w)=(.~v, ,~w) in              *)
+ (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
+ val vadd3 : (Vec -> Vec -> Vec) code
+ # (run vadd3) [1;2;3] [4;5;6];;
   - : Vec = [5;7;9]
@@
     Runtime error occurs for wrong length vectors.
-    \renewcommand{\V}{\text{Vec}}
-    \begin{tabbing}
-        \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
-        \( \longrightarrow \textbf{RUNTIME ERROR!} \)
-    \end{tabbing}
+    \begin{verbatim}
+    # (run vadd3) [1;2] [4;5];;
+    Exception: Failure
+    \end{verbatim}
     \note{
@@
 \begin{frame}[fragile]{Dependent Types}
+    \renewcommand{\V}{\text{Vec}\ }
     Types dependent on values
     \begin{itemize}
-            \item Can give more fine restriction on terms.
+        \item Can prevents illegal use of {\verb|vadd3|}.
     \end{itemize}
-    \renewcommand{\V}{\text{Vec}\ }
-    \begin{tabbing}
-        \( [1;2;3]:\ (\V 3) \) \\
-        \( [1;2;3;4]:\ (\V 4) \) \\
-        \( \text{vadd3}:\ (\V 3) \to (\V 3) \to (\V 3) \)
-    \end{tabbing}
+ \begin{verbatim}
+ - : [1;2]: Vec 2
+ - : vadd3 : (Vec 3 -> Vec 3 -> Vec 3) code
 
+ # (run vadd3) [1;2] [4;5];;
+ [1;2] has type Vec 2
+ but was expected of type Vec 3
+ \end{verbatim}
     \note{
@@
 \end{frame}
+
+% \begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
+%     Type system prevents illegal use of generated function.
+%     \renewcommand{\V}{\text{Vec}}
+%     \begin{tabbing}
+%         \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
+%         \( - : \V = [5;7;9] \) \\[2mm]
+%         \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
+%         \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
+%     \end{tabbing}
+%     \note{
+%         Type of generated functions by vadd-gen in \LMD have the length information in their types.
+%     }
+% \end{frame}
 
@@
         Thanks to dependent types ...
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
-    Type system prevents illegal use of generated function.
-    \renewcommand{\V}{\text{Vec}}
-    \begin{tabbing}
-        \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
-        \( - : \V = [5;7;9] \) \\[2mm]
-        \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
-        \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
-    \end{tabbing}
-    \note{
-        Type of generated functions by vadd-gen in \LMD have the length information in their types.
     }

### 2019-11-20 slides/main.tex
Writing a page on LTP.
Explaing Hanada&Igarashi.

@@
     }
+\end{frame}
+
+\begin{frame}[fragile]{\LTP [Hanada\&Igarashi'14]}
+    Multi-stage calculus with Cross Stage Persistence (CSP)
+    \begin{table}
+        \begin{tabular}{ c | c | c }
+            & MetaOCaml & \LTP \\
+            \hline
+            Make code & \verb| let a = .<(1+2)>.| & \( \textbf{let } a = \TB_\alpha (1 + 2) \) \\
+            Embed code & \verb| .<(.~a)+(.~a)>.| & \( (\TB_\alpha (\TBL_\alpha a + \TBL_\alpha a)) \) \\
+            Run code & \verb| run .<(1+2)>.| & \( \textbf{run } (\TB_\alpha (1 + 2)) \) \\
+            Code type & \verb| int code | & \( \TW_\alpha \text{Int} \)
+        \end{tabular}
+    \end{table}
 \end{frame}

### 2019-11-20 slides/main.tex
Finished Hanada.

--- 2019-11-20 slides/main.tex
@@
         We call our multi-stage calculus as \LMD.
+    }
+\end{frame}
+
+\begin{frame}[fragile]{\LTP [Hanada\&Igarashi'14]}
+    Multi-stage calculus with Cross Stage Persistence (CSP)
+    \begin{block}{Terms}
+    \begin{tabbing}
+        \hspace{5mm} \( M \) \= \( ::= c \) \hspace{20mm} \= (constants) \\
+        \> \( \mid \TB M \) \> (quote) \\
+        \> \( \mid \TBL M \) \> (unquote) \\
+        \> \( \mid \textbf{run}\ M \) \> (run) \\
+        \> \( \mid \% M \) \> (CSP) \\
+        \> \( \mid x \mid \lambda x:\tau.M \mid M\ M \) \\
+    \end{tabbing}
+    \end{block}
+\end{frame}
+
+\begin{frame}[fragile]{Types of \LTP}
+    \begin{block}{Types}
+    \begin{tabbing}
+        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
+        \> \( \mid \tau \to \tau \) \> (function type) \\
+        \> \( \mid \TW\ \tau \) \> (code type)
+        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
+    \end{tabbing}
+    \end{block}
+   \note{
+    }
+\end{frame}
+
+\begin{frame}[fragile]{Example of \LTP}
+    \begin{table}
+        \begin{tabular}{ c | c | c }
+            & \LTP & MetaOCaml \\[2mm]
+            \hline
+            Make code & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
+            Embed code & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
+            Run code & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
+            Code type & \( \TW\ \text{Int} \) & \verb| int code |
+        \end{tabular}
+    \end{table}
+\end{frame}
+
+\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
+\end{frame}
+
+\begin{frame}[fragile]{Types of \LMD}
+    \begin{block}{Types}
+    \begin{tabbing}
+        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
+        \> \( \mid \tau \to \tau \) \> (function type) \\
+        \> \( \mid \TW\ \tau \) \> (code type)
+        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
+    \end{tabbing}
+    \end{block}
+   \note{
     }

### 2019-11-21 slides/main.tex
Finished making the second draft.

@@
 \usepackage{pgfpages}
+\usepackage{bm}
 
@@
  # let vadd3 = vadd-gen 3;;
+ val vadd3 : (Vec -> Vec -> Vec) code
  (* vadd3 v w =                             *)
@@
  (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
- val vadd3 : (Vec -> Vec -> Vec) code
- # (run vadd3) [1;2;3] [4;5;6];;
-  - : Vec = [5;7;9]
     \end{verbatim}
@@
     \begin{verbatim}
+ val vadd3 : (Vec -> Vec -> Vec) code
+ # (run vadd3) [1;2;3] [4;5;6];;
+ - : Vec = [5;7;9]
  # (run vadd3) [1;2] [4;5];;
@@
         \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
-        \> \( \mid \tau \to \tau \) \> (function type) \\
-        \> \( \mid \TW\ \tau \) \> (code type)
-        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
+        \> \( \mid \TW\ \tau \) \> (code type) \\
+        \> \( \mid \tau \to \tau \) \> (function type)
     \end{tabbing}
@@
 \begin{frame}[fragile]{Cross Stage Persistence (CSP)}
+    Use normal values in code values
+    \begin{tabbing}
+        \hspace{5mm} \= \( \textbf{let}\ \text{mul3}\ x = 2 * x\ \textbf{in} \) \\
+        \> \( \TB (\% \text{mul3}\ 5) \)
+    \end{tabbing}
 \end{frame}
@@
         \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
-        \> \( \mid \tau \to \tau \) \> (function type) \\
-        \> \( \mid \TW\ \tau \) \> (code type)
-        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
+        \> \( \mid \TW\ \tau \) \> (code type) \\
+        \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (function dependent type) \\
+        \> \( \bm{\mid \tau\ M} \) \> (application of term to dependent type)
     \end{tabbing}
     \end{block}
+    We need CSP to use normal variables in code types.
+    \begin{itemize}
+        \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
+        \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
+    \end{itemize}
    \note{
@@
     Type tells us the length of vector.
-    \newcommand{\Vn}{\text{Vec}\ n}
-    \newcommand{\Vt}{\text{Vec}\ 3}
+    \newcommand{\Vn}{\text{Vec}\ \%n}
+    \newcommand{\Vt}{\text{Vec}\ \%3}
     \begin{tabbing}
-        \( \text{vadd-gen} : \Pi n:\I \to \TW_\alpha (\Vn \to \Vn \to \Vn) \) \\[2mm]
-        \( \textbf{let}\ \text{vadd3} = \textbf{run}\ (\text{vadd-gen}\ 3);; \) \\
-        \( \text{val}\ \text{vadd3} : \Vt \to \Vt \to \Vt \) \\[2mm]
+        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I \to \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
+        \> \( \textbf{let}\ \text{vadd3} = \text{vadd-gen}\ 3;; \) \\
+        \> \( \text{val}\ \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\[2mm]
     \end{tabbing}
-    Now, vadd3 takes only vectors of 3 length.
+    Now, vadd3 takes only vectors of length 3.
     \note{
@@
 
-\begin{frame}[fragile]{Terms of \LMD}
-    \begin{block}{Terms}
-        \( M ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M \mid \textbf{run}\ M \mid \TBL_\alpha M \)
-    \end{block}
-    \begin{itemize}
-        \item \( c \): constants
-            \begin{itemize}
-                    \item true, false, etc.
-            \end{itemize}
-        \item \( \TB_\alpha M \): code value
-        \item \( \textbf{run}\ M \): run a code value \( M \)
-            \begin{itemize}
-                \item \( \textbf{run }(\text{vadd-gen }3)\)
-            \end{itemize}
-    \end{itemize}
-    \note{
-        Then, let me explain details of \LMD. \\
-        \( \TBL_\alpha M \) is not needed?
-    }
+\begin{frame}[fragile]{Problem of vadd3}
+    Hard to compose with other functions.
+    \newcommand{\Vn}{\text{Vec}\ \%n}
+    \newcommand{\Vpt}{\text{Vec}\ \%3}
+    \newcommand{\Vt}{\text{Vec}\ 3}
+    \begin{tabbing}
+        \hspace{5mm} \= \( \text{val}\ \text{vadd3} : \TW (\Vpt \to \Vpt \to \Vpt) \) \\
+        \> \( \text{val}\ \text{double} : \TW (\Vt \to \Vt) \) \\[2mm]
+        \> \( \textbf{let}\ \text{add-double}\ v\ w = \) \\
+        \> \hspace{5mm} \( \TB (\TBL\text{double}\ (\TBL \text{vadd3}\ \TBL v\ \TBL w));; \) \\
+    \end{tabbing}
 \end{frame}
 
-\begin{frame}[fragile]{Types of \LMD}
-    \begin{block}{Types}
-    \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
-    \end{block}
+\begin{frame}[fragile]{Solution}
+    \newcommand{\Vt}{\text{Vec}\ 3}
+    Introduce \QPercent.
+    \begin{center}
+        \infrule[{\QPercent}]{
+            M \text{ is a closed term.}
+        }{
+            \G\vdash \%_\alpha M \E M : \tau
+        }
+    \end{center}
+    Erase the symbol of \( \% \) under the condition.
     \begin{itemize}
-        \item \( X \): type-level constants 
-            \begin{itemize}
-                \item \( \text{Vec} \), \( \text{Int} \).
+        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
+        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \)
     \end{itemize}
-        \item \( \Pi x:\tau.\sigma \): dependent type.
-        \item \( \tau\ M \): Application of term to dependent type.
-            \begin{itemize}
-                \item \( \text{Vec } 3 \)
-            \end{itemize}
-        \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
-            \begin{itemize}
-                \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
-            \end{itemize}
-    \end{itemize}
-    \note{
-    }
 \end{frame}
 
-\begin{frame}[fragile]{Kinds of \LMD}
-    \begin{block}{Kinds}
-        \( K ::= * \mid \Pi x:\tau.K \)
-    \end{block}
-    \begin{itemize}
-        \item \( * \): kind of proper type
-            \begin{itemize}
-                \item \( \text{Int} :: * \)
-            \end{itemize}
-        \item \( \Pi x:\tau.K \): kind dependent on term.
-            \begin{itemize}
-                \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
-            \end{itemize}
-    \end{itemize}
-    \note{
-    }
-\end{frame}
+% \begin{frame}[fragile]{Terms of \LMD}
+%     \begin{block}{Terms}
+%         \( M ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M \mid \textbf{run}\ M \mid \TBL_\alpha M \)
+%     \end{block}
+%     \begin{itemize}
+%         \item \( c \): constants
+%             \begin{itemize}
+%                     \item true, false, etc.
+%             \end{itemize}
+%         \item \( \TB_\alpha M \): code value
+%         \item \( \textbf{run}\ M \): run a code value \( M \)
+%             \begin{itemize}
+%                 \item \( \textbf{run }(\text{vadd-gen }3)\)
+%             \end{itemize}
+%     \end{itemize}
+%     \note{
+%         Then, let me explain details of \LMD. \\
+%         \( \TBL_\alpha M \) is not needed?
+%     }
+% \end{frame}
 
-\begin{frame}[fragile]{Judgements of \LMD}
-    \begin{itemize}
-        \item \( \G \V K @ A \)
-            \begin{itemize}
-                \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
-            \end{itemize}
-        \item \( \G \V \tau :: K @ A \)
-            \begin{itemize}
-                \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
-            \end{itemize}
-        \item \( \G \V M : \tau @ A \)
-        \item \( \G \V K \E K' @ A \)
-            \begin{itemize}
-                \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
-            \end{itemize}
-        \item \( \G \V \tau \E \tau' @ A \)
-        \item \( \G \V M \E M' @ A \)
-    \end{itemize}
-    \note{
-    }
-\end{frame}
+% \begin{frame}[fragile]{Types of \LMD}
+%     \begin{block}{Types}
+%     \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
+%     \end{block}
+%     \begin{itemize}
+%         \item \( X \): type-level constants 
+%             \begin{itemize}
+%                 \item \( \text{Vec} \), \( \text{Int} \).
+%             \end{itemize}
+%         \item \( \Pi x:\tau.\sigma \): dependent type.
+%         \item \( \tau\ M \): Application of term to dependent type.
+%             \begin{itemize}
+%                 \item \( \text{Vec } 3 \)
+%             \end{itemize}
+%         \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
+%             \begin{itemize}
+%                 \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
+%             \end{itemize}
+%     \end{itemize}
+%     \note{
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Kinds of \LMD}
+%     \begin{block}{Kinds}
+%         \( K ::= * \mid \Pi x:\tau.K \)
+%     \end{block}
+%     \begin{itemize}
+%         \item \( * \): kind of proper type
+%             \begin{itemize}
+%                 \item \( \text{Int} :: * \)
+%             \end{itemize}
+%         \item \( \Pi x:\tau.K \): kind dependent on term.
+%             \begin{itemize}
+%                 \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
+%             \end{itemize}
+%     \end{itemize}
+%     \note{
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Judgements of \LMD}
+%     \begin{itemize}
+%         \item \( \G \V K @ A \)
+%             \begin{itemize}
+%                 \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
+%             \end{itemize}
+%         \item \( \G \V \tau :: K @ A \)
+%             \begin{itemize}
+%                 \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
+%             \end{itemize}
+%         \item \( \G \V M : \tau @ A \)
+%         \item \( \G \V K \E K' @ A \)
+%             \begin{itemize}
+%                 \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
+%             \end{itemize}
+%         \item \( \G \V \tau \E \tau' @ A \)
+%         \item \( \G \V M \E M' @ A \)
+%     \end{itemize}
+%     \note{
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{What is stage\ \( A \)\ ?}
+%     % I copied this underwrite macro from
+%     % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
+%     % \underwrite[<thickness>]{<numerator>}{<denominator>}
+%     \newcommand{\underwrite}[3][]{
+%         \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
+%     }
+%
+%     Level of nested brankets
+%     \begin{block}{Stages}
+%         \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
+%     \end{block}
+%     \begin{center}
+%         \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
+%     \end{center}
+%     \note{
+%         Stage is a sequence of stage variables which appended to each brack triangles.
+%         \( \varepsilon \) means the empty sequence
+%
+%         The wholes expression is a term on stage \( \varepsilon \),
+%         But subexpression in the brack triangle is a term on stage \( \alpha \).
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
+%     Signature \( \Sigma \) is a sequence of type-level constants and constant values.
+%     \begin{itemize}
+%         \item For example,
+%             \begin{itemize}
+%                 \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
+%             \end{itemize}
+%         \item Elements of \( \Sigma \) can be used at any stages.
+%     \end{itemize}
+%     \note{
+%         自然数が無限個あるというツッコミを誘発する気がする。
+%         後者関数が存在することにするか?
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Typing Rules of \LMD}
+%     \begin{center}
+%         \infrule[{\TTB}]{
+%             \G\V M:\tau@{A\alpha}
+%         }{
+%             \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
+%         } \\[2mm]
+%         \infrule[{\textsc{T-App}}]{
+%             \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
+%             \G\V N:\sigma@A
+%         }{
+%             \G\V M\ N : \tau[x\mapsto N]@A
+%         } \\[2mm]
+%         \infrule[{\TConst}]{
+%             c:\tau \in \Sigma \andalso
+%         }{
+%             \G \V c:\tau@A
+%         }
+%     \end{center}
+%     \begin{itemize}
+%         \item Terms are stage sensitive so cannot ignore stages.
+%         \item Constants in \( \Sigma \) can be used at any stages.
+%     \end{itemize}
+%     \note{
+%         Let's have a look on some typing rules.
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Kinding Rules of \LMD}
+%     \begin{center}
+%         \infrule[{\KTW}]{
+%             \G\V \tau::*@A\alpha
+%         }{
+%             \G\V\TW_\alpha \tau::*@A
+%         }\\[2mm]
+%         \infrule[{\KApp}]{
+%             \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
+%         }{
+%             \G\V \sigma\ M::K[x\mapsto M]@A
+%         }
+%         \infrule[{\KTConst}]{
+%             X::K \in \Sigma
+%         }{
+%             \G \V X::K@A
+%         }
+%     \end{center}
+%     \begin{itemize}
+%         \item Types are also stage sensitive.
+%         \item Type-level constants in \( \Sigma \) can be used at any stages.
+%     \end{itemize}
+%     \note{
+%         Kinding rules have something in common with typing rules.
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Example of Kinding Derivation}
+%     \renewcommand{\Vec}{\text{Vec}}
+%     \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
+%     \pause
+%     \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
+%     \begin{center}
+%         \footnotesize
+%         \begin{minipage}{0.7\hsize}
+%             \infer[\KTW]
+%             {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
+%             {
+%                 \infer[\KApp]
+%                 {\V \Vec\ 3 :: * @ \alpha}
+%                 {
+%                     \infer[\KTConst]
+%                     {\V \Vec :: \Pi x:\I.* @ \alpha}
+%                     {\Vec :: \Pi x:\I.* \in \Sigma}
+%                     \andalso
+%                     \infer[\TConst]
+%                     {\V 3 : \I @ \alpha}
+%                     {3 : \I \in \Sigma}
+%                 }
+%             }
+%         \end{minipage}
+%     \end{center}
+%     We can use \Vec\ and integers at any stages.
+%     \note{
+%         The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
+%         but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
+%     \begin{center}
+%         \footnotesize{
+%             \infrule[{\QTApp}]{
+%                 \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
+%                 \G\V M \E N : \rho @A
+%             }{
+%                 \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
+%             } \\[2mm]
+%             \infrule[{\QBeta}]{
+%                 \G,x:\sigma@A\V M:\tau@A \andalso
+%                 \G\V N:\sigma@A
+%             }{
+%                 \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
+%             } \\[2mm]
+%             \infrule[{\QPercent}]{
+%                 \G\V M:\tau@{A\alpha} \andalso
+%                 \G\V M:\tau@A
+%             }{
+%                 \G\V\%_\alpha M \E M : \tau@{A\alpha}
+%             } \\[2mm]
+%             \infrule[{\textsc{T-Conv}}]{
+%                 \G\V M:\tau@A \andalso
+%                 \G\V \tau\equiv \sigma :: K@A
+%             }{
+%                 \G\V M:\sigma@A
+%             }
+%         }
+%     \end{center}
+%     \note{
+%     }
+% \end{frame}
+%
+% \begin{frame}[fragile]{Examples of Type Equality}
+%     \renewcommand{\V}{\text{Vec}}
+%     \begin{itemize}
+%         \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
+%             \begin{itemize}
+%                 \item From \QBeta.
+%             \end{itemize}
+%         \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
+%             \begin{itemize}
+%                 \item From \QTApp and \QBeta.
+%             \end{itemize}
+%         \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
+%             \begin{itemize}
+%                 \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
+%             \end{itemize}
+%     \end{itemize}
+%     \note{
+%         Shold I show complete derivation tree?
+%     }
+% \end{frame}
 
-\begin{frame}[fragile]{What is stage\ \( A \)\ ?}
-    % I copied this underwrite macro from
-    % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
-    % \underwrite[<thickness>]{<numerator>}{<denominator>}
-    \newcommand{\underwrite}[3][]{
-        \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
-    }
-
-    Level of nested brankets
-    \begin{block}{Stages}
-        \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
-    \end{block}
-    \begin{center}
-        \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
-    \end{center}
-    \note{
-        Stage is a sequence of stage variables which appended to each brack triangles.
-        \( \varepsilon \) means the empty sequence
-
-        The wholes expression is a term on stage \( \varepsilon \),
-        But subexpression in the brack triangle is a term on stage \( \alpha \).
-    }
-\end{frame}
-
-\begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
-    Signature \( \Sigma \) is a sequence of type-level constants and constant values.
-    \begin{itemize}
-        \item For example,
-            \begin{itemize}
-                \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
-            \end{itemize}
-        \item Elements of \( \Sigma \) can be used at any stages.
-    \end{itemize}
-    \note{
-        自然数が無限個あるというツッコミを誘発する気がする。
-        後者関数が存在することにするか?
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Typing Rules of \LMD}
-    \begin{center}
-        \infrule[{\TTB}]{
-            \G\V M:\tau@{A\alpha}
-        }{
-            \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
-        } \\[2mm]
-        \infrule[{\textsc{T-App}}]{
-            \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
-            \G\V N:\sigma@A
-        }{
-            \G\V M\ N : \tau[x\mapsto N]@A
-        } \\[2mm]
-        \infrule[{\TConst}]{
-            c:\tau \in \Sigma \andalso
-        }{
-            \G \V c:\tau@A
-        }
-    \end{center}
-    \begin{itemize}
-        \item Terms are stage sensitive so cannot ignore stages.
-        \item Constants in \( \Sigma \) can be used at any stages.
-    \end{itemize}
-    \note{
-        Let's have a look on some typing rules.
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Kinding Rules of \LMD}
-    \begin{center}
-        \infrule[{\KTW}]{
-            \G\V \tau::*@A\alpha
-        }{
-            \G\V\TW_\alpha \tau::*@A
-        }\\[2mm]
-        \infrule[{\KApp}]{
-            \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
-        }{
-            \G\V \sigma\ M::K[x\mapsto M]@A
-        }
-        \infrule[{\KTConst}]{
-            X::K \in \Sigma
-        }{
-            \G \V X::K@A
-        }
-    \end{center}
-    \begin{itemize}
-        \item Types are also stage sensitive.
-        \item Type-level constants in \( \Sigma \) can be used at any stages.
-    \end{itemize}
-    \note{
-        Kinding rules have something in common with typing rules.
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Example of Kinding Derivation}
-    \renewcommand{\Vec}{\text{Vec}}
-    \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
-    \pause
-    \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
-    \begin{center}
-        \footnotesize
-        \begin{minipage}{0.7\hsize}
-            \infer[\KTW]
-            {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
-            {
-                \infer[\KApp]
-                {\V \Vec\ 3 :: * @ \alpha}
-                {
-                    \infer[\KTConst]
-                    {\V \Vec :: \Pi x:\I.* @ \alpha}
-                    {\Vec :: \Pi x:\I.* \in \Sigma}
-                    \andalso
-                    \infer[\TConst]
-                    {\V 3 : \I @ \alpha}
-                    {3 : \I \in \Sigma}
-                }
-            }
-        \end{minipage}
-    \end{center}
-    We can use \Vec\ and integers at any stages.
-    \note{
-        The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
-        but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
-    \begin{center}
-        \footnotesize{
-            \infrule[{\QTApp}]{
-                \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
-                \G\V M \E N : \rho @A
-            }{
-                \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
-            } \\[2mm]
-            \infrule[{\QBeta}]{
-                \G,x:\sigma@A\V M:\tau@A \andalso
-                \G\V N:\sigma@A
-            }{
-                \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
-            } \\[2mm]
-            \infrule[{\QPercent}]{
-                \G\V M:\tau@{A\alpha} \andalso
-                \G\V M:\tau@A
-            }{
-                \G\V\%_\alpha M \E M : \tau@{A\alpha}
-            } \\[2mm]
-            \infrule[{\textsc{T-Conv}}]{
-                \G\V M:\tau@A \andalso
-                \G\V \tau\equiv \sigma :: K@A
-            }{
-                \G\V M:\sigma@A
-            }
-        }
-    \end{center}
-    \note{
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Examples of Type Equality}
-    \renewcommand{\V}{\text{Vec}}
-    \begin{itemize}
-        \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
-            \begin{itemize}
-                \item From \QBeta.
-            \end{itemize}
-        \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
-            \begin{itemize}
-                \item From \QTApp and \QBeta.
-            \end{itemize}
-        \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
-            \begin{itemize}
-                \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
-            \end{itemize}
-    \end{itemize}
-    \note{
-        Shold I show complete derivation tree?
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Propaties}
+\begin{frame}[fragile]{Properties}
+    We proved
     \begin{itemize}

### 2019-11-22 slides/main.tex
Add section pages.
Fixing.

@@
 % \begin{frame}{Contents}
-%   \tableofcontents
+%     \tableofcontents[currentsection]
 %   \note{
@@
 \end{frame}
-
-% \begin{frame}[fragile]{Styles of Multi-stage Programming}
-%     \begin{itemize}
-%         \item Strings
-%             \begin{itemize}
-%                     \item Ruby, Perl, etc.
-%             \end{itemize}
-%         \item ASTs
-%             \begin{itemize}
-%                     \item Lisp
-%             \end{itemize}
-%         \item ASTs and code types
-%             \begin{itemize}
-%                     \item MetaOCaml
-%             \end{itemize}
-%     \end{itemize}
-%     \note{
-%         There are three kinds of multi-stage Programming.
-%     }
-% \end{frame}
 
@@
         \item Features of multi-stage programming
+        \item Features of dependent types
+    \end{itemize}
+    Our contribution
     \begin{itemize}
-                \item Code type
-                \item Type safe {\bf{run}}
-                \item Cross Stage Persistence(CSP)
-            \end{itemize}
-        \item Features of dependent types
-            \begin{itemize}
-                \item Typing, Kinding, Well-formed kind rules with stages
-                \item Equivalence rules including CSP
-            \end{itemize}
+        \item Define typing, kinding, well-formed kind rules with stages
+        \item Define equivalence rules including CSP
     \end{itemize}
@@
         We call our multi-stage calculus as \LMD.
+    }
+\end{frame}
+
+\section{Existing Multi-stage Calculus \LTP}
+
+\begin{frame}{Contents}
+    \tableofcontents[currentsection]
+    \note{
     }
@@
             \hline
-            Make code & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
-            Embed code & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
-            Run code & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
+            Quote & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
+            Unquote & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
+            Run & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
             Code type & \( \TW\ \text{Int} \) & \verb| int code |
@@
     \end{tabbing}
+\end{frame}
+
+\section{Extend \LTP with Dependent Types}
+
+\begin{frame}{Contents}
+    \tableofcontents[currentsection]
+  \note{
+  }
 \end{frame}
@@
 
-\begin{frame}[fragile]{Problem of vadd3}
-    Hard to compose with other functions.
+\begin{frame}[fragile]{Problem of type of vadd3}
+    Hard to combine with other functions.
     \newcommand{\Vn}{\text{Vec}\ \%n}
@@
     \newcommand{\Vt}{\text{Vec}\ 3}
+    \newcommand{\Vpt}{\text{Vec}\ \%3}
     Introduce \QPercent.
@@
         }{
-            \G\vdash \%_\alpha M \E M : \tau
+            \G\vdash \%_\alpha M \E M
         }
@@
         \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
-        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \)
+        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\
+            \hspace{15mm} \( (\E  \TW (\Vpt \to \Vpt \to \Vpt)) \)
     \end{itemize}
 \end{frame}
+
+\begin{frame}[fragile]{Properties}
+    We proved
+    \begin{itemize}
+        \item Subject Reduction
+        \item Strong Normalization
+        \item Confluence
+        \item Progress
+    \end{itemize}
+    \note{
+    }
+\end{frame}
+
+\begin{frame}[fragile]{Related Works}
+    \begin{itemize}
+        \item \LTP [Hanada\&Igarashi'14]
+            \begin{itemize}
+                \item Multi-stage programming including explicit CSP
+            \end{itemize}
+    \end{itemize}
+    \note{
+    }
+\end{frame}
+
+\begin{frame}[fragile]{Conclusion}
+        We introduced dependent types into muti-stage programming.
+        \begin{itemize}
+            \item Define typing, kinding, well-formed kinding rules for multi-stage calculus.
+            \item Define equality rules.
+                \begin{itemize}
+                        \item Especially, dealing with CSP.
+                \end{itemize}
+            \item Prove type soundness.
+        \end{itemize}
+    \note{
+    }
+\end{frame}
+
+% \begin{frame}[fragile]{Styles of Multi-stage Programming}
+%     \begin{itemize}
+%         \item Strings
+%             \begin{itemize}
+%                     \item Ruby, Perl, etc.
+%             \end{itemize}
+%         \item ASTs
+%             \begin{itemize}
+%                     \item Lisp
+%             \end{itemize}
+%         \item ASTs and code types
+%             \begin{itemize}
+%                     \item MetaOCaml
+%             \end{itemize}
+%     \end{itemize}
+%     \note{
+%         There are three kinds of multi-stage Programming.
+%     }
+% \end{frame}
 
@@
 
-\begin{frame}[fragile]{Properties}
-    We proved
-    \begin{itemize}
-        \item Subject Reduction
-        \item Strong Normalization
-        \item Confluence
-        \item Progress
-    \end{itemize}
-    \note{
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Conclusion \& Future Works}
-    \begin{block}{Conclusion}
-        We introduced dependent types into muti-stage programming.
-        \begin{itemize}
-            \item Define typing, kinding, well-formed kinding rules including stages.
-            \item Define equality rules.
-            \item Prove type soundness.
-        \end{itemize}
-    \end{block}
-    \begin{block}{Future Works}
-        \begin{itemize}
-            \item Algorithmic Typing
-        \end{itemize}
-    \end{block}
-    \note{
-    }
-\end{frame}
-
-\begin{frame}[fragile]{Related Works}
-    \begin{itemize}
-        \item \LTP [Hanada\&Igarashi'14]
-            \begin{itemize}
-                \item Multi-stage programming including explicit CSP
-            \end{itemize}
-    \end{itemize}
-    \note{
-    }
-\end{frame}
-
 \end{document}

### 2019-11-22 slides/main.tex
Spell checked.

@@
 \author{\underline{Akira Kawata} and Atsushi Igarashi}
-\institute{Gradudate School of Informatics, Kyoto University}
+\institute{Graduate School of Informatics, Kyoto University}
 \date{Dec 2, 2019}
@@
     \begin{itemize}
-        \item Define typing, kinding, well-formed kind rules with stages
+        \item Define typing, kinding, well-formed kind rules for multi-stage calculus
         \item Define equivalence rules including CSP
@@
 \begin{frame}[fragile]{Cross Stage Persistence (CSP)}
-    Use normal values in code values
-    \begin{tabbing}
-        \hspace{5mm} \= \( \textbf{let}\ \text{mul3}\ x = 2 * x\ \textbf{in} \) \\
-        \> \( \TB (\% \text{mul3}\ 5) \)
-    \end{tabbing}
+    Enable using normal values in code values
+    \begin{center}
+        \( \textbf{let}\ \underbrace{\text{mul3}}_{\text{normal value}}\ x = 2 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul3}\ 5)}_{\text{code value}} \)
+    \end{center}
+    CSP symbol \( \% \) {\bf{lift up}} an normal value into code value.
 \end{frame}
@@
         \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (function dependent type) \\
-        \> \( \bm{\mid \tau\ M} \) \> (application of term to dependent type)
+        \> \( \bm{\mid \tau\ M} \) \> (application, e.g. \(\text{Vec}\ 3\))
     \end{tabbing}
     \end{block}
-    We need CSP to use normal variables in code types.
+    Note: We need CSP to use normal variables in code types.
     \begin{itemize}
@@
 \begin{frame}[fragile]{Problem of type of vadd3}
-    Hard to combine with other functions.
+    Hard to compose with other functions.
     \newcommand{\Vn}{\text{Vec}\ \%n}
@@
         \> \( \textbf{let}\ \text{add-double}\ v\ w = \) \\
-        \> \hspace{5mm} \( \TB (\TBL\text{double}\ (\TBL \text{vadd3}\ \TBL v\ \TBL w));; \) \\
+        \> \hspace{5mm} \( \TB (\underbrace{\TBL\text{double}}_{\Vt \to \Vt}\ \underbrace{(\TBL \text{vadd3}\ \TBL v\ \TBL w)}_{\Vpt});; \) \\
     \end{tabbing}
+    We cannot compose because of type mismatch.
 \end{frame}
@@
             \end{itemize}
+        \item Concoqtion [Forgarty et al]
+            \begin{itemize}
+                \item Introduce indexed type into MetaOCaml.
+            \end{itemize}
     \end{itemize}
@@
 \begin{frame}[fragile]{Conclusion}
-        We introduced dependent types into muti-stage programming.
+    We introduced dependent types into multi-stage programming.
     \begin{itemize}

### 2019-11-22 slides/main.tex
Fix bugs.

@@
 \begin{frame}[fragile]{What is Multi-stage Programming}
-    A programming paradigm enables that
+    A programming paradigm that enables
     \begin{itemize}
@@
     \begin{center}
-        \( \textbf{let}\ \underbrace{\text{mul3}}_{\text{normal value}}\ x = 2 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul3}\ 5)}_{\text{code value}} \)
+        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{normal value}}\ x = 5 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul5}\ 4)}_{\text{code value}} \)
     \end{center}
@@
     \begin{tabbing}
-        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I \to \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
+        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I. \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
         \> \( \textbf{let}\ \text{vadd3} = \text{vadd-gen}\ 3;; \) \\
@@
         }{
-            \G\vdash \%_\alpha M \E M
+            \G\vdash \% M \E M
         }
@@
 \begin{frame}[fragile]{Conclusion}
-    We introduced dependent types into multi-stage programming.
+    We introduced dependent types into multi-stage calculus.
     \begin{itemize}

### 2019-11-26 slides/main.tex
Slides on types of LTP.

@@
 
+% Settings of Table of Contents page.
+% Append underline to currentsection.
+% https://tex.stackexchange.com/questions/280813/beamer-change-color-underline-but-do-not-hide-shade-other-section-in-table-of-c/283585
+% https://tex.stackexchange.com/questions/414250/numbers-shading-and-alert-in-beamer-table-of-contents
+% Page 101 of http://tug.ctan.org/macros/latex/contrib/beamer/doc/beameruserguide.pdf
+\setbeamertemplate{section in toc}{
+    \inserttocsectionnumber.\ \bf{\underline{\inserttocsection}}
+}
+\setbeamertemplate{section in toc shaded}{
+    \inserttocsectionnumber.\  \inserttocsection
+}
+
 \setbeamertemplate{bibliography item}{\insertbiblabel}
@@
 
-\newcommand{\toc}[0]{
-  \begin{frame}{Contents}
-  \tableofcontents[currentsection]
-  \end{frame}
-}
-
 \defbeamertemplate{description item}{align left}{\insertdescriptionitem\hfill}
@@
 \input{symboldef.tex}
+
+% I don't use sigma in this slides.
+\renewcommand{\V}{\vdash}
 
@@
 \section{Introduction to Multistage programming}
+
+\begin{frame}{Contents}
+
+    \setbeamertemplate{section in toc}{
+        \inserttocsectionnumber.\ \inserttocsection
+    }
+
+    \tableofcontents
+    \note{
+    }
+\end{frame}
 
@@
  (* vadd3 v w =                            *)
- (*   let (v, w)=(.~v, ,~w) in              *)
- (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
+ (*   < let (v, w)=(~v, ~w) in             *)
+ (*      [v[0]+w[0];v[1]+w[1];v[2]+w[2]] > *)
     \end{verbatim}
@@
 
+\begin{frame}[fragile]{What is a stage?}
+    Level of nested quote
+    \begin{center}
+        \( \underbrace{(\textbf{run}\ (\TB\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{\text{stage }1}})) + 1}_{\let\scriptstyle\textstyle\substack{\text{stage }0}} \)
+    \end{center}
+
+    Typing judgements of \LTP include a stage.
+    \begin{center}
+    \( \G \vdash 2 + 3 : \I @ 1 \)
+    \end{center}
+    \note{
+    }
+\end{frame}
+
+\begin{frame}[fragile]{Typing Rules of \LMD}
+    Cannot apply a term to a function in a different stage.
+    \begin{center}
+        {\small \infrule[\TApp]{
+            \G\V M:\sigma \to \tau @ n \andalso
+            \G\V N:\sigma @ n
+        }{
+            \G\V M\ N : \tau @ n
+        }}
+    \end{center}
+    Increase and decrease stage using \( \TB \) and \( \TBL \).
+    \begin{center}
+        {\small \infrule[{\TTB}]{
+            \G\V M:\tau @ n+1
+        }{
+            \G\V\TB M:\TW \tau @ n
+        } \hfil
+        \infrule[{\TTBL}]{
+            \G\V M:\TW \tau @ n
+        }{
+            \G\V\TBL M:\tau @ n + 1
+        }}
+    \end{center}
+    \note{
+        Let's have a look on some typing rules.
+    }
+\end{frame}
+
 \begin{frame}[fragile]{Cross Stage Persistence (CSP)}
-    Enable using normal values in code values
+    Enable using terms at lower stages at higer stages. \\[3mm]
+
+    Want to use \( \text{mul5} \) in a code value.
     \begin{center}
-        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{normal value}}\ x = 5 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul5}\ 4)}_{\text{code value}} \)
+        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{stage }0}\ x = 5 * x\ \textbf{in} \TB\ \underbrace{(\% \text{mul5}\ 4)}_{\text{stage }1} \)
     \end{center}

### 2019-11-26 slides/main.tex
Spell check.

@@
         \begin{verbatim}
- # let a = .< (1 + 2) >.;;
- val a : int code = .< (1 + 2) >.
+ # let a = < (1 + 2) >;;
+ val a : int code = < (1 + 2) >
  # run a;;
@@
 
- # let b = .<(.~a) + (.~a)>.;;
- val b : int code = .< ((1 + 2) + (1 + 2)) >. 
- # run b;;
+ # let b = <(~a) + (~a)>
+ val b : int code = < ((1 + 2) + (1 + 2)) >
+ # run b
  - : int = 6
@@
  val vadd-gen : Int -> (Vec -> Vec -> Vec) code
- # let vadd3 = vadd-gen 3;;
+ # let vadd3 = vadd-gen 3
  val vadd3 : (Vec -> Vec -> Vec) code
@@
  val vadd3 : (Vec -> Vec -> Vec) code
- # (run vadd3) [1;2;3] [4;5;6];;
+ # (run vadd3) [1;2;3] [4;5;6]
  - : Vec = [5;7;9]
- # (run vadd3) [1;2] [4;5];;
+ # (run vadd3) [1;2] [4;5]
  Exception: Failure
@@
 
- # (run vadd3) [1;2] [4;5];;
+ # (run vadd3) [1;2] [4;5]
  [1;2] has type Vec 2
@@
 \end{frame}
-
-% \begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
-%     Type system prevents illegal use of generated function.
-%     \renewcommand{\V}{\text{Vec}}
-%     \begin{tabbing}
-%         \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
-%         \( - : \V = [5;7;9] \) \\[2mm]
-%         \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
-%         \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
-%     \end{tabbing}
-%     \note{
-%         Type of generated functions by vadd-gen in \LMD have the length information in their types.
-%     }
-% \end{frame}
 
@@
     \begin{center}
-    \( \G \vdash 2 + 3 : \I @ 1 \)
+        \( \G \vdash 2 + 3 : \I {\mathbf{@ 1}} \)
     \end{center}
@@
 
-\begin{frame}[fragile]{Typing Rules of \LMD}
+\begin{frame}[fragile]{Typing Rules of \LTP}
     Cannot apply a term to a function in a different stage.
@@
     \end{center}
+    In general, we cannot use terms of one stage at other stages.
     \note{
@@
 \begin{frame}[fragile]{Cross Stage Persistence (CSP)}
-    Enable using terms at lower stages at higer stages. \\[3mm]
+    Enable using terms at lower stages at higher stages. \\[3mm]
 
@@
 
-\begin{frame}[fragile]{Types of \LMD}
+\begin{frame}[fragile]{Types and Kinds of \LMD}
+    Append function dependent types to types of \LTP.
     \begin{block}{Types}
@@
     \end{block}
-    Note: We need CSP to use normal variables in code types.
-    \begin{itemize}
-        \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
-        \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
-    \end{itemize}
+    \begin{block}{Kinds}
+        \( K ::= * \mid \Pi x:\tau.K \)
+    \end{block}
+    % Note: We need CSP to use normal variables in code types.
+    % \begin{itemize}
+    %     \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
+    %     \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
+    % \end{itemize}
     \note{
     }
+\end{frame}
+
+\begin{frame}[fragile]{Kinding rules of \LMD}
+    Types have also stages because types may contains terms.
+    \begin{center}
+    \infrule[{\KApp}]{
+        \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
+    }{
+        \G\V \sigma\ M::K[x\mapsto M] @ n
+    }
+    \infrule[{\KAbs}]{
+        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
+    }{
+        \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
+    }
+    \end{center}
+    So, we need CSP in types also.
+    \begin{center}
+    \( \underbrace{\Pi n:\I. \TW (\overbrace{\text{Vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
+    \end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Constants and type-level constants of \LMD}
+    Constants and type-level constants can be used at any stage.
+    \begin{itemize}
+        \item Integers: \( 0,1,2,3,\dots \)
+        \item Int, Vec, \dots
+    \end{itemize}
+
+    \begin{tabbing}
+        \hspace{5mm} \= \text{val doub3} : \( \text{Vec }3 \to \text{Vec }3 \) \\[2mm]
+        \> \textbf{let } \text{double} = \( \TB (\% \text{doub3}) \) \\
+        \> \text{val double} : \( \TW ( \text{Vec }3 \to \text{Vec }3) \)
+    \end{tabbing}
 \end{frame}
@@
 
-\begin{frame}[fragile]{Related Works}
+\begin{frame}[fragile]{Related Work}
     \begin{itemize}
@@
             \end{itemize}
-        \item Concoqtion [Forgarty et al]
+        \item Concoqtion [Forgarty et al.]
             \begin{itemize}
                 \item Introduce indexed type into MetaOCaml.
+                \item Types are indexed by Coq terms.
             \end{itemize}
@@
 %         There are three kinds of multi-stage Programming.
+%     }
+% \end{frame}
+
+% \begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
+%     Type system prevents illegal use of generated function.
+%     \renewcommand{\V}{\text{Vec}}
+%     \begin{tabbing}
+%         \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
+%         \( - : \V = [5;7;9] \) \\[2mm]
+%         \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
+%         \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
+%     \end{tabbing}
+%     \note{
+%         Type of generated functions by vadd-gen in \LMD have the length information in their types.
 %     }
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Kinds of \LMD}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Judgements of \LMD}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{What is stage\ \( A \)\ ?}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Typing Rules of \LMD}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Kinding Rules of \LMD}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Example of Kinding Derivation}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
@@
 % \end{frame}
-%
+
 % \begin{frame}[fragile]{Examples of Type Equality}

### 2019-11-26 slides/main.tex
Add future works.
Reflect Igarashi's comments.

@@
 \begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
-    Runtime error occurs for wrong length vectors.
+    Runtime error occurs for vectors of wrong length.
     \begin{verbatim}
@@
     \begin{itemize}
-        \item Can prevents illegal use of {\verb|vadd3|}.
+        \item Can prevent illegal use of {\verb|vadd3|}.
     \end{itemize}
  \begin{verbatim}
- - : [1;2]: Vec 2
- - : vadd3 : (Vec 3 -> Vec 3 -> Vec 3) code
+ [1;2]: Vec 2
+ vadd3 : (Vec 3 -> Vec 3 -> Vec 3) code
 
@@
             \> \( \mid \textbf{run}\ M \) \> (run) \\
-        \> \( \mid \% M \) \> (CSP) \\
+            \> \( \mid \% M \) \> (Cross Stage Persistence (CSP)) \\
             \> \( \mid x \mid \lambda x:\tau.M \mid M\ M \) \\
@@
     \end{center}
-    CSP symbol \( \% \) {\bf{lift up}} an normal value into code value.
+    CSP symbol \( \% \) {\bf{lift up}} mul5 from stage 0 to stage 1.
 \end{frame}
@@
         \begin{tabbing}
-            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
+            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (type-level constants) \\
             \> \( \mid \TW\ \tau \) \> (code type) \\
@@
     \newcommand{\Vpt}{\text{Vec}\ \%3}
-    Introduce \QPercent.
+    Erase the CSP symbol \( \% \) of an closed term.
     \begin{center}
@@
     \end{center}
-    Erase the symbol of \( \% \) under the condition.
     \begin{itemize}
@@
             \end{itemize}
-        \item Concoqtion [Forgarty et al.]
+        \item Concoqtion [Forgarty et al.'14]
             \begin{itemize}
@@
         \item Prove type soundness.
+        \item Future work: algorithmic typing
     \end{itemize}

### 2019-11-26 slides/main.tex
Finished third draft.

@@
 \setbeamerfont{itemize/enumerate body}{size=\small}
-\setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
+\setbeamerfont{itemize/enumerate subbody}{size=\small}
 \setbeamerfont{frametitle continuation}{size=\small}
@@
 \begin{frame}[fragile]{Example of Multi-stage Programming in MetaOCaml}
-    \begin{center}
+    \begin{exampleblock}{}
         \begin{verbatim}
@@
         \end{verbatim}
-    \end{center}
+    \end{exampleblock}
     \note{
@@
     Generate efficient vector addition functions for given length.
-
+    \begin{exampleblock}{}
     \begin{verbatim}
@@
     \end{verbatim}
+    \end{exampleblock}
     \note{
@@
     Runtime error occurs for vectors of wrong length.
+    \begin{exampleblock}{}
     \begin{verbatim}
@@
     \end{itemize}
+    \begin{exampleblock}{}
  \begin{verbatim}
@@
  \end{verbatim}
+    \end{exampleblock}
     \note{
@@
 \begin{frame}[fragile]{\LTP [Hanada\&Igarashi'14]}
-    Multi-stage calculus with Cross Stage Persistence (CSP)
+    \begin{table}
+        \begin{tabular}{ c | c | c }
+            & \LTP & MetaOCaml \\[2mm]
+            \hline
+            Quote & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = <(1+2)> | \\[2mm]
+            Unquote & \( (\TB (\TBL a + \TBL a)) \) & \verb| <(~a)+(~a)> | \\[2mm]
+            Run & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run <(1+2)> | \\[2mm]
+            Code type & \( \TW\ \text{Int} \) & \verb| int code |
+        \end{tabular}
+    \end{table}
+\end{frame}
+
+\begin{frame}[fragile]{Terms of \LTP}
     \begin{block}{Terms}
@@
             \> \( \mid \% M \) \> (Cross Stage Persistence (CSP)) \\
-            \> \( \mid x \mid \lambda x:\tau.M \mid M\ M \) \\
+            \> \( \mid x \mid \lambda x:\tau.M \mid M\ M \)
         \end{tabbing}
     \end{block}
+    * Simplified version
 \end{frame}
@@
 
-\begin{frame}[fragile]{Example of \LTP}
-    \begin{table}
-        \begin{tabular}{ c | c | c }
-            & \LTP & MetaOCaml \\[2mm]
-            \hline
-            Quote & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
-            Unquote & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
-            Run & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
-            Code type & \( \TW\ \text{Int} \) & \verb| int code |
-        \end{tabular}
-    \end{table}
-\end{frame}
-
 \begin{frame}[fragile]{What is a stage?}
     Level of nested quote
+    \begin{exampleblock}{}
     \begin{center}
@@
     \end{center}
+    \end{exampleblock}
 
@@
     \begin{center}
-        {\small \infrule[\TApp]{
+        {\footnotesize \infrule[\TApp]{
             \G\V M:\sigma \to \tau @ n \andalso
@@
     \begin{center}
-        {\small \infrule[{\TTB}]{
+        {\footnotesize \infrule[{\TTB}]{
             \G\V M:\tau @ n+1
@@
     Want to use \( \text{mul5} \) in a code value.
+    \begin{exampleblock}{}
     \begin{center}
@@
     \end{center}
+    \end{exampleblock}
     CSP symbol \( \% \) {\bf{lift up}} mul5 from stage 0 to stage 1.
@@
     \begin{center}
+    {\footnotesize
     \infrule[{\KApp}]{
@@
         \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
-    }
+    }}
     \end{center}
     So, we need CSP in types also.
+    \begin{exampleblock}{}
     \begin{center}
@@
     \end{center}
+    \end{exampleblock}
 \end{frame}
@@
 \begin{frame}[fragile]{Constants and type-level constants of \LMD}
-    Constants and type-level constants can be used at any stage.
     \begin{itemize}
-        \item Integers: \( 0,1,2,3,\dots \)
-        \item Int, Vec, \dots
+        \item Constants: \( 0,1,2,3,\dots \)
+        \item Type-level constants: Int, Vec, \dots
     \end{itemize}
+    can be used at any stage.
 
+    \begin{exampleblock}{}
         \begin{tabbing}
-        \hspace{5mm} \= \text{val doub3} : \( \text{Vec }3 \to \text{Vec }3 \) \\[2mm]
-        \> \textbf{let } \text{double} = \( \TB (\% \text{doub3}) \) \\
-        \> \text{val double} : \( \TW ( \text{Vec }3 \to \text{Vec }3) \)
+            \hspace{5mm} \= \text{val double-at-0} : \( \text{Vec }3 \to \text{Vec }3 \) \\[2mm]
+            \> \textbf{let } \text{double} = \( \TB (\%\ \text{double-at-0}) \) \\
+            \> \text{val double} : \( \TW \underbrace{(\text{Vec }3 \to \text{Vec }3)}_{\text{stage 1}} \)
         \end{tabbing}
+    \end{exampleblock}
+    Vec and integer 3 can be used at stage 1.
 \end{frame}
@@
     \newcommand{\Vt}{\text{Vec}\ \%3}
+    \begin{exampleblock}{}
     \begin{tabbing}
@@
     \end{tabbing}
+    \end{exampleblock}
     Now, vadd3 takes only vectors of length 3.
@@
 
-\begin{frame}[fragile]{Problem of type of vadd3}
+\begin{frame}[fragile]{Technical challenge of vadd3}
     Hard to compose with other functions.
@@
     \newcommand{\Vt}{\text{Vec}\ 3}
+    \begin{exampleblock}{}
     \begin{tabbing}
@@
     \end{tabbing}
+    \end{exampleblock}
     We cannot compose because of type mismatch.
@@
     \end{center}
+    \begin{exampleblock}{}
     \begin{itemize}
@@
     \end{itemize}
+    \end{exampleblock}
 \end{frame}

### 2019-11-26 slides/main.tex
Finished making third draft.

@@
     \begin{itemize}
-        \item Define typing, kinding, well-formed kind rules for multi-stage calculus
-        \item Define equivalence rules including CSP
+        \item Prevent illegal use of generated code values with dependent types.
     \end{itemize}
@@
 
-    Want to use \( \text{mul5} \) in a code value.
     \begin{exampleblock}{}
@@
     \begin{itemize}
-        \item Define typing, kinding, well-formed kinding rules for multi-stage calculus.
-        \item Define equality rules.
-            \begin{itemize}
-                \item Especially, dealing with CSP.
-            \end{itemize}
+        \item Avoid illegal use of generated code values with dependent types.
         \item Prove type soundness.

### 2019-11-27 slides/main.tex
Add.

@@
     \begin{itemize}
-        \item Generation of code at runtime
-        \item Evaluation of code at runtime
+        \item Generation of code at run-time
+        \item Evaluation of code at run-time
     \end{itemize}
@@
     \begin{itemize}
-        \item Speeding up programs using runtime information
+        \item Speeding up programs using run-time information
     \end{itemize}
@@
         \begin{verbatim}
- # let a = < (1 + 2) >;;
+ # let a = < (1 + 2) >     (* Make a code *)
  val a : int code = < (1 + 2) >
- # run a;;
+ # run a                   (* Run a code *)
  - : int = 3
 
- # let b = <(~a) + (~a)>
+ # let b = <(~a) + (~a)>   (* Embed codes *)
  val b : int code = < ((1 + 2) + (1 + 2)) >
@@
 
-\begin{frame}[fragile]{\LTP [Hanada\&Igarashi'14]}
+\begin{frame}[fragile]{Quick Overview of \LTP [Hanada\&Igarashi'14]}
     \begin{table}
@@
     \end{block}
+
+    \begin{block}{Typing Judgement}
+        \begin{center}
+            \( \G \V M : \tau @ n \)
+        \end{center}
+        * \( n \) is a stage.
+    \end{block}
+
     \note{
@@
 
-\section{Extend \LTP with Dependent Types}
+\section{Extension \LTP with Dependent Types}
 
@@
     \newcommand{\Vpt}{\text{Vec}\ \%3}
-    Erase the CSP symbol \( \% \) of an closed term.
+    Erase the CSP symbol \( \% \) under the condition \(M \) is closed.
     \begin{center}
@@
     }
+\end{frame}
+
+\begin{frame}[fragile]{Why a Stage is Needed?}
+    Without stage, \textbf{run} may causes a run-time error.
+    \begin{exampleblock}{}
+        \begin{center}
+    \( \TB (\lambda x:\tau. \TBL (\textbf{run}\ \TB x)) \)
+        \end{center}
+    \end{exampleblock}
+
+    With stage, the same code cannot be typed.\\
+    Because the subterm \( (\Lambda\alpha.\ \TB_\alpha x) \) is ill-typed.
+    \begin{exampleblock}{}
+        \begin{center}
+    \( \TB_\alpha (\lambda x:\tau. \TBL_\alpha ((\Lambda\alpha.\ \TB_\alpha x)\ \varepsilon)) \)
+        \end{center}
+    \end{exampleblock}
 \end{frame}

### 2019-11-29 slides/main.tex
Fix.
Add related work.
The last work is adding the kinding judgement slide.

@@
 \usepackage{fancybox}
+\usepackage{fancyvrb}
 \usepackage{float}
@@
     \begin{itemize}
-        \item Speeding up programs using run-time information
+        \item Speeding up programs using run-time information \\
+            (a.k.a. run-time specialization)
+        \item DSLs
     \end{itemize}
     \note{
+        a.k.a = Also known as
     }
@@
     \begin{exampleblock}{}
-        \begin{verbatim}
- # let a = < (1 + 2) >     (* Make a code *)
+        \begin{Verbatim}[numbers=left]
+ # let a = < (1 + 2) >     (* Make code *)
  val a : int code = < (1 + 2) >
- # run a                   (* Run a code *)
+ # run a                   (* Run code *)
  - : int = 3
 
- # let b = <(~a) + (~a)>   (* Embed codes *)
+ # let b = <(~a) + (~a)>   (* Embed code *)
  val b : int code = < ((1 + 2) + (1 + 2)) >
@@
  - : int = 6
-        \end{verbatim}
+        \end{Verbatim}
     \end{exampleblock}
@@
     \begin{exampleblock}{}
-    \begin{verbatim}
- val vadd-gen : Int -> (Vec -> Vec -> Vec) code
+    \begin{Verbatim}[numbers=left]
+ val vadd-gen : int -> (vec -> vec -> vec) code
  # let vadd3 = vadd-gen 3
- val vadd3 : (Vec -> Vec -> Vec) code
- (* vadd3 v w =                            *)
- (*   < let (v, w)=(~v, ~w) in             *)
+ val vadd3 : (vec -> vec -> vec) code
+ (* vadd3 = < fun v w ->                 *)
+ (*   let (v, w)=(~v, ~w) in             *)
  (*   [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >  *)
-    \end{verbatim}
+    \end{Verbatim}
     \end{exampleblock}
@@
     \begin{exampleblock}{}
-    \begin{verbatim}
- val vadd3 : (Vec -> Vec -> Vec) code
+    \begin{Verbatim}[numbers=left]
+ val vadd3 : (vec -> vec -> vec) code
  # (run vadd3) [1;2;3] [4;5;6]
- - : Vec = [5;7;9]
+ - : vec = [5;7;9]
  # (run vadd3) [1;2] [4;5]
  Exception: Failure
-    \end{verbatim}
+    \end{Verbatim}
     \end{exampleblock}
@@
 
-\begin{frame}[fragile]{Dependent Types}
-    \renewcommand{\V}{\text{Vec}\ }
+\begin{frame}[fragile]{Our Approach: Dependent Types [Martin-L{\"o}f'73]}
+    \renewcommand{\V}{\text{vec}\ }
     Types dependent on values
@@
     \begin{exampleblock}{}
- \begin{verbatim}
- [1;2]: Vec 2
- vadd3 : (Vec 3 -> Vec 3 -> Vec 3) code
+ \begin{Verbatim}[numbers=left]
+ [1;2]: vec 2
+ vadd3 : (vec 3 -> vec 3 -> vec 3) code
 
  # (run vadd3) [1;2] [4;5]
- [1;2] has type Vec 2
- but was expected of type Vec 3
- \end{verbatim}
+ [1;2] has type vec 2
+ but was expected of type vec 3
+ \end{Verbatim}
     \end{exampleblock}
@@
 
-\begin{frame}[fragile]{Our Approach: \LMD}
-    Introduce dependent types into \LTP [Hanada\&Igarashi'14].
+\begin{frame}[fragile]{Our Contribution: \LMD}
+    We design a multi-stage calculus \LMD by
+    introducing dependent types into \LTP [Hanada\&Igarashi'14].
     \begin{itemize}
@@
     \end{itemize}
-    Our contribution
+    Technically
     \begin{itemize}
-        \item Prevent illegal use of generated code values with dependent types.
+            \item Define well-formed kind, kinding, typing and equivalence rules. 
+                \item Prove type soundness.
     \end{itemize}
@@
             Unquote & \( (\TB (\TBL a + \TBL a)) \) & \verb| <(~a)+(~a)> | \\[2mm]
-            Run & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run <(1+2)> | \\[2mm]
-            Code type & \( \TW\ \text{Int} \) & \verb| int code |
+            Code type & \( \TW\ \text{int} \) & \verb| int code |
         \end{tabular}
@@
             \> \( \mid \TBL M \) \> (unquote) \\
-            \> \( \mid \textbf{run}\ M \) \> (run) \\
             \> \( \mid \% M \) \> (Cross Stage Persistence (CSP)) \\
@@
         \begin{tabbing}
-            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (type-level constants) \\
+            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (type-level constants, e.g., int, vec) \\
             \> \( \mid \TW\ \tau \) \> (code type) \\
@@
             \begin{center}
-                \( \underbrace{(\textbf{run}\ (\TB\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{\text{stage }1}})) + 1}_{\let\scriptstyle\textstyle\substack{\text{stage }0}} \)
+                \( \underbrace{\TB\ \overbrace{(\lambda x:\text{int}.x + 1)}^{\let\scriptstyle\textstyle\substack{\text{stage }1}}}_{\let\scriptstyle\textstyle\substack{\text{stage }0}} \)
             \end{center}
@@
 
-    Typing judgements of \LTP include a stage.
+    Typing judgements and environments of \LTP include a stage.
     \begin{center}
-        \( \G \vdash 2 + 3 : \I {\mathbf{@ 1}} \)
+        \( x:\text{int}@1 \vdash x + 1 : \text{int} {\mathbf{@ 1}} \)
     \end{center}
@@
 \begin{frame}[fragile]{Cross Stage Persistence (CSP)}
-    Enable using terms at lower stages at higher stages. \\[3mm]
+    Allow terms at lower stages to be used at higher stages. \\[3mm]
 
@@
     \end{exampleblock}
-    CSP symbol \( \% \) {\bf{lift up}} mul5 from stage 0 to stage 1.
+    CSP symbol \( \% \) {\bf{lifts up}} mul5 from stage 0 to stage 1. \\
+    (In MetaOCaml, variables are lifted up implicitly.)
 \end{frame}
 
-\section{Extension \LTP with Dependent Types}
+\section{\LMD: Extension of \LTP with Dependent Types}
 
@@
 
+\begin{frame}[fragile]{Overview of \LMD}
+    Extension of multi-stage calculus \LTP with dependent types
+    \begin{itemize}
+        \item \LMD terms are the same as \LTP.
+        \item Types are extended with dependent function type.
+        \item There are equivalence rules for dependent types.
+    \end{itemize}
+\end{frame}
+
 \begin{frame}[fragile]{Types and Kinds of \LMD}
-    Append function dependent types to types of \LTP.
+    Append dependent function types to types of \LTP.
     \begin{block}{Types}
@@
             \> \( \mid \TW\ \tau \) \> (code type) \\
-            \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (function dependent type) \\
-            \> \( \bm{\mid \tau\ M} \) \> (application, e.g. \(\text{Vec}\ 3\))
+            \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (dependent function type) \\
+            \> \( \bm{\mid \tau\ M} \) \> (application, e.g. \(\text{vec}\ 3\))
         \end{tabbing}
@@
     % \begin{itemize}
-    %     \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
-    %     \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
+    %     \item OK  \( \Pi n: \TW (\text{vec}\ \%n) \)
+    %     \item NG  \( \Pi n: \TW (\text{vec}\ n) \)
     % \end{itemize}
@@
     \begin{center}
-    \( \underbrace{\Pi n:\I. \TW (\overbrace{\text{Vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
+    \( \underbrace{\Pi n:\text{int}. \TW (\overbrace{\text{vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
     \end{center}
@@
         \item Constants: \( 0,1,2,3,\dots \)
-        \item Type-level constants: Int, Vec, \dots
+        \item Type-level constants: int, vec, \dots
     \end{itemize}
     can be used at any stage.
-
     \begin{exampleblock}{}
         \begin{tabbing}
-            \hspace{5mm} \= \text{val double-at-0} : \( \text{Vec }3 \to \text{Vec }3 \) \\[2mm]
+            \hspace{5mm} \= \text{val double-at-0} : \( \text{vec }3 \to \text{vec }3 \) \\[2mm]
             \> \textbf{let } \text{double} = \( \TB (\%\ \text{double-at-0}) \) \\
-            \> \text{val double} : \( \TW \underbrace{(\text{Vec }3 \to \text{Vec }3)}_{\text{stage 1}} \)
+            \> \text{val double} : \( \TW \underbrace{(\text{vec }3 \to \text{vec }3)}_{\text{stage 1}} \)
         \end{tabbing}
     \end{exampleblock}
-    Vec and integer 3 can be used at stage 1.
 \end{frame}
@@
     Type tells us the length of vector.
-    \newcommand{\Vn}{\text{Vec}\ \%n}
-    \newcommand{\Vt}{\text{Vec}\ \%3}
+    \newcommand{\Vn}{\text{vec}\ \%n}
+    \newcommand{\Vt}{\text{vec}\ \%3}
     \begin{exampleblock}{}
     \begin{tabbing}
-        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I. \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
+        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\text{int}. \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
         \> \( \textbf{let}\ \text{vadd3} = \text{vadd-gen}\ 3;; \) \\
@@
     Hard to compose with other functions.
-    \newcommand{\Vn}{\text{Vec}\ \%n}
-    \newcommand{\Vpt}{\text{Vec}\ \%3}
-    \newcommand{\Vt}{\text{Vec}\ 3}
+    \newcommand{\Vn}{\text{vec}\ \%n}
+    \newcommand{\Vpt}{\text{vec}\ \%3}
+    \newcommand{\Vt}{\text{vec}\ 3}
     \begin{exampleblock}{}
@@
 \begin{frame}[fragile]{Solution}
-    \newcommand{\Vt}{\text{Vec}\ 3}
-    \newcommand{\Vpt}{\text{Vec}\ \%3}
-    Erase the CSP symbol \( \% \) under the condition \(M \) is closed.
+    \newcommand{\Vt}{\text{vec}\ 3}
+    \newcommand{\Vpt}{\text{vec}\ \%3}
+    Erase the CSP symbol \( \% \) when \(M \) is closed (\QPercent).
+    {\footnotesize{
     \begin{center}
@@
             \G\vdash \% M \E M
+        } \\[2mm]
+        \infrule[{\TConv}]{
+            \G\V M:\tau@n \andalso
+            \G\V \tau\equiv \sigma @n
+        }{
+            \G\V M:\sigma@n
         }
     \end{center}
+    }}
     \begin{exampleblock}{}
         \begin{itemize}
-        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
+            \item \( \text{vec}\ \%3 \E \text{vec}\ 3 \)
             \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\
@@
         \item \LTP [Hanada\&Igarashi'14]
-            \begin{itemize}
-                \item Multi-stage programming including explicit CSP
-            \end{itemize}
-        \item Concoqtion [Forgarty et al.'14]
+        \item Concoqtion [Forgarty et al.'07]
             \begin{itemize}
                 \item Introduce indexed type into MetaOCaml.
-                \item Types are indexed by Coq terms.
+                \item Types are indexed by Coq terms. \\ (not full dependent types)
+            \end{itemize}
+        \item \( \lambda_{H\circ} \) [Pasalic'04]
+            \begin{itemize}
+                \item Meta-programming with dependent types
+                \item No run and CSP
             \end{itemize}
@@
         \item Avoid illegal use of generated code values with dependent types.
+            \begin{itemize}
+                \item Full dependent types not restricted ones.
+            \end{itemize}
+        \item Define equivalence rules.
+            \begin{itemize}
+                \item Especially, for CSP
+            \end{itemize}
         \item Prove type soundness.
@@
 %     Type system prevents illegal use of generated function.
-%     \renewcommand{\V}{\text{Vec}}
+%     \renewcommand{\V}{\text{vec}}
 %     \begin{tabbing}
@@
 %             \begin{itemize}
-%                 \item \( \text{Vec} \), \( \text{Int} \).
+%                 \item \( \text{vec} \), \( \text{int} \).
 %             \end{itemize}
@@
 %             \begin{itemize}
-%                 \item \( \text{Vec } 3 \)
+%                 \item \( \text{vec } 3 \)
 %             \end{itemize}
@@
 %             \begin{itemize}
-%                 \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
+%                 \item \( \text{vadd-gen 3} : \TW_\alpha (\text{vec}\ 3 \to \text{vec}\ 3 \to \text{vec}\ 3) \)
 %             \end{itemize}
@@
 %             \begin{itemize}
-%                 \item \( \text{Int} :: * \)
+%                 \item \( \text{int} :: * \)
 %             \end{itemize}
@@
 %             \begin{itemize}
-%                 \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
+%                 \item \( \text{vec} :: (\Pi x:\text{int}.*) \)
 %             \end{itemize}
@@
 %             \begin{itemize}
-%                 \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
+%                 \item \( \Sigma = \text{int}::*, \text{vec}::\Pi x:\text{int}.*, 0:\text{int} \)
 %             \end{itemize}
@@
 % \begin{frame}[fragile]{Example of Kinding Derivation}
-%     \renewcommand{\Vec}{\text{Vec}}
-%     \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
+%     \renewcommand{\vec}{\text{vec}}
+%     \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\vec\ 3)}_{\TW_\alpha (\vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
 %     \pause
-%     \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
+%     \( \Sigma = \vec::\Pi x:\text{int}.*, 0:\text{int}, 1:\text{int}, \cdots \)
 %     \begin{center}
@@
 %             \infer[\KTW]
-%             {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
+%             {\V \TW_\alpha (\vec\ 3) :: * @ \varepsilon}
 %             {
 %                 \infer[\KApp]
-%                 {\V \Vec\ 3 :: * @ \alpha}
+%                 {\V \vec\ 3 :: * @ \alpha}
 %                 {
 %                     \infer[\KTConst]
-%                     {\V \Vec :: \Pi x:\I.* @ \alpha}
-%                     {\Vec :: \Pi x:\I.* \in \Sigma}
+%                     {\V \vec :: \Pi x:\text{int}.* @ \alpha}
+%                     {\vec :: \Pi x:\text{int}.* \in \Sigma}
 %                     \andalso
 %                     \infer[\TConst]
-%                     {\V 3 : \I @ \alpha}
-%                     {3 : \I \in \Sigma}
+%                     {\V 3 : \text{int} @ \alpha}
+%                     {3 : \text{int} \in \Sigma}
 %                 }
@@
 %     \end{center}
-%     We can use \Vec\ and integers at any stages.
+%     We can use \vec\ and integers at any stages.
 %     \note{
-%         The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
-%         but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
+%         The constructed type vec 3 is stage sensitive so we cannot use at arbitrary stages
+%         but the elements, vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
 %     }
@@
 % \begin{frame}[fragile]{Examples of Type Equality}
-%     \renewcommand{\V}{\text{Vec}}
+%     \renewcommand{\V}{\text{vec}}
 %     \begin{itemize}
-%         \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
+%         \item \( (\lambda x:\text{int}.x)\ 3\E 3 \)
 %             \begin{itemize}
@@
 %             \end{itemize}
-%         \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
+%         \item \( \V\ ((\lambda x:\text{int}.x)\ 3) \E \V\ 3 \)
 %             \begin{itemize}
@@
 %             \begin{itemize}
-%                 \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
+%                 \item Because \( 3 \) has type \text{int} at any stage, we can use \QPercent.
 %             \end{itemize}

### 2019-11-29 slides/main.tex
I must blush up from now

@@
 \begin{frame}[fragile]{Kinding rules of \LMD}
+    Kiding judgements also inculde stages.
+    \begin{center}
+        \( \G \vdash \tau :: K @ n \)
+    \end{center}
     Types have also stages because types may contains terms.
@@
     }}
+    \end{center}
+\end{frame}
+
+\begin{frame}[fragile]{CSP in Types}
+    Code type \( \TW \) decreases the stage.
+    \begin{center}
+        \infrule[{\KTW}]{
+            \G\V \tau::*@ n + 1
+        }{
+            \G\V\TW \tau::*@ n
+        }
     \end{center}

### 2019-11-30 slides/main.tex
Fix.
Making speach draft.

@@
     \note{
+        Thank you for coming. I am Akira Kawata at Graduate School of
+        Informatics, Kyoto University. Today, I talk about Dependently Typed
+        Multi-stage Calculus.
+
+        This is today's outline. Firstly, I will introduce multi-stage
+        programming paradigm. Secondly, I explain existing multi-stage
+        calculus lambda-triangle-percent, which I call it lambda-T-P from now
+        because lambda-triangle-present is quite long. Lastly, I talk about
+        lambda-M-D which is an extension of lambda-T-P with dependent types.
     }
@@
     \note{
-        a.k.a = Also known as
+        So, what is multi-stage programming? It is a programming paradigm that
+        enables generation of code at run-time and evaluation of code at
+        run-time simultaneously. Famous applications of multi-stage programming
+        is speeding up programs using run-time information, which is also known
+        as run-time specialization and DSLs, for example TODO.
     }
@@
 \begin{frame}[fragile]{Kinding rules of \LMD}
-    Kiding judgements also inculde stages.
+    Kiding judgements also include stages.
     \begin{center}
@@
     \end{center}
-    Types have also stages because types may contains terms.
+    Because types may contains terms. (e.g. vec n)
     \begin{center}
@@
         \G\V \sigma\ M::K[x\mapsto M] @ n
-    }
+    } \\[2mm]
     \infrule[{\KAbs}]{

### 2019-11-30 slides/main.tex
Finish making speach draft.

@@
 % This option generate pdf files showing notes on the right hand side of each
-% pages. But this optionn has some bugs. I recommend you tou do not use this
+% pages. But this optionn has some bugs. I recommend you not to use this
 % option.
@@
 % Note options
-% \setbeameroption{show notes}
+% Show plain text in note pages.
+\setbeamertemplate{note page}[plain]
+% Show / hide note
+\setbeameroption{show notes}
 % \setbeameroption{hide notes}
@@
 % Show grid for debug
-\setbeamertemplate{background}[grid][step=1cm]
+% \setbeamertemplate{background}[grid][step=1cm]
 
@@
 \setbeamerfont{footline}{size=\tiny}
+\setbeamerfont{note page}{size=\scriptsize}
 
@@
         is speeding up programs using run-time information, which is also known
-        as run-time specialization and DSLs, for example TODO.
+        as run-time specialization and DSLs, such as DSL for linear algebra or
+        image processing.
     }
@@
     \note{
+        This is example code of multi-stage programming in MetaOCaml. In line
+        one, I make a code value of 1 + 2 and bind it to variable "a". Angle
+        brackets are symbols to make a code values. So, "a" is a value of int
+        code type. In line three, I run a code value bounded to "a" using "run"
+        primitive. As a result, I get integer 3. We can embed code values into
+        another code value.  In line 6, I make a code value by embedding the
+        code value banded to "a". Tilde symbol is a symbol to embed a code
+        value. Then, I bind a code of 1 + 2 + 1 + 2 to variable "b". When I run
+        variable "b", we get integer 6 as a result.
     }
@@
 \begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
-    Generate efficient vector addition functions for given length.
+    Generate efficient vector addition functions for given lengths.
     \begin{exampleblock}{}
@@
     \note{
+        Speeding up programs is important application of multi-stage
+        programming as I said in the two before slide. vadd-gen function in
+        this slide generates efficient addition function for given lengths.
+        vadd-gen function takes a integer as the vector length and return a
+        code value of function which takes two fixed length vectors and return
+        the sum of them. For example, when I apply 3 to vadd-gen function and
+        bind it to vadd3, vadd3 is a code value which takes two 3 length
+        vectors. I show the contents of vadd3 in commented out lines. It is
+        important that there is no loop. Loop is unrolled at generation of a
+        code value and it helps to make an efficient function.
     }
@@
     \note{
+        But there is a problem in vadd3. It is that vadd3 raises runtime errors
+        for vectors of wrong length. For example, when I apply correct length
+        vectors, [1,2,3] and [4,5,6], I can get the sum of them [5,7,9]. But
+        when I apply wrong length vectors, [1,2] and [4,5], I get exception at
+        run-time.
     }
@@
     \note{
-        By the way, we can write types dependent on values using dependent types.
+        Our approach to the problem is using dependent types. Dependent types
+        are types dependent on values and can prevent illegal value of vadd3.
+        Using dependent types, we can express the length of vectors in their
+        types. For example, a vector [1;2] can be typed as vec 2 and vadd3 can
+        be typed code of function which takes values of vec 3 type and return a
+        value of vec 3 type. Now, if I apply wrong length vectors, [1;2] and
+        [4;5] to vadd3, I get only type error not run-time error.
     }
@@
     \note{
-        Our approach to the problem of multi-stage programming is introducing dependent types into a multi-stage calculus by Hanada and Igarashi.
-        We call our multi-stage calculus as \LMD.
+        Our contribution of this research is designing lambda-M-D by
+        introducing dependent types into multi-stage calculus lambda-T-P by
+        Hanada and Igarashi. lambda-T-P have both of features of multi-stage
+        programming and features of dependent types. Technically, we define
+        well-formed kind, kinding, typing and equivalence rules and prove type
+        soundness.
     }
@@
     \note{
+        From the next slide, I explain existing multi-stage calculus lambda-T-P which we used as our lambda-M-D.
     }
@@
     \end{table}
+    \note{
+        This is a quick overview of lambda-TP. In lambda-TP, we can make a code
+        value with a black triangle which corresponds to angle brackets in
+        MetaOCaml. Left-directed black triangle is used to embed a code values
+        which corresponds to tilde in MetaOCaml. Code type is represented with
+        white triangle.
+    }
 \end{frame}
@@
     * Simplified version
+    \note{
+        These are terms of lambda-TP. We omit some of them for simplicity. A
+        term of lambda-TP is a constant such as integer, a quoted term which
+        means code value in MetaOCaml, an unquote term which is the same as
+        tilde in MetaOCaml, Cross Stage Persistence (CSP) which I will explain
+        later slides or stuffs of simply typed lambda calculus.
+    }
 \end{frame}
@@
         \begin{tabbing}
-            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (type-level constants, e.g., int, vec) \\
+            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (type-level constants, e.g., int) \\
             \> \( \mid \TW\ \tau \) \> (code type) \\
@@
     \note{
+        Type of lambda-TP is type-level constants for example int or code type
+        or function type. Typing judgements of lambda-TP have shape of M is
+        typed tau at stage n under environment gamma.
     }
@@
     \note{
+        What is a stage? A stage is a level of nested quote surrounding a term
+        . For example, this whole term is on stage 0 because there is no black
+        triangle around this term. However, the subterm lambda x dot x + 1 is
+        on stage 1 because there is one black triangle around the subterm.
+        Typing judgements and environments of lambda-TP include a stage.
     }
@@
     \note{
-        Let's have a look on some typing rules.
+        Let's have a look on some typing rules of lambda-TP. The application
+        rule is T-App. As Simply Typed Lambda Calculus, types of a function and
+        an argument must correspond. In addition to it, there is another
+        restriction. It is the function and the argument must live in the same
+        stage. Typing rules of quote and unquote is T-black triangle and T-left
+        directed black triangle. They say that black triangles increase and
+        decrease the stage of terms. In general, we cannot use terms of one
+        stage at other stages.
     }
@@
     (In MetaOCaml, variables are lifted up implicitly.)
+    \note{
+        But we want to use terms at different stage. Cross Stage Persistence
+        (CSP) enables it. CSP allow terms at lower stages to be used at higher
+        stages. For example, when we define a mul5 function at stage 0, we
+        cannot use it other stages. However, when we insert \% which is a
+        symbol of CSP, we can use mul5 at stage 1. CSP symbol \( \% \)
+        lifts up mul5 from stage 0 to stage 1.
+    }
 \end{frame}
@@
   \note{
+        Finally, I explain our work lambda-MD.
   }
@@
     \end{itemize}
+    \note{
+        This is overview of lambda-MD. Lambda-MD is an extension of multi-stage
+        calculus lambda-TP with dependent types. Its term are the same as
+        lambda-TP but types are extended with dependent function type. And
+        there are equivalence rules because dependent type system need them.
+    }
 \end{frame}
@@
 \begin{frame}[fragile]{Types and Kinds of \LMD}
-    Append dependent function types to types of \LTP.
+    Add dependent function types to types of \LTP.
     \begin{block}{Types}
@@
     \end{block}
-    % Note: We need CSP to use normal variables in code types.
-    % \begin{itemize}
-    %     \item OK  \( \Pi n: \TW (\text{vec}\ \%n) \)
-    %     \item NG  \( \Pi n: \TW (\text{vec}\ n) \)
-    % \end{itemize}
     \note{
+        These are types and kinds of lambda-MD. We add dependent function type
+        to lambda-TP. So, there is a pi type which means dependent function
+        type and application such as vec 3 type. There are kinds also in
+        lambda-MD in order to classify types into types of values which is
+        represented with star symbol and types dependent on terms which is
+        represented with pi x dot K.
     }
@@
         \infrule[{\KAbs}]{
-        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
+            \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@n
         }{
@@
     \end{center}
+    \note{
+        Kiding judgements also include stages. Because types may contains terms
+        such as vec n. It is natural that types dependent on a value live in
+        the same stage of the value. So, application rule, K-App, says that if
+        you want to apply term M to type sigma, they must live in the same
+        stage n. K-Abs says when sigma is kinded at stage n and variable x in
+        the environment is on stage n also, you can abstract x using Pi.
+    }
 \end{frame}
@@
     \end{center}
-    So, we need CSP in types also.
+    So, we need CSP in types also in order to use \( n \) in \( \TW \).
     \begin{exampleblock}{}
         \begin{center}
-            \( \underbrace{\Pi n:\text{int}. \TW (\overbrace{\text{vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
+            \( \lambda n:\text{int}. \text{zeros}(n): \underbrace{\Pi n:\text{int}. \TW (\overbrace{\text{vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
         \end{center}
     \end{exampleblock}
+    \note{
+        Code type decreases the stage as you can see in K-white triangle rule.
+        So we need CSP in types also. For example, let's consider a function
+        which takes integer n and returns a vector of length n filled with
+        zero. Because n is a variable at stage 0, you must insert \% symbol
+        when you use it in code type. But vec is used without \% symbol. I will
+        explain the reason in the next slide.
+    }
 \end{frame}
@@
     \end{exampleblock}
+    \note{
+        We design our lambda-MD so that we can use constants such as integer
+        numbers and type-level constants such as int, vec at any stage. For
+        example, when we have double-at-0 function which double the given
+        length 3 vector. It has type of vec 3 to vec 3. Then, we get double by
+        lifting up double-at-0 with CSP. double function has type of code of a
+        function from vec 3 to vec 3. And there is no problem in the type.
+        Because both vec and 3 are constants and we can use them at any stages.
+    }
 \end{frame}
@@
     \note{
-        vadd-gen is changed as follows in \LMD.
-        Thanks to dependent types ...
+        Let's return back to vadd-gen function.  vadd-gen is changed as follows
+        in \LMD.  The type of vadd-gen says that it takes integer n and returns
+        a code value of function which takes two \% n length vectors and
+        returns a \% n length vector.  Thanks to dependent types we can see it
+        takes length 3 vectors.
     }
@@
     We cannot compose because of type mismatch.
+    \note{
+        But there is a technical challenge in vadd3. It is vadd3 is hard to
+        compose with other functions. For example, as you have seen, vadd3 has
+        the type of code which takes two vec \% 3 values and returns vec \% 3
+        values. However, double has type of code which takes vec 3. So we
+        cannot compose them because \% symbol raises a type error.
+    }
 \end{frame}
@@
     \end{exampleblock}
+    \note{
+        Our solution for this problem is erasing the CSP symbol \( \% \) when
+        \(M \) is closed. \QPercent says that if M is a closed term, \% M is
+        equivalent to M. And \TConv says we change the type of term to an
+        equivalent type. So, vec \% 3 is equivalent to vec 3 and vadd3 can have
+        type of code of function which takes two vec 3 values and returns a vec
+        3 value. The type is equivalent to the original type of vadd3.
+    }
 \end{frame}
@@
     \note{
+        We proved following four properties Subject Reduction, Strong Normalization, Confluence, Progress. Type soundness is followed from these properties.
     }
@@
                 \item Meta-programming with dependent types
-                \item No run and CSP
+                \item No run or CSP
             \end{itemize}
@@
     \note{
+        We list up some of related works. First one is lambda-TP which is the
+        base of lambda-MD. Second one is Concoqtion by Forgartys. They
+        introduced indexed type into MetaOCaml. Types are indexed by Coq term.
+        But it is restricted dependent type because we cannot use full language
+        features for indexes such as quote, unquote or run. lambda-H-circle by
+        Pasalic studied meta-programming with dependent types but there is no
+        run or CSP in it.
     }
@@
             \begin{itemize}
-                \item Especially, for CSP
+                \item Especially for CSP
             \end{itemize}
@@
     \note{
+        Here is conclusion. We introduced dependent types into multi-stage
+        calculus. It can avoid illegal use of generated code values with
+        dependent types. And it dependent types is full dependent types not
+        restricted ones. We define equivalence rules for dependent types
+        especially for CSP. And we proved type soundness. There is a future
+        work of algorithmic typing but we have designed almost all rules of
+        algorithmic typing.
+
+        Thank you for listening.
     }

### 2019-11-30 slides/main.tex
fix.

@@
 
+\begin{frame}{}
+\end{frame}
+
 % Output the outline slide
@@
 
-\begin{frame}[fragile]{What is Multi-stage Programming}
+\begin{frame}[fragile]{What is Multi-stage Programming?}
     A programming paradigm that enables
@@
  [1;2] has type vec 2
- but was expected of type vec 3
+ but a value of type Vec 3 was expected
  \end{Verbatim}
@@
 \begin{frame}[fragile]{Kinding rules of \LMD}
-    Kiding judgements also include stages.
+    Kiding judgements as well include stages.
     \begin{center}

### 2019-11-30 slides/main.tex
Fix typo in speach draft.

--- 2019-11-30 slides/main.tex
@@
         enables generation of code at run-time and evaluation of code at
-        run-time simultaneously. Famous applications of multi-stage programming
-        is speeding up programs using run-time information, which is also known
-        as run-time specialization and DSLs, such as DSL for linear algebra or
-        image processing.
+        run-time simultaneously. One of famous applications of multi-stage
+        programming is speeding up programs using run-time information, which
+        is also known as run-time specialization. A DSL is also a famous
+        application such as a DSL for linear algebra or image processing.
     }
@@
         another code value.  In line 6, I make a code value by embedding the
-        code value banded to "a". Tilde symbol is a symbol to embed a code
+        code value bounded to "a". Tilde symbol is a symbol to embed a code
         value. Then, I bind a code of 1 + 2 + 1 + 2 to variable "b". When I run
@@
         this slide generates efficient addition function for given lengths.
-        vadd-gen function takes a integer as the vector length and return a
-        code value of function which takes two fixed length vectors and return
-        the sum of them. For example, when I apply 3 to vadd-gen function and
-        bind it to vadd3, vadd3 is a code value which takes two 3 length
-        vectors. I show the contents of vadd3 in commented out lines. It is
-        important that there is no loop. Loop is unrolled at generation of a
-        code value and it helps to make an efficient function.
+        vadd-gen function takes a integer as the length of vectors and return
+        code of function which takes two vectors of the length and return the
+        sum of them. For example, when I apply 3 to vadd-gen function and bind
+        it to vadd3, vadd3 is code which takes two 3 length vectors and returns
+        the sum. I show the contents of vadd3 in commented out lines. It is
+        important that there is no loop. Loop is unrolled at generation of code
+        and it make generated functions efficient.
     }
@@
         But there is a problem in vadd3. It is that vadd3 raises runtime errors
-        for vectors of wrong length. For example, when I apply correct length
+        for vectors of wrong lengths. For example, when I apply correct length
         vectors, [1,2,3] and [4,5,6], I can get the sum of them [5,7,9]. But
@@
         Our approach to the problem is using dependent types. Dependent types
-        are types dependent on values and can prevent illegal value of vadd3.
+        are types dependent on values and can prevent illegal use of vadd3.
         Using dependent types, we can express the length of vectors in their
-        types. For example, a vector [1;2] can be typed as vec 2 and vadd3 can
-        be typed code of function which takes values of vec 3 type and return a
-        value of vec 3 type. Now, if I apply wrong length vectors, [1;2] and
-        [4;5] to vadd3, I get only type error not run-time error.
+        types. For example, a vector [1;2] is as vec 2 and vadd3 is typed code
+        of function from vec 3 type to vec 3. Now, if I apply wrong length
+        vectors, [1;2] and [4;5] to vadd3, I get only type error not run-time
+        error.
     }
@@
     \note{
-        Our contribution of this research is designing lambda-M-D by
+        The contribution of our research is designing lambda-M-D by
         introducing dependent types into multi-stage calculus lambda-T-P by
-        Hanada and Igarashi. lambda-T-P have both of features of multi-stage
+        Hanada and Igarashi. lambda-MD have both of features of multi-stage
         programming and features of dependent types. Technically, we define
@@
     \note{
-        From the next slide, I explain existing multi-stage calculus lambda-T-P which we used as our lambda-M-D.
+        From the next slide, I explain existing multi-stage calculus lambda-TP
+        which is the base of our lambda-MD.
     }
@@
         This is a quick overview of lambda-TP. In lambda-TP, we can make a code
-        value with a black triangle which corresponds to angle brackets in
-        MetaOCaml. Left-directed black triangle is used to embed a code values
-        which corresponds to tilde in MetaOCaml. Code type is represented with
-        white triangle.
+        value with a black triangle, quote, which corresponds to angle brackets
+        in MetaOCaml. Left-directed black triangle, unquote, is used to embed a
+        code values which corresponds to tilde in MetaOCaml. Code type is
+        represented with white triangle.
     }
@@
         Type of lambda-TP is type-level constants for example int or code type
-        or function type. Typing judgements of lambda-TP have shape of M is
-        typed tau at stage n under environment gamma.
+        or function type. Typing judgements of lambda-TP is that M is typed tau
+        at stage n under environment gamma.
     }
@@
     \note{
-        What is a stage? A stage is a level of nested quote surrounding a term
-        . For example, this whole term is on stage 0 because there is no black
-        triangle around this term. However, the subterm lambda x dot x + 1 is
-        on stage 1 because there is one black triangle around the subterm.
-        Typing judgements and environments of lambda-TP include a stage.
+        What is a stage? A stage is a level of nested quote surrounding a term.
+        For example, this whole term is on stage 0 because there is no quote
+        around this term. However, the subterm lambda x dot x + 1 is on stage 1
+        because there is one quote around the subterm.  Typing judgements and
+        environments of lambda-TP include a stage.
     }
@@
         an argument must correspond. In addition to it, there is another
-        restriction. It is the function and the argument must live in the same
-        stage. Typing rules of quote and unquote is T-black triangle and T-left
-        directed black triangle. They say that black triangles increase and
-        decrease the stage of terms. In general, we cannot use terms of one
-        stage at other stages.
+        restriction. It is that the function and the argument must live in the
+        same stage. Typing rules of quote and unquote is T-quote and T-unquote.
+        They say that black triangles increase and decrease the stage of terms.
+        In general, we cannot use terms of one stage at other stages.
     }
@@
     \note{
-        But we want to use terms at different stage. Cross Stage Persistence
+        But we want to use terms at different stage, sometime. Cross Stage Persistence
         (CSP) enables it. CSP allow terms at lower stages to be used at higher
         stages. For example, when we define a mul5 function at stage 0, we
-        cannot use it other stages. However, when we insert \% which is a
+        cannot use it other stages. However, when we insert \%, which is a
         symbol of CSP, we can use mul5 at stage 1. CSP symbol \( \% \)
@@
         This is overview of lambda-MD. Lambda-MD is an extension of multi-stage
-        calculus lambda-TP with dependent types. Its term are the same as
+        calculus lambda-TP with dependent types. Its terms are the same with
         lambda-TP but types are extended with dependent function type. And
@@
         to lambda-TP. So, there is a pi type which means dependent function
-        type and application such as vec 3 type. There are kinds also in
+        type and application such as vec 3. There are kinds also in
         lambda-MD in order to classify types into types of values which is
@@
         Kiding judgements also include stages. Because types may contains terms
-        such as vec n. It is natural that types dependent on a value live in
-        the same stage of the value. So, application rule, K-App, says that if
-        you want to apply term M to type sigma, they must live in the same
-        stage n. K-Abs says when sigma is kinded at stage n and variable x in
-        the environment is on stage n also, you can abstract x using Pi.
+        such as n in vec n. It is natural that types dependent on a value live
+        in the same stage of the value. So, application rule, K-App, says that
+        if you want to apply term M to type sigma, they must live in the same
+        stage n. K-Abs says that when sigma is kinded at stage n and variable x
+        in the environment is on stage n also, you can abstract x using Pi.
     }
@@
     \note{
-        Code type decreases the stage as you can see in K-white triangle rule.
-        So we need CSP in types also. For example, let's consider a function
-        which takes integer n and returns a vector of length n filled with
-        zero. Because n is a variable at stage 0, you must insert \% symbol
-        when you use it in code type. But vec is used without \% symbol. I will
-        explain the reason in the next slide.
+        Code type decreases the stage as you can see in K-code.  So we need CSP
+        in types also. For example, let's consider a function which takes
+        integer n and returns a code of length n vector filled with zeros.
+        Because n is a variable at stage 0, you must insert \% symbol when you
+        use it in code type. But vec is used without \% symbol. I will explain
+        the reason in the next slide.
     }
@@
         returns a \% n length vector.  Thanks to dependent types we can see it
-        takes length 3 vectors.
+        takes only length 3 vectors.
     }
@@
     \note{
-        But there is a technical challenge in vadd3. It is vadd3 is hard to
+        But there is a technical challenge in vadd3. vadd3 is hard to
         compose with other functions. For example, as you have seen, vadd3 has
         the type of code which takes two vec \% 3 values and returns vec \% 3
-        values. However, double has type of code which takes vec 3. So we
+        values. However, double has type of code from vec 3 to vec 3. So we
         cannot compose them because \% symbol raises a type error.
@@
         equivalent to M. And \TConv says we change the type of term to an
-        equivalent type. So, vec \% 3 is equivalent to vec 3 and vadd3 can have
-        type of code of function which takes two vec 3 values and returns a vec
-        3 value. The type is equivalent to the original type of vadd3.
+        equivalent type. So, vec \% 3 is equivalent to vec 3 and vadd3 can be 
+        typed of code of function which takes two vec 3 values and returns a vec
+        3 value. And the type is equivalent to the original type of vadd3.
     }
@@
         calculus. It can avoid illegal use of generated code values with
-        dependent types. And it dependent types is full dependent types not
+        dependent types. And its dependent types is full dependent types not
         restricted ones. We define equivalence rules for dependent types
